### 2022-01-26 src/prestige_bias_paper/PrestigeBias.tex
Prestige project init

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}          
\usepackage{graphicx}
\usepackage{amsthm, amsmath, amssymb}
\usepackage[font=small]{caption, subcaption}
\usepackage{setspace}\onehalfspacing
\usepackage[loose,nice]{units}
\usepackage{array}
\usepackage[super]{nth}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage[displaymath, mathlines]{lineno}
\usepackage{natbib}
\usepackage[all]{nowidow}
\usepackage{wrapfig}
\usepackage{pdfpages}
\newenvironment{conditions}
  {\par\vspace{\abovedisplayskip}\noindent\begin{tabular}{>{$}l<{$} @{${}={}$} l}}
  {\end{tabular}\par\vspace{\belowdisplayskip}}
\newcommand{\R}{\mathbb{R}}  
\DeclareMathOperator*{\E}{\mathbb{E}}

\author{
	Dr. Yoav Ram
	\and
	Saar Egozi
}

\begin{document}

\begin{titlepage}
\centering

\vspace{4cm}

{\LARGE\bfseries Prestige as a Driving Force in Cultural Transmission}

\vspace{2cm}

{\large\bfseries Saar Egozi}

\vspace{1cm}

{\large together with Yoav Ram}

\vspace{2cm}

\vfill

{\large Efi Arazi School of Computer Science, IDC Herzliya}

\vspace{1cm}

{\itshape \today}

{\large saartk@gmail.com}
\end{titlepage}

\renewcommand\linenumberfont{\normalfont\small\sffamily}
\linenumbers
\modulolinenumbers[2]
\setcounter{secnumdepth}{0}
\tableofcontents

\clearpage

% what is cultural transmission, and its not only in humans
\section{Introduction}
Traits transmission is when an individual passes on a trait, genetic or behavioral, to another individual. Transmission in nature manifests in two main ways: genetic and cultural.
Genetic transmission is when an individual, or several, transmit their genes to their offspring by duplication of their own cells.
Cultural transmission is the way individuals transmit cultural traits (i.e behavior) from one another, typically via teaching and demonstrating.
 Cultural transmission is most common in humans \citep[pg. 3]{transmissionVectorsBook} and in primates like chimpanzees \citep{chimpsPrestige, chimpsCopy}.
 The common cultural traits in humans are behavioral patterns, like personalities and habits, transmitted via observations and verbal discussions.
\citet{dualEvolution} suggest that cultural learning may be particular to humans, but \citet{elepahntsRepo} suggest that it appears in other mammals as well, elephants for example:
 \begin{quote}
	   ... the possession of enhanced discriminatory abilities by the oldest individual [matriarch] in a group can influence the social knowledge of the group as a whole.
 \end{quote}
 They showed that once a matriarch is removed from the group, the group's survival instincts are inferior.
 They support their hypothesis by exacting an experiment: playing audio recordings of African elephants, showing that groups with a matriarch recognize and react better to hostile or friendly calls than the groups without one.
Moreover, cultural transmission appears in other species, even simpler than mammals, such as \textit{Drosophila}.
\citet{fliesPaper} show that oviposition site choice in fruit flies is culturally transmitted.
They showed that flies without experience in choosing sites, after spending some time with "experienced" flies, chose the same type of site without directly observing this behavior. 
\citet{fliesPaper} mention that how the information is transferred is still an open question, but suggest that the flies may use olfactory cues, like other animals such as rodents and bees.\\

%the differences and similarities between cultural and genetic transmission 
Cultural transmission is similar to genetic transmission in many ways, while different in others.
Similar to genetic transmission, the effects of culturally transmitted traits can be physiological rather than behavioral, and transmitted from parents to offspring.
 For example, parents can teach their children to be strong or tall, within some biological limits, by instructing them to maintain a healthy diet and engage in physical activity.
Contrary to genetic transmission, the sources of the traits can be many, and not only parents. They can even be unrelated, like teachers, celebrities, coaches, the media, or any stranger that comes in contact with them. 
 Cultural transmission can be vertical, where parents transmit to their children, but also oblique, where other adults transmit traits to children (not their own).
  Horizontal transmission is also possible, where peers transmit traits to one another. 
   Lastly, vertical transmission in the opposite direction is possible too, where parents copy traits from their children (e.g playing video games) as \citet{transmissionVectorsBook} and \citet{transmissionVectors} suggest. 
In addition, even when a cultural trait is disfavored by natural selection, it still may spread across a population given transmission biases strong enough to negate the selection bias \citep[Ch. 8 pg. 279]{evolutionBook}.\\

%transmission biases - what they are, what are the types.
Transmission bias occurs when a trait has a disproportionate probability from its frequency in the population to be transmitted.
For example, \citet{wtfGene} show that there are genes of yeast called \textit{wtf genes}, that bias their transmission to the gametes.
They secrete a long life expectancy poison, together with a short life expectancy antidote, so a gamete without the gene will perish (the poison will outlive the antidote).
Transmission biases, though exist in genetic transmission, are probably more common in cultural transmission.
Much like mutation in genetic evolution, one could learn behavioral patterns or traits on his own, usually referred to as \textit{innovation}, also called individual learning, and just like mutation, without it humans might have been remained at the stone age, or even go extinct.
\citet{strategiesPaper} suggest that success biased social transmission contribute more to the general success of the population than individual learning.
 They conducted a tournament for developing learning strategies of a population, where each participant need to devise a strategy.
 Each strategy must define when individuals should observe and copy from others, and when to engage in individual learning.
 The best strategies contained a high percentage of social learning relative to individual learning, even when the error when copying was as high as almost 0.5. It is important to add that all of the strategies include some percentage of individual learning, and without it the results would be a lot worse.
In addition to \citet{strategiesPaper}, \citet{complexityPaper} define different types of transmission biases based on success.
They define several types of role-model choosing methods, all assuming that the copier correctly identifies the successful ones.
Both studies assume that individuals can successfully evaluate successful individuals.
\citet[Ch. 5]{evolutionBook} suggest that the \textbf{evaluation} of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
A direct bias is when a variation of a trait is more attractive than others, and is evaluated by \textit{directly} testing the variation of the trait.
For example, an individual observing a Ping-Pong match between two others can try both of the paddle grips it observed, and decide what grip is better for it.
An indirect bias is when an individual uses the value of one trait to determine the attractiveness of another, so it \textit{indirectly} evaluates the attractiveness of the role-model.
Continuing with the example, a bystander could copy the paddle grip of the Ping-Pong player who scored more points in the match.
A frequency-dependent bias is when an individual has a probability to copy a variant of the trait that is nonlinear to the trait's frequency in the parent's generation. 
Continuing with the example, when an individual is 80\% likely to copy the common paddle grip even when only 60\% of the population is using it, it is said to be frequency-biased.\\
Frequency bias could be negative too. \citet{negativeFrequency} show that societies under competitive conditions are likely to develop diversity in foraging specialization rather than uniformity.

%prestige bias - what is it, what's missing
Prestige means having a good reputation or high-esteem, therefore does not directly signify success (although it may imply it), making it an \textit{indirect bias}.
Both \citet[Ch. 8]{evolutionBook} and \citet{complexityPaper} claim that prestige biases are probably more common in humans than success biases.
\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population, if the indirect bias is strong enough.
They claim the bias could lead to a \textit{runaway process}, caused by a cultural equivalent of \textit{sexual selection} \citep{sexualSelectionBook}.
On the other hand, \citet{henrichBroesch} claim that prestige biases, over generations, can lead to cultural adaptations.
According to them, prestige can make a maladaptive trait spread in the population, but can also accelerate the spread of adaptive traits as well.
\textit{Prestige bias} is often mentioned in the literature, but seldom modeled.
\citet{evolutionBook} have modeled the prestige bias, but didn't include the effects the copiers of a role-model has on the probability of other individuals to choose the same role model.\\
This effect is similar to \textit{conformity} \citep{conformity}, which is usually modeled as a different bias.
\textit{Conformist learning} (imitating locally common behaviors) is a known bias in cultural transmission \citep{conformism}, and we suggest that prestige bias is made up by both indirect bias and a new type of conformity.
Our new component, \textit{influence}, is assigned to a role-model, contrary to conformity, which refers to the frequency of a trait in the population, regardless which individuals posses it.
\textbf{The goal of this study is to define a more realistic model for prestige bias and analyze the dynamics of the population it causes}.

Today, due to social media, it is easier than ever to estimate the influence individuals have over others, therefore it is probably a major part of humans decision-making process. For example, the number of \textit{followers} a person has in the mobile application \textit{Instagram} may significantly affect how his beliefs are perceived by the population.
We want to create a model that better fits reality and simulate scenarios that better mimic cultural transmission dynamics.
With a more accurate model of prestige bias, we may understand better how cultural traits are transmitted, and why.
Moreover, we could better explain the cause for the spread of maladaptive traits, or the acceleration of adaptive traits often seen in humans.

\section{Models}
\paragraph{Reminder:} A \textit{Wright–Fisher model} is a mathematical model meant to describe a genetic drift process. This model assumes that generations do not overlap and that each copy of the gene found in the new generation is drawn independently at random from all copies of the gene in the old generation.

A \textit{Moran model} assumes overlapping generations. At each time step, one individual is chosen to reproduce and one individual is chosen to die. In our models we harness these two models and modify them to describe new mathematical models that we use to expand the basic indirect bias model \citet{evolutionBook} suggest.

\paragraph{Model.} Consider a population of N individuals, each individual has one trait on a continuous scale. Every generation, $N$ naive individuals (\textit{copiers}) must choose a trait to copy from one of the individuals of the previous generation (\textit{role-models}). Similar to a Wright–Fisher model, we assume the generations don’t overlap. We base our model on the model of \citet{evolutionBook}, by assuming only oblique transmission of the traits (\textit{Indicator trait - A}). Unlike their model, we omit a second trait called \textbf{Indirectly biased trait} to lower complexity. The model’s state at time $t$ can be described by:
\begin{equation}
\vec{A}_t=(A_{t,1}, \ldots, A_{t,N})
\end{equation}
where $\vec{A}_t$ is a vector describing the indicator traits at time $t$, and $\vec{A}_0$ is drawn from a standard normal distribution.
Each individual from generation $t+1$, a \textit{copier}, inherits traits like so:
\begin{equation}
A_i' = F_i(\vec{A}_t)
\end{equation}
where $A_i'$ is the indicator and indirect trait values correspondingly, that copier $i$ acquires.
We use $A_i'$ as an alias for $A_{i,(t+1)}$ for simplicity for the transition between generations $t \rightarrow t+1$.
$F$ is a function over the $t$ generation traits vector, and is defined differently for every implementation of the \textbf{Generic model}.

\paragraph{Success bias.} \citet[Ch.8, p.247-249]{evolutionBook} describe a method of inheritance using a \textit{blend}, i.e weighted average of the trait of the entire generation. They define $F$ as a weighted average  of the role-models' traits in a single generation:
\begin{equation}
F_i(\vec{X}) = \sum_{j=1}^N \Big(G_{ij}\cdot X_{ij}\Big) \\\\
\end{equation}
where $G_{i,j}$ is: 
\begin{equation}
G_{ij} = \frac{\beta(A_{ij})}{\sum_{l=1}^{N} \beta(A_{il})}
\end{equation}
We define $G_{ij}$ to be the \textit{Success bias} of role-model $j$ in the eyes of copier $i$.
$A_{i,j}$ is the absolute indicator trait value copier $i$ estimates role-model $j$ has:
\begin{equation}\label{eq:relativeIndicator}
A_{i,j} = A_j + e_i,
\end{equation}
where $e_i$ is the copier's error of estimation, $\vec{e} \sim N(0,\frac{1}{\eta^2})$.
$\beta(X)$ is the bias function, meant to quantify the success bias of a role-model:
\begin{equation}\label{eq:success_bias}
\beta(A_{i,j}) = b \cdot \exp^{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)},
\end{equation} 
where $\hat{A}$ is the optimal indicator value and $J,b$ are model parameters to control the "strength" of the bias.
$G_{i,j}$ is therefore the relative success score copier $i$ assigns to role-model $j$, resembling \textit{relative fitness} in genetic transmission models.

\paragraph{Random choice transmission.}
\citet{evolutionBook} note that the method of transmission they use in their model has alternatives. We follow their suggestion and create a model similar to theirs, with random choice as a transmission method: The probability of copier $i$ to choose role-model $j$ as his role-model to copy its traits from is $G_{i,j}$.
Once a copier chose its role-model, it will copy both its traits only from his role-model, instead of a weighted average of the entire role-model generation:
\begin{equation}
A_i' = A_{i,j}
\end{equation}

\paragraph{Influence bias.}
Copiers choose their role-models one by one.
After copier $i$ chose a role-model, we denote $K_{ij}$ as the number of copiers that chose role-model $j$ until that point, such that $\sum_{j=1}^N{K_{i,j}} = i$. 
The stochastic process of role-model choice, 
\begin{equation} \label{eq:process}
\big\{\vec{K}_i\big\}_{i=1}^N, \quad \vec{K}_i=(K_{i1}, \ldots, K_{iN}),
\end{equation}
is described by the recurrence equation
\begin{equation} \label{eq:recurrence}
K_{i,j} = K_{i-1,j} + S_{i,j}, \quad i,j=1,2,\ldots,N
\end{equation}
where $S_{i,j}=1$ if the $i$-th copier chose role-model~$j$ and 0 otherwise, and the initial state is $K_{0,j}=0$.

The probability that the $i$-th copier chose role-model $j$
\begin{equation}\label{eq:recPrestige}
G_{i,j}=P(S_{i,j}=1| S_{1,j},S_{2,j},...,S_{i-1,j})
\end{equation}
is the prestige of role-model $j$ in the eyes of copier $i$.
This prestige $G_{i,j}$ is determined as follows.
First, role-model~$j$ is characterized by its indicator value $A_j$ as before, and the estimated indicator value by copier $i$, $A_{i,j}$ remains as Eq. \ref{eq:relativeIndicator}.
Finally, the prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased indicator value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, 
\begin{equation}\label{prestige_eq}
G_{i,j} = \frac{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}{W_i},
\end{equation}
where the weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of the indicator and the influence in the prestige, and $W_i$ is a normalizing factor to ensure $\sum_{j=1}^N{G_{i,j}}=1$,
\begin{equation}
W_i = \sum_{j=1}^N{\Big(\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}\Big)}.
\end{equation}
\\

Currently $\big\{\vec{K}_i\big\}_{i=1}^N$ is a stochastic process where each state depends on the previous state, i.e a Markov chain.
We wanted to find an equivalent stochastic process that has the same joint distribution on $\big\{\vec{K}_i\big\}_{i=1}^N$, but it is possible to evaluate the joint distribution directly without evaluating all the marginal conditional distributions (eq. \ref{eq:recurrence},\ref{eq:recPrestige}).

We found two approximations to our process, which are summarized here and explained in detail later on:
\begin{enumerate}
\item 
$K_{i,j}$ follows the general binomial distribution defined by \citet{GBD}.
Moreover, $\mathbb{E}[K_{N,j}] = N \cdot G_{1,j}$ if $e=e_l=e_m$ for all $l,m$.
 That is, the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers. 
 In addition, we find that when $\alpha$ is homogeneous, $\alpha_l=\alpha_m$ for all $l,m$, then $\mathbb{E}[K_{N,j}] = \beta(A'_j) \; / \; \overline{\beta(A') }$, where $A'_j$ is the estimated indicator value $A'_j=A_j+e$, and 
 $\overline{ \beta(A') }$ is the population mean estimated indicator value. 
 That is, the expected number of copiers of a role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models.
\item The role-model choice process (equation~\ref{eq:process}) is equivalent to a P\'{o}lya urn model if $e_l=e_m$ for all $l,m$. 
Therefore, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$ follows a Dirichlet-Multinomial distribution,
\begin{equation}
\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big), 
\end{equation}
where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$.
Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$.
\end{enumerate}

\section{General Binomial Distribution Approximation}
The general binomial distribution (GBD) is achieved by a series of Bernoulli experiments, with possible dependency between experiments.
\paragraph{Proposition:} The number of copiers $K_{i,j}$ follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A'_j))$, when $e_l=e_m$ for all $l,m \in N$ and $A'_j=A_j + e$ 
\paragraph{Proof: } We'll denote $Q_j(k,i)=P(K_{i,j} = k | K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$, using conditional probability and equation \ref{eq:recurrence}:
\begin{equation}\label{recursive}
Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1)
\end{equation}
where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.

Equation \ref{recursive} is equivalent to equation 2.1 that \citet{GBD} define.
$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$.
By describing the process of equation \ref{eq:process} as \citep{GBD} did, we've completed the proof.

\paragraph{Corollary 1: } $\mathbb{E}[K_{N,j}] = N \cdot G_{1,j}$.\\
In \citep[equation 2.3]{GBD}, they show that the expected value of $k$ is: \\
$\mathbb{E}[k] = N \cdot Q_j(1,1)$ (using different notations).
$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any choices are made.
$Q_j(1,1) = G_{1,j}$ by definition, therefore we can say that $\mathbb{E}[K_{N,j}]=N \cdot G_{1,j}$.\\

\paragraph{Corollary 2: } $\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) / \overline{\alpha \cdot \beta(A')}$.
\paragraph{Proof: } The initial prestige of role-model $j$ based on equation \ref{prestige_eq} is:
\begin{equation}\label{initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A'_j)}{\sum\limits_{m=1}^{N}\alpha_m\cdot\beta(A'_m)}
\end{equation}
The denominator of equation \ref{initial_prob} can also be formulated as:
\begin{equation}\label{denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A'_m) = N \cdot \overline{\alpha \cdot \beta(A')}
\end{equation}
where $\overline{\alpha\beta(A')}$ is the mean value of $\alpha_m\cdot\beta(A'_m)$ for all $m$.
Using equation \ref{denominator} we get:
\begin{equation}
\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) \bigg/ \overline{\alpha \cdot \beta(A')}
\end{equation},
completing our proof.

The special case where $\alpha = \alpha_l=\alpha_m$ for all $l,m \in N$ is interesting, because we can evaluate the expected number of copiers using a linear equation:
\begin{equation}
\mathbb{E}[K_{Nj}]= N\cdot\frac{\alpha\cdot\beta(A'_j)}{\sum\limits_{m=1}^{N}\alpha\cdot\beta(A'_m)} =\beta(A'_j) \bigg/ \overline{\beta(A')}
\end{equation}
where the only variable is $A'_j$, because $\overline{\beta(A')}$ is the mean of the distribution we draw the indicator values from, modified by some constant parameters of $\beta$.
We can then denote $L = 1/\overline{\beta(A')}$ and write:

\begin{equation}\label{linearEq}
\mathbb{E}[K_{Nj}] = L\cdot \beta(A'_j)
\end{equation}

\section{Dirichlet-Multinomial Distribution Approximation}
\paragraph{Reminder: \textit{Pólya urn model}}  is a stochastic process that is defined as such: 
The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors. When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same colour.\\
Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
Let $S_{i,j}=1$ when drawing a $j$ colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is:
\begin{equation}\label{polya}
\begin{split}
P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\\\
 & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
\end{split}
\end{equation}
where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.

\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
\paragraph{Proof:} 
We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
Using equation \ref{prestige_eq} we get:
\begin{equation}\label{copier_choose}
\begin{split}
G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\\\
&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\\\
& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
\end{split}
\end{equation}
Equations \ref{polya} and \ref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.

\paragraph{Corollary 1:}
In their paper, \citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{Pólya urn model} will converge to the Dirichlet distribution as the number of draws approaches infinity, based on \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative "weight" or the proportion each role-model has when evaluated as a role-model. Drawing from a Multinomial distribution where the parameters are the modified weights gained from the Dirichlet distribution is viable for selecting the role-model for the next generation.
We can therefore sample from a Dirichlet-Multinomial distribution to approximate how many copiers each of the role-models will have:
$\vec{K_i} \sim DM(N,\vec{G_1})$.

\paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population. To test if our process is still DM distributed when there are copying errors in the population, we ran 400 simulations for three different error scales ($\eta$). To check the resemblance of the DM approximation to the original iterative process, we measure the $\chi^2$ statistic of both processes and the results can be seen in Fig. \ref{fig:chiSquaredHist}.
Even with a relatively high error scales (1\% and 10\% of J) we can see the distributions of the $\chi^2$ metrics are very similar.
With a higher $\eta$ (e.g $\eta=J$), which is approximately 100\% error when evaluating a trait, the distributions are noticeably different.

In addition to the chi-squared test, we want to observe how well does the Dirichlet-Multinomial distribution approximates our entire model, and not just one generation in it.
To do that we simplify our model to a binary model, so the simulations of the model to run in a feasible amount of time.

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../../graphs/chi_square_stats/chi_hist_homogenous_0_01.pdf}
    \subcaption{Error scale is 0.01}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../../graphs/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
    \subcaption{Error scale is 0.1}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../../graphs/chi_square_stats/chi_hist_homogenous_J.pdf}
  \subcaption{Error scale is 1(=J)}  
  \end{subfigure}
  \caption{DM approximation vs iterative process. Population size 2000. 			Aggregated values of 400 simulations}	
  \label{fig:chiSquaredHist}
  \end{center}
\end{figure}

\section{The binary model} The indicator trait can now manifest in only two phenotypes, and for simplicity we define they can be either $\hat{A}$ or $A$. In the binary model, the influence is determined by the number of copiers already chosen \textbf{any} role-model with either $A$ or $\hat{A}$, as all role-models with $A$ will contribute to the probability of the trait to be inherited just the same (can be proved with simple induction). Simply put, assuming there are two role-models with the $A$ trait, the probability a copier will copy from either role-model will be the same, and the probability the $A$ trait will be inherited is the sum of both role-models.
In the general case, the probability of the $i$-th individual to inherit trait $A$, based on eq.\ref{copier_choose} is:
\begin{equation}\label{eq:binary-model}
P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_A$ is the number of copiers that already chose $A$.\\

In the first generation there is a single individual with $\hat{A}$, and the rest have $A$.
We're interesting in studying the difference between the real binary model as we defined in eq. \ref{eq:binary-model}, and the Dirichlet-Multinomial approximation. Specifically, we're interesting in the fixation probability of the favored trait ($\hat{A}$) and its time to fixation.

\begin{figure}
    \includegraphics[width=\linewidth]{../../graphs/binary/num_sims.pdf}
  \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$}	
  \label{fig:num_sims}
\end{figure}

The first step was to find the number of simulations needed to sufficiently approximate the real model with the DM approximation. From fig. \ref{fig:num_sims} we see that $1000$ simulations or higher is enough.

The next step was to see how the observed metrics (fixation probability and time) varies when relaxing our assumptions we used to prove the DM approximation.
First we relaxed our assumption of no mutation. To include mutation in the binary model, it needs to be redefined, since in the original model it was based on the fact the traits are drawn from a continuous scale. In the binary model mutation will be manifested as an error when evaluating the bias itself. This is easily done by using a heterogeneous $J$ parameter, which controls the strength of the success bias (see eq. \ref{eq:success_bias}).

\begin{figure}
    \includegraphics[width=\linewidth]{../../graphs/binary/full_vs_dm_mutation.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis}	
  \label{fig:hetro_mutation}
\end{figure}

In fig. \ref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models. When mutation is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).

\begin{figure}
    \includegraphics[width=\linewidth]{../../graphs/binary/full_vs_dm_changing_alpha.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$}	
  \label{fig:hetro_alpha}
\end{figure}

In fig. \ref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead. Similar to the mutation comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale. We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.

\section{Fixation probability and time - binary model}
\paragraph{Kimura's approximation:}
After establishing a case in the favor of our DM approximation, we wanted to use it to examine the behavior of the population. Specifically, we wanted to analyze the influence of the indicator weight ($\alpha$) on the fixation probability and time to fixation of the favored phenotype in a binary model.
For simplicity, we don't include mutation rate in the binary model approximations.
Following \citet{durret}, we used our DM approximation of the model to find the effective population size. From eq. \ref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.

\paragraph{Proposition:} $1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.

\paragraph{Proof:} Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals. Let $X$ be the number of individuals of type $\hat{A}$ so $x=X/N$. $X'$ is the number of individuals with $\hat{A}$ in the next generation and $x'$ their frequency.
By definition $\beta(\hat{A})=1$, and for simplicity we'll denote $\beta(A)=\beta$ ($\beta<1$).

The expected number of individuals of a DM distribution is:
\begin{equation}
E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2},
\end{equation}
where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from eq. \ref{eq:binary-model}.
We want to use frequencies instead of quantities to follow Durret's process so:
\begin{equation}
E[x'] = E[\frac{X'}{N}] = \frac{1}{N}E[X']
\end{equation}
Putting it together we get:
\begin{equation}
\begin{split}
E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\\\
	 &= \frac{x}{x + (1-x)\beta}
\end{split}
\end{equation}

which is identical to the equation in the top of page 253, chap 7.2 in \citet{durret}. We therefore use the same approximation and say that:
\begin{equation}
\begin{split}
E[x'] =& \frac{x}{x + (1-x)\beta} = \frac{x}{x + (1-x)(1-s)} =\\
 &= x + x(1-x)s + o(s)\\
  &= x + x(1-x)(1-\beta) + o(1-\beta)
\end{split}
\end{equation}

By definition, $x$ is constant, so $E[x] = x$. We continue to calculate $E[x'-x]$:
\begin{equation}\label{eq:expec_freq}
E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta)
\end{equation}
where when substituting $1-\beta$ with $s$, we get the same result as \citet{durret} which is the desired result.

\paragraph{Proposition:} $Ne=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.

\paragraph{Proof:} The variance of a DM distribution is:
\begin{equation}
V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}(1-\frac{\alpha_1}{\alpha_1+\alpha_2})
(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2})
\end{equation}
And again, we want to use frequencies so:
\begin{equation}
V(\frac{X'}{N}) = \frac{1}{N^2}V(x')
\end{equation}

Putting it together with our model's notations:
\begin{equation}
V(x') = \frac{1}{N^2}N\frac{x}{x+(1-x)\beta}(1-\frac{x}{x+(1-x)\beta})
(\frac{N + \alpha' xN + \alpha' N(1-x)\beta}{1 + \alpha' xN + \alpha' N(1-x)\beta}) 
\end{equation}

Like Durret, we'll use the zero order of the approximation when $\beta\approx1$,so:
\begin{equation}
\frac{x}{x + (1-x)\beta} \approx x
\end{equation}
and we also use $\beta\approx1$ for the entire variance expression and get:
\begin{equation}
\begin{split}
V(x') & \approx  \frac{1}{N} x(1-x)
(\frac{N + \alpha' xN + \alpha' N - \alpha' xN}{1 + \alpha' xN + \alpha' N - \alpha' xN})\\
&=  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N}) 
\end{split}
\end{equation}

Again following Durret we want to calculate:
\begin{equation}
V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N})
\end{equation}
because $x$ is a constant so $V(x) = 0$

In our model, $\alpha'$ is the odds ratio of a parameter we called "indicator weight", denoted in our model as $\alpha$, so:
\begin{equation}
\alpha' = \frac{\alpha}{1-\alpha}
\end{equation}

And combining with the previous equations we get:
\begin{equation}\label{eq:const_var}
\begin{split}
V(x'-x) & \approx x(1-x)(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N})\\\\
 &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\\\
 &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\\\
  &= x(1-x)(\frac{1}{\alpha N + (1-\alpha)})\\\\
  &= x(1-x)\frac{1}{N_e}
\end{split}
\end{equation}

Using our substitute for a selection coefficient, $1-\beta$, and the effective population size $N_e$, we can estimate the fixation probability and time of our binary model.

The fixation probability derived from Kimura is therefore:
\begin{equation}\label{eq:kimura_p}
P_{fix} = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
\end{equation}

where $x$ is the initial frequency of the advantageous phenotype $\hat{A}$.

The time to fixation can be estimated by:
\begin{equation}\label{eq:kimura_t}
T_{fix}=\frac{1-P_{fix}}{1-\beta}\int_0^x\frac{e^{2(1-\beta) \xi}-1}{\xi(1-\xi)}d\xi+ \frac{P_{fix}}{1-\beta}\int_x^1\frac{1-e^{-2(1-\beta)(1-\xi)}}{\xi(1-\xi)}d\xi
\end{equation}
where the integrals cannot be solved in closed form, so we can only estimate them numerically.

To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
In fig \ref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
In fig \ref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations (eq. \ref{eq:kimura_p} and \ref{eq:kimura_t})

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../../graphs/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../../graphs/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=0.044$}
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../../graphs/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../../graphs/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$}
  \label{fig:var_beta}
\end{figure}

\section{Changing environment}
After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.

For that we will find an expression for the expected and variance of the change in frequency between $t$ generations.
Let $s_t=N(1-\beta_t)$, and $S_n=\sum\limits_{i=1}^n s_i$, where $\beta_t$ is $\beta(A)$ at time/generation $t$.

\paragraph{Proposition:} $E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$ , $V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
\paragraph{Proof by induction:} From eq. \ref{eq:expec_freq} we know that
\begin{equation}\label{eq:ch_1}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\\\
&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
\end{split}
\end{equation}
Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
\end{split}
\end{equation}

we can now use the induction assumption of $V(\frac{X_t}{N})$ and get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &\simeq
E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x)
\end{split}
\end{equation}
From eq. \ref{eq:ch_1} we know that
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] \\\\
&\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\\\
&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x)
\end{split}
\end{equation}
Now we'll omit $O(\frac{1}{Ne\cdot N})$ and get
\begin{equation}\label{eq:ch_2}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)
\end{equation}

We'll now look at the induction assumption to see that
\begin{equation}
E\left[\frac{X_t}{N}-x\right]=E\left[\frac{X_t}{N}\right]-E[x]=E\left[\frac{X_t}{N}\right]-x ,
\end{equation}
so using the assumption we get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\right] &\simeq \frac{1}{N} S_t x(1-x)+x \\
1 - E\left[\frac{X_t}{N}\right] &\simeq 1- \frac{1}{N} S_t x(1-x)+x
\end{split}
\end{equation}
we'll use both expressions in eq. \ref{eq:ch_2} and get
\begin{equation}\label{eq:ch_3}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\\\
&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x)
\end{split}
\end{equation}
after again omitting $O(\frac{1}{N^2})$ parts of the equation.
To conclude our proof, we see that
\begin{equation}
E\left[\frac{X_{t+1}}{N}-x\right] = E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right]
\end{equation}
so again using the induction assumption, together with eq. \ref{eq:ch_3} we get
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-x\right] &\simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
& \simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) \\
& \simeq \frac{1}{N} S_{t+1} x(1-x)
\end{split}
\end{equation}
which proves the first part of our preposition.

For the second part, we'll use a property of variance:
\begin{equation}\label{eq:ch_var}
V\left(\frac{X_{t+1}}{N}\right) = E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right)
\end{equation}

using eq.\ref{eq:ch_1} we see that:
\begin{equation}\label{eq:ch_var1}
\begin{split}
E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] &= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\\\
E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] = \frac{X_t}{N} &+ \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right)
\end{split}
\end{equation}

Using eq.\ref{eq:const_var} we get:
\begin{equation}
V\left(\frac{X_{t+1}}{N} \bigg|X_t \right) = \frac{1}{N_e}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right)
\end{equation}

and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of eq.\ref{eq:ch_var} we get:
\begin{equation}\label{eq:ch_var2}
E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] = \frac{1}{N_e}E\left[\frac{X_t}{N}\left(1- \frac{X_t}{N}\right) \right] \simeq \frac{1}{N_e} x(1-x)
\end{equation}

and moving on to simplify the second part of eq.\ref{eq:ch_var} using eq.\ref{eq:ch_var1}:
\begin{equation}
V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) = V\left(\frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)
\end{equation}

and now, because $\frac{X_t}{N}$ is a frequency, i.e $0\leq\frac{X_t}{N}\leq1$, we know that $V\left(\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq\frac{1}{4}$. We therefore see that:
\begin{equation}
V\left(\frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq \frac{1}{4N^2}s^2_{t+1}
\end{equation}
and so it can be ignored.
Combining our equations we get:
\begin{equation}
V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) = V\left(\frac{X_t}{N}\right) + O\left(\frac{1}{N^2}\right)\simeq V\left(\frac{X_t}{N}\right)
\end{equation}

Using the induction assumption and eq.\ref{eq:ch_var2}:
\begin{equation}
V\left(\frac{X_{t+1}}{N}\right) \simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1)
\end{equation}
proving the second part of our preposition.

Following our proof, we can say that after many cycles, we can use a modified version of our fixation probability:
\begin{equation}
P_{fix} = \frac{1-e^{-2 S_n N_e x}}{1-e^{-2 S_n N_e}}
\end{equation}
where $S_n = ((k-l)/(k+l))*(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.

We wanted again to validate our results, using simulations.
This time, the number of parameters increased: in addition to $\alpha,\beta$, there are also $k,l$ as model parameters.

We again tried different variations of the parameters, changing only one of them at a time.
In fig.\ref{fig:ch_env_alpha_beta} we can see that $\alpha$ on it's own doesn't cause any deviation for the the estimation. $\beta$ however affects the results greatly.

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{$1-\beta=s=0.005$}
    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{$\alpha=0.1$}
    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$}
  \label{fig:ch_env_alpha_beta}
\end{figure}

We plotted along the modified estimation the original Kimura's estimation, as a limiter. We suspect that when $\beta$ is too large, there won't be many cycles in the simulations. This might happen if either the population reaches a high frequency of the ideal trait after only a few cycles, or it get extinct very quickly, because the advantage it had in the $k$ generations wasn't sufficient, and the same $s$ becomes a greater disadvantage when the environment changes, resulting in a fast extinction.

In the larger values of $beta$ we even see a deviation from the original estimation environment, but it's to be expected, because Kimura's equations are only viable for small $s$ values.

We then also tried changing the composition of the cycle, by keeping a constant $n$, but changing $k,l$ accordingly.

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$}
  \label{fig:ch_env_k_l}
\end{figure}

In fig.\ref{fig:ch_env_k_l} we see again that the simulations results are mostly above our modified estimation, but still contained in the area between it and the original (constant environment) estimation.
We see that the larger $k$ in relation to $l$, the closer the simulation results to the original estimation.
This was again to be expected - the larger $k$ than $l$, the more time the ideal trait has to be acquired in the population, resulting in a state where the influence alone will accelerate its fixation. So when the cycle reaches the $l$ part, the frequency of the trait is high enough to not be affected by the negative change in the environment, due to the influence.

\section{Conclusion}
Cultural transmission is the phenomenon of which cultural elements, in the form of attitudes, values, beliefs, and behavioral patterns, are transmitted between individuals, typically via copying.
Some cultural traits can be more likely to be copied by others, regardless of their frequency in the population.  
Such transmission biases are common in cultural transmission processes. 
Many models are based on the assumption that success can be correctly identified, and easily copied.
Here we assume that success isn't correctly identified, therefore individuals may use other indicators to try and estimate the success of potential role-models.
We believe, as \citet{complexityPaper} suggest, that \textit{prestige biases} are more common in nature than success biases, since estimating success is probably harder.
We believe prestige is composed of two main components: a trait that indicates success (but doesn't guarantee it), and the influence the individual already has on others, i.e number of individuals already chose him as a role-model.
We suggest a model for \textit{prestige bias}, following the \textit{indirect bias} model \citet{evolutionBook} have suggested, and added the \textit{influence trait} to it.
We believe that in this era of social media it is easy to estimate one's influence over others.
It is therefore crucial to model the cultural biases more realistically than success bias based model, and we believe including influence is crucial for that purpose.\\
With a more realistic model of a common cultural transmission bias, we may be able to better understand decision-making processes in humans, including life-changing choices such as occupation or a life partner. 
Our model can be expanded in multiple ways: observing the effects of different bias functions, including errors in estimating the influence, combining factors of cost when copying from an influential role model (not all could afford to copy from the most popular role-model), and analyzing the differences when including several optimal values for the indicator trait (multiple preference traits in the population).

\clearpage
\section{Appendix A - Time table}

\paragraph{Today - Oct 2021:}
Find approximation replacing Durrett's equations for the time to fixation.

\paragraph{Nov - Mar 2021:}
Combining the findings to a paper and a thesis.

\clearpage
\bibliography{refs}
\bibliographystyle{apalike}
\end{document}

### 2022-01-26 ms/PrestigeBias.tex
rename and remove unecessary files

--- 2022-01-26 src/prestige_bias_paper/PrestigeBias.tex
@@
   \begin{subfigure}[a]{0.3\textwidth}
-    \includegraphics[width=\linewidth]{../../graphs/chi_square_stats/chi_hist_homogenous_0_01.pdf}
+    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
     \subcaption{Error scale is 0.01}
@@
     \begin{subfigure}[a]{0.3\textwidth}
-    \includegraphics[width=\linewidth]{../../graphs/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
+    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
     \subcaption{Error scale is 0.1}
@@
     \begin{subfigure}[a]{0.3\textwidth}
-    \includegraphics[width=\linewidth]{../../graphs/chi_square_stats/chi_hist_homogenous_J.pdf}
+    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
   \subcaption{Error scale is 1(=J)}  
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{../../graphs/binary/num_sims.pdf}
+    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
   \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$}	
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{../../graphs/binary/full_vs_dm_mutation.pdf}
+    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
   \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis}	
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{../../graphs/binary/full_vs_dm_changing_alpha.pdf}
+    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
   \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$}	
@@
   \begin{subfigure}[a]{0.49\linewidth}
-    \includegraphics[width=\linewidth]{../../graphs/binary/fix_prob_var_alpha.pdf}
+    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
    \end{subfigure}
    \begin{subfigure}[a]{0.49\linewidth}
-    \includegraphics[width=\linewidth]{../../graphs/binary/fix_time_var_alpha.pdf}
+    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
    \end{subfigure}
@@
   \begin{subfigure}[a]{0.49\linewidth}
-    \includegraphics[width=\linewidth]{../../graphs/binary/fix_prob_var_beta.pdf}
+    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
    \end{subfigure}
    \begin{subfigure}[a]{0.49\linewidth}
-    \includegraphics[width=\linewidth]{../../graphs/binary/fix_time_var_beta.pdf}
+    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
    \end{subfigure}
@@
   \caption{$1-\beta=s=0.005$}
-    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_alpha.pdf}
+    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
    \end{subfigure}
@@
    \caption{$\alpha=0.1$}
-    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_beta.pdf}
+    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
    \end{subfigure}
@@
   \begin{subfigure}[a]{0.49\linewidth}
-    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_k_div_l.pdf}
+    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
    \end{subfigure}
    \begin{subfigure}[a]{0.49\linewidth}
-    \includegraphics[width=\linewidth]{../../graphs/changed_env/ch_env_var_k_min_l.pdf}
+    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
    \end{subfigure}

### 2022-01-30 ms/PrestigeBias.tex
presentation + minor changes

@@
 \paragraph{Proposition:} $E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$ , $V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
-\paragraph{Proof by induction:} From eq. \ref{eq:expec_freq} we know that
+
+The proof is based on the proof of \citet{changeEnv}, proving a similar scenario.
+\paragraph{Proof by induction:}
+From eq. \ref{eq:expec_freq} we know that
 \begin{equation}\label{eq:ch_1}
@@
 \begin{equation}
-P_{fix} = \frac{1-e^{-2 S_n N_e x}}{1-e^{-2 S_n N_e}}
+P_{fix} = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
 \end{equation}
-where $S_n = ((k-l)/(k+l))*(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
+where $\frac{S_n}{n} = \frac{k-l}{k+l}(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
 In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.
@@
 
-We then also tried changing the composition of the cycle, by keeping a constant $n$, but changing $k,l$ accordingly.
+We then also tried changing the composition of the cycle, by keeping a constant $n=40$, but changing $k,l$ accordingly.
 
@@
 
-In fig.\ref{fig:ch_env_k_l} we see again that the simulations results are mostly above our modified estimation, but still contained in the area between it and the original (constant environment) estimation.
-We see that the larger $k$ in relation to $l$, the closer the simulation results to the original estimation.
-This was again to be expected - the larger $k$ than $l$, the more time the ideal trait has to be acquired in the population, resulting in a state where the influence alone will accelerate its fixation.
-So when the cycle reaches the $l$ part, the frequency of the trait is high enough to not be affected by the negative change in the environment, due to the influence.
+In fig.\ref{fig:ch_env_k_l} we see that the larger $k$ relative to $l$, the closer the modified equation is to the original estimation of the constant environment. 
+When using higher values of $n$, the simulation results doesn't fit the equation result as with lower values.
+This is due to the fact that our proof, and therefore our equation is more accurate when more cycles occur.
+When $n$ is high, there will be less cycles, and the simulations will get closer to the constant environment equation.
 

### 2022-02-06 ms/PrestigeBias.tex
update

@@
 \clearpage
+
+\section{Abstract}
+Copying our role-models have always been an efficient method of acquiring knowledge.
+Copying successful role-model is one of the methods of cultural transmission of traits.
+In this paper, we study the various biases and their effects of the population and it's evolution.
+The most common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears successful to us.
+This estimation is based on the performance of the role-model alone, without any other factors.
+Here, we study another factor we believe aids to better model the cultural inheritance of traits in a large population.
+\textit{Influence bias} is a bias evaluated by the number of copiers a role-model already has.
+In our model we combine these components to what we call the \textbf{Prestige bias} and analyze its relationship to the dynamics of the population.
+We successfully found mathematical approximations to our model, easing the mathematical analysis and the computation power required for simulations.
+We show the value of these approximations using simulations, and their robustness to variations such as mutation and other relaxations required for the mathematical proofs.
+In the binary form of our model, we found alternatives to \textit{Kimura's} equations for approximating fixation probability and time to fixation of an invading advantageous trait, in both a constant and changing environment.
+We show that \textit{Influence} solely affects the effective population size.
+We found that influence acts as an accelerator for a state of the population, matching the \textit{rich getting richer} it was based on.
+We believe such model better describes how humans acquire knowledge from one another, mainly in the last years where social networks are very popular.
+Social networks allow easy access to estimate number of copiers a role-model has, with little to no effort.
 
@@
 
-\section{Models}
+\section{Models and Methods}
 \paragraph{Reminder:} A \textit{Wright–Fisher model} is a mathematical model meant to describe a genetic drift process.
@@
 
-\paragraph{Model.} Consider a population of N individuals, each individual has one trait on a continuous scale.
+\subsection{Continuous Model}
+Consider a population of N individuals, each individual has one trait on a continuous scale.
 Every generation, $N$ naive individuals (\textit{copiers}) must choose a trait to copy from one of the individuals of the previous generation (\textit{role-models}).
@@
 \end{equation}
-\\
 
+\subsection{Binary model} The indicator trait can now manifest in only two phenotypes, and for simplicity we define they can be either $\hat{A}$ or $A$.
+In the binary model, the influence is determined by the number of copiers already chosen \textbf{any} role-model with either $A$ or $\hat{A}$, as all role-models with $A$ will contribute to the probability of the trait to be inherited just the same (can be proved with simple induction).
+Simply put, assuming there are two role-models with the $A$ trait, the probability a copier will copy from either role-model will be the same, and the probability the $A$ trait will be inherited is the sum of both role-models.
+In the general case, the probability of the $i$-th individual to inherit trait $A$, based on eq.\ref{copier_choose} is:
+\begin{equation}\label{eq:binary-model}
+P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
+\end{equation}
+where $X$ is the number of role-models with trait $\hat{A}$ and $K_A$ is the number of copiers that already chose $A$.\\
+The model begins with the first generation having a single individual with $\hat{A}$, and the rest have $A$. The process itself is the same stochastic process as the continuous model.
+
+\subsection{Methods}
+The main methods we used to experiment and compare our models is using computer generated simulations.
+In order to establish our claims and base our mathematical approximations of our models, we used the $\chi^2$ test for the full continuous model, and the Kimura's equations of fixation probability and time to fixation for the binary model.
+
+\section{Results}
+\subsection{Approximations}
 Currently $\big\{\vec{K}_i\big\}_{i=1}^N$ is a stochastic process where each state depends on the previous state, i.e a Markov chain.
@@
 
-\section{General Binomial Distribution Approximation}
+\subsection{General Binomial Distribution Approximation}
 The general binomial distribution (GBD) is achieved by a series of Bernoulli experiments, with possible dependency between experiments.
@@
 
-\section{Dirichlet-Multinomial Distribution Approximation}
+\subsection{Dirichlet-Multinomial Distribution Approximation}
 \paragraph{Reminder: \textit{Pólya urn model}}  is a stochastic process that is defined as such: 
@@
 
-\section{The binary model} The indicator trait can now manifest in only two phenotypes, and for simplicity we define they can be either $\hat{A}$ or $A$.
-In the binary model, the influence is determined by the number of copiers already chosen \textbf{any} role-model with either $A$ or $\hat{A}$, as all role-models with $A$ will contribute to the probability of the trait to be inherited just the same (can be proved with simple induction).
-Simply put, assuming there are two role-models with the $A$ trait, the probability a copier will copy from either role-model will be the same, and the probability the $A$ trait will be inherited is the sum of both role-models.
-In the general case, the probability of the $i$-th individual to inherit trait $A$, based on eq.\ref{copier_choose} is:
-\begin{equation}\label{eq:binary-model}
-P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
-\end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$ and $K_A$ is the number of copiers that already chose $A$.\\
-
-In the first generation there is a single individual with $\hat{A}$, and the rest have $A$.
+\subsection{Numeric comparisons}
 We're interesting in studying the difference between the real binary model as we defined in eq.
@@
 
-\section{Fixation probability and time - binary model}
+\subsection{Fixation probability and time - binary model}
 \paragraph{Kimura's approximation:}
@@
 
-\section{Changing environment}
+\subsection{Changing environment}
 After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.
@@
 
-\section{Conclusion}
+\section{Discussion}
 Cultural transmission is the phenomenon of which cultural elements, in the form of attitudes, values, beliefs, and behavioral patterns, are transmitted between individuals, typically via copying.
@@
 Here we assume that success isn't correctly identified, therefore individuals may use other indicators to try and estimate the success of potential role-models.
-We believe, as \citet{complexityPaper} suggest, that \textit{prestige biases} are more common in nature than success biases, since estimating success is probably harder.
+We believe, as \citet{complexityPaper} suggest, that \textit{prestige biases} are more common in nature than success biases, since estimating success is harder.
 We believe prestige is composed of two main components: a trait that indicates success (but doesn't guarantee it), and the influence the individual already has on others, i.e number of individuals already chose him as a role-model.
-We suggest a model for \textit{prestige bias}, following the \textit{indirect bias} model \citet{evolutionBook} have suggested, and added the \textit{influence trait} to it.
+We suggest a model for \textit{prestige bias}, inspired by the model \citet{evolutionBook} have suggested, and added the \textit{influence bias} to it.
+We approximated our models using various distributions, and compared them to the original model using simulations.
+We showed that a \textit{Rich getting richer} type of model can be approximated well by the general binomial distribution and the dirichlet multinomial distribution.
+We experimented with constant and changing environment in our model, and created a variation of a binary model for easier mathematical and computational analysis.
 We believe that in this era of social media it is easy to estimate one's influence over others.

### 2022-02-12 ms/PrestigeBias.tex
update

@@
   \end{subfigure}
-  \caption{DM approximation vs iterative process. Population size 2000. 			Aggregated values of 400 simulations}	
+  \caption{DM approximation vs iterative process. Population size 2000. 			Aggregated values of 400 simulations. Demonstrates the similarities between the $\chi ^2$ metric of both models.}	
   \label{fig:chiSquaredHist}
@@
     \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
-  \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$}	
+  \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$.
+  Used to support the number of simulations needed for the DM approximation.}	
   \label{fig:num_sims}
@@
     \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
-  \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis}	
+  \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis.
+  Comparison of the DM approximation and the full model when mutation is included}	
   \label{fig:hetro_mutation}
@@
     \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
-  \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$}	
+  \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.
+  Comparison of the DM approximation and the full model when the indicator weight is homogeneous}	
   \label{fig:hetro_alpha}
@@
   \end{center}
-  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=0.044$}
+  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=0.044$.
+  Comparison of the DM approximation and the WF model for different values of the effective population size}
   \label{fig:var_alpha}
@@
   \end{center}
-  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$}
+  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.
+  Comparison of the DM approximation and the WF model for different values of the selection coefficient}
   \label{fig:var_beta}
@@
   \end{center}
-  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$}
+  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$.
+  Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients}
   \label{fig:ch_env_alpha_beta}
@@
   \end{center}
-  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$}
+  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.
+  Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle}
   \label{fig:ch_env_k_l}

### 2022-02-16 ms/PrestigeBias.tex
update

--- 2022-02-06 ms/PrestigeBias.tex
@@
 \usepackage{float}
+\usepackage{cleveref}
 \usepackage{subcaption}
@@
 This prestige $G_{i,j}$ is determined as follows.
-First, role-model~$j$ is characterized by its indicator value $A_j$ as before, and the estimated indicator value by copier $i$, $A_{i,j}$ remains as Eq. \ref{eq:relativeIndicator}.
+First, role-model~$j$ is characterized by its indicator value $A_j$ as before, and the estimated indicator value by copier $i$, $A_{i,j}$ remains as \cref{eq:relativeIndicator}.
 Finally, the prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased indicator value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$,
@@
 Simply put, assuming there are two role-models with the $A$ trait, the probability a copier will copy from either role-model will be the same, and the probability the $A$ trait will be inherited is the sum of both role-models.
-In the general case, the probability of the $i$-th individual to inherit trait $A$, based on eq.\ref{copier_choose} is:
+In the general case, the probability of the $i$-th individual to inherit trait $A$, based on \cref{copier_choose} is:
 \begin{equation}\label{eq:binary-model}
@@
 Currently $\big\{\vec{K}_i\big\}_{i=1}^N$ is a stochastic process where each state depends on the previous state, i.e a Markov chain.
-We wanted to find an equivalent stochastic process that has the same joint distribution on $\big\{\vec{K}_i\big\}_{i=1}^N$, but it is possible to evaluate the joint distribution directly without evaluating all the marginal conditional distributions (eq.
-\ref{eq:recurrence},\ref{eq:recPrestige}).
+We wanted to find an equivalent stochastic process that has the same joint distribution on $\big\{\vec{K}_i\big\}_{i=1}^N$, but it is possible to evaluate the joint distribution directly without evaluating all the marginal conditional distributions: \cref{eq:recurrence}, \cref{eq:recPrestige}.
 
@@
  That is, the expected number of copiers of a role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models.
-\item The role-model choice process (equation~\ref{eq:process}) is equivalent to a P\'{o}lya urn model if $e_l=e_m$ for all $l,m$. 
+\item The role-model choice process \cref{eq:process} is equivalent to a P\'{o}lya urn model if $e_l=e_m$ for all $l,m$. 
 Therefore, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$ follows a Dirichlet-Multinomial distribution,
@@
 \paragraph{Proposition:} The number of copiers $K_{i,j}$ follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A'_j))$, when $e_l=e_m$ for all $l,m \in N$ and $A'_j=A_j + e$ 
-\paragraph{Proof: } We'll denote $Q_j(k,i)=P(K_{i,j} = k | K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$, using conditional probability and equation \ref{eq:recurrence}:
+\paragraph{Proof: } We'll denote $Q_j(k,i)=P(K_{i,j} = k | K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$, using conditional probability and \cref{eq:recurrence}:
 \begin{equation}\label{recursive}
@@
 
-Equation \ref{recursive} is equivalent to equation 2.1 that \citet{GBD} define.
+We see that \cref{recursive} is equivalent to eq. (2.1) that \citet{GBD} define.
 $Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$.
-By describing the process of equation \ref{eq:process} as \citep{GBD} did, we've completed the proof.
+By describing the process of \cref{eq:process} as \citep{GBD} did, we've completed the proof.
 
@@
 \paragraph{Corollary 2: } $\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) / \overline{\alpha \cdot \beta(A')}$.
-\paragraph{Proof: } The initial prestige of role-model $j$ based on equation \ref{prestige_eq} is:
+\paragraph{Proof: } The initial prestige of role-model $j$ based on \cref{prestige_eq} is:
 \begin{equation}\label{initial_prob}
@@
 \end{equation}
-The denominator of equation \ref{initial_prob} can also be formulated as:
+The denominator of \cref{initial_prob} can also be formulated as:
 \begin{equation}\label{denominator}
@@
 where $\overline{\alpha\beta(A')}$ is the mean value of $\alpha_m\cdot\beta(A'_m)$ for all $m$.
-Using equation \ref{denominator} we get:
+Using \cref{denominator} we get:
 \begin{equation}
@@
 We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
-Using equation \ref{prestige_eq} we get:
+Using \cref{prestige_eq} we get:
 \begin{equation}\label{copier_choose}
@@
 \end{equation}
-Equations \ref{polya} and \ref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
+We see that \cref{polya} and \cref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
 
@@
 To test if our process is still DM distributed when there are copying errors in the population, we ran 400 simulations for three different error scales ($\eta$).
-To check the resemblance of the DM approximation to the original iterative process, we measure the $\chi^2$ statistic of both processes and the results can be seen in Fig.
-\ref{fig:chiSquaredHist}.
+To check the resemblance of the DM approximation to the original iterative process, we measure the $\chi^2$ statistic of both processes and the results can be seen in \cref{fig:chiSquaredHist}.
 Even with a relatively high error scales (1\% and 10\% of J) we can see the distributions of the $\chi^2$ metrics are very similar.
@@
   \begin{subfigure}[a]{0.3\textwidth}
+  \subcaption{Error scale is 0.01}
     \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
-    \subcaption{Error scale is 0.01}
     \end{subfigure}
     \begin{subfigure}[a]{0.3\textwidth}
+    \subcaption{Error scale is 0.1}
     \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
-    \subcaption{Error scale is 0.1}
     \end{subfigure}
     \begin{subfigure}[a]{0.3\textwidth}
+     \subcaption{Error scale is 1(=J)}
     \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
-  \subcaption{Error scale is 1(=J)}  
   \end{subfigure}
-  \caption{DM approximation vs iterative process. Population size 2000. 			Aggregated values of 400 simulations}	
+  \caption{Demonstrates the similarities between the $\chi ^2$ metric of 	           the DM approximation and the full model, showing the approximation is good until a very high error rate.
+Population size $N=2000$.
+400 simulations per figure}
   \label{fig:chiSquaredHist}
@@
 \subsection{Numeric comparisons}
-We're interesting in studying the difference between the real binary model as we defined in eq.
-\ref{eq:binary-model}, and the Dirichlet-Multinomial approximation.
+We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation.
 Specifically, we're interesting in the fixation probability of the favored trait ($\hat{A}$) and its time to fixation.
@@
     \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
-  \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$}	
+  \caption{The number of simulations needed to get a good approximation.
+At $1,000$ the approximation is good enough.
+Error bars represent 95\% confidence interval.
+Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$.}
   \label{fig:num_sims}
@@
 The first step was to find the number of simulations needed to sufficiently approximate the real model with the DM approximation.
-From fig.
-\ref{fig:num_sims} we see that $1000$ simulations or higher is enough.
+From \cref{fig:num_sims} we see that $1000$ simulations or higher is enough.
 
@@
 In the binary model mutation will be manifested as an error when evaluating the bias itself.
-This is easily done by using a heterogeneous $J$ parameter, which controls the strength of the success bias (see eq.
-\ref{eq:success_bias}).
+This is easily done by using a heterogeneous $J$ parameter, which controls the strength of the success bias in \cref{eq:success_bias}.
 
@@
     \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
-  \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis}	
+  \caption{Comparison of the DM approximation and the full model when mutation is included.
+Even high mutation rate doesn't worsen the approximation, and the data points are close to the mathematical estimation (Kimura's).
+Error bars are 95\% confidence intervals, and are condensed (+- 0.01 probability and +-40 generations)
+  $5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis.
+  }	
   \label{fig:hetro_mutation}
@@
 
-In fig.
-\ref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models.
+In \cref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models.
 When mutation is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
@@
     \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
-  \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$}	
+  \caption{Comparison of the DM approximation and the full model when success weight is heterogeneous.
+High success weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it).
+Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
+  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
   \label{fig:hetro_alpha}
@@
 
-In fig.
-\ref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead.
+In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead.
 Similar to the mutation comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale.
@@
 Following \citet{durret}, we used our DM approximation of the model to find the effective population size.
-From eq.
-\ref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.
+From \cref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.
 
@@
 \end{equation}
-where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from eq. \ref{eq:binary-model}.
+where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
 We want to use frequencies instead of quantities to follow Durret's process so:
@@
 To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
-In fig \ref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
-In fig \ref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
-In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations (eq. \ref{eq:kimura_p} and \ref{eq:kimura_t})
+In \cref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
+In \cref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
+In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations: \cref{eq:kimura_p} and \cref{eq:kimura_t}.
 
@@
   \begin{subfigure}[a]{0.49\linewidth}
+    \caption{}
     \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
@@
    \begin{subfigure}[a]{0.49\linewidth}
+     \caption{}
     \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
@@
   \end{center}
-  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=0.044$}
+  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size.
+The approximation seems very good, and is also condensed around the mathematical equation expectancy.
+Error bars are 95\% confidence intervals.
+  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
+  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
   \label{fig:var_alpha}
@@
   \begin{subfigure}[a]{0.49\linewidth}
+  \caption{}
     \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
@@
    \begin{subfigure}[a]{0.49\linewidth}
+    \caption{}
     \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
@@
   \end{center}
-  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$}
+  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model.
+The approximation seems good, and is also condensed around the mathematical equation expectancy.
+Error bars are 95\% confidence intervals.
+  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
+  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
   \label{fig:var_beta}
@@
 \paragraph{Proof by induction:}
-From eq. \ref{eq:expec_freq} we know that
+From \cref{eq:expec_freq} we know that
 \begin{equation}\label{eq:ch_1}
@@
 \end{equation}
-From eq. \ref{eq:ch_1} we know that
+From \cref{eq:ch_1} we know that
 \begin{equation}
@@
 \end{equation}
-we'll use both expressions in eq. \ref{eq:ch_2} and get
+we'll use both expressions in \cref{eq:ch_2} and get
 \begin{equation}\label{eq:ch_3}
@@
 \end{equation}
-so again using the induction assumption, together with eq. \ref{eq:ch_3} we get
+so again using the induction assumption, together with \cref{eq:ch_3} we get
 \begin{equation}
@@
 
-using eq.\ref{eq:ch_1} we see that:
+using \cref{eq:ch_1} we see that:
 \begin{equation}\label{eq:ch_var1}
@@
 
-Using eq.\ref{eq:const_var} we get:
+Using \cref{eq:const_var} we get:
 \begin{equation}
@@
 
-and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of eq.\ref{eq:ch_var} we get:
+and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of \cref{eq:ch_var} we get:
 \begin{equation}\label{eq:ch_var2}
@@
 
-and moving on to simplify the second part of eq.\ref{eq:ch_var} using eq.\ref{eq:ch_var1}:
+and moving on to simplify the second part of \cref{eq:ch_var} using \cref{eq:ch_var1}:
 \begin{equation}
@@
 
-Using the induction assumption and eq.\ref{eq:ch_var2}:
+Using the induction assumption and \cref{eq:ch_var2}:
 \begin{equation}
@@
 We again tried different variations of the parameters, changing only one of them at a time.
-In fig.\ref{fig:ch_env_alpha_beta} we can see that $\alpha$ on it's own doesn't cause any deviation for the the estimation. $\beta$ however affects the results greatly.
+In \cref{fig:ch_env_alpha_beta} we can see that $\alpha$ on it's own doesn't cause any deviation for the the estimation. $\beta$ however affects the results greatly.
 
@@
   \begin{subfigure}[a]{0.49\linewidth}
-  \caption{$1-\beta=s=0.005$}
+  \caption{success bias/selection coefficient is: $1-\beta=s=0.005$}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
@@
    \begin{subfigure}[a]{0.49\linewidth}
-   \caption{$\alpha=0.1$}
+   \caption{success weight is: $\alpha=0.1$}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
@@
   \end{center}
-  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$}
+  \caption{Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients.
+Changing the effective population size doesn't affect the approximation, and it is condensed the mathematical expected values across all values.
+High values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values.
+Very high values ($s>0.35$) will even deviate from the constant environment expected values.
+This is expected because Kimura's approximation are only viable for low selection coefficient values.
+  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$.}
   \label{fig:ch_env_alpha_beta}
@@
   \begin{subfigure}[a]{0.49\linewidth}
+  \caption{}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
@@
    \begin{subfigure}[a]{0.49\linewidth}
+   \caption{}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
@@
   \end{center}
-  \caption{$10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$}
+  \caption{Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle.
+When $k<l$ the approximation is good.
+When $k>l$, the approximation and the simulations are both very close to the constant environment approximation.
+  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
   \label{fig:ch_env_k_l}
@@
 
-In fig.\ref{fig:ch_env_k_l} we see that the larger $k$ relative to $l$, the closer the modified equation is to the original estimation of the constant environment. 
+In \cref{fig:ch_env_k_l} we see that the larger $k$ relative to $l$, the closer the modified equation is to the original estimation of the constant environment. 
 When using higher values of $n$, the simulation results doesn't fit the equation result as with lower values.

### 2022-03-03 ms/PrestigeBias.tex
update

@@
 \begin{equation}
-F_i(\vec{X}) = \sum_{j=1}^N \Big(G_{ij}\cdot X_{ij}\Big) \\\\
+F_i(\vec{X}) = \sum_{j=1}^N \Big(G_{ij}\cdot X_{ij}\Big) \\
 \end{equation}
@@
 \begin{split}
-P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\\\
+P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\
  & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
@@
 \begin{split}
-G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\\\
-&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\\\
+G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\
+&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\
 & =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
@@
 \paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population.
-To test if our process is still DM distributed when there are copying errors in the population, we ran 400 simulations for three different error scales ($\eta$).
-To check the resemblance of the DM approximation to the original iterative process, we measure the $\chi^2$ statistic of both processes and the results can be seen in \cref{fig:chiSquaredHist}.
-Even with a relatively high error scales (1\% and 10\% of J) we can see the distributions of the $\chi^2$ metrics are very similar.
-With a higher $\eta$ (e.g $\eta=J$), which is approximately 100\% error when evaluating a trait, the distributions are noticeably different.
+To support our proof, we tested our approximation empirically using computer simulations.
+To test our hypothesis, we used a \textit{goodness of fit} method known as \textit{Pearson's chi-squared test}.
+In this test, one can reject or accept the null hypothesis, which in our case is the hypothesis that the simulations results were drawn from a DM distribution.
 
-In addition to the chi-squared test, we want to observe how well does the Dirichlet-Multinomial distribution approximates our entire model, and not just one generation in it.
-To do that we simplify our model to a binary model, so the simulations of the model to run in a feasible amount of time.
+To use this test, we ran many simulations of our original model, and used the mean distribution of copiers.
+This mean distribution is our observed distribution, and we tested it with the DM expected distribution, using said chi-squared test.
+We tested multiple variations of the trait weight parameter ($\alpha$).
 
-\begin{figure}[t]
-  \begin{center}
-  \begin{subfigure}[a]{0.3\textwidth}
-  \subcaption{Error scale is 0.01}
-    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
-    \end{subfigure}
-    \begin{subfigure}[a]{0.3\textwidth}
-    \subcaption{Error scale is 0.1}
-    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
-    \end{subfigure}
-    \begin{subfigure}[a]{0.3\textwidth}
-     \subcaption{Error scale is 1(=J)}
-    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
-  \end{subfigure}
-  \caption{Demonstrates the similarities between the $\chi ^2$ metric of 	           the DM approximation and the full model, showing the approximation is good until a very high error rate.
-Population size $N=2000$.
-400 simulations per figure}
-  \label{fig:chiSquaredHist}
-  \end{center}
-\end{figure}
+In all our tests, the p-value was \textbf{1}.
+This means that the probability to reject the null hypothesis is essentially nonexistent (the usual threshold for a p-value needed to reject $H_0$ is 0.05 or lower).
+In addition, we found out that for high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value 1.
+(less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
+For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100, which is still a relatively small amount.
+To verify our codes results, we also ran the test for different distributions, for example the uniform distribution (all role-models have exactly one copier).
+
+All these tests resulted in a p-value 0, which means we can likely reject $H_0$ for these distributions, as expected.
+
+Once we validated our proof for a single iteration of the model, we went on to more complex validations for the entire model.
 
@@
 \begin{split}
-E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\\\
+E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\
 	 &= \frac{x}{x + (1-x)\beta}
@@
 Again following Durret we want to calculate:
-\begin{equation}
+\begin{equation}\label{eq:var_diff_durret}
 V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N})
@@
 In our model, $\alpha'$ is the odds ratio of a parameter we called "indicator weight", denoted in our model as $\alpha$, so:
-\begin{equation}
+\begin{equation}\label{eq:success_ratio}
 \alpha' = \frac{\alpha}{1-\alpha}
@@
 
-And combining with the previous equations we get:
+Combining \cref{eq:var_diff_durret} and \cref{eq:success_ratio} we get:
 \begin{equation}\label{eq:const_var}
 \begin{split}
-V(x'-x) & \approx x(1-x)(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N})\\\\
- &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\\\
- &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\\\
-  &= x(1-x)(\frac{1}{\alpha N + (1-\alpha)})\\\\
+V(x'-x) & \approx x(1-x)(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N})\\
+ &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\
+ &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\
+  &= x(1-x)(\frac{1}{\alpha N + (1-\alpha)})\\
   &= x(1-x)\frac{1}{N_e}
@@
 \begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\\\
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\
 &= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
@@
 \begin{split}
-E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\\\
-&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\\\
+E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\
+&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\
 &= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
@@
 \begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] \\\\
-&\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\\\
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] \\
+&\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\
 &\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x)
@@
 \begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\\\
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
 &\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x)
@@
 \begin{split}
-E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] &= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\\\
+E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] &= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\
 E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] = \frac{X_t}{N} &+ \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right)
@@
 \clearpage
-\section{Appendix A - Time table}
-
-\paragraph{Today - Oct 2021:}
-Find approximation replacing Durrett's equations for the time to fixation.
-
-\paragraph{Nov - Mar 2021:}
-Combining the findings to a paper and a thesis.
+\section{Summaries}
+\subsection{Animal leadership \citep{animal_leadership}}
+There are two main approaches to decision makings of groups in nature: leadership and consensus.
+Prey leaders would lead the pact when traveling, while other animal group leaders will decide on a nesting site or foraging patches.
+They found out that leadership is observed mostly when there is a profound social network in the group, and when there are individuals that present leadership behavior.
+Leaders would usually be high ranking members in the group, such as elders, individuals with many kin relations, or posses other dominant traits.
+When no individual posses such traits, or when the social network is lacking, a consensus is more likely to occur.
+When a leader is present, they will have greater selection costs, such as higher risk for predation, being poisoned by unknown experimental patch, but also greater benefits.
+For example, given the route to the foraging site was successful, the leader and his closest followers would gain most of the food, unlike in a consensus, where the food would be shared more equally.
+It appears leaders appear in simple organisms as well, like fish.
+In these organisms however, the leader would usually be the hungriest or the weakest, while the rest would prefer to follow, minimizing their costs.
+In baboons however, \citet{animal_leadership} describe many benefits for the closest associates of the dominant male, such as protection from predators.
+This is an instance of sexual-selection, where the leader, whose survival chances are lower, gains more sexual partners due to the benefits.
+("The greater the risk, the greater the reward")
+In humans, leadership also has its perks and costs.
+Leaders can make decisions that would benefit them and their closest followers the most, while still maintaining group cohesion.
+However, wrong decision making that would harm the group could result in harm (media, social status, even violent behavior of subjects on certain cases).
+In our binary model, we consider a single trait.
+Consider this trait a trait that would be seen as desirable for a leader.
+Assuming that, our binary model could be used to predict and explain leader-selection processes, from prom-king to president.
 

### 2022-03-07 ms/PrestigeBias.tex
summaries

@@
 However, wrong decision making that would harm the group could result in harm (media, social status, even violent behavior of subjects on certain cases).
-In our binary model, we consider a single trait.
-Consider this trait a trait that would be seen as desirable for a leader.
-Assuming that, our binary model could be used to predict and explain leader-selection processes, from prom-king to president.
+
+\subsection{Prestige as a type of leadership \citep{dual_leadership}}
+In their paper, \citet{dual_leadership} suggest a different view of leadership.
+They say that most discussions assume there is one type of leadership, and so they differ in their definition.
+\citet{dual_leadership} suggest a way to solve said contradiction by defining two types of leaderships: prestige-based and dominance-based.
+They present classical views of leaderships by Confucius and Machiavelli. Confucius views leaders as role models who exercise influence through possessing superior knowledge, skills,
+and (outstanding) personal qualities.
+This description is very similar to our indicator trait.
+By contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment.
+They say that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view into the complex and dynamic processes of leadership.
+
+Our current model doesn't reflect the model described in this article, but several adjustments could be made in order to match it.
+If we assume there's a correlation between trait value to a type of leadership (so in our binary model, one trait would be of prestige, and the other of dominance) we can implement their suggested model.
+For that we would need to add cost-benefit parameters, so the ones choosing prestige will be rewarded, but pay more, while the ones choosing dominance would pay less, but gain less benefits.
+It could be interesting to see the dynamics and relations between our model parameters and these cost-benefit parameters.
+
+\subsection{Evidence from Fijian villages for adaptive learning biases \citep{fijian_social_bias}}
+\citet{fijian_social_bias} researched Fijian villages, looking for evidence of social learning biases and their origins. They mention that:
+\begin{quote}
+evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
+\end{quote}
+Their goal is to bridge from the laboratory to the field by examining if and how these biases emerge in a small-scale society.
+During their research they found that:
+\begin{quote}
+Fijian villagers (ages 10 and up) are biased to learn from others perceived as more successful/knowledgeable, both within and across domains (prestige effects).
+\end{quote}
+Their research shows promising evidence for our prestige model, suggesting that copying from others who are \textit{perceived} as successful, rather than actually are successful.
+In their paper, they show that the social networks representing copier-role-model relationships are centralized, suggesting:
+\begin{quote}
+This degree of centralization is consistent with the prediction that people substantially share notions about who is a good cultural model (network centrality), but that individuals’ model selections are influenced by multiple factors.
+\end{quote}
+We see here support for both our indicator trait and our influence bias in their data.
 

### 2022-03-08 ms/PrestigeBias.tex
added summary

@@
 
+\subsection{Using social influence to reverse harmful traditions \citep{harmful_traditions}}
+Social influence could be a powerful tool to end traditions, harmful or advantageous. Harmful traditions can be child marriage, open defecation, and domestic violence, to name a few. 
+\citet{harmful_traditions} suggest a mechanism called \textit{spillover}.
+By their definition, a spillover is when an intervention affect a large enough group in a target population, so that others not included in the intervention starts changing their behavior as well.
+In their research, they found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions.
+This is the same concept as our role-models, where a more prestigious individual will be copied more, therefore spreading his trait wider in the population.
+Their research support therefore in our assumption that there are social biases, conformist influence specifically.
+They also suggest a way to use this phenomena to change existing traditions in a population.
+It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.
 \clearpage

### 2022-03-09 ms/PrestigeBias.tex
update

@@
 It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.
+
+\subsection{The evolution of prestige \citep{prestige_evolution}}
+One cannot mention prestige and cultural transmission without the work of \citet{prestige_evolution}.
+They as well distinguish between prestige and dominance.
+The latter is is defined by acquiring social status by using aggression, intimidation and violence.
+They also mention dominance is more common than prestige in non humans.
+Their definition of prestige is somewhat synonymous with ours.
+Specifically prestige is composed both of estimation in the eyes of people (our indicator/success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
+In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
+Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
+It could be interesting in the future to enhance our model with this idea, i.e observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
+\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers.
+This is consistent with our findings, and in a way our model is a mathematical equivalent to their suggested model.
+
 \clearpage

### 2022-03-15 ms/PrestigeBias.tex
update

@@
 
+\subsection{Biased learning may be disfavored when payoffs are uncertain \citep{best_of_k}}
+\citet{best_of_k} remind that social learning not only takes the form of random copying of other individuals, but also involves learners’ choice of what to learn or from whom to learn.
+They suggest a best-of-K model where an individual samples k role-models and choose the one he deems most "successful".
+They mentioned that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
+In such a case, learners may be selectively disfavored and in the long run replaced by unbiased learners, who simply copy someone chosen at random.
+They develop new mathematical models that are more simplified and mathematically tractable.
+They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff.
+Our model, which includes influence bias, is consistent with that claim.
+When a maladaptive trait is "piggybacking" a role-model with high influence, said trait could spread in the population, as mentioned.
+In addition, they show that best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning.
+Our model is based on copying based learning only, but it could be interesting to combine it with individual learning and see how it affects the dynamics of the population.
+
 \clearpage

### 2022-03-17 ms/PrestigeBias.tex
update

@@
 
+\subsection{Prestige in medicine \citep{medical_prestige}}
+So far we presented the existence of prestige in nature and in humans.
+We mostly discussed it in regard of social ranking in animals, and what are the costs and benefits.
+In humans, we mostly addressed spread of adaptive or maladaptive traits due to the prestige bias.
+\citet{medical_prestige} present a specific and important effect of prestige - its significance for medical specialties and diseases.
+They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices.
+They discovered that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
+They have concluded that such differences in prestige bear consequences for actual priority setting in healthcare systems.
+They discovered that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
+In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered \textit{easier} are less prestigious.
+\citet{medical_prestige} found that the advance in technology and research was in accordance with the prestige rankings.
 \clearpage

### 2022-03-22 ms/PrestigeBias.tex
update

@@
 \citet{medical_prestige} found that the advance in technology and research was in accordance with the prestige rankings.
+
+\subsection{Collective brains \citep{collective_brains}}
+We showed cultural transmission is a process that manifests in many species, with emphasis on humans.
+We also displayed similarities between this process and genetic transmission, while presenting differences between them, specifically selective biases such as influence and prestige.
+\citet{collective_brains} offer a take on prestige as a factor of human physical evolution.
+They present a concept called \textit{cultural brains} - brains that evolved primarily for the acquisition of adaptive knowledge.
+They build on the hypothesis of \citet{social_brains} that shows that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
+\citet{collective_brains} built a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge.
+They later present their \textit{cumulative cultural brain} hypothesis, an approach which proposes that human brains have evolved with an ability and proclivity for selective, high fidelity social learning.
+As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge.
+These strategies and biases include direct and indirect cues of the popularity of cultural traits (e.g.
+success and prestige biases).
+In short, they suggest that some of the reasons for the extreme increase in brain size in humans, are the ability to "cheaply" acquire adaptive knowledge, i.e transmission biases, such as prestige.
+
+\subsection{Prestige-biased cultural learning \citep{prestige_cultural_learning}}
+Culture–gene coevolutionary (CGC) researchers theorize that humans should possess several learning biases which robustly enhance the fitness of cultural learners. 
+\citet{prestige_cultural_learning} report the first direct tests in children of CGC's prediction of \textit{prestige bias}, a tendency to learn from individuals to whom others have preferentially attended, learned or deferred.
+Their definition of prestige is similar to our \textit{influence bias}, and brings concrete proof of its existence and effects.
+Their study showed that the odds of 3-4 years-old children learning from an adult model to whom bystanders had previously preferentially attended for 10 seconds were over twice those of their learning from a model whom bystanders ignored.
+In addition to this first study, they also discovered prestige effects are domain-sensitive.
+They saw that prestigious models were listened to by most when demonstrating artifact-use, but not as much as when presenting food preferences.
+It lead \citet{prestige_cultural_learning} to believe that when the trait is costly to learn individually, prestige will have a higher effect.
+It would be interesting to include costs in our model to try and observe these effects and their dynamics in the simulations of a larger population than this study.
+
 \clearpage

### 2022-03-22 ms/PrestigeBias.tex
update

@@
 \section{Abstract}
-Copying our role-models have always been an efficient method of acquiring knowledge.
-Copying successful role-model is one of the methods of cultural transmission of traits.
-In this paper, we study the various biases and their effects of the population and it's evolution.
-The most common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears successful to us.
+Copying our role-models have always been an efficient method of acquiring knowledge \citep{strategiesPaper}.
+\textbf{In this paper, we study the effects of prestige as a cultural transmission bias} on the population.
+A common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears successful to us \citep{evolution_of_cultural_evolution}.
 This estimation is based on the performance of the role-model alone, without any other factors.
-Here, we study another factor we believe aids to better model the cultural inheritance of traits in a large population.
-\textit{Influence bias} is a bias evaluated by the number of copiers a role-model already has.
-In our model we combine these components to what we call the \textbf{Prestige bias} and analyze its relationship to the dynamics of the population.
+We propose an additional factor we believe aids to better model the cultural inheritance of traits in a large population.
+\textit{Influence bias} is a bias evaluated by the number of copiers a role-model already has \citep{prestige_evolution}.We combine these components to what we call the \textit{prestige bias} and analyze its effects on the dynamics of the population.
+\textbf{We present a model of prestige bias} as we defined it, and \textbf{observe the dynamics of the population using computer simulations}.
+We also \textbf{analyze our model using mathematical approximations}.
 We successfully found mathematical approximations to our model, easing the mathematical analysis and the computation power required for simulations.
@@
 We found that influence acts as an accelerator for a state of the population, matching the \textit{rich getting richer} it was based on.
-We believe such model better describes how humans acquire knowledge from one another, mainly in the last years where social networks are very popular.
-Social networks allow easy access to estimate number of copiers a role-model has, with little to no effort.
+\textbf{We believe such model better describes how humans acquire knowledge from one another, mainly in the last years where social networks are very popular}.
+Furthermore, we believe that our model could predict various phenomena in human culture once supplemented with more natural concepts like natural selection and costs.
 
@@
 They claim the bias could lead to a \textit{runaway process}, caused by a cultural equivalent of \textit{sexual selection} \citep{sexualSelectionBook}.
-On the other hand, \citet{henrichBroesch} claim that prestige biases, over generations, can lead to cultural adaptations.
+On the other hand, \citet{fijian_social_bias} claim that prestige biases, over generations, can lead to cultural adaptations.
 According to them, prestige can make a maladaptive trait spread in the population, but can also accelerate the spread of adaptive traits as well.

### 2022-03-26 ms/PrestigeBias.tex
update

@@
 \section{Discussion}
+\subsection{summary}
 Cultural transmission is the phenomenon of which cultural elements, in the form of attitudes, values, beliefs, and behavioral patterns, are transmitted between individuals, typically via copying.
@@
 Here we assume that success isn't correctly identified, therefore individuals may use other indicators to try and estimate the success of potential role-models.
-We believe, as \citet{complexityPaper} suggest, that \textit{prestige biases} are more common in nature than success biases, since estimating success is harder.
+We believe, as \citet{complexityPaper} suggest, that \textit{prestige biases} are more common in nature than success biases, since estimating success accurately is harder.
+\textbf{We investigated the effects of prestige on a population:} we studied the behavior of an invading trait, analyzed its dynamics mathematically, and extended the basic constant environment to a changing one.
 We believe prestige is composed of two main components: a trait that indicates success (but doesn't guarantee it), and the influence the individual already has on others, i.e number of individuals already chose him as a role-model.
 We suggest a model for \textit{prestige bias}, inspired by the model \citet{evolutionBook} have suggested, and added the \textit{influence bias} to it.
-We approximated our models using various distributions, and compared them to the original model using simulations.
+\textbf{We approximated our models using various distributions, and compared them to the original model using simulations.}
 We showed that a \textit{Rich getting richer} type of model can be approximated well by the general binomial distribution and the dirichlet multinomial distribution.
@@
 It is therefore crucial to model the cultural biases more realistically than success bias based model, and we believe including influence is crucial for that purpose.\\
-With a more realistic model of a common cultural transmission bias, we may be able to better understand decision-making processes in humans, including life-changing choices such as occupation or a life partner.
+\textbf{With a more realistic model of a common cultural transmission bias, we may be able to better understand decision-making processes in humans, including life-changing choices such as occupation or a life partner.}
 Our model can be expanded in multiple ways: observing the effects of different bias functions, including errors in estimating the influence, combining factors of cost when copying from an influential role model (not all could afford to copy from the most popular role-model), and analyzing the differences when including several optimal values for the indicator trait (multiple preference traits in the population).
 
-\clearpage
-\section{Summaries}
-\subsection{Animal leadership \citep{animal_leadership}}
-There are two main approaches to decision makings of groups in nature: leadership and consensus.
+\subsection{Prestige in the literature}
+So far we discussed prestige as a main bias in humans, and to some extent in non-human species.
+Here we further base our claims and present additional appearances of prestige in nature and in the literature.
+\\
+
+\citet{animal_leadership} describe a manifestation of prestige in the form of leadership in animals.
+According to them, there are two main approaches to decision makings of groups in nature: leadership and consensus.
 Prey leaders would lead the pact when traveling, while other animal group leaders will decide on a nesting site or foraging patches.
@@
 ("The greater the risk, the greater the reward")
+What they describe could be the origins of what we know today as prestige.
+In their paper, they show that in nature, when survival is the main concern at all times, the leaders wouldn't be chosen due to their superior abilities, but because they have the least to lose.
+When in said position of leadership, there are greater risks, but greater rewards to come with it.
 In humans, leadership also has its perks and costs.
@@
 However, wrong decision making that would harm the group could result in harm (media, social status, even violent behavior of subjects on certain cases).
+In our society it is less common to worry about mere survival, and so the prestigious positions, even though are not without risks and costs, are not as dangerous as for animals in nature.
+This may be the reason humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them.
+This is in complete contrast to animals, where the weakest/hungriest is driven to lead, compared to humans where leadership positions are mostly competitive.\\
 
-\subsection{Prestige as a type of leadership \citep{dual_leadership}}
-In their paper, \citet{dual_leadership} suggest a different view of leadership.
-They say that most discussions assume there is one type of leadership, and so they differ in their definition.
+\citet{dual_leadership} suggest a different view of leadership.
+They note that most discussions assume there is one type of leadership, as seen above, and so they differ in their definitions.
 \citet{dual_leadership} suggest a way to solve said contradiction by defining two types of leaderships: prestige-based and dominance-based.
@@
 For that we would need to add cost-benefit parameters, so the ones choosing prestige will be rewarded, but pay more, while the ones choosing dominance would pay less, but gain less benefits.
-It could be interesting to see the dynamics and relations between our model parameters and these cost-benefit parameters.
+It could be interesting to see the dynamics and relations between our model parameters and these cost-benefit parameters.\\
 
-\subsection{Evidence from Fijian villages for adaptive learning biases \citep{fijian_social_bias}}
+\citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige based and dominance based leadership types.
+By their definition, the latter is defined by acquiring social status by using aggression, intimidation and violence.
+It is also more common than prestige in non humans.
+Their definition of prestige is somewhat synonymous with ours.
+According to their manuscript, prestige is composed both of estimation in the eyes of people (our indicator/success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
+In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
+Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
+It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
+\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions and results, is consistent with ours.\\
+
+So far we presented the theory behind prestige, and it's appearance in nature. The following will show the appearances of prestige biases in humans, and in recent times.
+
+\citet{prestige_cultural_learning}, for example, tested the existence of prestige in young children.
+\citet{prestige_cultural_learning} report the first direct tests in children that suggest the existence of \textit{prestige bias}, a tendency to learn from individuals to whom others have preferentially attended, learned or deferred.
+Their definition of prestige is similar to our \textit{influence bias}, and brings concrete proof of its existence and effects.
+Their study showed that the odds of 3-4 years-old children learning from an adult model to whom bystanders had previously preferentially attended for 10 seconds were over twice those of their learning from a model whom bystanders ignored.
+In addition to this first study, they also discovered prestige effects are domain-sensitive.
+They saw that prestigious models were listened to by most when demonstrating artifact-use, but not as much as when presenting food preferences.
+It lead \citet{prestige_cultural_learning} to believe that when the trait is costly to learn individually, prestige will have a higher effect.
+It would be interesting to include costs in our model to try and observe these effects and their dynamics in the simulations of a larger population than this study.\\
+
 \citet{fijian_social_bias} researched Fijian villages, looking for evidence of social learning biases and their origins. They mention that:
@@
 \end{quote}
-We see here support for both our indicator trait and our influence bias in their data.
+We see here support for both our indicator trait and our influence bias in their data.\\
 
-\subsection{Using social influence to reverse harmful traditions \citep{harmful_traditions}}
-Social influence could be a powerful tool to end traditions, harmful or advantageous. Harmful traditions can be child marriage, open defecation, and domestic violence, to name a few. 
+Aside from children's learning biases and small villages in a relatively primitive population, we can see prestige in more advanced domains as well, like western medicine.\citet{medical_prestige} present a specific and important effect of prestige - its significance for medical specialties and diseases.
+They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices.
+They discovered that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
+They have concluded that such differences in prestige bear consequences for actual priority setting in healthcare systems.
+They discovered that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
+In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered \textit{easier} are less prestigious.
+Simply put, they found that the advance in technology and research was in accordance with the prestige rankings.
+This means that there may be very important practices that are neglected due to the prestige bias.\\
+
+As we seen so far, prestige can explain many behaviors and evolution of cultural traits.
+It is a tool to cheaply estimate and acquire knowledge, which helps an individual to survive and breed.
+However, it is not always the case, and there could be negative repercussions to this bias, such as invasion of maladaptive traits.
+
+\citet{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners’ choice of what to learn and from whom to learn.
+They suggest a best-of-K model where an individual samples k role-models and choose the one he deems most "successful".
+They mentioned that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
+In such a case, learners may be selectively disfavored and in the long run replaced by unbiased learners, who simply copy someone chosen at random.
+They develop new mathematical models that are simpler and mathematically tractable.
+They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff.
+Our model, which includes influence bias, is consistent with that claim.
+When a maladaptive trait is "piggybacking" a role-model with high influence, said trait could spread in the population, as mentioned.
+In addition, they show that best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning.
+Our model is based on copying based learning only, but it could be interesting to combine it with individual learning and see how it affects the dynamics of the population.
+
+We discussed prestige in depth, and provided several proofs for its existence in nature, humans, and even medicine.
+We saw it could aid invasion of maladaptive traits, or neglect of important medicinal specialities.
+But, it can also accelerate reversal of harmful traditions.
+Harmful traditions can be child marriage, open defecation, and domestic violence, to name a few. 
 \citet{harmful_traditions} suggest a mechanism called \textit{spillover}.
@@
 They also suggest a way to use this phenomena to change existing traditions in a population.
-It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.
+It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.\\
 
-\subsection{The evolution of prestige \citep{prestige_evolution}}
-One cannot mention prestige and cultural transmission without the work of \citet{prestige_evolution}.
-They as well distinguish between prestige and dominance.
-The latter is is defined by acquiring social status by using aggression, intimidation and violence.
-They also mention dominance is more common than prestige in non humans.
-Their definition of prestige is somewhat synonymous with ours.
-Specifically prestige is composed both of estimation in the eyes of people (our indicator/success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
-In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
-Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
-It could be interesting in the future to enhance our model with this idea, i.e observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
-\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers.
-This is consistent with our findings, and in a way our model is a mathematical equivalent to their suggested model.
-
-\subsection{Biased learning may be disfavored when payoffs are uncertain \citep{best_of_k}}
-\citet{best_of_k} remind that social learning not only takes the form of random copying of other individuals, but also involves learners’ choice of what to learn or from whom to learn.
-They suggest a best-of-K model where an individual samples k role-models and choose the one he deems most "successful".
-They mentioned that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
-In such a case, learners may be selectively disfavored and in the long run replaced by unbiased learners, who simply copy someone chosen at random.
-They develop new mathematical models that are more simplified and mathematically tractable.
-They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff.
-Our model, which includes influence bias, is consistent with that claim.
-When a maladaptive trait is "piggybacking" a role-model with high influence, said trait could spread in the population, as mentioned.
-In addition, they show that best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning.
-Our model is based on copying based learning only, but it could be interesting to combine it with individual learning and see how it affects the dynamics of the population.
-
-\subsection{Prestige in medicine \citep{medical_prestige}}
-So far we presented the existence of prestige in nature and in humans.
-We mostly discussed it in regard of social ranking in animals, and what are the costs and benefits.
-In humans, we mostly addressed spread of adaptive or maladaptive traits due to the prestige bias.
-\citet{medical_prestige} present a specific and important effect of prestige - its significance for medical specialties and diseases.
-They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices.
-They discovered that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
-They have concluded that such differences in prestige bear consequences for actual priority setting in healthcare systems.
-They discovered that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
-In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered \textit{easier} are less prestigious.
-\citet{medical_prestige} found that the advance in technology and research was in accordance with the prestige rankings.
-
-\subsection{Collective brains \citep{collective_brains}}
-We showed cultural transmission is a process that manifests in many species, with emphasis on humans.
+Up until now, we showed that cultural transmission is a process that manifests in many species, with emphasis on humans.
 We also displayed similarities between this process and genetic transmission, while presenting differences between them, specifically selective biases such as influence and prestige.
-\citet{collective_brains} offer a take on prestige as a factor of human physical evolution.
+We also presented examples of good and bad usages of such biases.
+All of these are mainly presented as a parallel process to the natural selection process in regards to physical anatomy, or at least have an indirect effect on it.
+\citet{collective_brains} offer a take on prestige as a factor of human physical evolution directly.
 They present a concept called \textit{cultural brains} - brains that evolved primarily for the acquisition of adaptive knowledge.
@@
 
-\subsection{Prestige-biased cultural learning \citep{prestige_cultural_learning}}
-Culture–gene coevolutionary (CGC) researchers theorize that humans should possess several learning biases which robustly enhance the fitness of cultural learners. 
-\citet{prestige_cultural_learning} report the first direct tests in children of CGC's prediction of \textit{prestige bias}, a tendency to learn from individuals to whom others have preferentially attended, learned or deferred.
-Their definition of prestige is similar to our \textit{influence bias}, and brings concrete proof of its existence and effects.
-Their study showed that the odds of 3-4 years-old children learning from an adult model to whom bystanders had previously preferentially attended for 10 seconds were over twice those of their learning from a model whom bystanders ignored.
-In addition to this first study, they also discovered prestige effects are domain-sensitive.
-They saw that prestigious models were listened to by most when demonstrating artifact-use, but not as much as when presenting food preferences.
-It lead \citet{prestige_cultural_learning} to believe that when the trait is costly to learn individually, prestige will have a higher effect.
-It would be interesting to include costs in our model to try and observe these effects and their dynamics in the simulations of a larger population than this study.
-
 \clearpage

### 2022-03-27 ms/PrestigeBias.tex
revised introduction

@@
 \author{
-	Dr. Yoav Ram
+	Saar Egozi
 	\and
-	Saar Egozi
+	Yoav Ram
 }
@@
 
-{\large together with Yoav Ram}
+{\large supervised by Dr. Yoav Ram}
 
@@
 
-{\large Efi Arazi School of Computer Science, IDC Herzliya}
+{\large Efi Arazi School of Computer Science, Reichman University}
 
@@
 \section{Abstract}
-Copying our role-models have always been an efficient method of acquiring knowledge \citep{strategiesPaper}.
-\textbf{In this paper, we study the effects of prestige as a cultural transmission bias} on the population.
-A common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears successful to us \citep{evolution_of_cultural_evolution}.
-This estimation is based on the performance of the role-model alone, without any other factors.
-We propose an additional factor we believe aids to better model the cultural inheritance of traits in a large population.
-\textit{Influence bias} is a bias evaluated by the number of copiers a role-model already has \citep{prestige_evolution}.We combine these components to what we call the \textit{prestige bias} and analyze its effects on the dynamics of the population.
-\textbf{We present a model of prestige bias} as we defined it, and \textbf{observe the dynamics of the population using computer simulations}.
-We also \textbf{analyze our model using mathematical approximations}.
-We successfully found mathematical approximations to our model, easing the mathematical analysis and the computation power required for simulations.
-We show the value of these approximations using simulations, and their robustness to variations such as mutation and other relaxations required for the mathematical proofs.
-In the binary form of our model, we found alternatives to \textit{Kimura's} equations for approximating fixation probability and time to fixation of an invading advantageous trait, in both a constant and changing environment.
-We show that \textit{Influence} solely affects the effective population size.
-We found that influence acts as an accelerator for a state of the population, matching the \textit{rich getting richer} it was based on.
-\textbf{We believe such model better describes how humans acquire knowledge from one another, mainly in the last years where social networks are very popular}.
-Furthermore, we believe that our model could predict various phenomena in human culture once supplemented with more natural concepts like natural selection and costs.
+Copying role-models can be an efficient method of acquiring knowledge \citep{strategiesPaper}.
+\textbf{Here, we study the effects of prestige as a cultural transmission bias} in cultural-evolution model.
+A common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears more successful \citep{evolution_of_cultural_evolution}.
+This bias depends on the performance of the role-model alone, without other factors.
+We propose an additional bias that may be prevalent in cultural transmission: \textit{Influence bias}, which is evaluated by the number of individuals that have already copied a specific role-model \citep{prestige_evolution}.
+We combine these biases together to a \textit{prestige bias} and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations.
+We find analytic approximations to our model, facilitating further mathematical analysis and reducing the computational complexity of the simulations.
+We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
+For a dichotomous cultural trait, we find  an approximation to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resembles Kimura's classical formulas.
+These approximations show that influence effectively reduces the population size. % TODO reduce or increase?
+We also find that influence accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
+Our model may provide a better description of how human cultural transmission, 
+especially in the last years where social networks are very popular. % TODO to discuss this last sentence
+Further work is needed to test if this model could predict various phenomena in human cultural evolution when extended with the effects of selection and innovation.
 
-% what is cultural transmission, and its not only in humans
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Traits transmission is when an individual passes on a trait, genetic or behavioral, to another individual. Transmission in nature manifests in two main ways: genetic and cultural.
-Genetic transmission is when an individual, or several, transmit their genes to their offspring by duplication of their own cells.
-Cultural transmission is the way individuals transmit cultural traits (i.e behavior) from one another, typically via teaching and demonstrating.
- Cultural transmission is most common in humans \citep[pg. 3]{transmissionVectorsBook} and in primates like chimpanzees \citep{chimpsPrestige, chimpsCopy}.
- The common cultural traits in humans are behavioral patterns, like personalities and habits, transmitted via observations and verbal discussions.
-\citet{dualEvolution} suggest that cultural learning may be particular to humans, but \citet{elepahntsRepo} suggest that it appears in other mammals as well, elephants for example:
- \begin{quote}
-	   ... the possession of enhanced discriminatory abilities by the oldest individual [matriarch] in a group can influence the social knowledge of the group as a whole.
- \end{quote}
- They showed that once a matriarch is removed from the group, the group's survival instincts are inferior.
- They support their hypothesis by exacting an experiment: playing audio recordings of African elephants, showing that groups with a matriarch recognize and react better to hostile or friendly calls than the groups without one.
-Moreover, cultural transmission appears in other species, even simpler than mammals, such as \textit{Drosophila}.
-\citet{fliesPaper} show that oviposition site choice in fruit flies is culturally transmitted.
-They showed that flies without experience in choosing sites, after spending some time with "experienced" flies, chose the same type of site without directly observing this behavior. 
-\citet{fliesPaper} mention that how the information is transferred is still an open question, but suggest that the flies may use olfactory cues, like other animals such as rodents and bees.\\
 
-%the differences and similarities between cultural and genetic transmission 
-Cultural transmission is similar to genetic transmission in many ways, while different in others.
-Similar to genetic transmission, the effects of culturally transmitted traits can be physiological rather than behavioral, and transmitted from parents to offspring.
- For example, parents can teach their children to be strong or tall, within some biological limits, by instructing them to maintain a healthy diet and engage in physical activity.
-Contrary to genetic transmission, the sources of the traits can be many, and not only parents.
-They can even be unrelated, like teachers, celebrities, coaches, the media, or any stranger that comes in contact with them.
- Cultural transmission can be vertical, where parents transmit to their children, but also oblique, where other adults transmit traits to children (not their own).
-  Horizontal transmission is also possible, where peers transmit traits to one another. 
-   Lastly, vertical transmission in the opposite direction is possible too, where parents copy traits from their children (e.g playing video games) as \citet{transmissionVectorsBook} and \citet{transmissionVectors} suggest.
-In addition, even when a cultural trait is disfavored by natural selection, it still may spread across a population given transmission biases strong enough to negate the selection bias \citep[Ch.
+\paragraph{Cultural transmission.}
+In cultural transmission, individuals transmit cultural traits (i.e., behavior, beliefs, norms) to one another, typically via learning and demonstrating \citep{transmissionVectorsBook}.
+Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations. % TODO reference
+Although cultural transmission is most common in humans, it is also observed in other animals such as chimpanzees \citep{chimpsPrestige, chimpsCopy}.
+% TODO but also birds, Cetacea (Whitehead, PNAS 2017)
+In elephants, \citet{elepahntsRepo} showed that once a matriarch is removed from the group, the group's survival instincts are inferior and that ``the possession of enhanced discriminatory abilities by the oldest individual [matriarch] in a group can influence the social knowledge of the group as a whole.''
+By playing audio recordings of African elephants, they showed that groups with a matriarch recognize and react better to hostile or friendly calls than groups without a matriarch.
+\citet{fliesPaper} showed that choice of oviposition site in fruit flies is culturally transmitted: inexperiences flies that spent some time with experienced flies chose the same type of oviposition site even without directly observing this behavior.
+How the information is transmitted is still an open question, but it has been suggested that flies may use olfactory cues like other animals, such as rodents and bees.
+
+\paragraph{Direction of transmission.}
+Similar to genetic transmission, culturally transmitted traits can be transmitted from parents to offspring, and their effects of can be physiological rather than behavioral.
+For example, parents can "teach" their children to be strong or tall, within some biological limits, by instructing them to maintain a specific diet and engage in physical activity.
+Contrary to genetic transmission, cultural transmission can be non-vertical, that is, traits may be transmitted via social learning from non-parental individuals, and even unrelated individuals such as teachers, leaders, media, or any stranger that interacts with the learning individual.
+Thus, cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
+Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring (e.g playing video games)\citep{transmissionVectorsBook,transmissionVectors}.
+% TODO did they suggest video games or did they have some other trait?
+not sure I want to mention video games...
+
+\paragraph{Transmission biases.}
+In social learning, transmission biases cause a trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
+Although more common in cultural transmission, transmission biases do occur in genetic transmission.
+For example, \textit{wtf genes} in yeast bias their transmission to the gamete by secreting a long life-expectancy poison together with a short life-expectancy antidote, so that a gamete without the gene will perish because the poison will outlive the antidote \citep{wtfGene}.
+Importantly, even when a trait is disfavored by natural selection, it may still spread in a population due to transmission biases that are strong enough to overcome selection \citep[Ch.
 8 pg.
-279]{evolutionBook}.\\
+279]{evolutionBook}.
+% TODO we have an example of this in Dor's paper, in which cooperation can evolve due to horizontal transmission bias even when the benefit is zero:
+% 1. Cohen, D., Lewin-Epstein, O., Feldman, M. W. & Ram, Y. Non-vertical cultural transmission, assortment and the evolution of cooperation. Proc. R. Soc. B Biol. Sci. 288, 20203162 (2021).
 
-%transmission biases - what they are, what are the types.
-Transmission bias occurs when a trait has a disproportionate probability from its frequency in the population to be transmitted.
-For example, \citet{wtfGene} show that there are genes of yeast called \textit{wtf genes}, that bias their transmission to the gametes.
-They secrete a long life expectancy poison, together with a short life expectancy antidote, so a gamete without the gene will perish (the poison will outlive the antidote).
-Transmission biases, though exist in genetic transmission, are probably more common in cultural transmission.
-Much like mutation in genetic evolution, one could learn behavioral patterns or traits on his own, usually referred to as \textit{innovation}, also called individual learning, and just like mutation, without it humans might have been remained at the stone age, or even go extinct.
-\citet{strategiesPaper} suggest that success biased social transmission contribute more to the general success of the population than individual learning.
- They conducted a tournament for developing learning strategies of a population, where each participant need to devise a strategy.
- Each strategy must define when individuals should observe and copy from others, and when to engage in individual learning.
- The best strategies contained a high percentage of social learning relative to individual learning, even when the error when copying was as high as almost 0.5.
-It is important to add that all of the strategies include some percentage of individual learning, and without it the results would be a lot worse.
-In addition to \citet{strategiesPaper}, \citet{complexityPaper} define different types of transmission biases based on success.
-They define several types of role-model choosing methods, all assuming that the copier correctly identifies the successful ones.
-Both studies assume that individuals can successfully evaluate successful individuals.
-\citet[Ch. 5]{evolutionBook} suggest that the \textbf{evaluation} of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
-A direct bias is when a variation of a trait is more attractive than others, and is evaluated by \textit{directly} testing the variation of the trait.
-For example, an individual observing a Ping-Pong match between two others can try both of the paddle grips it observed, and decide what grip is better for it.
-An indirect bias is when an individual uses the value of one trait to determine the attractiveness of another, so it \textit{indirectly} evaluates the attractiveness of the role-model.
-Continuing with the example, a bystander could copy the paddle grip of the Ping-Pong player who scored more points in the match.
-A frequency-dependent bias is when an individual has a probability to copy a variant of the trait that is nonlinear to the trait's frequency in the parent's generation. 
-Continuing with the example, when an individual is 80\% likely to copy the common paddle grip even when only 60\% of the population is using it, it is said to be frequency-biased.\\
-Frequency bias could be negative too. \citet{negativeFrequency} show that societies under competitive conditions are likely to develop diversity in foraging specialization rather than uniformity.
+\paragraph{Success bias.}
+\citet{strategiesPaper} have conducted a tournament between learning strategies.
+Each strategy defines when individuals observe and copy from others, and when they engage in individual learning, in which an individual learns a cultural trait on his own.
+The best strategies had a high frequency of social learning relative to individual learning, even when the transmission error was almost 50\%.
+It is important to note that all of the strategies included some frequency of individual learning.
+%The authors suggested that success-biased social transmission contribute more to the general success of the population than individual learning.
+% TODO how is the last sentence related to the results of the tournament?
+did the best strategies use success-bias?
+it is not clear
 
-%prestige bias - what is it, what's missing
-Prestige means having a good reputation or high-esteem, therefore does not directly signify success (although it may imply it), making it an \textit{indirect bias}.
-Both \citet[Ch. 8]{evolutionBook} and \citet{complexityPaper} claim that prestige biases are probably more common in humans than success biases.
-\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population, if the indirect bias is strong enough.
-They claim the bias could lead to a \textit{runaway process}, caused by a cultural equivalent of \textit{sexual selection} \citep{sexualSelectionBook}.
-On the other hand, \citet{fijian_social_bias} claim that prestige biases, over generations, can lead to cultural adaptations.
-According to them, prestige can make a maladaptive trait spread in the population, but can also accelerate the spread of adaptive traits as well.
-\textit{Prestige bias} is often mentioned in the literature, but seldom modeled.
-\citet{evolutionBook} have modeled the prestige bias, but didn't include the effects the copiers of a role-model has on the probability of other individuals to choose the same role model.\\
-This effect is similar to \textit{conformity} \citep{conformity}, which is usually modeled as a different bias.
-\textit{Conformist learning} (imitating locally common behaviors) is a known bias in cultural transmission \citep{conformism}, and we suggest that prestige bias is made up by both indirect bias and a new type of conformity.
-Our new component, \textit{influence}, is assigned to a role-model, contrary to conformity, which refers to the frequency of a trait in the population, regardless which individuals posses it.
-\textbf{The goal of this study is to define a more realistic model for prestige bias and analyze the dynamics of the population it causes}.
+% TODO do we need the following paragraph? it doesn't say much, and the paragraph after it covers "different type of success evaluation", so what is this paragraph doing?
+%\citet{complexityPaper} define different types of transmission biases based on success.
+They define several types of role-model choice methods, all assuming that the copier correctly identifies the successful role-models.
 
-Today, due to social media, it is easier than ever to estimate the influence individuals have over others, therefore it is probably a major part of humans decision-making process.
-For example, the number of \textit{followers} a person has in the mobile application \textit{Instagram} may significantly affect how his beliefs are perceived by the population.
-We want to create a model that better fits reality and simulate scenarios that better mimic cultural transmission dynamics.
-With a more accurate model of prestige bias, we may understand better how cultural traits are transmitted, and why.
-Moreover, we could better explain the cause for the spread of maladaptive traits, or the acceleration of adaptive traits often seen in humans.
+\paragraph{Evaluating success.}
+\citet[Ch. 5]{evolutionBook} suggest that the evaluation of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
+A direct bias occurs when a variation of a trait is more attractive than others, and is evaluated by \textit{directly} testing the variation of the trait.
+For example, an individual observing a Ping-Pong match can attempt both of the observed paddle grips to determine which grip is better.
+An indirect bias occurs when an individual uses the value of one trait to determine the attractiveness of another, so it \textit{indirectly} evaluates the attractiveness of the role-model.
+For example, an observer may copy the paddle grip of the Ping-Pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
+A frequency-dependent bias occurs when an individual has a probability to copy a variant of the trait that higher or lower than trait's frequency among demonstrators. 
+For example, when an individual is 80\% likely to copy the common paddle grip even when only 60\% of the population is using it, it is said to be frequency-biased, or in this case, conformist.
+Frequency bias could be negative, i.e., non-conformist bias. 
+Conformity and non-conformity are well-known biases in cultural transmission \citep{conformism}, and its effect on cultural evolution have been studied with both models (Denton 2020 PNAS; Denton TPB 2021) and experiments \citet{negativeFrequency}
+% TODO references for the above
+% 1. Denton, K. K., Ram, Y. & Feldman, M. W. Conformity and content-biased cultural transmission in the evolution of altruism. Theor. Popul. Biol. (2021) doi:10.1016/j.tpb.2021.10.004.
+% 2. Denton, K. K., Ram, Y., Liberman, U. & Feldman, M. W. Cultural evolution of conformity and anticonformity. Proc. Natl. Acad. Sci. U. S. A. 202004102 (2020) doi:10.1073/pnas.2004102117.
 
+\paragraph{Prestige.}
+Prestige means having a good reputation or high esteem, therefore does not directly signify success (although it may imply it), making it an indirect bias.
+Both \citet[Ch. 8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
+\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population if indirect biases are strong enough.
+They suggest that such biases could lead to a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
+On the other hand, \citet{fijian_social_bias} suggest that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
+Prestige is often mentioned in the cultural-evolution literature, but seldom modeled, although \citet{evolutionBook} have modeled prestige via success bias. % TODO is this correct?
+
+\paragraph{Influence bias.}
+Today, social media provides an easy way to estimate the influence individuals have over others, and therefore may have a major effect on human decision making.
+For example, the number of "followers" a person has on social networks such as \textit{Facebook} or \textit{Instagram} may significantly affect how his beliefs are perceived by the population.
+% TODO this must have some reference in the literature.
+Here we propose an indirect bias that we call \textit{influence bias}, in which the choice of a role-model depends on the the choices made by other individuals that have already chosen a role-model. 
+This is a context bias, % TODO right?
+ which depends on the role-model rather than the trait, in contrast to frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models. 
+We define a model for prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Models and Methods}

### 2022-03-27 ms/PrestigeBias.tex
revised models and methods

@@
 \section{Models and Methods}
-\paragraph{Reminder:} A \textit{Wright–Fisher model} is a mathematical model meant to describe a genetic drift process.
-This model assumes that generations do not overlap and that each copy of the gene found in the new generation is drawn independently at random from all copies of the gene in the old generation.
 
-A \textit{Moran model} assumes overlapping generations.
+%A \textit{Wright–Fisher model} describes an evolutionary process with random genetic.
+This model assumes non-overlapping generations such that the entire population is replaced in every generation by the offspring population.
+The parent of each offspring is independently drawn at random from the parental generation.
+%A \textit{Moran model} also describes an evolutionary process with drift, but assumes overlapping generations.
 At each time step, one individual is chosen to reproduce and one individual is chosen to die.
-In our models we harness these two models and modify them to describe new mathematical models that we use to expand the basic indirect bias model \citet{evolutionBook} suggest.
 
-\subsection{Continuous Model}
-Consider a population of N individuals, each individual has one trait on a continuous scale.
-Every generation, $N$ naive individuals (\textit{copiers}) must choose a trait to copy from one of the individuals of the previous generation (\textit{role-models}).
-Similar to a Wright–Fisher model, we assume the generations don’t overlap.
-We base our model on the model of \citet{evolutionBook}, by assuming only oblique transmission of the traits (\textit{Indicator trait - A}).
-Unlike their model, we omit a second trait called \textbf{Indirectly biased trait} to lower complexity.
-The model’s state at time $t$ can be described by:
-\begin{equation}
-\vec{A}_t=(A_{t,1}, \ldots, A_{t,N})
+We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
+We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python with NumPy and Matplotlib. % TODO references: 
+%- Van Rossum, G. & others. Python Programming Language. in USENIX Annual Technical Conference (2007).
+%- van der Walt, S., Colbert, S. C. & Varoquaux, G. The NumPy Array: A Structure for Efficient Numerical Computation. Comput. Sci. Eng. 13, 22–30 (2011). 
+%- Hunter, J. D. Matplotlib: A 2D Graphics Environment. Comput. Sci. Eng. 9, 90–95 (2007).
+Source code is available at % TODO GitHub link; currently it is private but will be public when paper is accepted.
+
+\subsection{Continuous trait}
+We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the indicator trait and omitting the indirect trait in order to reduce model complexity. 
+We consider a population of $N$ individuals, described by a single indicator trait with a continuous value.
+Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait.
+Similar to a Wright–Fisher model, we assume non-overlapping generations such that the entire population is replaced in each generation.
+The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t$.
+We assume the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
+Cultural transmission is modeled by a function $F$ such that 
+\begin{equation}\label{eq:transmission}
+A_{i}(t+1) = F_i(\vec{A}(t)) \;.
 \end{equation}
-where $\vec{A}_t$ is a vector describing the indicator traits at time $t$, and $\vec{A}_0$ is drawn from a standard normal distribution.
-Each individual from generation $t+1$, a \textit{copier}, inherits traits like so:
-\begin{equation}
-A_i' = F_i(\vec{A}_t)
+
+\paragraph{Success bias.}
+\citet[Ch.8, p.247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$ as a weighted average of the traits of all role-models, 
+\begin{equation}\label{eq:boydF}
+% TODO I changed X to A, and Aij to Aj, verify its ok
+F_i(\vec{A}) = \sum_{j=1}^N G_{i,j}\cdot A_{j} \;, 
 \end{equation}
-where $A_i'$ is the indicator and indirect trait values correspondingly, that copier $i$ acquires.
-We use $A_i'$ as an alias for $A_{i,(t+1)}$ for simplicity for the transition between generations $t \rightarrow t+1$.
-$F$ is a function over the $t$ generation traits vector, and is defined differently for every implementation of the \textbf{Generic model}.
-
-\paragraph{Success bias.} \citet[Ch.8, p.247-249]{evolutionBook} describe a method of inheritance using a \textit{blend}, i.e weighted average of the trait of the entire generation.
-They define $F$ as a weighted average  of the role-models' traits in a single generation:
-\begin{equation}
-F_i(\vec{X}) = \sum_{j=1}^N \Big(G_{ij}\cdot X_{ij}\Big) \\
+where $G_{i,j}$ is the success bias of role-model $j$ in the eyes of copier $i$,
+\begin{equation}\label{eq:boydG}
+G_{i,j} = \frac{\beta(A_{i,j})}{\sum_{k=1}^{N} \beta(A_{i,k})} \;,
 \end{equation}
-where $G_{i,j}$ is: 
-\begin{equation}
-G_{ij} = \frac{\beta(A_{ij})}{\sum_{l=1}^{N} \beta(A_{il})}
-\end{equation}
-We define $G_{ij}$ to be the \textit{Success bias} of role-model $j$ in the eyes of copier $i$.
-$A_{i,j}$ is the absolute indicator trait value copier $i$ estimates role-model $j$ has:
+$A_{i,j}$ is the absolute indicator trait value copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\frac{1}{\eta^2})$,
 \begin{equation}\label{eq:relativeIndicator}
@@
 \end{equation}
-where $e_i$ is the copier's error of estimation, $\vec{e} \sim N(0,\frac{1}{\eta^2})$.
-$\beta(X)$ is the bias function, meant to quantify the success bias of a role-model:
+and $\beta(\cdot)$ is the bias function that quantifies the success bias of a role-model,
 \begin{equation}\label{eq:success_bias}
-\beta(A_{i,j}) = b \cdot \exp^{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)},
+\beta(A_{i,j}) = b \cdot \exp{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)},
 \end{equation} 
-where $\hat{A}$ is the optimal indicator value and $J,b$ are model parameters to control the "strength" of the bias.
-$G_{i,j}$ is therefore the relative success score copier $i$ assigns to role-model $j$, resembling \textit{relative fitness} in genetic transmission models.
+with $\hat{A}$ as the arbitrary optimal indicator value, and $J$ and $b$ as parameters that control the bias strength.
+Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$, equivalent to relative fitness in evolutionary-genetic transmission models.
 
-\paragraph{Random choice transmission.}
-\citet{evolutionBook} note that the method of transmission they use in their model has alternatives.
-We follow their suggestion and create a model similar to theirs, with random choice as a transmission method: The probability of copier $i$ to choose role-model $j$ as his role-model to copy its traits from is $G_{i,j}$.
-Once a copier chose its role-model, it will copy both its traits only from his role-model, instead of a weighted average of the entire role-model generation:
-\begin{equation}
-A_i' = A_{i,j}
+\citet{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
+We thus develop a similar stochastic model with transmission from a single random role-model.
+Instead of \cref{eq:boydF}, we define the transmission function $F$ as a random variable with its distribution given by
+\begin{equation}\label{eq:ourF}
+\Pr\big(F_i(\vec{A}) = A_{j}\big) = G_{i,j} \;,
 \end{equation}
+such that $G_{i,j}$ gives the probability of copier $i$ to choose to copy the trait of role-model $j$.
 
 \paragraph{Influence bias.}
-Copiers choose their role-models one by one.
-After copier $i$ chose a role-model, we denote $K_{ij}$ as the number of copiers that chose role-model $j$ until that point, such that $\sum_{j=1}^N{K_{i,j}} = i$. 
+Here we introduce a new element to the model.
+We assume that in each generation, copiers choose their role-models one by one.
+We denote $K_{i,j}$ as the number of copiers that chose role-model $j$ after copier $i$ chose a role-model.
+Thus, $i$ out of $N$ copiers already chose a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
 The stochastic process of role-model choice, 
 \begin{equation} \label{eq:process}
-\big\{\vec{K}_i\big\}_{i=1}^N, \quad \vec{K}_i=(K_{i1}, \ldots, K_{iN}),
+\big\{\vec{K}_i = (K_{i,1}, \ldots, K_{i,N}) \big\}_{i=1}^N \;,
 \end{equation}
@@
 \begin{equation} \label{eq:recurrence}
-K_{i,j} = K_{i-1,j} + S_{i,j}, \quad i,j=1,2,\ldots,N
+K_{i,j} = K_{i-1,j} + S_{i,j}, \quad i,j=1,2,\ldots,N \;,
 \end{equation}
@@
 
-The probability that the $i$-th copier chose role-model $j$
+Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the prestige of role-model $j$ in the eyes of copier $i$,
 \begin{equation}\label{eq:recPrestige}
-G_{i,j}=P(S_{i,j}=1| S_{1,j},S_{2,j},...,S_{i-1,j})
+Pr(S_{i,j}=1 \mid S_{1,j},S_{2,j},...,S_{i-1,j}) = G_{i,j} \;.
 \end{equation}
-is the prestige of role-model $j$ in the eyes of copier $i$.
-This prestige $G_{i,j}$ is determined as follows.
-First, role-model~$j$ is characterized by its indicator value $A_j$ as before, and the estimated indicator value by copier $i$, $A_{i,j}$ remains as \cref{eq:relativeIndicator}.
-Finally, the prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased indicator value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$,
-\begin{equation}\label{prestige_eq}
-G_{i,j} = \frac{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}{W_i},
+The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased indicator value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citet{evolutionBook} with
+\begin{equation}\label{eq:prestige}
+G_{i,j} = \frac{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}{W_i} \;.
 \end{equation}
-where the weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of the indicator and the influence in the prestige, and $W_i$ is a normalizing factor to ensure $\sum_{j=1}^N{G_{i,j}}=1$,
-\begin{equation}
-W_i = \sum_{j=1}^N{\Big(\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}\Big)}.
+Here, the weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of success and influence in his prestige, the indicator value of role-model $j$ estimates by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeIndicator}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
+%\begin{equation}
+%W_i = \sum_{j=1}^N{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}.
+%\end{equation}
+
+\subsection{Dichotomous trait}
+To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$.
+All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
+Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
+% based on \cref{eq:copier_choose} is % TODO you refer an equation that did not yet appear!
+\begin{equation}\label{eq:binary-model}
+P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} % TODO should it be G_{i,A} rather than P_i,A ?
 \end{equation}
+where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model.
+% TODO what is alpha' ?
+Initially, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. The rest of the details follow the continuous trait model.
 
-\subsection{Binary model} The indicator trait can now manifest in only two phenotypes, and for simplicity we define they can be either $\hat{A}$ or $A$.
-In the binary model, the influence is determined by the number of copiers already chosen \textbf{any} role-model with either $A$ or $\hat{A}$, as all role-models with $A$ will contribute to the probability of the trait to be inherited just the same (can be proved with simple induction).
-Simply put, assuming there are two role-models with the $A$ trait, the probability a copier will copy from either role-model will be the same, and the probability the $A$ trait will be inherited is the sum of both role-models.
-In the general case, the probability of the $i$-th individual to inherit trait $A$, based on \cref{copier_choose} is:
-\begin{equation}\label{eq:binary-model}
-P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
-\end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$ and $K_A$ is the number of copiers that already chose $A$.\\
-The model begins with the first generation having a single individual with $\hat{A}$, and the rest have $A$. The process itself is the same stochastic process as the continuous model.
-
-\subsection{Methods}
-The main methods we used to experiment and compare our models is using computer generated simulations.
-In order to establish our claims and base our mathematical approximations of our models, we used the $\chi^2$ test for the full continuous model, and the Kimura's equations of fixation probability and time to fixation for the binary model.
-
+%%%%%%%
 \section{Results}
@@
 \paragraph{Corollary 2: } $\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) / \overline{\alpha \cdot \beta(A')}$.
-\paragraph{Proof: } The initial prestige of role-model $j$ based on \cref{prestige_eq} is:
+\paragraph{Proof: } The initial prestige of role-model $j$ based on \cref{eq:prestige} is:
 \begin{equation}\label{initial_prob}
@@
 We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
-Using \cref{prestige_eq} we get:
-\begin{equation}\label{copier_choose}
+Using \cref{eq:prestige} we get:
+\begin{equation}\label{eq:copier_choose}
 \begin{split}
@@
 \end{equation}
-We see that \cref{polya} and \cref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
+We see that \cref{polya} and \cref{eq:copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
 

### 2022-03-27 ms/PrestigeBias.tex
revised GBD section

@@
 \usepackage{pdfpages}
+
+% line numbers
+ \usepackage[displaymath, mathlines]{lineno}
+ \renewcommand\linenumberfont{\normalfont\small\sffamily}
+\linenumbers
+\modulolinenumbers[2]
+
+% math stuff
+\DeclareMathOperator*{\E}{{\rm I\kern-.3em E}}
+\let\vec\mathbf
 \newenvironment{conditions}
@@
   {\end{tabular}\par\vspace{\belowdisplayskip}}
-\newcommand{\R}{\mathbb{R}}  
-\DeclareMathOperator*{\E}{\mathbb{E}}
 
+% title page stuff
 \author{
@@
 
-%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
 \subsection{Approximations}
-Currently $\big\{\vec{K}_i\big\}_{i=1}^N$ is a stochastic process where each state depends on the previous state, i.e a Markov chain.
-We wanted to find an equivalent stochastic process that has the same joint distribution on $\big\{\vec{K}_i\big\}_{i=1}^N$, but it is possible to evaluate the joint distribution directly without evaluating all the marginal conditional distributions: \cref{eq:recurrence}, \cref{eq:recPrestige}.
-
-We found two approximations to our process, which are summarized here and explained in detail later on:
+Our model is defined by two nested stochastic processes.
+Change over multiple generations is described by the phenotype distribution at each generation, $\{\vec{A}(t)\}_t$.
+The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
+We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$.
+However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
+Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$.
+We found two approximations such processes, summarized here and explained in detail below:
 \begin{enumerate}
 \item 
-$K_{i,j}$ follows the general binomial distribution defined by \citet{GBD}.
-Moreover, $\mathbb{E}[K_{N,j}] = N \cdot G_{1,j}$ if $e=e_l=e_m$ for all $l,m$.
- That is, the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers. 
- In addition, we find that when $\alpha$ is homogeneous, $\alpha_l=\alpha_m$ for all $l,m$, then $\mathbb{E}[K_{N,j}] = \beta(A'_j) \; / \; \overline{\beta(A') }$, where $A'_j$ is the estimated indicator value $A'_j=A_j+e$, and
- $\overline{ \beta(A') }$ is the population mean estimated indicator value. 
- That is, the expected number of copiers of a role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models.
-\item The role-model choice process \cref{eq:process} is equivalent to a P\'{o}lya urn model if $e_l=e_m$ for all $l,m$. 
-Therefore, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$ follows a Dirichlet-Multinomial distribution,
-\begin{equation}
-\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big), 
-\end{equation}
-where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$.
-Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$.
+The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
+\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
+$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
+\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if $\alpha$ is uniform for all role-models ($\alpha=\alpha_k$ for $k=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
+\end{enumerate}
+\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$). 
+Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
+$\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
+Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$, as the estimation error is uniform. % TODO correct? anything else need to be assumed?
 \end{enumerate}
 
-\subsection{General Binomial Distribution Approximation}
-The general binomial distribution (GBD) is achieved by a series of Bernoulli experiments, with possible dependency between experiments.
-\paragraph{Proposition:} The number of copiers $K_{i,j}$ follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A'_j))$, when $e_l=e_m$ for all $l,m \in N$ and $A'_j=A_j + e$ 
-\paragraph{Proof: } We'll denote $Q_j(k,i)=P(K_{i,j} = k | K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$, using conditional probability and \cref{eq:recurrence}:
+\subsection{Generalized Binomial Distribution Approximation}
+The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
+
+\paragraph{Proposition.} The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$.
+
+\paragraph{Proof.} We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$.
+Using conditional probability and \cref{eq:recurrence},
 \begin{equation}\label{recursive}
-Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1)
+Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1),
 \end{equation}
 where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
+\Cref{recursive} is equivalent to eq.~(2.1) by \citet{GBD}, which completes the proof.
+%$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$. % TODO do you need this sentence?
 
-We see that \cref{recursive} is equivalent to eq. (2.1) that \citet{GBD} define.
-$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$.
-By describing the process of \cref{eq:process} as \citep{GBD} did, we've completed the proof.
+\paragraph{Corollary 1.} $\E[K_{N,j}] = N \cdot G_{1,j}$.
+\paragraph{Proof.} \citet[eq.~(2.3)]{GBD} show that 
+$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
+$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
+$Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
 
-\paragraph{Corollary 1: } $\mathbb{E}[K_{N,j}] = N \cdot G_{1,j}$.\\
-In \citep[equation 2.3]{GBD}, they show that the expected value of $k$ is: \\
-$\mathbb{E}[k] = N \cdot Q_j(1,1)$ (using different notations).
-$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any choices are made.
-$Q_j(1,1) = G_{1,j}$ by definition, therefore we can say that $\mathbb{E}[K_{N,j}]=N \cdot G_{1,j}$.\\
+\paragraph{Corollary 2: } $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
+\paragraph{Proof.} The initial prestige of role-model $j$ based on \cref{eq:prestige} is
+\begin{equation}\label{eq:initial_prob}
+G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
+\end{equation}
+The denominator of \cref{eq:initial_prob} can also be formulated as:
+\begin{equation}\label{eq:denominator}
+ \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
+\end{equation}
+where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
+Using \cref{eq:denominator} we get, % TODO something is missing here? how did you get E[KNj] to relate to the previous two equations?
+\begin{equation}
+\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
+\end{equation}
+completing the proof.
 
-\paragraph{Corollary 2: } $\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) / \overline{\alpha \cdot \beta(A')}$.
-\paragraph{Proof: } The initial prestige of role-model $j$ based on \cref{eq:prestige} is:
-\begin{equation}\label{initial_prob}
-G_{1,j} = \frac{\alpha_j\cdot\beta(A'_j)}{\sum\limits_{m=1}^{N}\alpha_m\cdot\beta(A'_m)}
+The special case where the weight is uniform for all role-models ($\alpha = \alpha_j$ for $j=1,\ldots, N$) is interesting, because we can evaluate the expected number of copiers using a linear equation
+\begin{equation}
+\E[K_{Nj}]= N\cdot\frac{\alpha\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N}\alpha\cdot\beta(A_m+e)} =\beta(A_j+e) \bigg/ \overline{\beta(A+e)} \;,
 \end{equation}
-The denominator of \cref{initial_prob} can also be formulated as:
-\begin{equation}\label{denominator}
- \sum\limits_{m=1}^{N}\alpha_m\beta(A'_m) = N \cdot \overline{\alpha \cdot \beta(A')}
-\end{equation}
-where $\overline{\alpha\beta(A')}$ is the mean value of $\alpha_m\cdot\beta(A'_m)$ for all $m$.
-Using \cref{denominator} we get:
-\begin{equation}
-\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) \bigg/ \overline{\alpha \cdot \beta(A')}
-\end{equation},
-completing our proof.
-
-The special case where $\alpha = \alpha_l=\alpha_m$ for all $l,m \in N$ is interesting, because we can evaluate the expected number of copiers using a linear equation:
-\begin{equation}
-\mathbb{E}[K_{Nj}]= N\cdot\frac{\alpha\cdot\beta(A'_j)}{\sum\limits_{m=1}^{N}\alpha\cdot\beta(A'_m)} =\beta(A'_j) \bigg/ \overline{\beta(A')}
-\end{equation}
-where the only variable is $A'_j$, because $\overline{\beta(A')}$ is the mean of the distribution we draw the indicator values from, modified by some constant parameters of $\beta$.
-We can then denote $L = 1/\overline{\beta(A')}$ and write:
-
-\begin{equation}\label{linearEq}
-\mathbb{E}[K_{Nj}] = L\cdot \beta(A'_j)
+where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution we draw the indicator values from, modified by some constant parameters of $\beta$.
+We can then denote $L = 1/\overline{\beta(A+e)}$ and write
+\begin{equation}\label{eq:linearEq}
+\E[K_{Nj}] = L\cdot \beta(A_j+e) \;.
 \end{equation}

### 2022-03-28 ms/PrestigeBias.tex
reformat as paper

@@
-\documentclass[11pt]{article}
-\usepackage[margin=1in]{geometry}          
+\documentclass[12pt]{extarticle}
+\usepackage{geometry}
+\geometry{
+a4paper,
+total={170mm,257mm},
+left=20mm,
+top=20mm,
+headheight=12pt
+}
+
+%\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
 \usepackage{graphicx}
@@
 \usepackage{mathtools}
-\usepackage[displaymath, mathlines]{lineno}
-\usepackage{natbib}
+\usepackage[round,colon,authoryear]{natbib}
 \usepackage[all]{nowidow}
@@
 \usepackage{pdfpages}
+\usepackage{authblk}
 
@@
 \DeclareMathOperator*{\E}{{\rm I\kern-.3em E}}
+\newcommand*{\tr}{^\intercal}
 \let\vec\mathbf
-\newenvironment{conditions}
-  {\par\vspace{\abovedisplayskip}\noindent\begin{tabular}{>{$}l<{$} @{${}={}$} l}}
-  {\end{tabular}\par\vspace{\belowdisplayskip}}
+\newcommand{\matrx}[1]{{\left[ \stackrel{}{#1}\right]}}
+\newcommand{\diag}[1]{\mbox{diag}\matrx{#1}}
+\newcommand{\goesto}{\rightarrow}
+\newcommand{\dspfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2} }
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{lemma}{Lemma}
+\newtheorem{remark}{Remark}
+\newtheorem{result}{Result}
+\renewcommand\qedsymbol{} % no square at end of proof
+\newcommand{\cl}{\mathbf{L}}
+\newcommand{\cj}{\mathbf{J}}
+\newcommand{\ci}{I}
 
 % title page stuff
-\author{
-	Saar Egozi
-	\and
-	Yoav Ram
-}
+\title{Prestige as a Driving Force in Cultural Transmission}
+
+\author[1]{Saar Egozi}
+\author[2,3,*]{Yoav Ram}
+\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
+\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
+\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
+\affil[*]{Corresponding author: yoav@yoavram.com}
+
+\date{\today}
 
 \begin{document}
+\maketitle
 
-\begin{titlepage}
-\centering
-
-\vspace{4cm}
-
-{\LARGE\bfseries Prestige as a Driving Force in Cultural Transmission}
-
-\vspace{2cm}
-
-{\large\bfseries Saar Egozi}
-
-\vspace{1cm}
-
-{\large supervised by Dr. Yoav Ram}
-
-\vspace{2cm}
-
-\vfill
-
-{\large Efi Arazi School of Computer Science, Reichman University}
-
-\vspace{1cm}
-
-{\itshape \today}
-
-{\large saartk@gmail.com}
-\end{titlepage}
-
-\renewcommand\linenumberfont{\normalfont\small\sffamily}
-\linenumbers
-\modulolinenumbers[2]
-\setcounter{secnumdepth}{0}
-\tableofcontents
-
-\clearpage
-
-\section{Abstract}
-Copying role-models can be an efficient method of acquiring knowledge \citep{strategiesPaper}.
-\textbf{Here, we study the effects of prestige as a cultural transmission bias} in cultural-evolution model.
-A common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears more successful \citep{evolution_of_cultural_evolution}.
+\begin{abstract}
+Copying role-models can be an efficient method of acquiring knowledge.
+Here, we study the effects of prestige as a cultural transmission bias in cultural-evolution model.
+A common bias when choosing a role-model to copy is success bias, i.e copying whoever appears more successful.
 This bias depends on the performance of the role-model alone, without other factors.
-We propose an additional bias that may be prevalent in cultural transmission: \textit{Influence bias}, which is evaluated by the number of individuals that have already copied a specific role-model \citep{prestige_evolution}.
-We combine these biases together to a \textit{prestige bias} and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations.
+We propose an additional bias that may be prevalent in cultural transmission: influence bias, which is evaluated by the number of individuals that have already copied a specific role-model .
+We combine these biases together to a prestige bias and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations.
 We find analytic approximations to our model, facilitating further mathematical analysis and reducing the computational complexity of the simulations.
@@
 Further work is needed to test if this model could predict various phenomena in human cultural evolution when extended with the effects of selection and innovation.
+\end{abstract}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section*{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Models and Methods}
+\section*{Models and Methods}
 
@@
 
-\subsection{Continuous trait}
+\subsection*{Continuous trait}
 We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the indicator trait and omitting the indirect trait in order to reduce model complexity. 
@@
 
-\subsection{Dichotomous trait}
+\subsection*{Dichotomous trait}
 To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\subsection{Approximations}
+\section*{Results}
+\subsection*{Approximations}
 Our model is defined by two nested stochastic processes.
@@
 
-\subsection{Generalized Binomial Distribution Approximation}
+\subsection*{Generalized Binomial Distribution}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
 
-\paragraph{Proposition.} The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$.
+\begin{result}[GBD approximation]
+The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$. 
+\end{result}
 
-\paragraph{Proof.} We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$.
+\begin{proof}
+We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$. 
 Using conditional probability and \cref{eq:recurrence},
@@
 %$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$. % TODO do you need this sentence?
+\end{proof}
 
-\paragraph{Corollary 1.} $\E[K_{N,j}] = N \cdot G_{1,j}$.
-\paragraph{Proof.} \citet[eq.~(2.3)]{GBD} show that 
+\begin{corollary}
+$\E[K_{N,j}] = N \cdot G_{1,j}$.
+\end{corollary}
+
+\begin{proof}
+\citet[eq.~(2.3)]{GBD} show that 
 $\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
@@
 $Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
+\end{proof}
 
-\paragraph{Corollary 2: } $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
-\paragraph{Proof.} The initial prestige of role-model $j$ based on \cref{eq:prestige} is
+\begin{corollary}
+$\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
+\end{corollary}
+
+\begin{proof}
+The initial prestige of role-model $j$ based on \cref{eq:prestige} is
 \begin{equation}\label{eq:initial_prob}
@@
 completing the proof.
+\end{proof}
 
@@
 
-\subsection{Dirichlet-Multinomial Distribution Approximation}
-\paragraph{Reminder: \textit{Pólya urn model}}  is a stochastic process that is defined as such: 
+\subsection*{Dirichlet-Multinomial Distribution}
+
+\begin{remark}
+\textit{Pólya urn model}  is a stochastic process that is defined as such: 
 The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors.
@@
 where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.
+\end{remark}
 
-\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
-\paragraph{Proof:} 
+\begin{result}[Pólya urn model]
+$\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
+\end{result}
+
+\begin{proof} 
 We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
@@
 We see that \cref{polya} and \cref{eq:copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
+\end{proof}
 
-\paragraph{Corollary 1:}
+\begin{remark}
 In their paper, \citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{Pólya urn model} will converge to the Dirichlet distribution as the number of draws approaches infinity, based on \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
@@
 $\vec{K_i} \sim DM(N,\vec{G_1})$.
+\end{remark}
 
@@
 
-\subsection{Numeric comparisons}
+\subsection*{Numeric comparisons}
 We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation.
@@
 
-\subsection{Fixation probability and time - binary model}
+\subsection*{Fixation probability and time - binary model}
 \paragraph{Kimura's approximation:}
@@
 
-\paragraph{Proposition:} $1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.
+\begin{result}[Effective selection coefficient]
+$1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.
+\end{result}
 
-\paragraph{Proof:} Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals.
+\begin{proof}
+Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals.
 Let $X$ be the number of individuals of type $\hat{A}$ so $x=X/N$.
@@
 where when substituting $1-\beta$ with $s$, we get the same result as \citet{durret} which is the desired result.
+\end{proof}
 
-\paragraph{Proposition:} $Ne=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
+\begin{result}[Effective population size]
+$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
+\end{result}
 
-\paragraph{Proof:} The variance of a DM distribution is:
+\begin{proof}
+The variance of a DM distribution is:
 \begin{equation}
@@
 
-Like Durret, we'll use the zero order of the approximation when $\beta\approx1$,so:
+Like Durrett, we'll use the zero order of the approximation when $\beta\approx1$,so:
 \begin{equation}
@@
 
-Again following Durret we want to calculate:
+Again following Durrett we want to calculate:
 \begin{equation}\label{eq:var_diff_durret}
@@
 
-\subsection{Changing environment}
+\subsection*{Changing environment}
 After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.
@@
 proving the second part of our preposition.
+\end{proof}
 
@@
 
-\section{Discussion}
-\subsection{summary}
+\section*{Discussion}
+\subsection*{summary}
 Cultural transmission is the phenomenon of which cultural elements, in the form of attitudes, values, beliefs, and behavioral patterns, are transmitted between individuals, typically via copying.
@@
 
-\subsection{Prestige in the literature}
+\subsection*{Prestige in the literature}
 So far we discussed prestige as a main bias in humans, and to some extent in non-human species.
@@
 
-\clearpage
+\pagebreak
 \bibliography{refs}

### 2022-03-28 ms/PrestigeBias.tex
reformat some more

@@
 
-%\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
+\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
 \usepackage{graphicx}
@@
 \usepackage{mathtools}
-\usepackage[round,colon,authoryear]{natbib}
 \usepackage[all]{nowidow}
@@
 \usepackage{authblk}
+
+% unbreakable dashes
+\usepackage[shortcuts]{extdash}
+% footnotes
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+% less space before sections 
+% \titlespacing*{<command>}{<left>}{<before-sep>}{<after-sep>}
+\usepackage{titlesec}
+\titlespacing*{\section}
+{0pt}{2ex plus 1ex minus .2ex}{2ex plus .2ex}
+\titlespacing*{\subsection}
+{0pt}{1ex plus 1ex minus .2ex}{1ex plus .2ex}
+\titlespacing*{\paragraph}
+{0pt}{1ex plus 1ex minus .2ex}{1ex plus .2ex}
+
+%SetFonts
+% newtxtext+newtxmath
+\usepackage{newtxtext} %loads helv for ss, txtt for tt
+\usepackage{amsmath}
+\usepackage[bigdelims]{newtxmath}
+\usepackage[T1]{fontenc}
+\usepackage{textcomp}
+%SetFonts
 
@@
 \modulolinenumbers[2]
+
+% Supplementary
+\newcommand{\beginsupplement}{%
+      	\setcounter{table}{0}
+        \renewcommand{\thetable}{S\arabic{table}}%
+        \setcounter{figure}{0}
+        \renewcommand{\thefigure}{S\arabic{figure}}%
+}
+
+% NatBib
+%\usepackage[super,comma]{natbib}
+\usepackage[round,colon,authoryear]{natbib}
+%\use-package[numbers,super,sort&compress]{natbib}
+\renewcommand{\bibsection}{}
+%\renewcommand{\bibfont}{\small}
 
@@
 
+\renewcommand\Affilfont{\small}
 \author[1]{Saar Egozi}
 \author[2,3,*]{Yoav Ram}
-\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
-\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
-\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
-\affil[*]{Corresponding author: yoav@yoavram.com}
+\affil[1]{School of Computer Science, Reichman University, Herzliya 4610101, Israel}
+\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
+\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel}
+\affil[*]{Corresponding author: yoav@yoavram.com, ORCID 0000-0002-9653-4458}
 
@@
 This bias depends on the performance of the role-model alone, without other factors.
-We propose an additional bias that may be prevalent in cultural transmission: influence bias, which is evaluated by the number of individuals that have already copied a specific role-model .
+We propose an additional bias that may be prevalent in cultural transmission: influence bias, which is evaluated by the number of individuals that have already copied a specific role-model.
 We combine these biases together to a prestige bias and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations.
@@
 \end{abstract}
-
+\pagebreak
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \pagebreak
+
+\section*{References}
+\nolinenumbers
 \bibliography{refs}
+%\bibliographystyle{agsm}
 \bibliographystyle{apalike}

### 2022-03-28 ms/PrestigeBias.tex
finished GBD and DM

@@
 \usepackage{graphicx}
-\usepackage{amsthm, amsmath, amssymb}
+\usepackage{amsmath, amssymb, amsthm}
 \usepackage[font=small]{caption, subcaption}
@@
 \usepackage{float}
+\usepackage[unicode=true,colorlinks=true,urlcolor=Blue,citecolor=black,linkcolor=black]{hyperref}
 \usepackage{cleveref}
@@
 $\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
-\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if $\alpha$ is uniform for all role-models ($\alpha=\alpha_k$ for $k=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
+\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the success weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
 \end{enumerate}
@@
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
+\\
 
@@
 
+% TODO what about a numerical validation for GBD?
+
 \subsection*{Dirichlet-Multinomial Distribution}
 
-\begin{remark}
-\textit{Pólya urn model}  is a stochastic process that is defined as such: 
-The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors.
-When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same colour.\\
+\paragraph{P\'{o}lya urn model.}
+This stochastic process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors.
+When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same color.
 Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
-Let $S_{i,j}=1$ when drawing a $j$ colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is:
-\begin{equation}\label{polya}
+Let $S_{i,j}=1$ when drawing a $j$-colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is
+\begin{equation}\label{eq:polya}
 \begin{split}
-P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\
- & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
+P(S_{i,j} = 1 \mid \vec{U_{i-1}}) = 
+\frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = 
+\frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}} = 
+\frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m} \;,
 \end{split}
 \end{equation}
-where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.
-\end{remark}
+where $o_j$ is the initial number of balls of the color $j$ in the urn, and $w_{i,j}$ is the cumulative number of new balls that were added to the urn after $i$ draws of the color $j$.
+\\
 
-\begin{result}[Pólya urn model]
-$\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
+\begin{result}[P{\'{o}}lya urn model]\label{result:polya}
+The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \textit{P\'{o}lya urn model} if both trait estimation error and success weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
 \end{result}
@@
 \begin{proof} 
-We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
-Using \cref{eq:prestige} we get:
+Denote $\alpha'=\frac{\alpha}{1-\alpha}$ as the odds ratio between the weights of success and influence bias and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
 \begin{equation}\label{eq:copier_choose}
-\begin{split}
-G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\
-&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\
-& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
-\end{split}
+G_{i,j} = 
+\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}
+ =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N}\alpha'\beta(A'_m)} \;.
 \end{equation}
-We see that \cref{polya} and \cref{eq:copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
+Substituting $M=N$, $o_j = \alpha'\beta(A'_j)$, and $w_{i,j} = K_{i,j}$ in \cref{eq:polya} gives \cref{eq:copier_choose}, thus completing the proof.
 \end{proof}
 
-\begin{remark}
-In their paper, \citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{Pólya urn model} will converge to the Dirichlet distribution as the number of draws approaches infinity, based on \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
-We therefore have an approximation for the relative "weight" or the proportion each role-model has when evaluated as a role-model.
-Drawing from a Multinomial distribution where the parameters are the modified weights gained from the Dirichlet distribution is viable for selecting the role-model for the next generation.
-We can therefore sample from a Dirichlet-Multinomial distribution to approximate how many copiers each of the role-models will have:
-$\vec{K_i} \sim DM(N,\vec{G_1})$.
-\end{remark}
+\citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
+We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
+Thus, choosing the role-models for all copiers is equivalent to drawing from a Multinomial distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
+\\
 
-\paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population.
-To support our proof, we tested our approximation empirically using computer simulations.
-To test our hypothesis, we used a \textit{goodness of fit} method known as \textit{Pearson's chi-squared test}.
-In this test, one can reject or accept the null hypothesis, which in our case is the hypothesis that the simulations results were drawn from a DM distribution.
+\begin{corollary}\label{cor:dirichlet}
+The number of copiers of each role-model follows a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \textit{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
+\end{corollary}
 
-To use this test, we ran many simulations of our original model, and used the mean distribution of copiers.
-This mean distribution is our observed distribution, and we tested it with the DM expected distribution, using said chi-squared test.
-We tested multiple variations of the trait weight parameter ($\alpha$).
+\paragraph{Numerical validation.}
+To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations.
+We executed many simulations of our original model to  % TODO exactly how many 
+compute an observed distribution of number of copiers from the average empirical distribution.
+To compare the observed distribution with the expected DM distribution, we use a Pearson's chi-squared test of goodness-of-fit to reject or accept the null hypothesis that the simulation results are drawn from a DM distribution.
 
-In all our tests, the p-value was \textbf{1}.
-This means that the probability to reject the null hypothesis is essentially nonexistent (the usual threshold for a p-value needed to reject $H_0$ is 0.05 or lower).
-In addition, we found out that for high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value 1.
-(less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
-For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100, which is still a relatively small amount.
-To verify our codes results, we also ran the test for different distributions, for example the uniform distribution (all role-models have exactly one copier).
+When testing multiple values of the bias weight parameter $\alpha$, the test p-value was 1, meaning means that the null hypothesis cannot be rejected
+For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
+For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
+When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required.
+% TODO did you test other distributions?
+% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
+% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?
 
-All these tests resulted in a p-value 0, which means we can likely reject $H_0$ for these distributions, as expected.
-
-Once we validated our proof for a single iteration of the model, we went on to more complex validations for the entire model.
-
-\subsection*{Numeric comparisons}
+\subsection*{Numeric comparisons} % TODO rename section
 We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation.

### 2022-03-28 ms/PrestigeBias.tex
revise abstract

@@
 \begin{abstract}
-Copying role-models can be an efficient method of acquiring knowledge.
-Here, we study the effects of prestige as a cultural transmission bias in cultural-evolution model.
-A common bias when choosing a role-model to copy is success bias, i.e copying whoever appears more successful.
-This bias depends on the performance of the role-model alone, without other factors.
-We propose an additional bias that may be prevalent in cultural transmission: influence bias, which is evaluated by the number of individuals that have already copied a specific role-model.
-We combine these biases together to a prestige bias and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations.
-We find analytic approximations to our model, facilitating further mathematical analysis and reducing the computational complexity of the simulations.
+Copying role-models can be an efficient method for acquiring knowledge.
+A common bias when choosing a role-model to copy is success bias: copying whoever appears more successful.
+This bias depends on the performance of the role-model alone, with no other factors.
+We propose an additional bias that may be prevalent in cultural transmission: influence bias, in which role-model choice is affected by the number of individuals that have already copied each potential role-model.
+We combine success and influence bias together to a ``prestige bias'' and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
+We find analytic approximations to our stochastic model, facilitating further mathematical analysis and reducing the computational complexity of simulations.
 We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
-For a dichotomous cultural trait, we find  an approximation to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resembles Kimura's classical formulas.
-These approximations show that influence effectively reduces the population size. % TODO reduce or increase?
-We also find that influence accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
-Our model may provide a better description of how human cultural transmission, 
+We also find approximations to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resemble Kimura's classical formulas.
+These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size. % TODO reduce or increase?
+It also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
+Our model may provide a better description of human cultural transmission, 
 especially in the last years where social networks are very popular. % TODO to discuss this last sentence

### 2022-03-28 ms/PrestigeBias.tex
revise name of alpha; add todos for fig 1 and 2

@@
 \usepackage{amsmath, amssymb, amsthm}
-\usepackage[font=small]{caption, subcaption}
+\usepackage[font=small,labelfont=bf]{caption, subcaption}
 \usepackage{setspace}\onehalfspacing
@@
 \end{equation}
-Here, the weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of success and influence in his prestige, the indicator value of role-model $j$ estimates by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeIndicator}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
+Here, the bias weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of success and influence in his prestige, the indicator value of role-model $j$ estimates by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeIndicator}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
 %\begin{equation}
@@
 $\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
-\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the success weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
+\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
 \end{enumerate}
@@
 $\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
-Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$, as the estimation error is uniform. % TODO correct? anything else need to be assumed?
+Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform. % TODO correct? anything else need to be assumed?
 \end{enumerate}
@@
 
-The special case where the weight is uniform for all role-models ($\alpha = \alpha_j$ for $j=1,\ldots, N$) is interesting, because we can evaluate the expected number of copiers using a linear equation
+The special case where the bias weight is uniform for all role-models ($\alpha = \alpha_j$ for $j=1,\ldots, N$) is interesting, because we can evaluate the expected number of copiers using a linear equation
 \begin{equation}
@@
 \begin{result}[P{\'{o}}lya urn model]\label{result:polya}
-The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \textit{P\'{o}lya urn model} if both trait estimation error and success weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
+The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \textit{P\'{o}lya urn model} if both trait estimation error and bias weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
 \end{result}
@@
 \begin{proof} 
-Denote $\alpha'=\frac{\alpha}{1-\alpha}$ as the odds ratio between the weights of success and influence bias and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
+Denote $\alpha'=\frac{\alpha}{1-\alpha}$ as the bias weight ratio, and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
 \begin{equation}\label{eq:copier_choose}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
+  \caption{
+  \textbf{Number of simulations needed to get a good approximation.}
+  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. % 1000 simulations of the model or of DM ??
+  Markers for average value across simulations, error bars for 95\% confidence interval.
+  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
+  \label{fig:num_sims}
+  % TODO
+  % remove legend
+  % change y labels: "Fixation probability" "Fixation time"
+  % change x label: "Number of simulations"
+  % Kimura - black solid line
+  % I removed J as you give beta(A) below, ok
+  % it is not clear what "number of simulations needed" means.
+  % what does "good enough" mean?
+  % maybe y axis should be in relative error?
+  % you should point to the equation for kimura.
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection*{Numeric comparisons} % TODO rename section
-We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation.
-Specifically, we're interesting in the fixation probability of the favored trait ($\hat{A}$) and its time to fixation.
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
-  \caption{The number of simulations needed to get a good approximation.
-At $1,000$ the approximation is good enough.
-Error bars represent 95\% confidence interval.
-Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$.}
-  \label{fig:num_sims}
-\end{figure}
-
-The first step was to find the number of simulations needed to sufficiently approximate the real model with the DM approximation.
-From \cref{fig:num_sims} we see that $1000$ simulations or higher is enough.
-
-The next step was to see how the observed metrics (fixation probability and time) varies when relaxing our assumptions we used to prove the DM approximation.
-First we relaxed our assumption of no mutation.
-To include mutation in the binary model, it needs to be redefined, since in the original model it was based on the fact the traits are drawn from a continuous scale.
-In the binary model mutation will be manifested as an error when evaluating the bias itself.
+
+Here we examine the difference between the dichotomous trait model defined in \cref{eq:binary-model} and the Dirichlet-Multinomial approximation we presented in \cref{cor:dirichlet}.
+We focus on the fixation probability and fixation time of the advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$.
+
+First, we find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1000$ (\Cref{fig:num_sims}).
+Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions
+First we relaxed our assumption of no mutation. % TODO what is the mutation parameters? e? I thought this was estimation error. does it only affect the bias or also the copying? we should discuss!
+To include mutation in the dichotomous trait model, it needs to be redefined, since in the original model it was based on the fact the traits are drawn from a continuous scale.
+In the dichotomous trait model mutation will be manifested as an error when evaluating the bias itself.
 This is easily done by using a heterogeneous $J$ parameter, which controls the strength of the success bias in \cref{eq:success_bias}.
+% NOT CLEAR AT ALL - do you redefine now the model?
+or is this leftover from before???
+% I dont like that we call this mutation, we should call it copying error or something else, see if Boyd or Fogarty has a name for it.
 
@@
     \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
-  \caption{Comparison of the DM approximation and the full model when mutation is included.
-Even high mutation rate doesn't worsen the approximation, and the data points are close to the mathematical estimation (Kimura's).
-Error bars are 95\% confidence intervals, and are condensed (+- 0.01 probability and +-40 generations)
-  $5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis.
+  \caption{
+  \textbf{Robustness of DM approximations to inclusion of mutation.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high mutation rate.
+Markers for average across simulations, error bars for 95\% confidence intervals.
+  % and are condensed (+- 0.01 probability and +-40 generations) % what does that mean?
+  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis.
+% not clear enough.
   }	
+  % TODO
+  % see comments in previous figure
   \label{fig:hetro_mutation}
@@
 
+% YOAV HERE
 In \cref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models.
@@
 We again tried different variations of the parameters, changing only one of them at a time.
-In \cref{fig:ch_env_alpha_beta} we can see that $\alpha$ on it's own doesn't cause any deviation for the the estimation. $\beta$ however affects the results greatly.
+In \cref{fig:ch_env_alpha_beta} we can see that $\alpha$ on its own does not cause any deviation for the the estimation. $\beta$ however affects the results greatly.
 

### 2022-03-29 ms/PrestigeBias.tex
added todos for diffusion eq analysis results

@@
 
-\subsection*{Generalized Binomial Distribution}
+\subsection*{Generalized binomial distribution}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
@@
 
-\subsection*{Dirichlet-Multinomial Distribution}
+\subsection*{Dirichlet-Multinomial distribution}
 
@@
 First we relaxed our assumption of no mutation. % TODO what is the mutation parameters? e? I thought this was estimation error. does it only affect the bias or also the copying? we should discuss!
+% no mutation or no variation in mutation?
 To include mutation in the dichotomous trait model, it needs to be redefined, since in the original model it was based on the fact the traits are drawn from a continuous scale.
@@
   % see comments in previous figure
+  % maybe 50% CI looks better? the bars are too large to understand. maybe a wider y range? say from 0 to 0.02?
   \label{fig:hetro_mutation}
@@
 
-% YOAV HERE
+% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
 In \cref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models.
@@
   \label{fig:hetro_alpha}
+	% TODO
+	% see comments in previous figure
 \end{figure}
 
+% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
 In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead.
@@
 
-\subsection*{Fixation probability and time - binary model}
-\paragraph{Kimura's approximation:}
-After establishing a case in the favor of our DM approximation, we wanted to use it to examine the behavior of the population.
-Specifically, we wanted to analyze the influence of the indicator weight ($\alpha$) on the fixation probability and time to fixation of the favored phenotype in a binary model.
-For simplicity, we don't include mutation rate in the binary model approximations.
-Following \citet{durret}, we used our DM approximation of the model to find the effective population size.
-From \cref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Fixation probability and time}
+% I think this subsection should come before the numerical validation (prev subsection) because the numerical validation also presents Kimura's equation
+
+After finding that the DM distribution is a good approximation of the role-model choice process we turn our attention to the evolutionary dynamics.
+We focus on the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias, on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models.
+% References:
+% Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
+% Kimura, M. & Ohta, T. The Average Number of Generations until Fixation of a Mutant Gene in a Finite Population. Genetics 61, 763–71 (1969).
+% Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
+For simplicity, we do not include mutation in this analysis.
+As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?
+% $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?
+\\
+
+% TODO in the following, I would organize differently:
+% 1.  remark for E[x'-x] the "drift" (1st order) coefficient in a diffusion equation approximation
+% 2. result on effective selection coefficient
+% 3. remark for V[x'-x] the "diffusion" (2nd order) coefficient in a diffusion equation approximation
+% 4. result of effective population size
+% 5. result for fixation prob
+% 6. result for fixation time
+% 7. result for changing environment
 
 \begin{result}[Effective selection coefficient]
-$1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.
+$1-\beta(A)$ is equivalent to the selection coefficient $s$ in the diffusion-equation approximation of the a classic Wright-Fisher model that approximate the fixation probability and fixation time of an advantageous allele.
 \end{result}
@@
 \end{equation}
+\end{proof}
 
@@
 proving the second part of our preposition.
-\end{proof}
 

### 2022-03-30 ms/PrestigeBias.tex
fixes

--- 2022-03-28 ms/PrestigeBias.tex
@@
-\documentclass[12pt]{extarticle}
-\usepackage{geometry}
-\geometry{
-a4paper,
-total={170mm,257mm},
-left=20mm,
-top=20mm,
-headheight=12pt
-}
-
-\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
+\documentclass[11pt]{article}
+\usepackage[margin=1in]{geometry}          
 \usepackage{graphicx}
-\usepackage{amsmath, amssymb, amsthm}
+\usepackage{amsthm, amsmath, amssymb}
 \usepackage[font=small]{caption, subcaption}
@@
 \usepackage{float}
-\usepackage[unicode=true,colorlinks=true,urlcolor=Blue,citecolor=black,linkcolor=black]{hyperref}
 \usepackage{cleveref}
@@
 \usepackage{mathtools}
+\usepackage[displaymath, mathlines]{lineno}
+\usepackage{natbib}
 \usepackage[all]{nowidow}
@@
 \usepackage{pdfpages}
-\usepackage{authblk}
-
-% unbreakable dashes
-\usepackage[shortcuts]{extdash}
-% footnotes
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-
-% less space before sections 
-% \titlespacing*{<command>}{<left>}{<before-sep>}{<after-sep>}
-\usepackage{titlesec}
-\titlespacing*{\section}
-{0pt}{2ex plus 1ex minus .2ex}{2ex plus .2ex}
-\titlespacing*{\subsection}
-{0pt}{1ex plus 1ex minus .2ex}{1ex plus .2ex}
-\titlespacing*{\paragraph}
-{0pt}{1ex plus 1ex minus .2ex}{1ex plus .2ex}
-
-%SetFonts
-% newtxtext+newtxmath
-\usepackage{newtxtext} %loads helv for ss, txtt for tt
-\usepackage{amsmath}
-\usepackage[bigdelims]{newtxmath}
-\usepackage[T1]{fontenc}
-\usepackage{textcomp}
-%SetFonts
 
@@
 
-% Supplementary
-\newcommand{\beginsupplement}{%
-      	\setcounter{table}{0}
-        \renewcommand{\thetable}{S\arabic{table}}%
-        \setcounter{figure}{0}
-        \renewcommand{\thefigure}{S\arabic{figure}}%
+% math stuff
+\DeclareMathOperator*{\E}{{\rm I\kern-.3em E}}
+\let\vec\mathbf
+\newenvironment{conditions}
+  {\par\vspace{\abovedisplayskip}\noindent\begin{tabular}{>{$}l<{$} @{${}={}$} l}}
+  {\end{tabular}\par\vspace{\belowdisplayskip}}
+
+% title page stuff
+\author{
+	Saar Egozi
+	\and
+	Yoav Ram
 }
 
-% NatBib
-%\usepackage[super,comma]{natbib}
-\usepackage[round,colon,authoryear]{natbib}
-%\use-package[numbers,super,sort&compress]{natbib}
-\renewcommand{\bibsection}{}
-%\renewcommand{\bibfont}{\small}
+\begin{document}
 
-% math stuff
-\DeclareMathOperator*{\E}{{\rm I\kern-.3em E}}
-\newcommand*{\tr}{^\intercal}
-\let\vec\mathbf
-\newcommand{\matrx}[1]{{\left[ \stackrel{}{#1}\right]}}
-\newcommand{\diag}[1]{\mbox{diag}\matrx{#1}}
-\newcommand{\goesto}{\rightarrow}
-\newcommand{\dspfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2} }
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{remark}{Remark}
-\newtheorem{result}{Result}
-\renewcommand\qedsymbol{} % no square at end of proof
-\newcommand{\cl}{\mathbf{L}}
-\newcommand{\cj}{\mathbf{J}}
-\newcommand{\ci}{I}
+\begin{titlepage}
+\centering
 
-% title page stuff
-\title{Prestige as a Driving Force in Cultural Transmission}
+\vspace{4cm}
 
-\renewcommand\Affilfont{\small}
-\author[1]{Saar Egozi}
-\author[2,3,*]{Yoav Ram}
-\affil[1]{School of Computer Science, Reichman University, Herzliya 4610101, Israel}
-\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
-\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel}
-\affil[*]{Corresponding author: yoav@yoavram.com, ORCID 0000-0002-9653-4458}
+{\LARGE\bfseries Prestige as a Driving Force in Cultural Transmission}
 
-\date{\today}
+\vspace{2cm}
 
-\begin{document}
-\maketitle
+{\large\bfseries Saar Egozi}
 
-\begin{abstract}
-Copying role-models can be an efficient method for acquiring knowledge.
-A common bias when choosing a role-model to copy is success bias: copying whoever appears more successful.
-This bias depends on the performance of the role-model alone, with no other factors.
-We propose an additional bias that may be prevalent in cultural transmission: influence bias, in which role-model choice is affected by the number of individuals that have already copied each potential role-model.
-We combine success and influence bias together to a ``prestige bias'' and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
-We find analytic approximations to our stochastic model, facilitating further mathematical analysis and reducing the computational complexity of simulations.
+\vspace{1cm}
+
+{\large supervised by Dr. Yoav Ram}
+
+\vspace{2cm}
+
+\vfill
+
+{\large Efi Arazi School of Computer Science, Reichman University}
+
+\vspace{1cm}
+
+{\itshape \today}
+
+{\large saartk@gmail.com}
+\end{titlepage}
+
+\renewcommand\linenumberfont{\normalfont\small\sffamily}
+\linenumbers
+\modulolinenumbers[2]
+\setcounter{secnumdepth}{0}
+\tableofcontents
+
+\clearpage
+
+\section{Abstract}
+Copying role-models can be an efficient method of acquiring knowledge.
+Here, we study the effects of prestige as a cultural transmission bias in cultural-evolution model.
+A common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears more successful.
+This bias depends on the performance of the role-model alone, without other factors.
+We propose an additional bias that may be prevalent in cultural transmission: \textit{Influence bias}, which is evaluated by the number of individuals that have already copied a specific role-model.
+We combine these biases together to a \textit{prestige bias} and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations.
+We find analytic approximations to our model, facilitating further mathematical analysis and reducing the computational complexity of the simulations.
 We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
-We also find approximations to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resemble Kimura's classical formulas.
-These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size. % TODO reduce or increase?
-It also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
-Our model may provide a better description of human cultural transmission, 
+For a dichotomous cultural trait, we find  an approximation to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resembles Kimura's classical formulas.
+These approximations show that influence effectively reduces the population size. % TODO reduce or increase?
+We also find that influence accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
+Our model may provide a better description of how human cultural transmission, 
 especially in the last years where social networks are very popular. % TODO to discuss this last sentence
 Further work is needed to test if this model could predict various phenomena in human cultural evolution when extended with the effects of selection and innovation.
-\end{abstract}
-\pagebreak
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Introduction}
+\section{Introduction}
 
@@
 In cultural transmission, individuals transmit cultural traits (i.e., behavior, beliefs, norms) to one another, typically via learning and demonstrating \citep{transmissionVectorsBook}.
-Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations. % TODO reference
+Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted both verbally and by observations \citep{cultural_traits}.
 Although cultural transmission is most common in humans, it is also observed in other animals such as chimpanzees \citep{chimpsPrestige, chimpsCopy}.
@@
 Thus, cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
-Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring (e.g playing video games)\citep{transmissionVectorsBook,transmissionVectors}.
-% TODO did they suggest video games or did they have some other trait?
-not sure I want to mention video games...
+Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring. \citep{transmissionVectorsBook,transmissionVectors}
 
@@
 \paragraph{Success bias.}
-\citet{strategiesPaper} have conducted a tournament between learning strategies.
-Each strategy defines when individuals observe and copy from others, and when they engage in individual learning, in which an individual learns a cultural trait on his own.
+Believed to be a main bias in nature for choosing a role-model for copying \citep{evolution_of_cultural_evolution}
+\citet{strategiesPaper} have conducted a tournament between learning strategies based on that assumption.In their tournament, each strategy defines when individuals observe and copy from others, and when they engage in individual learning, in which an individual learns a cultural trait on his own.
 The best strategies had a high frequency of social learning relative to individual learning, even when the transmission error was almost 50\%.
@@
 it is not clear
-
-% TODO do we need the following paragraph? it doesn't say much, and the paragraph after it covers "different type of success evaluation", so what is this paragraph doing?
-%\citet{complexityPaper} define different types of transmission biases based on success.
-They define several types of role-model choice methods, all assuming that the copier correctly identifies the successful role-models.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Models and Methods}
+\section{Models and Methods}
 
@@
 
-\subsection*{Continuous trait}
+\subsection{Continuous trait}
 We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the indicator trait and omitting the indirect trait in order to reduce model complexity. 
@@
 
-\subsection*{Dichotomous trait}
+\subsection{Dichotomous trait}
 To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-\subsection*{Approximations}
+\section{Results}
+\subsection{Approximations}
 Our model is defined by two nested stochastic processes.
@@
 $\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
-\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the success weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
+\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if $\alpha$ is uniform for all role-models ($\alpha=\alpha_k$ for $k=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
 \end{enumerate}
@@
 
-\subsection*{Generalized Binomial Distribution}
+\subsection{Generalized Binomial Distribution Approximation}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
-\\
 
-\begin{result}[GBD approximation]
-The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$. 
-\end{result}
+\paragraph{Proposition.} The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$.
 
-\begin{proof}
-We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$. 
+\paragraph{Proof.} We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$.
 Using conditional probability and \cref{eq:recurrence},
@@
 %$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$. % TODO do you need this sentence?
-\end{proof}
 
-\begin{corollary}
-$\E[K_{N,j}] = N \cdot G_{1,j}$.
-\end{corollary}
-
-\begin{proof}
-\citet[eq.~(2.3)]{GBD} show that 
+\paragraph{Corollary 1.} $\E[K_{N,j}] = N \cdot G_{1,j}$.
+\paragraph{Proof.} \citet[eq.~(2.3)]{GBD} show that 
 $\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
@@
 $Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
-\end{proof}
 
-\begin{corollary}
-$\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
-\end{corollary}
-
-\begin{proof}
-The initial prestige of role-model $j$ based on \cref{eq:prestige} is
+\paragraph{Corollary 2: } $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
+\paragraph{Proof.} The initial prestige of role-model $j$ based on \cref{eq:prestige} is
 \begin{equation}\label{eq:initial_prob}
@@
 completing the proof.
-\end{proof}
 
@@
 
-% TODO what about a numerical validation for GBD?
-
-\subsection*{Dirichlet-Multinomial Distribution}
-
-\paragraph{P\'{o}lya urn model.}
-This stochastic process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors.
-When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same color.
+\subsection{Dirichlet-Multinomial Distribution Approximation}
+\paragraph{Reminder: \textit{Pólya urn model}}  is a stochastic process that is defined as such: 
+The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors.
+When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same colour.\\
 Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
-Let $S_{i,j}=1$ when drawing a $j$-colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is
-\begin{equation}\label{eq:polya}
+Let $S_{i,j}=1$ when drawing a $j$ colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is:
+\begin{equation}\label{polya}
 \begin{split}
-P(S_{i,j} = 1 \mid \vec{U_{i-1}}) = 
-\frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = 
-\frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}} = 
-\frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m} \;,
+P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\
+ & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
 \end{split}
 \end{equation}
-where $o_j$ is the initial number of balls of the color $j$ in the urn, and $w_{i,j}$ is the cumulative number of new balls that were added to the urn after $i$ draws of the color $j$.
-\\
+where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.
 
-\begin{result}[P{\'{o}}lya urn model]\label{result:polya}
-The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \textit{P\'{o}lya urn model} if both trait estimation error and success weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
-\end{result}
+\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
+\paragraph{Proof:} 
+We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
+Using \cref{eq:prestige} we get:
+\begin{equation}\label{eq:copier_choose}
+\begin{split}
+G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\
+&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\
+& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
+\end{split}
+\end{equation}
+We see that \cref{polya} and \cref{eq:copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
 
-\begin{proof} 
-Denote $\alpha'=\frac{\alpha}{1-\alpha}$ as the odds ratio between the weights of success and influence bias and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
-\begin{equation}\label{eq:copier_choose}
-G_{i,j} = 
-\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}
- =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N}\alpha'\beta(A'_m)} \;.
-\end{equation}
-Substituting $M=N$, $o_j = \alpha'\beta(A'_j)$, and $w_{i,j} = K_{i,j}$ in \cref{eq:polya} gives \cref{eq:copier_choose}, thus completing the proof.
-\end{proof}
+\paragraph{Corollary 1:}
+In their paper, \citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{Pólya urn model} will converge to the Dirichlet distribution as the number of draws approaches infinity, based on \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
+We therefore have an approximation for the relative "weight" or the proportion each role-model has when evaluated as a role-model.
+Drawing from a Multinomial distribution where the parameters are the modified weights gained from the Dirichlet distribution is viable for selecting the role-model for the next generation.
+We can therefore sample from a Dirichlet-Multinomial distribution to approximate how many copiers each of the role-models will have:
+$\vec{K_i} \sim DM(N,\vec{G_1})$.
 
-\citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
-We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
-Thus, choosing the role-models for all copiers is equivalent to drawing from a Multinomial distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
-\\
+\paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population.
+To support our proof, we tested our approximation empirically using computer simulations.
+To test our hypothesis, we used a \textit{goodness of fit} method known as \textit{Pearson's chi-squared test}.
+In this test, one can reject or accept the null hypothesis, which in our case is the hypothesis that the simulations results were drawn from a DM distribution.
 
-\begin{corollary}\label{cor:dirichlet}
-The number of copiers of each role-model follows a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \textit{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
-\end{corollary}
+To use this test, we ran many simulations of our original model, and used the mean distribution of copiers.
+This mean distribution is our observed distribution, and we tested it with the DM expected distribution, using said chi-squared test.
+We tested multiple variations of the trait weight parameter ($\alpha$).
 
-\paragraph{Numerical validation.}
-To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations.
-We executed many simulations of our original model to  % TODO exactly how many 
-compute an observed distribution of number of copiers from the average empirical distribution.
-To compare the observed distribution with the expected DM distribution, we use a Pearson's chi-squared test of goodness-of-fit to reject or accept the null hypothesis that the simulation results are drawn from a DM distribution.
+In all our tests, the p-value was \textbf{1}.
+This means that the probability to reject the null hypothesis is essentially nonexistent (the usual threshold for a p-value needed to reject $H_0$ is 0.05 or lower).
+In addition, we found out that for high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value 1.
+(less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
+For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100, which is still a relatively small amount.
+To verify our codes results, we also ran the test for different distributions, for example the uniform distribution (all role-models have exactly one copier).
 
-When testing multiple values of the bias weight parameter $\alpha$, the test p-value was 1, meaning means that the null hypothesis cannot be rejected
-For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
-For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
-When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required.
-% TODO did you test other distributions?
-% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
-% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?
+All these tests resulted in a p-value 0, which means we can likely reject $H_0$ for these distributions, as expected.
 
-\subsection*{Numeric comparisons} % TODO rename section
+Once we validated our proof for a single iteration of the model, we went on to more complex validations for the entire model.
+
+\subsection{Numeric comparisons}
 We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation.
@@
 
-\subsection*{Fixation probability and time - binary model}
+\subsection{Fixation probability and time - binary model}
 \paragraph{Kimura's approximation:}
@@
 
-\begin{result}[Effective selection coefficient]
-$1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.
-\end{result}
+\paragraph{Proposition:} $1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.
 
-\begin{proof}
-Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals.
+\paragraph{Proof:} Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals.
 Let $X$ be the number of individuals of type $\hat{A}$ so $x=X/N$.
@@
 where when substituting $1-\beta$ with $s$, we get the same result as \citet{durret} which is the desired result.
-\end{proof}
 
-\begin{result}[Effective population size]
-$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
-\end{result}
+\paragraph{Proposition:} $Ne=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
 
-\begin{proof}
-The variance of a DM distribution is:
+\paragraph{Proof:} The variance of a DM distribution is:
 \begin{equation}
@@
 
-Like Durrett, we'll use the zero order of the approximation when $\beta\approx1$,so:
+Like Durret, we'll use the zero order of the approximation when $\beta\approx1$,so:
 \begin{equation}
@@
 
-Again following Durrett we want to calculate:
+Again following Durret we want to calculate:
 \begin{equation}\label{eq:var_diff_durret}
@@
 
-\subsection*{Changing environment}
+\subsection{Changing environment}
 After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.
@@
 
-\section*{Discussion}
-\subsection*{summary}
+\section{Discussion}
+\subsection{summary}
 Cultural transmission is the phenomenon of which cultural elements, in the form of attitudes, values, beliefs, and behavioral patterns, are transmitted between individuals, typically via copying.
@@
 
-\subsection*{Prestige in the literature}
+\subsection{Prestige in the literature}
 So far we discussed prestige as a main bias in humans, and to some extent in non-human species.
@@
 
-\pagebreak
-
-\section*{References}
-\nolinenumbers
+\clearpage
 \bibliography{refs}
-%\bibliographystyle{agsm}
 \bibliographystyle{apalike}

### 2022-03-31 ms/PrestigeBias.tex

--- 2022-03-29 ms/PrestigeBias.tex
@@
 \usepackage{float}
-\usepackage[unicode=true,colorlinks=true,urlcolor=Blue,citecolor=black,linkcolor=black]{hyperref}
+\usepackage{varioref}
+\usepackage[unicode=true,colorlinks=true,urlcolor=blue,citecolor=black,linkcolor=black]{hyperref}
 \usepackage{cleveref}
@@
 We also find approximations to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resemble Kimura's classical formulas.
-These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size. % TODO reduce or increase?
+These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
 It also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
@@
 In cultural transmission, individuals transmit cultural traits (i.e., behavior, beliefs, norms) to one another, typically via learning and demonstrating \citep{transmissionVectorsBook}.
-Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations. % TODO reference
-Although cultural transmission is most common in humans, it is also observed in other animals such as chimpanzees \citep{chimpsPrestige, chimpsCopy}.
-% TODO but also birds, Cetacea (Whitehead, PNAS 2017)
+Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations \citep{cultural_traits}. 
+Although cultural transmission is most common in humans, it is also observed in other animals such as chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}.
 In elephants, \citet{elepahntsRepo} showed that once a matriarch is removed from the group, the group's survival instincts are inferior and that ``the possession of enhanced discriminatory abilities by the oldest individual [matriarch] in a group can influence the social knowledge of the group as a whole.''
 By playing audio recordings of African elephants, they showed that groups with a matriarch recognize and react better to hostile or friendly calls than groups without a matriarch.
-\citet{fliesPaper} showed that choice of oviposition site in fruit flies is culturally transmitted: inexperiences flies that spent some time with experienced flies chose the same type of oviposition site even without directly observing this behavior.
+\citet{fliesPaper} showed that choice of oviposition site in fruit flies is culturally transmitted: inexperienced flies that spent some time with experienced flies chose the same type of oviposition site even without directly observing this behavior.
 How the information is transmitted is still an open question, but it has been suggested that flies may use olfactory cues like other animals, such as rodents and bees.
@@
 Thus, cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
-Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring (e.g playing video games)\citep{transmissionVectorsBook,transmissionVectors}.
-% TODO did they suggest video games or did they have some other trait?
-not sure I want to mention video games...
+Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.
 
@@
 279]{evolutionBook}.
-% TODO we have an example of this in Dor's paper, in which cooperation can evolve due to horizontal transmission bias even when the benefit is zero:
-% 1. Cohen, D., Lewin-Epstein, O., Feldman, M. W. & Ram, Y. Non-vertical cultural transmission, assortment and the evolution of cooperation. Proc. R. Soc. B Biol. Sci. 288, 20203162 (2021).
+\citet{cooperation} show that cooperative behavior can evolve in an individual due to horizontal transmission bias even when there is no benefit to it, or when it benefits its competitors.
 
@@
 The best strategies had a high frequency of social learning relative to individual learning, even when the transmission error was almost 50\%.
-It is important to note that all of the strategies included some frequency of individual learning.
-%The authors suggested that success-biased social transmission contribute more to the general success of the population than individual learning.
-% TODO how is the last sentence related to the results of the tournament?
-did the best strategies use success-bias?
-it is not clear
-
-% TODO do we need the following paragraph? it doesn't say much, and the paragraph after it covers "different type of success evaluation", so what is this paragraph doing?
-%\citet{complexityPaper} define different types of transmission biases based on success.
-They define several types of role-model choice methods, all assuming that the copier correctly identifies the successful role-models.
+From these results we understand that all the winning strategies were mostly based on success biased social learning, meaning it contributed more to the general success of the population than individual learning.
+However, all winning strategies included individual learning to some degree, implying that success-biased learning alone isn't the best way to advance, even when success is measured accurately.
 
@@
 Frequency bias could be negative, i.e., non-conformist bias. 
-Conformity and non-conformity are well-known biases in cultural transmission \citep{conformism}, and its effect on cultural evolution have been studied with both models (Denton 2020 PNAS; Denton TPB 2021) and experiments \citet{negativeFrequency}
-% TODO references for the above
-% 1. Denton, K. K., Ram, Y. & Feldman, M. W. Conformity and content-biased cultural transmission in the evolution of altruism. Theor. Popul. Biol. (2021) doi:10.1016/j.tpb.2021.10.004.
-% 2. Denton, K. K., Ram, Y., Liberman, U. & Feldman, M. W. Cultural evolution of conformity and anticonformity. Proc. Natl. Acad. Sci. U. S. A. 202004102 (2020) doi:10.1073/pnas.2004102117.
+Conformity and non-conformity are well-known biases in cultural transmission \citep{conformism}, and its effect on cultural evolution have been studied with both models \citep{conformity,anticonformity} and experiments \citep{negativeFrequency}.
 
@@
 On the other hand, \citet{fijian_social_bias} suggest that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
-Prestige is often mentioned in the cultural-evolution literature, but seldom modeled, although \citet{evolutionBook} have modeled prestige via success bias. % TODO is this correct?
+Prestige is often mentioned in the cultural-evolution literature, but seldom modeled.
 
 \paragraph{Influence bias.}
-Today, social media provides an easy way to estimate the influence individuals have over others, and therefore may have a major effect on human decision making.
-For example, the number of "followers" a person has on social networks such as \textit{Facebook} or \textit{Instagram} may significantly affect how his beliefs are perceived by the population.
-% TODO this must have some reference in the literature.
+Today, social media provides an easy way to estimate the influence individuals have over others, and therefore may have an effect on decision making.
+Online social networks such as \textit{Facebook} or \textit{Instagram} are known to affect the social influence of individuals \citep{social_influence,influence_analysis,social_media}.
+For example, specific marketing practices were invented following this realization \citep{facebook_marketing},
 Here we propose an indirect bias that we call \textit{influence bias}, in which the choice of a role-model depends on the the choices made by other individuals that have already chosen a role-model. 
-This is a context bias, % TODO right?
- which depends on the role-model rather than the trait, in contrast to frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models. 
+This bias depends on the state of a role-model rather than a trait, in contrast to frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models.
 We define a model for prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
@@
 
-%A \textit{Wright–Fisher model} describes an evolutionary process with random genetic.
-This model assumes non-overlapping generations such that the entire population is replaced in every generation by the offspring population.
-The parent of each offspring is independently drawn at random from the parental generation.
-%A \textit{Moran model} also describes an evolutionary process with drift, but assumes overlapping generations.
-At each time step, one individual is chosen to reproduce and one individual is chosen to die.
-
 We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
-We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python with NumPy and Matplotlib. % TODO references: 
-%- Van Rossum, G. & others. Python Programming Language. in USENIX Annual Technical Conference (2007).
-%- van der Walt, S., Colbert, S. C. & Varoquaux, G. The NumPy Array: A Structure for Efficient Numerical Computation. Comput. Sci. Eng. 13, 22–30 (2011). 
-%- Hunter, J. D. Matplotlib: A 2D Graphics Environment. Comput. Sci. Eng. 9, 90–95 (2007).
-Source code is available at % TODO GitHub link; currently it is private but will be public when paper is accepted.
+We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}.
+
+Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias/blob/master/notebooks/Influence_model.ipynb}{this notebook}.
 
@@
 Here, the bias weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of success and influence in his prestige, the indicator value of role-model $j$ estimates by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeIndicator}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
-%\begin{equation}
-%W_i = \sum_{j=1}^N{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}.
-%\end{equation}
 
@@
 Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
-% based on \cref{eq:copier_choose} is % TODO you refer an equation that did not yet appear!
 \begin{equation}\label{eq:binary-model}
@@
 \end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model.
-% TODO what is alpha' ?
+where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the indicator trait $\alpha'= \frac{\alpha}{1-\alpha}$.
+
+We prove this equation later, based on the proof of the Dirichlet-Multinomial approximation.
+
 Initially, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. The rest of the details follow the continuous trait model.
@@
 \end{enumerate}
-\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$). 
+\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
 Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
 $\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
-Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform. % TODO correct? anything else need to be assumed?
+Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
 \end{enumerate}
@@
 \Cref{recursive} is equivalent to eq.~(2.1) by \citet{GBD}, which completes the proof.
-%$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$. % TODO do you need this sentence?
 \end{proof}
@@
 
+\paragraph{Numerical validation.}
+To be added
 % TODO what about a numerical validation for GBD?
@@
 
-When testing multiple values of the bias weight parameter $\alpha$, the test p-value was 1, meaning means that the null hypothesis cannot be rejected
+When testing multiple values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
+
 For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)

### 2022-04-03 ms/PrestigeBias.tex
update

@@
 To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations.
-We executed many simulations of our original model to  % TODO exactly how many 
-compute an observed distribution of number of copiers from the average empirical distribution.
+We executed varying amount of simulations of our original model to compute an observed distribution of number of copiers from the average empirical distribution.The number of simulation required depended on the parameters used.
 To compare the observed distribution with the expected DM distribution, we use a Pearson's chi-squared test of goodness-of-fit to reject or accept the null hypothesis that the simulation results are drawn from a DM distribution.
@@
 
-\subsection*{Numeric comparisons} % TODO rename section
+\subsection*{Model testing}
 
@@
 Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions
-First we relaxed our assumption of no mutation. % TODO what is the mutation parameters? e? I thought this was estimation error. does it only affect the bias or also the copying? we should discuss!
-% no mutation or no variation in mutation?
-To include mutation in the dichotomous trait model, it needs to be redefined, since in the original model it was based on the fact the traits are drawn from a continuous scale.
-In the dichotomous trait model mutation will be manifested as an error when evaluating the bias itself.
-This is easily done by using a heterogeneous $J$ parameter, which controls the strength of the success bias in \cref{eq:success_bias}.
-% NOT CLEAR AT ALL - do you redefine now the model?
-or is this leftover from before???
-% I dont like that we call this mutation, we should call it copying error or something else, see if Boyd or Fogarty has a name for it.
+First we relaxed our assumption of no estimation error $e$.
+Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
+
+In the dichotomous model the estimation error will be added by using heterogeneous $J$ parameter, which controls the strength of the bias of \cref{eq:success_bias}.
 

### 2022-04-03 ms/PrestigeBias.tex
update

@@
   \caption{
-  \textbf{Robustness of DM approximations to inclusion of mutation.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high mutation rate.
+  \textbf{Robustness of DM approximations to inclusion of estimation error.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high estimation error rate.
 Markers for average across simulations, error bars for 95\% confidence intervals.
   % and are condensed (+- 0.01 probability and +-40 generations) % what does that mean?
-  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis.
+  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; $J\sim N(1,x^2)$ where $x$ is the estimation error scale in the x-axis.
 % not clear enough.
@@
   % maybe 50% CI looks better? the bars are too large to understand. maybe a wider y range? say from 0 to 0.02?
-  \label{fig:hetro_mutation}
+  \label{fig:hetro_error}
 \end{figure}
@@
 % TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
-In \cref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models.
-When mutation is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
+In \cref{fig:hetro_error} we see the comparison when heterogeneous estimation error is applied to both models.
+When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
 We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).
@@
 In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead.
-Similar to the mutation comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale.
+Similar to the estimation error comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale.
 We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.
@@
 \subsection*{Fixation probability and time}
-% I think this subsection should come before the numerical validation (prev subsection) because the numerical validation also presents Kimura's equation
 
@@
 % Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
-For simplicity, we do not include mutation in this analysis.
+For simplicity, we do not include estimation error in this analysis.
 As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?

### 2022-04-04 ms/PrestigeBias.tex
update

@@
 where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
-Using \cref{eq:denominator} we get, % TODO something is missing here? how did you get E[KNj] to relate to the previous two equations?
+Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
 \begin{equation}
@@
 
-\paragraph{Numerical validation.}
-To be added
 % TODO what about a numerical validation for GBD?
+% ANS - The results of this approximation are contained in the next DM approximation.
+In here we find the expected number of copiers for a single role-model, and in the DM we find that (and get the same results of course) and more.
+I can make the Numerical Validation a subsection and say it's for both.
 
@@
 % TODO did you test other distributions?
+% ANS - No, mainly because I didn't know what paremeters to choose, we should discuss
+
 % TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
+% ANS - observed vs expected of what? Make a histogram of number of copiers per role-model? just the top role-models?
+
 % TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?
@@
   \textbf{Number of simulations needed to get a good approximation.}
-  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. % 1000 simulations of the model or of DM ??
+  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. 
   Markers for average value across simulations, error bars for 95\% confidence interval.
@@
   % TODO
-  % remove legend
-  % change y labels: "Fixation probability" "Fixation time"
-  % change x label: "Number of simulations"
   % Kimura - black solid line

### 2022-04-04 ms/PrestigeBias.tex
results validation; figures; discussion

--- 2022-04-03 ms/PrestigeBias.tex
@@
 We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
-
-Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias/blob/master/notebooks/Influence_model.ipynb}{this notebook}.
+Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
 
@@
 Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$.
-We found two approximations such processes, summarized here and explained in detail below:
+We found two such approximations, summarized here and explained in detail below:
 \begin{enumerate}
@@
 \paragraph{Numerical validation.}
-To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations.
-We executed varying amount of simulations of our original model to compute an observed distribution of number of copiers from the average empirical distribution.The number of simulation required depended on the parameters used.
-To compare the observed distribution with the expected DM distribution, we use a Pearson's chi-squared test of goodness-of-fit to reject or accept the null hypothesis that the simulation results are drawn from a DM distribution.
-
-When testing multiple values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
-
-For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
+To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
+First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
+We then compared this observed distribution with the expected theoretical DM distribution using Pearson's chi-squared test of goodness-of-fit.
+Thus, we can reject or accept the null hypothesis that simulation results are effectively drawn from a DM distribution.
+
+Examining variable values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
+For high $\alpha$ values (above 0.5), very few simulations were needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$).
 For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%
+Next, we examined the fixation probability and fixation time of an advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
+We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
+Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions.
+First, we relaxed our assumption of no estimation error $e$.
+Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$). 
+%In the dichotomous model the estimation error will be added by using heterogeneous $J$ parameter, which controls the strength of the bias of \cref{eq:success_bias}. % TODO do we need this sentence?
+When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
+Even when the standard deviation is $0.1$, the fixation probability and time is similar~(\cref{fig:hetro_error}). 
+We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
+We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(X,X)$.
+% TODO replace X and X with relevant symbols
+We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\cref{fig:hetro_alpha}).
+
 \begin{figure}[h]
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{Model testing}
-
-Here we examine the difference between the dichotomous trait model defined in \cref{eq:binary-model} and the Dirichlet-Multinomial approximation we presented in \cref{cor:dirichlet}.
-We focus on the fixation probability and fixation time of the advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$.
-
-First, we find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1000$ (\Cref{fig:num_sims}).
-Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions
-First we relaxed our assumption of no estimation error $e$.
-Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
-
-In the dichotomous model the estimation error will be added by using heterogeneous $J$ parameter, which controls the strength of the bias of \cref{eq:success_bias}.
 
@@
 
-% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
-In \cref{fig:hetro_error} we see the comparison when heterogeneous estimation error is applied to both models.
-When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
-We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).
-
 \begin{figure}
     \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
-  \caption{Comparison of the DM approximation and the full model when success weight is heterogeneous.
+  \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
    High success weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it).
@@
 
-% TODO I suggest you incorporate this text to the figure caption and then we can just replace this with a sentence about how well the approximation is robust to assumptions with reference to figure.
-In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead.
-Similar to the estimation error comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale.
-We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-After finding that the DM distribution is a good approximation of the role-model choice process we turn our attention to the evolutionary dynamics.
-We focus on the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias, on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models.
-% References:
+After finding that the DM distribution is a good approximation of the (within-generations) role-model choice process, we turn our attention to the (between-generations) evolutionary dynamics.
+We focus on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models. % References: 
 % Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
@@
 % Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
+We are mainly interested in the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias.
 For simplicity, we do not include estimation error in this analysis.
@@
 % $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?
-\\
 
@@
 % 7. result for changing environment
+% so I didn't read the rest of the results very carefully, waiting for you to think about the re-arrangement suggestion first.
 
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
   \begin{center}
+    %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
   \begin{subfigure}[a]{0.49\linewidth}
@@
   \caption{Comparison of the DM approximation and the WF model for different values of the effective population size.
-The approximation seems very good, and is also condensed around the mathematical equation expectancy.
-Error bars are 95\% confidence intervals.
-  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
-  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
+  Error bars show mean and 95\% confidence intervals.
+  Effective population, $N_e=\alpha N + (1-\alpha)$.
+  $5,000$ simulations per data point; Population size, $N=1,000$; $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
   \label{fig:var_alpha}
+  % TODO
+  % - better x and y label, as noted above
+  % - in legend, replace "kimura" with "Approx."
+  % - in legend, remove "=2s"
+  % - change approximation color, it is too similar to WF simulations
+  % - make the horizontal line black?
+  % - caption should start with bold sentence summarizing the figure. 
+  % - in caption add description of each parameter (as I did for N)
+  %
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h]
+  %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
   \begin{center}
@@
   \end{center}
-  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model.
-The approximation seems good, and is also condensed around the mathematical equation expectancy.
-Error bars are 95\% confidence intervals.
+  % TODO 
+  % - see previous figure
+  % - consider making the error bars smaller with more simulations or narrower CI (50%?)
+  % - consider using plt.xscale('log')
+  % - maybe you can merge this figure with the figure?
+  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. Error bars are 95\% confidence intervals.
   Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
@@
 
-\subsection*{Changing environment}
+\paragraph{Changing environment.}
 After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.
@@
 
-We wanted again to validate our results, using simulations.
-This time, the number of parameters increased: in addition to $\alpha,\beta$, there are also $k,l$ as model parameters.
-
-We again tried different variations of the parameters, changing only one of them at a time.
-In \cref{fig:ch_env_alpha_beta} we can see that $\alpha$ on its own does not cause any deviation for the the estimation. $\beta$ however affects the results greatly.
-
-\begin{figure}[t]
+\begin{figure}[h]
   \begin{center}
-  \begin{subfigure}[a]{0.49\linewidth}
-  \caption{success bias/selection coefficient is: $1-\beta=s=0.005$}
+  %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
+  \begin{subfigure}{0.49\linewidth}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
    \end{subfigure}
-   \begin{subfigure}[a]{0.49\linewidth}
-   \caption{success weight is: $\alpha=0.1$}
+   \begin{subfigure}{0.49\linewidth}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
@@
 This is expected because Kimura's approximation are only viable for low selection coefficient values.
-  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$.}
+  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success weight is: $\alpha=0.1$. 
+  }
+  % TODO 
+  % see previous figures..
+  % not sure you need the green curve in the left panel
+  % the right panel might be better with yscale('log')? or xscale('log')? right now it is hard to see that the blue even changes...
+  % 
   \label{fig:ch_env_alpha_beta}
@@
 
-We plotted along the modified estimation the original Kimura's estimation, as a limiter.
+We validate our results using simulations.
+We find that $\alpha$ does not have a significant effect on the approximations (\cref{fig:ch_env_alpha_beta}).
+However, $\beta$ does. 
+We plotted along the modified estimation the original Kimura's estimation, as a limiter. % TODO rephrase, this sentence is not clear at all
 We suspect that when $\beta$ is too large, there won't be many cycles in the simulations.
-This might happen if either the population reaches a high frequency of the ideal trait after only a few cycles, or it get extinct very quickly, because the advantage it had in the $k$ generations wasn't sufficient, and the same $s$ becomes a greater disadvantage when the environment changes, resulting in a fast extinction.
-
-In the larger values of $beta$ we even see a deviation from the original estimation environment, but it's to be expected, because Kimura's equations are only viable for small $s$ values.
-
-We then also tried changing the composition of the cycle, by keeping a constant $n=40$, but changing $k,l$ accordingly.
+This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or it get extinct very quickly, % TODO what gets extinct?
+what does "it" refers to?
+ because the advantage it had in the $k$ generations wasn't sufficient, and the same $s$ becomes a greater disadvantage when the environment changes, resulting in fast extinction.
+% TODO read and rephrase.
+For lower % TODO this was "higher" but should be "lower" right?
+values of $\beta$ we see a deviation from the original estimation environment, % TODO what is "estimation environment"?
+but it's to be expected, because Kimura's equations weak fitness (i.e., low selection coefficients, $s$).
 
@@
   \end{center}
-  \caption{Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle.
-When $k<l$ the approximation is good.
-When $k>l$, the approximation and the simulations are both very close to the constant environment approximation.
+  %TODO add panel labels (a) and (b) on figures corner.
+  % see previous figures todos
+  % move legend to upper left? it is currently hiding something
+  \caption{Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle. % TODO reminder what k and l are.
+   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
   $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
@@
 
-In \cref{fig:ch_env_k_l} we see that the larger $k$ relative to $l$, the closer the modified equation is to the original estimation of the constant environment. 
-When using higher values of $n$, the simulation results doesn't fit the equation result as with lower values.
-This is due to the fact that our proof, and therefore our equation is more accurate when more cycles occur.
-When $n$ is high, there will be less cycles, and the simulations will get closer to the constant environment equation.
-
+We also examined the effect of different choices of $k$ and $l$ while keeping a constant total cycle length, $n=k+l=40$.
+We found that larger $k$-to-$l$ ratio increases the agreement between the modified equation and the original estimation of the constant environment. % "modified....environment" unclear.
+When using higher values of $n$, the agreement between the approximation and simulation results is weaker.
+This is because our approximation is more precise when more cycles occur.
+When $n$ is high, there will be less cycles, % TODO why higher n gives less cycles?
+and the simulations will get closer to the constant environment equation.
+
+% TODO I think you can do a better job summarizing the results - does the approximation work? when doesn't it work? why?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discussion}
-\subsection*{summary}
-Cultural transmission is the phenomenon of which cultural elements, in the form of attitudes, values, beliefs, and behavioral patterns, are transmitted between individuals, typically via copying.
-Some cultural traits can be more likely to be copied by others, regardless of their frequency in the population.  
-Such transmission biases are common in cultural transmission processes. 
-Many models are based on the assumption that success can be correctly identified, and easily copied.
-Here we assume that success isn't correctly identified, therefore individuals may use other indicators to try and estimate the success of potential role-models.
-We believe, as \citet{complexityPaper} suggest, that \textit{prestige biases} are more common in nature than success biases, since estimating success accurately is harder.
-\textbf{We investigated the effects of prestige on a population:} we studied the behavior of an invading trait, analyzed its dynamics mathematically, and extended the basic constant environment to a changing one.
-We believe prestige is composed of two main components: a trait that indicates success (but doesn't guarantee it), and the influence the individual already has on others, i.e number of individuals already chose him as a role-model.
-We suggest a model for \textit{prestige bias}, inspired by the model \citet{evolutionBook} have suggested, and added the \textit{influence bias} to it.
-\textbf{We approximated our models using various distributions, and compared them to the original model using simulations.}
-We showed that a \textit{Rich getting richer} type of model can be approximated well by the general binomial distribution and the dirichlet multinomial distribution.
-We experimented with constant and changing environment in our model, and created a variation of a binary model for easier mathematical and computational analysis.
-We believe that in this era of social media it is easy to estimate one's influence over others.
-It is therefore crucial to model the cultural biases more realistically than success bias based model, and we believe including influence is crucial for that purpose.\\
-\textbf{With a more realistic model of a common cultural transmission bias, we may be able to better understand decision-making processes in humans, including life-changing choices such as occupation or a life partner.}
-Our model can be expanded in multiple ways: observing the effects of different bias functions, including errors in estimating the influence, combining factors of cost when copying from an influential role model (not all could afford to copy from the most popular role-model), and analyzing the differences when including several optimal values for the indicator trait (multiple preference traits in the population).
-
-\subsection*{Prestige in the literature}
-So far we discussed prestige as a main bias in humans, and to some extent in non-human species.
-Here we further base our claims and present additional appearances of prestige in nature and in the literature.
-\\
-
-\citet{animal_leadership} describe a manifestation of prestige in the form of leadership in animals.
-According to them, there are two main approaches to decision makings of groups in nature: leadership and consensus.
-Prey leaders would lead the pact when traveling, while other animal group leaders will decide on a nesting site or foraging patches.
-They found out that leadership is observed mostly when there is a profound social network in the group, and when there are individuals that present leadership behavior.
-Leaders would usually be high ranking members in the group, such as elders, individuals with many kin relations, or posses other dominant traits.
-When no individual posses such traits, or when the social network is lacking, a consensus is more likely to occur.
-When a leader is present, they will have greater selection costs, such as higher risk for predation, being poisoned by unknown experimental patch, but also greater benefits.
-For example, given the route to the foraging site was successful, the leader and his closest followers would gain most of the food, unlike in a consensus, where the food would be shared more equally.
-It appears leaders appear in simple organisms as well, like fish.
-In these organisms however, the leader would usually be the hungriest or the weakest, while the rest would prefer to follow, minimizing their costs.
-In baboons however, \citet{animal_leadership} describe many benefits for the closest associates of the dominant male, such as protection from predators.
-This is an instance of sexual-selection, where the leader, whose survival chances are lower, gains more sexual partners due to the benefits.
-("The greater the risk, the greater the reward")
-What they describe could be the origins of what we know today as prestige.
-In their paper, they show that in nature, when survival is the main concern at all times, the leaders wouldn't be chosen due to their superior abilities, but because they have the least to lose.
-When in said position of leadership, there are greater risks, but greater rewards to come with it.
-In humans, leadership also has its perks and costs.
-Leaders can make decisions that would benefit them and their closest followers the most, while still maintaining group cohesion.
-However, wrong decision making that would harm the group could result in harm (media, social status, even violent behavior of subjects on certain cases).
-In our society it is less common to worry about mere survival, and so the prestigious positions, even though are not without risks and costs, are not as dangerous as for animals in nature.
+\paragraph{Summary.}
+During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
+Some cultural traits or cultural role-models may be more likely to be copied due to transmission biases. 
+A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be correctly identified.
+However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful by some other indicator.
+
+Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias, which included both success and influence biases, where the latter is a bias towards role-models with many copiers.
+We found approximations for the role-model choice process: the generalized binomial distribution that approximates the number of copiers of a single role-model, and the Dirichlet-Multinomial distribution that approximates the distribution of copiers in the entire population in a \textit{rich-getting-richer} type of process.
+We then studied the effects of prestige bias on the fixation probability and time of an invading advantageous cultural phenotype in both a constant and a changing environment.
+% TODO what did we find?
+
+\paragraph{Prestige in the literature.}
+
+According to \citet{animal_leadership}, there are two main approaches to group decision-making in nature: leadership and consensus.
+Leaders may lead the group when traveling, decide on a nesting site, or choose foraging patches.
+They found that leadership is mostly observed when there is a profound social network in the group, % TODO profound sounds weird here.
+what do you mean by it?
+and when there are individuals that present leadership behavior.
+Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
+When no individual posseses such traits, or when the social network is lacking, % TODO lacking what?
+decisions are more likely to be made by consensus.
+Leader may carry selection costs, e.g. due to higher predation risk, poisoning when exploring new foraging patches.
+In some cases, %e.g. fish, % TODO ref for fish? otherwise don't mention fish
+ the leader may be the hungriest or the weakest individual, while the others would prefer to follow the leader and minimizing their risks and costs.
+However, leadership may also carry selection benefits.
+For example, given the route to the foraging site was successful, the leader and his closest followers would gain most or the best of the food, whereas in consensus decision making, the food would be shared more equally.
+Or, sexual selection may also provide a selection benefit advantage to leaders, who might gain more sexual partners due to their leadership of the group.
+\citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators.
+They show that leaders wouldn't be chosen due to their superior abilities, but because they have the least to lose. % TODO are you sure? this is in baboons?
+
+In humans, leadership also has its costs and benefits.
+Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion.
+However, wrong decision making that harms the group could result in harm.
+In modern society it is less common to worry about mere survival, and so the prestigious positions, even though they are not without risks and costs, are not as dangerous as for animals in nature.
+% TODO reference?
+I'm not sure this is correct
 This may be the reason humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them.
-This is in complete contrast to animals, where the weakest/hungriest is driven to lead, compared to humans where leadership positions are mostly competitive.\\
+% you give two reasons - "this may be the reason" and "as they may reap..." I think the latter is more correct.
+also I think it is personality and family driven, to an extent.
+This is in complete contrast to animals, where the weakest/hungriest is driven to lead, compared to humans where leadership positions are mostly competitive. % TODO I'm not sure, let's discuss!
 
@@
 \citet{dual_leadership} suggest a way to solve said contradiction by defining two types of leaderships: prestige-based and dominance-based.
-They present classical views of leaderships by Confucius and Machiavelli. Confucius views leaders as role models who exercise influence through possessing superior knowledge, skills,
-and (outstanding) personal qualities.
-This description is very similar to our indicator trait.
-By contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment.
+They present classical views of leaderships by Confucius and Machiavelli. Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills,
+and (outstanding) personal qualities. This description is very similar to success bias in our model. % TODO I changed the end of the sentence, is it ok?
+By contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence.
 They say that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view into the complex and dynamic processes of leadership. 
-
-Our current model doesn't reflect the model described in this article, but several adjustments could be made in order to match it.
-If we assume there's a correlation between trait value to a type of leadership (so in our binary model, one trait would be of prestige, and the other of dominance) we can implement their suggested model.
-For that we would need to add cost-benefit parameters, so the ones choosing prestige will be rewarded, but pay more, while the ones choosing dominance would pay less, but gain less benefits.
-It could be interesting to see the dynamics and relations between our model parameters and these cost-benefit parameters.\\
-
+Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style.
+This would require assuming some costs and benefits so that prestige has higher  rewards but greater costs, while dominance has lower rewards and lower costs.
+% TODO why?
+The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
+
+% YOAV Here
 \citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige based and dominance based leadership types.
@@
 It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
-\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions and results, is consistent with ours.\\
+\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions and results, is consistent with ours.
 
 So far we presented the theory behind prestige, and it's appearance in nature. The following will show the appearances of prestige biases in humans, and in recent times.
-
 \citet{prestige_cultural_learning}, for example, tested the existence of prestige in young children.
@@
 It lead \citet{prestige_cultural_learning} to believe that when the trait is costly to learn individually, prestige will have a higher effect.
-It would be interesting to include costs in our model to try and observe these effects and their dynamics in the simulations of a larger population than this study.\\
+It would be interesting to include costs in our model to try and observe these effects and their dynamics in the simulations of a larger population than this study.
 
@@
 \end{quote}
-We see here support for both our indicator trait and our influence bias in their data.\\
+We see here support for both our indicator trait and our influence bias in their data.
 
@@
 Simply put, they found that the advance in technology and research was in accordance with the prestige rankings.
-This means that there may be very important practices that are neglected due to the prestige bias.\\
+This means that there may be very important practices that are neglected due to the prestige bias.
 
@@
 They also suggest a way to use this phenomena to change existing traditions in a population.
-It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.\\
+It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.
 
@@
 \citet{collective_brains} offer a take on prestige as a factor of human physical evolution directly.
-They present a concept called \textit{cultural brains} - brains that evolved primarily for the acquisition of adaptive knowledge.
+They present a concept called \textit{cultural brains} | brains that evolved primarily for the acquisition of adaptive knowledge.
 They build on the hypothesis of \citet{social_brains} that shows that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
@@
 
-\pagebreak
-
+\paragraph{Further work.} 
+Our model can be expanded in various ways: observing the effects of different bias functions, % TODO unclear
+including errors when estimating influence or costs when copying from an influential role-model, and inclusion of multiple, rather than a single, optimal phenotype.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Acknowledgements
+{\small
+\section*{Acknowledgements}
+We thank Marcus Feldman, Martin Pontz, and Tal Simon for discussions and comments.
+This work was supported in part by 
+the Israel Science Foundation (YR 552/19),
+Minerva Stiftung Center for Lab Evolution (YR),
+and 
+John Templeton Foundation (YR 61809).
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{References}

### 2022-04-04 ms/PrestigeBias.tex
update

@@
 We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}.
+
 Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
@@
 \end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the indicator trait $\alpha'= \frac{\alpha}{1-\alpha}$.
+where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.
 
@@
 Examining variable values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
-For high $\alpha$ values (above 0.5), very few simulations were needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$).
+For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
 For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
@@
 Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
-%In the dichotomous model the estimation error will be added by using heterogeneous $J$ parameter, which controls the strength of the bias of \cref{eq:success_bias}. % TODO do we need this sentence?
 When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
@@
    \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   High success weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it).
+   High bias weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it).
 Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
@@
 After finding that the DM distribution is a good approximation of the (within-generations) role-model choice process, we turn our attention to the (between-generations) evolutionary dynamics.
-We focus on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models. % References: 
-% Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
-% Kimura, M. & Ohta, T. The Average Number of Generations until Fixation of a Mutant Gene in a Finite Population. Genetics 61, 763–71 (1969).
-% Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
+We focus on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models \citep{kimura,kimura_average,otto_fixation}.
+
 We are mainly interested in the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias.
 For simplicity, we do not include estimation error in this analysis.
-As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?
-% $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?
+As shown above, transmission in our model is approximately DM distributed with the parameters $\sim DM(\alpha'X,(N-X)\alpha'\beta(A))$ based on \cref{cor:dirichlet} and \cref{eq:copier_choose}.
 
@@
 
-In our model, $\alpha'$ is the odds ratio of a parameter we called "indicator weight", denoted in our model as $\alpha$, so:
+In our model, $\alpha'$ is the odds ratio of a parameter we called "bias weight", denoted in our model as $\alpha$, so:
 \begin{equation}\label{eq:success_ratio}
@@
 \begin{figure}[h]
+%TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
   \begin{center}
-    %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
   \begin{subfigure}[a]{0.49\linewidth}
@@
   $5,000$ simulations per data point; Population size, $N=1,000$; $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
-  \label{fig:var_alpha}
   % TODO
@@
   % - in caption add description of each parameter (as I did for N)
-  %
+  \label{fig:var_alpha}
 \end{figure}
@@
 \begin{figure}[h]
-  %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
   \begin{center}
@@
   \begin{center}
+  \begin{subfigure}[a]{0.49\linewidth}
   %TODO remove the (a) and (b) from the latex and put them on the figure 	itself (top left corenr).
-  \begin{subfigure}{0.49\linewidth}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
    \end{subfigure}
-   \begin{subfigure}{0.49\linewidth}
+   \begin{subfigure}[a]{0.49\linewidth}
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
@@
 This is expected because Kimura's approximation are only viable for low selection coefficient values.
-  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success weight is: $\alpha=0.1$. 
+  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} bias weight is: $\alpha=0.1$. 
   }
-  % TODO 
+   %TODO 
   % see previous figures..
   % not sure you need the green curve in the left panel
+  % ANS - to show it's not a valid option to use?
   % the right panel might be better with yscale('log')? or xscale('log')? right now it is hard to see that the blue even changes...
-  % 
   \label{fig:ch_env_alpha_beta}
@@
 However, $\beta$ does.
-We plotted along the modified estimation the original Kimura's estimation, as a limiter. % TODO rephrase, this sentence is not clear at all
+
 We suspect that when $\beta$ is too large, there won't be many cycles in the simulations.
-This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or it get extinct very quickly, % TODO what gets extinct?
-what does "it" refers to?
- because the advantage it had in the $k$ generations wasn't sufficient, and the same $s$ becomes a greater disadvantage when the environment changes, resulting in fast extinction.
-% TODO read and rephrase.
-For lower % TODO this was "higher" but should be "lower" right?
-values of $\beta$ we see a deviation from the original estimation environment, % TODO what is "estimation environment"?
-but it's to be expected, because Kimura's equations weak fitness (i.e., low selection coefficients, $s$).
-
-\begin{figure}[t]
+This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or the fitter phenotype get extinct very quickly.
+For the very high $\beta$ values (0.35 and above), the fixation probability exceeds even the constant environment approximation (which is the upper limit), but it's to be expected, because Kimura's equations are only appropriate for weak fitness (i.e., low selection coefficients, $s$).
+
+\begin{figure}[h]
   \begin{center}
@@
   % move legend to upper left? it is currently hiding something
-  \caption{Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle. % TODO reminder what k and l are.
+  \caption{Model simulations compared with both the constant environment and the changing environment equations for different values of $k,l$, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
    When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
-  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
+ We ran $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
   \label{fig:ch_env_k_l}
@@
 We also examined the effect of different choices of $k$ and $l$ while keeping a constant total cycle length, $n=k+l=40$.
-We found that larger $k$-to-$l$ ratio increases the agreement between the modified equation and the original estimation of the constant environment. % "modified....environment" unclear.
+We found that larger $k$-to-$l$ ratio increases the agreement between the changing environment equation and the original estimation of the constant environment. 
 When using higher values of $n$, the agreement between the approximation and simulation results is weaker.
 This is because our approximation is more precise when more cycles occur.
-When $n$ is high, there will be less cycles, % TODO why higher n gives less cycles?
-and the simulations will get closer to the constant environment equation.
-
-% TODO I think you can do a better job summarizing the results - does the approximation work? when doesn't it work? why?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+When $n$ is high, the cycles are longer.
+When the cycles are long, the settings are similar to a constant environment equation, and fixation/extinction is more likely to happen.
+This means there will be less cycles, which lowers our approximation accuracy.
+
 \section*{Discussion}
@@
 % TODO what did we find?
+% TODO I think you can do a better job summarizing the results - does the approximation work? when doesn't it work? why?
 
@@
 Leaders may lead the group when traveling, decide on a nesting site, or choose foraging patches.
-They found that leadership is mostly observed when there is a profound social network in the group, % TODO profound sounds weird here.
-what do you mean by it?
-and when there are individuals that present leadership behavior.
+They found that leadership is mostly observed when there are a lot of connections in the social network of the group, and when there are individuals that present leadership behavior.
 Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
-When no individual posseses such traits, or when the social network is lacking, % TODO lacking what?
-decisions are more likely to be made by consensus.
-Leader may carry selection costs, e.g. due to higher predation risk, poisoning when exploring new foraging patches.
-In some cases, %e.g. fish, % TODO ref for fish? otherwise don't mention fish
- the leader may be the hungriest or the weakest individual, while the others would prefer to follow the leader and minimizing their risks and costs.
+When no individual posseses such traits, or when there are not enough connections and relations in the social network, decisions are more likely to be made by consensus.
+Leaders may carry selection costs, e.g. due to higher predation risk, poisoning when exploring new foraging patches.
+In some cases, the leader may be the hungriest or the weakest individual, while the others would prefer to follow the leader and minimizing their risks and costs.
 However, leadership may also carry selection benefits.
@@
 \citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators.
-They show that leaders wouldn't be chosen due to their superior abilities, but because they have the least to lose. % TODO are you sure? this is in baboons?
+In some species, like the females of \textit{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}.
 
@@
 However, wrong decision making that harms the group could result in harm.
-In modern society it is less common to worry about mere survival, and so the prestigious positions, even though they are not without risks and costs, are not as dangerous as for animals in nature.
-% TODO reference?
-I'm not sure this is correct
-This may be the reason humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them.
-% you give two reasons - "this may be the reason" and "as they may reap..." I think the latter is more correct.
-also I think it is personality and family driven, to an extent.
-This is in complete contrast to animals, where the weakest/hungriest is driven to lead, compared to humans where leadership positions are mostly competitive. % TODO I'm not sure, let's discuss!
+
+In modern society humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure/education from the family.
 
@@
 They present classical views of leaderships by Confucius and Machiavelli. Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills,
-and (outstanding) personal qualities. This description is very similar to success bias in our model. % TODO I changed the end of the sentence, is it ok?
+and (outstanding) personal qualities. This description is very similar to success bias in our model. 
 By contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence.
@@
 Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style. 
-This would require assuming some costs and benefits so that prestige has higher  rewards but greater costs, while dominance has lower rewards and lower costs.
-% TODO why?
 The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
 
-% YOAV Here
 \citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige based and dominance based leadership types.
@@
 So far we presented the theory behind prestige, and it's appearance in nature. The following will show the appearances of prestige biases in humans, and in recent times.
+
 \citet{prestige_cultural_learning}, for example, tested the existence of prestige in young children.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Acknowledgements
 {\small
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{References}

### 2022-04-05 ms/PrestigeBias.tex
update

@@
 \pagebreak
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Introduction}
@@
 \begin{equation}\label{eq:boydF}
-% TODO I changed X to A, and Aij to Aj, verify its ok
-F_i(\vec{A}) = \sum_{j=1}^N G_{i,j}\cdot A_{j} \;, 
+F_i(\vec{A}) = \sum_{j=1}^N G_{i,j}\cdot A_{i,j} \;, 
 \end{equation}
@@
 \begin{equation}\label{eq:binary-model}
-P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} % TODO should it be G_{i,A} rather than P_i,A ?
+G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
 \end{equation}
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:GBD}
 $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
@@
 
-% TODO what about a numerical validation for GBD?
-% ANS - The results of this approximation are contained in the next DM approximation.
-In here we find the expected number of copiers for a single role-model, and in the DM we find that (and get the same results of course) and more.
-I can make the Numerical Validation a subsection and say it's for both.
+\paragraph{Numerical validation.}
+To validate our results we ran $1,000$ simulations of the full model, and compared the results with \cref{cor:GBD}.
+We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \cref{cor:GBD}.
+We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \cref{fig:GBD}.
+
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/chi_square_stats/GBD_validation.pdf}
+  \caption{
+  \textbf{Numerical validation for the GBD approximation.}
+  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
+  Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; idea phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
+  \label{fig:GBD}
+\end{figure}
+
+Although basic, \cref{fig:GBD} shows good fit of the GBD approximation.
+This validation is initial, and the more extensive validations we do on the Dirichlet-Multinomial approximation, because it is what we will use in our analysts.
 
@@
 When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required.
-% TODO did you test other distributions?
-% ANS - No, mainly because I didn't know what paremeters to choose, we should discuss
-
-% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
-% ANS - observed vs expected of what? Make a histogram of number of copiers per role-model? just the top role-models?
 
@@
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
-We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(X,X)$.
-% TODO replace X and X with relevant symbols
+We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,x)$ where $x \in [10^{-7},10^{-1}]$.
 We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\cref{fig:hetro_alpha}).
@@
   \caption{
-  \textbf{Number of simulations needed to get a good approximation.}
-  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. 
+  \textbf{Minimum number of simulations required to get a good approximation.}
+  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. The approximated value (black) is given by equation \cref{eq:kimura_p}.
   Markers for average value across simulations, error bars for 95\% confidence interval.
@@
   \label{fig:num_sims}
-  % TODO
-  % Kimura - black solid line
-  % I removed J as you give beta(A) below, ok
-  % it is not clear what "number of simulations needed" means.
-  % what does "good enough" mean?
-  % maybe y axis should be in relative error?
-  % you should point to the equation for kimura.
 \end{figure}
@@
 Markers for average across simulations, error bars for 95\% confidence intervals.
-  % and are condensed (+- 0.01 probability and +-40 generations) % what does that mean?
-  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; $J\sim N(1,x^2)$ where $x$ is the estimation error scale in the x-axis.
-% not clear enough.
+  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,x^2)$ where $x \in [10^{-7},10^{-1}]$.
   }	
-  % TODO
-  % see comments in previous figure
   % maybe 50% CI looks better? the bars are too large to understand. maybe a wider y range? say from 0 to 0.02?
@@
 \begin{figure}[h]
-%TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
   \begin{center}
@@
   % see previous figures todos
-  % move legend to upper left? it is currently hiding something
   \caption{Model simulations compared with both the constant environment and the changing environment equations for different values of $k,l$, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
@@
 
-\paragraph{Further work.} 
-Our model can be expanded in various ways: observing the effects of different bias functions, % TODO unclear
+\paragraph{Further work.} %TODO revisit
+Our model can be expanded in various ways: observing the effects of different bias functions, 
 including errors when estimating influence or costs when copying from an influential role-model, and inclusion of multiple, rather than a single, optimal phenotype.

### 2022-04-06 ms/PrestigeBias.tex
update

@@
 \subsection*{Continuous trait}
-We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the indicator trait and omitting the indirect trait in order to reduce model complexity. 
-We consider a population of $N$ individuals, described by a single indicator trait with a continuous value.
+We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
+We consider a population of $N$ individuals, described by a single trait with a continuous value.
 Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait.
@@
 \end{equation}
-$A_{i,j}$ is the absolute indicator trait value copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\frac{1}{\eta^2})$,
-\begin{equation}\label{eq:relativeIndicator}
+$A_{i,j}$ is the absolute trait value copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
+\begin{equation}\label{eq:relativeTrait}
 A_{i,j} = A_j + e_i,
@@
 \end{equation} 
-with $\hat{A}$ as the arbitrary optimal indicator value, and $J$ and $b$ as parameters that control the bias strength.
+with $\hat{A}$ as the arbitrary optimal trait value, and $J$ and $b$ as parameters that control the bias strength.
 Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$, equivalent to relative fitness in evolutionary-genetic transmission models.
@@
 \end{equation}
-The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased indicator value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citet{evolutionBook} with
+The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased trait value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citet{evolutionBook} with
 \begin{equation}\label{eq:prestige}
@@
 \end{equation}
-Here, the bias weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of success and influence in his prestige, the indicator value of role-model $j$ estimates by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeIndicator}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
+Here, the bias weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of success and influence in his prestige, the trait value of role-model $j$ estimates by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
 
 \subsection*{Dichotomous trait}
-To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$.
+To allow for mathematical analysis of the model, we introduce a simplified version where the trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
 All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
@@
 $\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
-\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value.
+\item the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
 \end{enumerate}
@@
 $\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
-Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
+Note that here $G_{i,j}$ is only a function of the trait values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
 \end{enumerate}
@@
 \end{equation}
-where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution we draw the indicator values from, modified by some constant parameters of $\beta$.
+where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution we draw the trait values from, modified by some constant parameters of $\beta$.
 We can then denote $L = 1/\overline{\beta(A+e)}$ and write
@@
 A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be correctly identified.
-However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful by some other indicator.
+However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful by some other trait.
 
@@
 Their definition of prestige is somewhat synonymous with ours.
-According to their manuscript, prestige is composed both of estimation in the eyes of people (our indicator/success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
+According to their manuscript, prestige is composed both of estimation in the eyes of people (our success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
 In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
 Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
-It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
+It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the trait copied.
 \citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions and results, is consistent with ours.
@@
 \end{quote}
-We see here support for both our indicator trait and our influence bias in their data.
+We see here support for both our trait and our influence bias in their data.
 

### 2022-04-25 ms/PrestigeBias.tex
update

@@
 % TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?
+% But what distributions? just some random distributions? (like normal and exponential? but what parameters?)
 
@@
   }	
-  % maybe 50% CI looks better? the bars are too large to understand. maybe a wider y range? say from 0 to 0.02?
   \label{fig:hetro_error}
@@
 Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
-  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
+  $5000$ simulations per data point; population size, $N=1000$; trait bias normally distributed, $\alpha\sim N(0.5,x^2)$; phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
   \label{fig:hetro_alpha}
-	% TODO
-	% see comments in previous figure
 \end{figure}
@@
 
-\begin{result}[Effective selection coefficient]
+\begin{result}[Effective selection coefficient]\label{res:selection_coef}
 $1-\beta(A)$ is equivalent to the selection coefficient $s$ in the diffusion-equation approximation of the a classic Wright-Fisher model that approximate the fixation probability and fixation time of an advantageous allele.
@@
 
-\begin{result}[Effective population size]
+\begin{result}[Effective population size]\label{res:effective_population}
 $N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
@@
 
-Using our substitute for a selection coefficient, $1-\beta$, and the effective population size $N_e$, we can estimate the fixation probability and time of our binary model.
-
-The fixation probability derived from Kimura is therefore:
+\begin{result}[Fixation probability approximation]
+The fixation probability is estimated by:
 \begin{equation}\label{eq:kimura_p}
@@
 \end{equation}
+where $x$ is the initial frequency of the advantageous phenotype $\hat{A}$.
+\end{result}
+\begin{proof}
+Using our substitute for a selection coefficient, $1-\beta$, and the effective population size $N_e$, we can estimate the fixation probability using the diffusion equation, $E[X'-X]$ (\cref{res:selection_coef}), and $V(X'-X)$ (\cref{res:effective_population}).
+\end{proof}
 
-where $x$ is the initial frequency of the advantageous phenotype $\hat{A}$.
-
-The time to fixation can be estimated by:
+\begin{result}[Fixation time approximation]
 \begin{equation}\label{eq:kimura_t}
@@
 \end{equation}
-where the integrals cannot be solved in closed form, so we can only estimate them numerically.
+\end{result}
 
+\begin{proof}
+Again using the diffusion equation and \cref{res:selection_coef,res:effective_population}, we get our result.
+the integrals cannot be solved in closed form, so we can only estimate them numerically.
+\end{proof}
+
+\paragraph{Numeric validation.}
 To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
@@
 \begin{figure}[h]
-  \begin{center}
-  \begin{subfigure}[a]{0.49\linewidth}
-    \caption{}
-    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
-   \end{subfigure}
-   \begin{subfigure}[a]{0.49\linewidth}
-     \caption{}
-    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
-   \end{subfigure}
-  \end{center}
-  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size.
-  Error bars show mean and 95\% confidence intervals.
-  Effective population, $N_e=\alpha N + (1-\alpha)$.
-  $5,000$ simulations per data point; Population size, $N=1,000$; $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
-  % TODO
-  % - better x and y label, as noted above
-  % - in legend, replace "kimura" with "Approx."
-  % - in legend, remove "=2s"
-  % - change approximation color, it is too similar to WF simulations
-  % - make the horizontal line black?
-  % - caption should start with bold sentence summarizing the figure. 
-  % - in caption add description of each parameter (as I did for N)
+    \includegraphics[width=\linewidth]{../figures/binary/kimura_var_alpha.pdf}
+  \caption{\textbf{Goodness of fit of Kimura's approximation for varying bias weights.}
+  The approximation (black) fits DM simulations results (green) and Wright Fisher simulation results (orange) when using \cref{eq:kimura_p}.
+  Fixation probability (a) is limited at approximately $2s$ (blue), like the classic WF model.
+  Markers for average values across $5,000$ simulations, error bars for 95\% confidence intervals.
+   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$; success coefficient, $1-\beta=s=0.044$.}
   \label{fig:var_alpha}
@@
 \begin{figure}[h]
-  \begin{center}
-  \begin{subfigure}[a]{0.49\linewidth}
-  \caption{}
-    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
-   \end{subfigure}
-   \begin{subfigure}[a]{0.49\linewidth}
-    \caption{}
-    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
-   \end{subfigure}
-  \end{center}
-  % TODO 
-  % - see previous figure
-  % - consider making the error bars smaller with more simulations or narrower CI (50%?)
-  % - consider using plt.xscale('log')
-  % - maybe you can merge this figure with the figure?
-  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. Error bars are 95\% confidence intervals.
-  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
-  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
+    \includegraphics[width=\linewidth]{../figures/binary/kimura_var_beta.pdf}
+  \caption{\textbf{Goodness of fit of Kimura's approximation for varying success coefficients.}
+   The approximation (black) fits DM simulations results (green) and Wright Fisher simulation results (orange) when using \cref{eq:kimura_p}.
+  Markers for average values across $5,000$ simulations, error bars for 75\% confidence intervals.
+ Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=a\cdot \hat{A}, a \in [0.01,0.99]$; bias weight, $\alpha=0.01$.}
   \label{fig:var_beta}
@@
 
-\paragraph{Changing environment.}
 After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.
@@
 
-\paragraph{Proposition:} $E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$ , $V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
+\begin{result} [Expected difference in frequency in a changing environment]\label{res:ch_expected}
+$E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
+\end{result}
+\begin{result}[Variance of difference in frequency in a changing environment]\label{res:ch_var}
+$V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
+\end{result}
 
-The proof is based on the proof of \citet{changeEnv}, proving a similar scenario.
-\paragraph{Proof by induction:}
+\begin{proof}
+Following the proof of \citet{changeEnv}, we prove by induction. We will prove \cref{res:ch_expected,res:ch_var} together, because the induction assumptions are needed for both.
+
 From \cref{eq:expec_freq} we know that
@@
 \end{equation}
-which proves the first part of our preposition.
+which proves \cref{res:ch_expected}.
 
-For the second part, we'll use a property of variance:
+For \cref{res:ch_var}, we'll use a property of variance:
 \begin{equation}\label{eq:ch_var}
@@
 \end{equation}
-proving the second part of our preposition.
+proving \cref{res:ch_var}.
+\end{proof}
 
 Following our proof, we can say that after many cycles, we can use a modified version of our fixation probability:
-\begin{equation}
+\begin{equation}\label{eq:ch_env}
 P_{fix} = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
@@
 \begin{figure}[h]
-  \begin{center}
-  \begin{subfigure}[a]{0.49\linewidth}
-  %TODO remove the (a) and (b) from the latex and put them on the figure 	itself (top left corenr).
-    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
-   \end{subfigure}
-   \begin{subfigure}[a]{0.49\linewidth}
-    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
-   \end{subfigure}
-  \end{center}
-  \caption{Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients.
-Changing the effective population size doesn't affect the approximation, and it is condensed the mathematical expected values across all values.
-High values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values.
-Very high values ($s>0.35$) will even deviate from the constant environment expected values.
+    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var.pdf}
+  \caption{\textbf{Robustness of approximation in a changing environment to varying success coefficient and success bias weight.}
+ Markers for average values across $10,000$ simulations, error bars for (a) are 75\% confidence intervals, and 95\% for (b).
+The approximation (blue) given by \cref{eq:ch_env} fits simulation results (orange) well when the effective population size varies (a).
+On (b) we see that for high values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values.
+Very high values ($s>0.35$) will even deviate from the constant environment expected values (green) given by \cref{eq:kimura_p}.
 This is expected because Kimura's approximation are only viable for low selection coefficient values.
-  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} bias weight is: $\alpha=0.1$. 
+  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$; \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success bias weight is: $\alpha=0.1$. 
   }
-   %TODO 
-  % see previous figures..
-  % not sure you need the green curve in the left panel
-  % ANS - to show it's not a valid option to use?
-  % the right panel might be better with yscale('log')? or xscale('log')? right now it is hard to see that the blue even changes...
   \label{fig:ch_env_alpha_beta}
@@
 \begin{figure}[h]
-  \begin{center}
-  \begin{subfigure}[a]{0.49\linewidth}
-  \caption{}
-    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
-   \end{subfigure}
-   \begin{subfigure}[a]{0.49\linewidth}
-   \caption{}
-    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
-   \end{subfigure}
-  \end{center}
-  %TODO add panel labels (a) and (b) on figures corner.
-  % see previous figures todos
-  \caption{Model simulations compared with both the constant environment and the changing environment equations for different values of $k,l$, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
-   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
- We ran $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
+    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_l.pdf}
+  \caption{\textbf{Robustness of approximation in a changing environment to varying sizes of the cycles.} 
+Markers for average values across $10,000$ simulations, error bars are 95\% confidence intervals.
+The approximation (blue) fits the simulations (orange) well for different sizes of the changing environment cycle, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
+   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green). 
+ Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.8$; success coefficient, $1-\beta=s=0.02$; success bias weight, $\alpha=0.1$.}
   \label{fig:ch_env_k_l}

### 2022-05-11 ms/PrestigeBias.tex
update

@@
 It also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
-Our model may provide a better description of human cultural transmission, 
-especially in the last years where social networks are very popular. % TODO to discuss this last sentence
+Our model may provide a good description of cultural transmission, 
+especially in human societies where social media is popular. 
 Further work is needed to test if this model could predict various phenomena in human cultural evolution when extended with the effects of selection and innovation.
@@
 Online social networks such as \textit{Facebook} or \textit{Instagram} are known to affect the social influence of individuals \citep{social_influence,influence_analysis,social_media}.
-For example, specific marketing practices were invented following this realization \citep{facebook_marketing},
-Here we propose an indirect bias that we call \textit{influence bias}, in which the choice of a role-model depends on the the choices made by other individuals that have already chosen a role-model. 
+For example, specific marketing practices were invented following this realization \citep{facebook_marketing}.
+Here, we propose an indirect bias that we call \textit{influence bias}, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
+Other than it's relative ease of evaluation, compared to the evaluation of the actual trait, choosing a role-model based on previous choices made may be advantageous on its own.
 This bias depends on the state of a role-model rather than a trait, in contrast to frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models.
 We define a model for prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
+To test if choosing an $\alpha$ value is really advantageous, we ran simulations of a single generation, where every copier evaluates the best $\alpha$ for it, which is the $\alpha$ that minimizes the mean error in estimation.
+This is calculated by minimizing the mean difference between the estimated value of every role-model to the ideal trait value $\hat{A}$.
 
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/influence_advantage/choose_bias.pdf}
+  \caption{
+  \textbf{Advantage of choosing success bias weight.}
+  The success bias weight decreases during the choosing process (a), showing that influence is more advantageous the later the copier chooses the role-model.
+In (b) we see that the estimation error decreases along the success bias weight.
+  Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
+  \label{fig:influence_advantage}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/influence_advantage/const_bias.pdf}
+  \caption{
+  \textbf{Estimation error when using constant success bias weight.}
+  The mean estimation error doesn't have any significant improvement relative to when every copier chooses a bias for himself.
+  The minimum error is no less than $0.74$, while the mean error of the model where $\alpha$ is chosen is $0.06$, converging to $0.046$, which is a factor of $10$ less than the constant $\alpha$ model, showing the clear advantage of choosing $\alpha$.
+  Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
+  \label{fig:const_influence}
+\end{figure}
+
+We see in \cref{fig:influence_advantage,fig:const_influence} a comparison between a model where every copier chooses its ideal success bias weight $\alpha_{ij}$, and when $\alpha$ is a constant homogeneous value.
+When copiers choose their $\alpha$ the estimation error decreases together with the success bias weight.Estimation error is the difference between the value estimated $A_{ij}$ and the ideal value $\hat{A}$ in this case.
+In addition, the estimation error converges to a value ($0.046$) much lower than when $\alpha$ is homogeneous (min $0.74$).
+We can learn that influence, when individually chosen by each copier, will aid the ideal trait to dominate the population.
+In addition, we see that homogeneous influence will not increase or decrease the estimation error in the population.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{equation}\label{eq:prestige}
-G_{i,j} = \frac{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}{W_i} \;.
+G_{i,j} = \frac{\alpha_{ij} \cdot \beta(A_{i,j}) + (1-\alpha_{ij}) \cdot K_{i-1,j}}{W_i} \;.
 \end{equation}
-Here, the bias weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of success and influence in his prestige, the trait value of role-model $j$ estimates by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
+Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$, that determines the relative significance of success and influence within the role-model's overall prestige, in the eyes if the copier.
+The trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
 
@@
 All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
+In addition, we assume homogeneous $\alpha$ for simplicity and for easier mathematical analysis.
 Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
@@
 Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$.
-We found two such approximations, summarized here and explained in detail below:
+We found two such approximations, summarized here and explained in detail below.
+In both we assume either $\alpha_j$ is a trait of role-model $j$ only (contrary to $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.
 \begin{enumerate}
@@
 First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then compared this observed distribution with the expected theoretical DM distribution using Pearson's chi-squared test of goodness-of-fit.
-Thus, we can reject or accept the null hypothesis that simulation results are effectively drawn from a DM distribution.
+We then compared this observed distribution with the expected theoretical DM distribution as can be seen in \cref{fig:DM_validation} (a).
+The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
+The maximum difference is 0.5 role-models, which indicate a very good fit.
+In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself, as seen in \cref{fig:DM_validation} (b).
+We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, supporting our approximation more.
 
-Examining variable values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
-For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
-For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
-When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required.
-
-% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?
-% But what distributions? just some random distributions? (like normal and exponential? but what parameters?)
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/chi_square_stats/DM_validation.pdf}
+  \caption{
+  \textbf{Goodness of fit of Dirichlet-Multinomial approximation to the model.}
+  The difference between the DM approximation distribution to observed model distribution (a) is very small, with the highest difference at 0.5 role-models.
+  The optimal negative log likelihood (b) is given when using the DM approximation (black vertical line), and is much better when compared to a shuffled vector of the DM distribution (blue bars).
+  Here, population size, $N=100$; number of distributions averaged, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; homogeneous success bias weight, $\alpha=0.5$.}	
+  \label{fig:DM_validation}
+\end{figure}
 
@@
    \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   High bias weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it).
-Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
-  $5000$ simulations per data point; population size, $N=1000$; trait bias normally distributed, $\alpha\sim N(0.5,x^2)$; phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
+   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variation in success bias weight.Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
+  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$; phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
   \label{fig:hetro_alpha}

### 2022-05-15 ms/PrestigeBias.tex
update

@@
 
-\begin{result}[GBD approximation]
+\begin{result}[GBD approximation]\label{res:GBD}
 The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$. 
@@
 
-% TODO in the following, I would organize differently:
-% 1.  remark for E[x'-x] the "drift" (1st order) coefficient in a diffusion equation approximation
-% 2. result on effective selection coefficient
-% 3. remark for V[x'-x] the "diffusion" (2nd order) coefficient in a diffusion equation approximation
-% 4. result of effective population size
-% 5. result for fixation prob
-% 6. result for fixation time
-% 7. result for changing environment
-% so I didn't read the rest of the results very carefully, waiting for you to think about the re-arrangement suggestion first.
+\begin{remark}[Effective selection coefficient]
+In population genetics a selection coefficient is a measure of differences in relative fitness.
+Selection coefficients are central to the quantitative description of evolution, since fitness differences determine the change in genotype frequencies attributable to selection.
+Effective selection coefficient is the equivalent in a model to the selection coefficient in a Wright-Fisher model.
+\end{remark}
 
@@
 
+\begin{remark}
+The effective size of a population, $N_e$, determines the rate of change in the composition of a population caused by genetic drift, which is the random sampling of genetic variants in a finite population.
+Ne is crucial in determining the level of variability in a population, and the effectiveness of selection relative to drift.
+\end{remark}
+
 \begin{result}[Effective population size]\label{res:effective_population}
-$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
+$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of the binary model.
 \end{result}
@@
 
-We suspect that when $\beta$ is too large, there won't be many cycles in the simulations.
+We suspect that when $1-\beta$ is too large, there won't be many cycles in the simulations.
 This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or the fitter phenotype get extinct very quickly.
-For the very high $\beta$ values (0.35 and above), the fixation probability exceeds even the constant environment approximation (which is the upper limit), but it's to be expected, because Kimura's equations are only appropriate for weak fitness (i.e., low selection coefficients, $s$).
+For the very high $1-\beta$ values (0.35 and above), the fixation probability exceeds even the constant environment approximation (which is the upper limit), but it's to be expected, because Kimura's equations are only appropriate for weak fitness (i.e., low selection coefficients, $s$).
 
@@
 Some cultural traits or cultural role-models may be more likely to be copied due to transmission biases. 
-A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be correctly identified.
-However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful by some other trait.
+A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
+However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful, portrayed by other traits or means.
 
 Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias, which included both success and influence biases, where the latter is a bias towards role-models with many copiers.
-We found approximations for the role-model choice process: the generalized binomial distribution that approximates the number of copiers of a single role-model, and the Dirichlet-Multinomial distribution that approximates the distribution of copiers in the entire population in a \textit{rich-getting-richer} type of process.
-We then studied the effects of prestige bias on the fixation probability and time of an invading advantageous cultural phenotype in both a constant and a changing environment.
-% TODO what did we find?
-% TODO I think you can do a better job summarizing the results - does the approximation work? when doesn't it work? why?
+As shown in \cref{fig:influence_advantage}, given the option to choose the ratio of success and influence, copiers will minimize their estimation error, hence will copy the traits that are closer to the ideal phenotype.
+We see that throughout the choosing process, the estimation error decreases, and the success bias rate also decreases.
+This suggests that the later a copier gets to choose, the less he should rely on his own estimation, and more on previous choices.
+In addition, we see that the process of choosing itself is necessary, and when using a constant ratio ($\alpha$), the mean estimation error in the population is greater by a factor of $10$, even when using the $\alpha$ the population converged to when being able to choose it (\cref{fig:const_influence}).
+After we showing that choosing one's success bias weight is beneficial to the copier, we continued to create our models- continuous and dichotomous, that incorporated both success and influence.
+However, running simulations for a nested iterative model is costly, and analyzing such model mathematically is very hard.
+We therefor found approximations for the role-model choice process: the generalized binomial distribution (\cref{res:GBD}) and the Dirichlet-Multinomial distribution (\cref{cor:dirichlet}).
+To use approximate our model with the GBD distribution, we must assume homogeneous estimation error, $e$, and homogeneous success bias weight, $\alpha$.
+Both assumptions are necessary to this approximation, because it requires all copiers to be identical (order of copiers must not be a factor).
+For the DM approximation we can relax the assumption for $\alpha$, and allow a varying $\alpha_j$ for each role-model $j$.
+This means that a copier is still not able to choose a success bias weight for itself, and instead it is a characteristic of the role-model only.
+Using the DM approximation, because it is easier to analyze, we found equivalents for Kimura's equations, for our dichotomous model.
+Following \cref{res:selection_coef,res:effective_population} we found an approximation for the fixation probability of the ideal trait, and an approximation for the time of fixation.
+These approximations hold only when the equivalent for the selection coefficient, in our model $1-\beta(A)$, is low (0.4 or lower).
+We also discovered that changing the success bias weight doesn't hurt the goodness of the approximations, and only affects the effective population size $N_e$.
+Once we found the equations for a constant environment, we moved on to a cyclic changing environment.
+Based on \cref{res:ch_expected,res:ch_var}, we found the approximations for the fixation probability and time to fixation.
+We discovered that as in the constant environment, the effective population size doesn't affect the goodness of fit of the approximation.
+The success coefficient however, must be even lower than before for the approximation to fit.
+When the success coefficient is higher than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation.
+We believe the reason is the structure of the cycle.
+Our proof and approximation in the changing environment are for a large amount of cycles, and when the success coefficient is too high, there might be very few cycles.
+Either the ideal trait is copied by enough copiers so that the influence is sufficient to negate the success bias when the cycle changes (and the beneficial trait becomes the maladaptive), or the opposite happens, and the ideal trait gets extinct before there were enough copiers that copied it.
+We then tried to change the ratio between the number of cycles where $\hat{A}$ is beneficial and maladaptive.
+We showed that the approximation fits well regardless of the ratio, but when the ratio of adaptive generations to maladaptive ones is very high, it is very similar to a constant environment model.
 

### 2022-05-29 ms/PrestigeBias.tex
update

@@
 This suggests that the later a copier gets to choose, the less he should rely on his own estimation, and more on previous choices.
+This behavior fits the intuitive thought - the more information you have, using others as an information source, the more informative your choice can be, therefore minimizing the distance from your choice of trait to the ideal one.
+
 In addition, we see that the process of choosing itself is necessary, and when using a constant ratio ($\alpha$), the mean estimation error in the population is greater by a factor of $10$, even when using the $\alpha$ the population converged to when being able to choose it (\cref{fig:const_influence}).
@@
 
+Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require replication of representations.
+They base their assumption on three claims - mental representations are non-discrete, cultural transmission is highly inaccurate, and mental representations are not replicated, but rather are 'reconstructed' through an inferential process that is strongly affected by cognitive 'attractors.' In their paper they describe three different models to support their points.
+We see a high similarity between their model and ours.
+Like them, we treat the cultural trait as non-discrete (in the main model, before simplifying it to dichotomous in order to analyze it).
+We also assume error in estimation, which the copiers aren't really replicating their role-models, but rather reconstructing them to create a different trait, which is their representation of the role-model's trait.
+In addition, the inferential process that they describe as strongly affected by cognitive attractors match our influence bias, resulting in a very similar base assumptions in our models.
+
 So far we presented the theory behind prestige, and it's appearance in nature. The following will show the appearances of prestige biases in humans, and in recent times.
@@
 
-\paragraph{Further work.} %TODO revisit
-Our model can be expanded in various ways: observing the effects of different bias functions, 
-including errors when estimating influence or costs when copying from an influential role-model, and inclusion of multiple, rather than a single, optimal phenotype.
+\paragraph{Further work.}
+In this paper we described several models and processes, analyzed them, and discovered some interesting approximations and results.
+But even though, there's much more to research in the direction we took, which can help us better model, understand, and maybe even predict, human behavior, specifically in this era where social media is very accessible and informative.
+Specifically, a deeper analysis of the first model, where every copier chooses its $\alpha$, is preferred.
+It would be interesting to see the if the mean error value and the $\alpha$ are converging to specific values, and what they depend on.
+Following that, it is possible to relax some assumptions we took in our main model in order to find approximations for it - like homogeneous estimation error and success bias weight.
+Lastly, it would be interesting to analyze the continuous model, instead of its dichotomous version. As we've discussed it is probably a much more accurate model of cultural evolution.
 

### 2022-05-29 ms/PrestigeBias.tex
revised abstract and intro a bit; moved optimal alpha to end of results

@@
 We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
-We also find approximations to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resemble Kimura's classical formulas.
+We also find approximations to the fixation probability and the fixation time of an invading advantageous cultural trait, in both constant and changing environments, which resemble Kimura's approximations for population-genetic models.
 These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
@@
 especially in human societies where social media is popular. 
-Further work is needed to test if this model could predict various phenomena in human cultural evolution when extended with the effects of selection and innovation.
+Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
 \end{abstract}
@@
 \paragraph{Influence bias.}
-Today, social media provides an easy way to estimate the influence individuals have over others, and therefore may have an effect on decision making.
-Online social networks such as \textit{Facebook} or \textit{Instagram} are known to affect the social influence of individuals \citep{social_influence,influence_analysis,social_media}.
-For example, specific marketing practices were invented following this realization \citep{facebook_marketing}.
-Here, we propose an indirect bias that we call \textit{influence bias}, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
-Other than it's relative ease of evaluation, compared to the evaluation of the actual trait, choosing a role-model based on previous choices made may be advantageous on its own.
-This bias depends on the state of a role-model rather than a trait, in contrast to frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models.
-We define a model for prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
-To test if choosing an $\alpha$ value is really advantageous, we ran simulations of a single generation, where every copier evaluates the best $\alpha$ for it, which is the $\alpha$ that minimizes the mean error in estimation.
-This is calculated by minimizing the mean difference between the estimated value of every role-model to the ideal trait value $\hat{A}$.
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/influence_advantage/choose_bias.pdf}
-  \caption{
-  \textbf{Advantage of choosing success bias weight.}
-  The success bias weight decreases during the choosing process (a), showing that influence is more advantageous the later the copier chooses the role-model.
-In (b) we see that the estimation error decreases along the success bias weight.
-  Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
-  \label{fig:influence_advantage}
-\end{figure}
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/influence_advantage/const_bias.pdf}
-  \caption{
-  \textbf{Estimation error when using constant success bias weight.}
-  The mean estimation error doesn't have any significant improvement relative to when every copier chooses a bias for himself.
-  The minimum error is no less than $0.74$, while the mean error of the model where $\alpha$ is chosen is $0.06$, converging to $0.046$, which is a factor of $10$ less than the constant $\alpha$ model, showing the clear advantage of choosing $\alpha$.
-  Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
-  \label{fig:const_influence}
-\end{figure}
-
-We see in \cref{fig:influence_advantage,fig:const_influence} a comparison between a model where every copier chooses its ideal success bias weight $\alpha_{ij}$, and when $\alpha$ is a constant homogeneous value.
-When copiers choose their $\alpha$ the estimation error decreases together with the success bias weight.Estimation error is the difference between the value estimated $A_{ij}$ and the ideal value $\hat{A}$ in this case.
-In addition, the estimation error converges to a value ($0.046$) much lower than when $\alpha$ is homogeneous (min $0.74$).
-We can learn that influence, when individually chosen by each copier, will aid the ideal trait to dominate the population.
-In addition, we see that homogeneous influence will not increase or decrease the estimation error in the population.
+Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making.
+Online social networks such as \textit{Facebook} or \textit{Instagram} are known to affect the influence of individuals \citep{social_influence,influence_analysis,social_media}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
+Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
+Other than its relative ease of evaluation, compared to the evaluation of the actual trait, choosing a role-model based on previous choices made may be advantageous on its own. % TODO rephrase
+This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity,% TODO cite doi 10.1111/j.1420-9101.2011.02236.x
+ which depend on the frequency of a trait in the population or in a sample of role-models. 
+ We define a model of cultural transmission with prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Adaptive success-bias weight}
+
+We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal $\alpha$ value.
+This is the $\alpha$ value that minimizes the mean error in estimation.
+% TODO estimation of what?
+This is computed by minimizing the mean difference between the estimated value of every role-model and the ideal trait value $\hat{A}$. % TODO write the explicit equation
+
+We see in \cref{fig:influence_advantage,fig:const_influence} a comparison between a model where every copier chooses its ideal success bias weight $\alpha_{ij}$, and when $\alpha$ is a constant homogeneous value.
+We find that when copiers adapt their success-bias weight, their success-bias weight decreases with the number of copiers that have already chose a role-model~(\cref{fig:influence_advantage}a).
+Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \cref{fig:influence_advantage}b and c): the estimation error converges to $0.046$ whereas a constant weight gives values $>0.74$ in this example.
+
+\begin{figure}[b!]
+    \includegraphics[width=\linewidth]{../figures/influence_advantage/choose_bias.pdf}
+    % TODO
+    % fonts too small
+    % capital letters in labels
+    % add "alpha" to ylabel in panel a
+    % "mean estimation error" in y label of panel b
+	% can you maybe add two more lines with different colors on the same plots for other parameters choices? say larger pop size or larger error?
+  \caption{
+  \textbf{Advantage of an adaptive success-bias weight.}
+  Both success-bias weight $\alpha$ (\textbf{a}) and estimation error (\textbf{b}) 
+   decrease during the role-model choosing process, demonstrating that influence is becomes more advantageous as more copiers have made their choice.
+   Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
+  \label{fig:influence_advantage}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/influence_advantage/const_bias.pdf}
+    % TODO 
+    % merge with previous plot
+  \caption{
+  \textbf{Estimation error when using constant success bias weight.}
+  The mean estimation error doesn't have any significant improvement relative to when every copier chooses a bias for himself.
+  The minimum error is no less than $0.74$, while the mean error of the model where $\alpha$ is chosen is $0.06$, converging to $0.046$, which is a factor of $10$ less than the constant $\alpha$ model, showing the clear advantage of choosing $\alpha$.
+  Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
+  \label{fig:const_influence}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Discussion}

### 2022-05-29 ms/PrestigeBias.tex
revised entire fixation prob section

@@
 Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait.
-Similar to a Wright–Fisher model, we assume non-overlapping generations such that the entire population is replaced in each generation.
+Similar to a Wright-Fisher model, we assume non-overlapping generations such that the entire population is replaced in each generation.
 The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t$.
@@
 \paragraph{Success bias.}
-\citet[Ch.8, p.247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$ as a weighted average of the traits of all role-models, 
+\citet[Ch.~8, p.~247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$ as a weighted average of the traits of all role-models, 
 \begin{equation}\label{eq:boydF}
@@
 
-After finding that the DM distribution is a good approximation of the (within-generations) role-model choice process, we turn our attention to the (between-generations) evolutionary dynamics.
-We focus on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models \citep{kimura,kimura_average,otto_fixation}.
-
-We are mainly interested in the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias.
-For simplicity, we do not include estimation error in this analysis.
-As shown above, transmission in our model is approximately DM distributed with the parameters $\sim DM(\alpha'X,(N-X)\alpha'\beta(A))$ based on \cref{cor:dirichlet} and \cref{eq:copier_choose}.
-
-\begin{remark}[Effective selection coefficient]
-In population genetics a selection coefficient is a measure of differences in relative fitness.
-Selection coefficients are central to the quantitative description of evolution, since fitness differences determine the change in genotype frequencies attributable to selection.
-Effective selection coefficient is the equivalent in a model to the selection coefficient in a Wright-Fisher model.
-\end{remark}
-
-\begin{result}[Effective selection coefficient]\label{res:selection_coef}
-$1-\beta(A)$ is equivalent to the selection coefficient $s$ in the diffusion-equation approximation of the a classic Wright-Fisher model that approximate the fixation probability and fixation time of an advantageous allele.
+After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
+We focus on the fixation probability and fixation time of an advantageous phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
+We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias. % TODO ref eq 10?
+For simplicity, we do not include role-model estimation error in this analysis. % TODO meaning epsilon=0?
+As shown above, transmission in our model is approximately DM distributed (\cref{cor:dirichlet} and \cref{eq:copier_choose}).
+
+We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.\\
+
+\begin{result}[Drift and diffusion terms in a constant environment]
+Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ is the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
+Then,
+\begin{equation}
+E[x'-x] \approx x(1-x)(1-\beta) \;, 
+\quad
+V(x'-x) \approx x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big) \;.
+\end{equation} 
 \end{result}
@@
 \begin{proof}
-Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals.
-Let $X$ be the number of individuals of type $\hat{A}$ so $x=X/N$.
-$X'$ is the number of individuals with $\hat{A}$ in the next generation and $x'$ their frequency.
-By definition $\beta(\hat{A})=1$, and for simplicity we'll denote $\beta(A)=\beta$ ($\beta<1$).
-
-The expected number of individuals of a DM distribution is:
-\begin{equation}
-E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2},
+Let $X$ be the number of individuals of type $\hat{A}$ such that $x=X/N$. $X'$ is the number of individuals with $\hat{A}$ in the next generation.
+The expected number of individuals is (due to the DM approximation),
+\begin{equation}
+E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2} \;,
 \end{equation}
 where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
-We want to use frequencies instead of quantities to follow Durret's process so:
-\begin{equation}
-E[x'] = E[\frac{X'}{N}] = \frac{1}{N}E[X']
-\end{equation}
-Putting it together we get:
+To use frequencies instead of counts, $E[x'] = E[X'/N] = \frac{1}{N}E[X']$.
+Putting it together,
 \begin{equation}
 \begin{split}
-E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\
-	 &= \frac{x}{x + (1-x)\beta}
+E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}
+	  = \frac{x}{x + (1-x)\beta} \\
+	  &= \frac{x}{x + (1-x) -(1-x) + (1-x)\beta}
+	  = x \frac{1}{1 -(1-x)(1-\beta)}  \\
+	  &= x \big(1 + (1-x)(1-\beta) + o(\beta)\big)
+	  = x + x(1-x)(1-\beta) + o(\beta) \;,
 \end{split}
 \end{equation}
-
-which is identical to the equation in the top of page 253, chap 7.2 in \citet{durret}. We therefore use the same approximation and say that:
-\begin{equation}
-\begin{split}
-E[x'] =& \frac{x}{x + (1-x)\beta} = \frac{x}{x + (1-x)(1-s)} =\\
- &= x + x(1-x)s + o(s)\\
-  &= x + x(1-x)(1-\beta) + o(1-\beta)
-\end{split}
-\end{equation}
-
-By definition, $x$ is constant, so $E[x] = x$. We continue to calculate $E[x'-x]$:
+following \citet[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
+
+By definition, $x$ is constant, so $E[x] = x$.
+We therefore have
 \begin{equation}\label{eq:expec_freq}
-E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta)
-\end{equation}
-where when substituting $1-\beta$ with $s$, we get the same result as \citet{durret} which is the desired result.
-\end{proof}
-
-\begin{remark}
-The effective size of a population, $N_e$, determines the rate of change in the composition of a population caused by genetic drift, which is the random sampling of genetic variants in a finite population.
-Ne is crucial in determining the level of variability in a population, and the effectiveness of selection relative to drift.
-\end{remark}
-
-\begin{result}[Effective population size]\label{res:effective_population}
-$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of the binary model.
-\end{result}
-
-\begin{proof}
-The variance of a DM distribution is:
-\begin{equation}
-V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}(1-\frac{\alpha_1}{\alpha_1+\alpha_2})
-(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2})
-\end{equation}
-And again, we want to use frequencies so:
-\begin{equation}
-V(\frac{X'}{N}) = \frac{1}{N^2}V(x')
-\end{equation}
-
-Putting it together with our model's notations:
-\begin{equation}
-V(x') = \frac{1}{N^2}N\frac{x}{x+(1-x)\beta}(1-\frac{x}{x+(1-x)\beta})
-(\frac{N + \alpha' xN + \alpha' N(1-x)\beta}{1 + \alpha' xN + \alpha' N(1-x)\beta}) 
-\end{equation}
-
-Like Durrett, we'll use the zero order of the approximation when $\beta\approx1$,so:
-\begin{equation}
-\frac{x}{x + (1-x)\beta} \approx x
-\end{equation}
-and we also use $\beta\approx1$ for the entire variance expression and get:
-\begin{equation}
-\begin{split}
-V(x') & \approx  \frac{1}{N} x(1-x)
-(\frac{N + \alpha' xN + \alpha' N - \alpha' xN}{1 + \alpha' xN + \alpha' N - \alpha' xN})\\
-&=  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N}) 
-\end{split}
-\end{equation}
-
-Again following Durrett we want to calculate:
+E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta) \;,
+\end{equation}
+which gives us the drift term of the diffusion equation.
+
+Using the variance of the DM distribution,
+\begin{equation}
+V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}
+\Big(1-\frac{\alpha_1}{\alpha_1+\alpha_2}\Big)
+\Big(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2}\Big) \;.
+\end{equation}
+Again, we want to use frequencies so we have $V(X'/N) = \frac{1}{N^2}V(x')$.
+Putting it together with our model notations,
+\begin{equation}
+V(x') = \frac{1}{N^2}N\frac{x}{x+(1-x)\beta}\Big(1-\frac{x}{x+(1-x)\beta}\Big)
+\Big(\frac{N + \alpha' xN + \alpha' N(1-x)\beta}{1 + \alpha' xN + \alpha' N(1-x)\beta}\Big) \;.
+\end{equation}
+
+Following \citet[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
+\begin{equation}
+\frac{x}{x + (1-x)\beta} \approx x \,
+\end{equation}
+and for the entire variance expression we get
+\begin{equation}
+%\begin{split}
+V(x') \approx  \frac{1}{N} x(1-x)
+\Big(\frac{N + \alpha' xN + \alpha' N - \alpha' xN}{1 + \alpha' xN + \alpha' N - \alpha' xN}\Big)
+= x(1-x)\Big(\frac{1 + \alpha'}{1 + \alpha' N}\Big) \;.
+%\end{split}
+\end{equation}
+Now because $x$ is a constant, $V(x) = 0$, and therefore
 \begin{equation}\label{eq:var_diff_durret}
-V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N})
-\end{equation}
-because $x$ is a constant so $V(x) = 0$
-
-In our model, $\alpha'$ is the odds ratio of a parameter we called "bias weight", denoted in our model as $\alpha$, so:
+V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N}) \;.
+\end{equation}
+$\alpha'$ is the odds ratio of the bias weight, 
 \begin{equation}\label{eq:success_ratio}
-\alpha' = \frac{\alpha}{1-\alpha}
-\end{equation}
-
+\alpha' = \frac{\alpha}{1-\alpha} \;.
+\end{equation}
 Combining \cref{eq:var_diff_durret} and \cref{eq:success_ratio} we get:
@@
 \begin{split}
-V(x'-x) & \approx x(1-x)(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N})\\
- &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\
- &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\
-  &= x(1-x)(\frac{1}{\alpha N + (1-\alpha)})\\
-  &= x(1-x)\frac{1}{N_e}
+V(x'-x) \approx x(1-x)\Big(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N}\Big)
+% &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\
+% &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\
+  = x(1-x)(\frac{1}{\alpha N + (1-\alpha)}) \;.
 \end{split}
 \end{equation}
+This gives the diffusion term of the diffusion equation, which completes the proof.
 \end{proof}
 
-\begin{result}[Fixation probability approximation]
-The fixation probability is estimated by:
+This analysis gives a surprising result relating the parameters $\alpha$ and $\beta$ to parameters of the classical Wright-Fisher model from population genetics:
+the selection coefficient $s$, a measure of the effect of natural selection on the change in frequency of genotypes, and the effective population size, $N_e$, a measure of the effect of random genetic drift on the change in frequency of genotypes.
+In a diffusion-equation approximation of the classical Wright-Fisher model, the expectation and variance of the change in frequency are $E[x'-x]=x+x(1-x)s+o(s)$ and $V[x'-x]=x(1-x)/N_e$ \citep[eq.~7]{kimura}.
+Therefore, we have the following result.\\
+
+\begin{result}[Effective selection coefficient and population size]\label{res:selection_coef}
+The effective selection coefficient $s$ and effective population size $N_e$ can be written in terms of the success coefficient $\beta$ (\cref{eq:success_bias}), the bias weight $\alpha$ (\cref{eq:prestige}), and the population size $N$ as
+\begin{equation}
+s=1-\beta(A), \quad N_e=\alpha N + (1-\alpha) \;.
+\end{equation}
+\end{result}
+
+Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citet[eq.~8]{kimura}, we get the following result.\\
+
+\begin{result}[Fixation probability]
+The fixation probability is approximately
 \begin{equation}\label{eq:kimura_p}
-P_{fix} = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
+\pi = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
 \end{equation}
@@
 \end{result}
-\begin{proof}
-Using our substitute for a selection coefficient, $1-\beta$, and the effective population size $N_e$, we can estimate the fixation probability using the diffusion equation, $E[X'-X]$ (\cref{res:selection_coef}), and $V(X'-X)$ (\cref{res:effective_population}).
-\end{proof}
+
+Similarly, we can use $1-\beta$ and $N_e$ in the population-genetics fixation time approximation given by \citet[eq.~8]{kimura_average}.\\
 
@@
 \begin{equation}\label{eq:kimura_t}
-T_{fix}=\frac{1-P_{fix}}{1-\beta}\int_0^x\frac{e^{2(1-\beta) \xi}-1}{\xi(1-\xi)}d\xi+ \frac{P_{fix}}{1-\beta}\int_x^1\frac{1-e^{-2(1-\beta)(1-\xi)}}{\xi(1-\xi)}d\xi
-\end{equation}
+T = \frac{1-\pi}{1-\beta}\int_0^x\frac{e^{2(1-\beta) \xi}-1}{\xi(1-\xi)}d\xi+ \frac{\pi}{1-\beta}\int_x^1\frac{1-e^{-2(1-\beta)(1-\xi)}}{\xi(1-\xi)}d\xi
+\end{equation}
+% TODO double check this, because eq 17 in Kimura 1969 looks different.
+% in particular, I don't see Ne here...
 \end{result}
-
-\begin{proof}
-Again using the diffusion equation and \cref{res:selection_coef,res:effective_population}, we get our result.
-the integrals cannot be solved in closed form, so we can only estimate them numerically.
-\end{proof}
-
-\paragraph{Numeric validation.}
-To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
-In \cref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
-In \cref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
-In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations: \cref{eq:kimura_p} and \cref{eq:kimura_t}.
+Note that these integrals cannot be solved in closed form, so we can only estimate them numerically.
+
+\paragraph{Numerical validation.}
+To validate our analysis we performed multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s=1-\beta$ and $N_e=\alpha N + (1-\alpha)$ for the Wright-Fisher simulations.
+%In \cref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
+%In \cref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
+We find see that the two models have similar dynamics, and both are well approximated the the approximations in \cref{eq:kimura_p,eq:kimura_t}.
 
 \begin{figure}[h]
+% TODO 
+% capital letters in panel labels
+% bigger font
     \includegraphics[width=\linewidth]{../figures/binary/kimura_var_alpha.pdf}
-  \caption{\textbf{Goodness of fit of Kimura's approximation for varying bias weights.}
-  The approximation (black) fits DM simulations results (green) and Wright Fisher simulation results (orange) when using \cref{eq:kimura_p}.
-  Fixation probability (a) is limited at approximately $2s$ (blue), like the classic WF model.
-  Markers for average values across $5,000$ simulations, error bars for 95\% confidence intervals.
+  \caption{\textbf{Fixation probability and time approximation for varying bias weight.}
+  Fixation probability (\textbf{a}) and time (\textbf{b}) for varying bias weight on the bottom x-axis. The corresponds effective population size is on the top x-axis.
+  The approximation (black) fits DM simulations results (green) and Wright-Fisher simulation results (orange) when using \cref{eq:kimura_p}.
+  Fixation probability (a) is limited at approximately $2s$ (blue), as in the classic WF model.
+  Markers are averages of $5,000$ simulations, error bars show 95\% confidence intervals.
    Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$; success coefficient, $1-\beta=s=0.044$.}
@@
     \includegraphics[width=\linewidth]{../figures/binary/kimura_var_beta.pdf}
-  \caption{\textbf{Goodness of fit of Kimura's approximation for varying success coefficients.}
+  \caption{\textbf{Fixation probability and time approximation for varying success coefficient.}
+  % TODO
+  % merge with previous figure; see comments there.
    The approximation (black) fits DM simulations results (green) and Wright Fisher simulation results (orange) when using \cref{eq:kimura_p}.
@@
 
-After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.
-
-For that we will find an expression for the expected and variance of the change in frequency between $t$ generations.
-Let $s_t=N(1-\beta_t)$, and $S_n=\sum\limits_{i=1}^n s_i$, where $\beta_t$ is $\beta(A)$ at time/generation $t$.
-
-\begin{result} [Expected difference in frequency in a changing environment]\label{res:ch_expected}
-$E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
+After finding a good approximation for our model in a constant environment, when the favorable trait is always $\hat{A}$, we continued to find an approximation for our model in a changing environment.
+Following \citet{changeEnv}, we find the following expressions for the expectation and variance of the change in frequency between $t$ generations.\\
+
+\begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
+Let $x$ be the initial frequency of the invading phenotype and $X_t$ is the number of individuals with the phenotype at time $t$.
+Then,
+\begin{equation}\label{eq:ch_expected_and_var}
+E[X_t/N - x] \simeq x(1-x) S_t / N \;, 
+\quad
+V(X_t/N ) \simeq x(1-x) t/N_e \;, % TODO shouldn't it be V[X_t/N - x] ?? or something like that? with square brackets and with "- something" ?
+\end{equation}
+where $S_t=\sum\limits_{i=1}^{t} N (1-\beta_t)$.
 \end{result}
-\begin{result}[Variance of difference in frequency in a changing environment]\label{res:ch_var}
-$V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
-\end{result}
 
 \begin{proof}
-Following the proof of \citet{changeEnv}, we prove by induction. We will prove \cref{res:ch_expected,res:ch_var} together, because the induction assumptions are needed for both.
-
+Let $s_t=N(1-\beta_t)$, and $S_n=\sum\limits_{i=1}^n s_i$, where $\beta_t$ is $\beta(A)$ at generation $t$.
+We prove by induction both terms in \cref{eq:ch_expected_and_var}.
 From \cref{eq:expec_freq} we know that
 \begin{equation}\label{eq:ch_1}
+%\begin{split}
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] 
+= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) 
+= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1} \;.
+%\end{split}
+\end{equation}
+Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
+\begin{equation}
 \begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\
-&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
+E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
+&= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] 
+= E\left[\frac{X_t}{N}\right] - E\left[\left(\frac{X_t}{N}\right)^2\right] \\
+&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2 \;.
 \end{split}
 \end{equation}
-Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
+
+We can now use the induction assumption of $V(\frac{X_t}{N})$ to get
 \begin{equation}
 \begin{split}
-E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\
-&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\
-&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
+E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
+&\simeq E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x) \;.
 \end{split}
 \end{equation}
-
-we can now use the induction assumption of $V(\frac{X_t}{N})$ and get
+From \cref{eq:ch_1} we know that
 \begin{equation}
 \begin{split}
-E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &\simeq
-E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x)
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
+&= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
+\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\
+&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x) \;.
 \end{split}
 \end{equation}
-From \cref{eq:ch_1} we know that
+Now we omit $O(\frac{1}{Ne\cdot N})$ and get
+\begin{equation}\label{eq:ch_2}
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) \;.
+\end{equation}
+
+We now look at the induction assumption to see that
+\begin{equation}
+E\left[\frac{X_t}{N}-x\right]
+= E\left[\frac{X_t}{N}\right]-E[x]
+= E\left[\frac{X_t}{N}\right]-x \;,
+\end{equation}
+so using the assumption we get
 \begin{equation}
 \begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] \\
-&\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\
-&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x)
+E\left[\frac{X_t}{N}\right] 
+&\simeq \frac{1}{N} S_t x(1-x)+x \\
+1 - E\left[\frac{X_t}{N}\right] 
+&\simeq 1- \frac{1}{N} S_t x(1-x)+x \;.
 \end{split}
 \end{equation}
-Now we'll omit $O(\frac{1}{Ne\cdot N})$ and get
-\begin{equation}\label{eq:ch_2}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)
-\end{equation}
-
-We'll now look at the induction assumption to see that
-\begin{equation}
-E\left[\frac{X_t}{N}-x\right]=E\left[\frac{X_t}{N}\right]-E[x]=E\left[\frac{X_t}{N}\right]-x ,
-\end{equation}
-so using the assumption we get
-\begin{equation}
-\begin{split}
-E\left[\frac{X_t}{N}\right] &\simeq \frac{1}{N} S_t x(1-x)+x \\
-1 - E\left[\frac{X_t}{N}\right] &\simeq 1- \frac{1}{N} S_t x(1-x)+x
-\end{split}
-\end{equation}
-we'll use both expressions in \cref{eq:ch_2} and get
+We use both expressions in \cref{eq:ch_2} and get
 \begin{equation}\label{eq:ch_3}
 \begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
-&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x)
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
+&\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
+&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x) \;,
 \end{split}
 \end{equation}
-after again omitting $O(\frac{1}{N^2})$ parts of the equation.
-To conclude our proof, we see that
-\begin{equation}
-E\left[\frac{X_{t+1}}{N}-x\right] = E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right]
+after again omitting $O(\frac{1}{N^2})$ terms.
+To conclude the proof, we note that
+\begin{equation}
+E\left[\frac{X_{t+1}}{N}-x\right] 
+= E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right] \;,
 \end{equation}
@@
 \begin{split}
-E\left[\frac{X_{t+1}}{N}-x\right] &\simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
-& \simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) \\
-& \simeq \frac{1}{N} S_{t+1} x(1-x)
+E\left[\frac{X_{t+1}}{N}-x\right] \simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
+\simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) 
+\simeq \frac{1}{N} S_{t+1} x(1-x) \;,
 \end{split}
 \end{equation}
-which proves \cref{res:ch_expected}.
-
-For \cref{res:ch_var}, we'll use a property of variance:
+which proves the drift term.
+
+For the diffusion term, we use a property of variance,
 \begin{equation}\label{eq:ch_var}
-V\left(\frac{X_{t+1}}{N}\right) = E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right)
-\end{equation}
-
-using \cref{eq:ch_1} we see that:
+V\left(\frac{X_{t+1}}{N}\right) 
+= E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) \;.
+\end{equation}
+
+Using \cref{eq:ch_1} we see that
 \begin{equation}\label{eq:ch_var1}
+% TODO check this - looks weird that you have such a similar expression on the left side
 \begin{split}
-E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] &= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\
-E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] = \frac{X_t}{N} &+ \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right)
+&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] 
+= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\
+&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] 
+= \frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;.
 \end{split}
@@
 
-Using \cref{eq:const_var} we get:
-\begin{equation}
-V\left(\frac{X_{t+1}}{N} \bigg|X_t \right) = \frac{1}{N_e}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right)
-\end{equation}
-
-and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of \cref{eq:ch_var} we get:
+Using \cref{eq:const_var} we get
+\begin{equation}
+V\left(\frac{X_{t+1}}{N} \bigg|X_t \right) 
+= \frac{1}{N_e}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;,
+\end{equation}
+and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of \cref{eq:ch_var} we get
 \begin{equation}\label{eq:ch_var2}
-E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] = \frac{1}{N_e}E\left[\frac{X_t}{N}\left(1- \frac{X_t}{N}\right) \right] \simeq \frac{1}{N_e} x(1-x)
-\end{equation}
-
-and moving on to simplify the second part of \cref{eq:ch_var} using \cref{eq:ch_var1}:
-\begin{equation}
-V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) = V\left(\frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)
-\end{equation}
-
-and now, because $\frac{X_t}{N}$ is a frequency, i.e $0\leq\frac{X_t}{N}\leq1$, we know that $V\left(\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq\frac{1}{4}$. We therefore see that:
-\begin{equation}
-V\left(\frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq \frac{1}{4N^2}s^2_{t+1}
+E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] 
+= \frac{1}{N_e}E\left[\frac{X_t}{N}\left(1- \frac{X_t}{N}\right) \right] \simeq \frac{1}{N_e} x(1-x) \;.
+\end{equation}
+Moving on to simplify the second part of \cref{eq:ch_var} using \cref{eq:ch_var1},
+\begin{equation}
+V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
+= V\left(\frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \;.\right) \right)
+\end{equation}
+Now, because $\frac{X_t}{N}$ is a frequency, i.e $0 \leq X_t/N \leq 1$, we know that $V\left(\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq\frac{1}{4}$. We therefore find that
+\begin{equation}
+V\left(\frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)
+\leq \frac{1}{4N^2}s^2_{t+1} ;,
 \end{equation}
 and so it can be ignored.
-Combining our equations we get:
-\begin{equation}
-V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) = V\left(\frac{X_t}{N}\right) + O\left(\frac{1}{N^2}\right)\simeq V\left(\frac{X_t}{N}\right)
-\end{equation}
-
-Using the induction assumption and \cref{eq:ch_var2}:
-\begin{equation}
-V\left(\frac{X_{t+1}}{N}\right) \simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1)
-\end{equation}
-proving \cref{res:ch_var}.
+Combining our equations we get
+\begin{equation}
+V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
+= V\left(\frac{X_t}{N}\right) + O\left(\frac{1}{N^2}\right)\simeq V\left(\frac{X_t}{N}\right) \;.
+\end{equation}
+Using the induction assumption and \cref{eq:ch_var2},
+\begin{equation}
+V\left(\frac{X_{t+1}}{N}\right) 
+\simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1) \,
+\end{equation}
+which proves the diffusion term.
 \end{proof}
 
-Following our proof, we can say that after many cycles, we can use a modified version of our fixation probability:
+Using the drift and diffusion terms and following \citet{changeEnv}, we can approximate the fixation probability in a changing environment using
 \begin{equation}\label{eq:ch_env}
-P_{fix} = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
-\end{equation}
-where $\frac{S_n}{n} = \frac{k-l}{k+l}(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
-In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.
+\tilde\pi = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
+\end{equation}
+where $\frac{S_n}{n} = \frac{k-l}{k+l}(1-\beta)$ and $n=k+l$.
+That is, we use the average selection coefficient during a cycle of $k+l$ generations as the selection coefficient \cref{eq:kimura_p}.
+% TODO what are you saying in the next paragraph?
+%In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.
+
+\paragraph{Numerical validation.}
+Comparing our approximation (\cref{eq:ch_env}) to numerical simulations, we find that the approximation fits simulations results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}a).
+
+However, the approximation is more sensitive to the value of the success bias coefficient $\beta$ (\Cref{fig:ch_env_alpha_beta}b).
+We suspect that when $\beta$ is too small, there will not be many cycles in the simulations, because either the population reaches a high frequency of the fitter phenotype after just a few cycles, or the fitter phenotype becomes extinct very quickly.
+For the very low $\beta$ values (0.65 and below),% TODO is that really "very low?"
+the fixation probability exceeds even the constant environment approximation (which is the upper limit).
+However, this is to be expected, because the diffusion-equation approximations assume weak selection (i.e., low selection coefficient $s$).
+
+% TODO what is k and l?
+We found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=40$) the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:p_kimura}), see \Cref{fig:ch_env_k_l}.
+When using higher values of $n$, the agreement between the approximation and simulation results is weaker. % TODO reference to figure?
+This is because our approximation is more precise when more cycles occur in the simulations. % TODO "in the simulations"-right?
+When $n$ is high, the cycles are longer, the dynamics are therefore similar to a constant environment, and fixation or extinction is more likely to happen before the next cycle.
+Thus, there will be less cycles, which lowers our approximation precision.
 
 \begin{figure}[h]
+% TODO
+% See comments on previous figures
+% make x axes as before, with alpha on bottom and Ne on top
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var.pdf}
-  \caption{\textbf{Robustness of approximation in a changing environment to varying success coefficient and success bias weight.}
- Markers for average values across $10,000$ simulations, error bars for (a) are 75\% confidence intervals, and 95\% for (b).
-The approximation (blue) given by \cref{eq:ch_env} fits simulation results (orange) well when the effective population size varies (a).
-On (b) we see that for high values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values.
-Very high values ($s>0.35$) will even deviate from the constant environment expected values (green) given by \cref{eq:kimura_p}.
-This is expected because Kimura's approximation are only viable for low selection coefficient values.
+  \caption{\textbf{Sensitivity of fixation probability approximation in a changing environment to varying success coefficient and bias weight.}
+\textbf{)a)} When the bias weight, or effective population size varies, the approximation (blue; \cref{eq:ch_env}) fits simulation results (orange). 
+\textbf{(b)} When success bias is large ($\beta > 0.1$),  % TODO it was s>0.1, and O changed to beta>0.1 because that's what the x axes says, but I am not sure, as below you say the approximation works for weak selection, and s=1-beta, so large beta should give weak selection...
+please check
+simulation results (orange) are underestimated by the approximation (blue; \cref{eq:ch_env}).
+With even larger success bias ($\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) underestimate simulation results, likely because the diffusion equation approximation assumes weak selection.
+Markers show average of $10,000$ simulations, error bars show are 75\% (a) and 95\% (b) confidence intervals.
   Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$; \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success bias weight is: $\alpha=0.1$. 
@@
 
-We validate our results using simulations.
-We find that $\alpha$ does not have a significant effect on the approximations (\cref{fig:ch_env_alpha_beta}).
-However, $\beta$ does.
-
-We suspect that when $1-\beta$ is too large, there won't be many cycles in the simulations.
-This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or the fitter phenotype get extinct very quickly.
-For the very high $1-\beta$ values (0.35 and above), the fixation probability exceeds even the constant environment approximation (which is the upper limit), but it's to be expected, because Kimura's equations are only appropriate for weak fitness (i.e., low selection coefficients, $s$).
-
 \begin{figure}[h]
+% TODO
+% merge with previous figure and edit the caption accordingly.
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_l.pdf}
@@
 \end{figure}
-
-We also examined the effect of different choices of $k$ and $l$ while keeping a constant total cycle length, $n=k+l=40$.
-We found that larger $k$-to-$l$ ratio increases the agreement between the changing environment equation and the original estimation of the constant environment. 
-When using higher values of $n$, the agreement between the approximation and simulation results is weaker.
-This is because our approximation is more precise when more cycles occur.
-When $n$ is high, the cycles are longer.
-When the cycles are long, the settings are similar to a constant environment equation, and fixation/extinction is more likely to happen.
-This means there will be less cycles, which lowers our approximation accuracy.
 

### 2022-06-06 ms/PrestigeBias.tex
update

@@
 Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
-Other than its relative ease of evaluation, compared to the evaluation of the actual trait, choosing a role-model based on previous choices made may be advantageous on its own. % TODO rephrase
-This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity,% TODO cite doi 10.1111/j.1420-9101.2011.02236.x
- which depend on the frequency of a trait in the population or in a sample of role-models. 
+In addition to using influence bias as an easy way to approximate role-models worth, it can also be a used to approximate it better than the copier's own estimation.
+This bias can save the copier costs: time, effort etc, and it can also improve its choice of role-model.
+
+This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity \citep{kin_selection}, which depend on the frequency of a trait in the population or in a sample of role-models.
  We define a model of cultural transmission with prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
@@
 We focus on the fixation probability and fixation time of an advantageous phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
-We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias. % TODO ref eq 10?
-For simplicity, we do not include role-model estimation error in this analysis. % TODO meaning epsilon=0?
+We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
+For simplicity, we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
 As shown above, transmission in our model is approximately DM distributed (\cref{cor:dirichlet} and \cref{eq:copier_choose}).
@@
 
-Similarly, we can use $1-\beta$ and $N_e$ in the population-genetics fixation time approximation given by \citet[eq.~8]{kimura_average}.\\
+Similarly, we can use $1-\beta$ and $N_e$ in the population-genetics fixation time approximation given by \citet[eq.~17]{kimura_average}.\\
 
 \begin{result}[Fixation time approximation]
+\begin{equation}
+T = J_1 + \frac{1-u(x)}{u(x)}\cdot J_2,
+\end{equation}
+where, given $S=Ne(1-\beta)$ and $x=\frac{1}{N_e}$,
+\begin{equation}
+u(x)=\frac{1-e^{-2Sx}}{1-e^{2S}}
+\end{equation}
+and,
+\begin{equation}
+J_1 = \frac{2}{(1-\beta)(1-e^{-2S})}\int_x^1 \frac{(e^{2S\xi}-1)(e^{-2S\xi}-e^{-2S})}{\xi(1-\xi)}d\xi,
+\end{equation}
+\begin{equation}
+J_2= \frac{2}{(1-\beta)(1-e^{-2S})}\int_0^p \frac{(e^{2S\xi}-1)(1-e^{-2S\xi})}{\xi(1-\xi)}d\xi
+\end{equation}
+
 \begin{equation}\label{eq:kimura_t}
@@
 \end{equation}
-% TODO double check this, because eq 17 in Kimura 1969 looks different.
-% in particular, I don't see Ne here...
 \end{result}
@@
 To validate our analysis we performed multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s=1-\beta$ and $N_e=\alpha N + (1-\alpha)$ for the Wright-Fisher simulations.
-%In \cref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
-%In \cref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
+
 We find see that the two models have similar dynamics, and both are well approximated the the approximations in \cref{eq:kimura_p,eq:kimura_t}.
@@
 \begin{figure}[h]
-% TODO 
-% capital letters in panel labels
-% bigger font
-    \includegraphics[width=\linewidth]{../figures/binary/kimura_var_alpha.pdf}
-  \caption{\textbf{Fixation probability and time approximation for varying bias weight.}
-  Fixation probability (\textbf{a}) and time (\textbf{b}) for varying bias weight on the bottom x-axis. The corresponds effective population size is on the top x-axis.
+    \includegraphics[width=\linewidth]{../figures/binary/kimura_var.pdf}
+  \caption{\textbf{Fixation probability and time approximation for varying bias weight and success coefficient.}
+  Fixation probability (\textbf{A}) and time (\textbf{B}) for varying bias weight on the bottom x-axis. The corresponds effective population size is on the top x-axis.
   The approximation (black) fits DM simulations results (green) and Wright-Fisher simulation results (orange) when using \cref{eq:kimura_p}.
-  Fixation probability (a) is limited at approximately $2s$ (blue), as in the classic WF model.
-  Markers are averages of $5,000$ simulations, error bars show 95\% confidence intervals.
-   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$; success coefficient, $1-\beta=s=0.044$.}
+  Fixation probability (\textbf{A}) is limited at approximately $2s$ (blue), as in the classic WF model.
+  Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for (\textbf{A,B}) and 75\% for (\textbf{C,D}).
+   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (\textbf{A,B}), $A=a\cdot \hat{A}, a \in [0.01,0.99]$ (\textbf{C,D}); success coefficient, $1-\beta=s=0.044$ (\textbf{A,B}); bias weight, $\alpha=0.01$ (\textbf{C,D}).}
   \label{fig:var_alpha}
-\end{figure}
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/binary/kimura_var_beta.pdf}
-  \caption{\textbf{Fixation probability and time approximation for varying success coefficient.}
-  % TODO
-  % merge with previous figure; see comments there.
-   The approximation (black) fits DM simulations results (green) and Wright Fisher simulation results (orange) when using \cref{eq:kimura_p}.
-  Markers for average values across $5,000$ simulations, error bars for 75\% confidence intervals.
- Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=a\cdot \hat{A}, a \in [0.01,0.99]$; bias weight, $\alpha=0.01$.}
-  \label{fig:var_beta}
 \end{figure}
@@
 \quad
-V(X_t/N ) \simeq x(1-x) t/N_e \;, % TODO shouldn't it be V[X_t/N - x] ?? or something like that? with square brackets and with "- something" ?
+V(X_t/N-x) = V(X_t/N) \simeq x(1-x) t/N_e \;,
 \end{equation}
@@
 \begin{equation}\label{eq:ch_var1}
-% TODO check this - looks weird that you have such a similar expression on the left side
 \begin{split}
@@
 That is, we use the average selection coefficient during a cycle of $k+l$ generations as the selection coefficient \cref{eq:kimura_p}.
-% TODO what are you saying in the next paragraph?
-%In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.
 
 \paragraph{Numerical validation.}
-Comparing our approximation (\cref{eq:ch_env}) to numerical simulations, we find that the approximation fits simulations results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}a).
-
-However, the approximation is more sensitive to the value of the success bias coefficient $\beta$ (\Cref{fig:ch_env_alpha_beta}b).
+Comparing our approximation (\cref{eq:ch_env}) to numerical simulations, we find that the approximation fits simulations results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
+
+However, the approximation is more sensitive to the value of the success bias coefficient $\beta$ (\Cref{fig:ch_env_alpha_beta}B).
 We suspect that when $\beta$ is too small, there will not be many cycles in the simulations, because either the population reaches a high frequency of the fitter phenotype after just a few cycles, or the fitter phenotype becomes extinct very quickly.
-For the very low $\beta$ values (0.65 and below),% TODO is that really "very low?"
-the fixation probability exceeds even the constant environment approximation (which is the upper limit).
+For the $\beta$ values (0.65 and below), the fixation probability exceeds even the constant environment approximation (which is the upper limit).
 However, this is to be expected, because the diffusion-equation approximations assume weak selection (i.e., low selection coefficient $s$).
 
-% TODO what is k and l?
-We found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=40$) the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:p_kimura}), see \Cref{fig:ch_env_k_l}.
-When using higher values of $n$, the agreement between the approximation and simulation results is weaker. % TODO reference to figure?
-This is because our approximation is more precise when more cycles occur in the simulations. % TODO "in the simulations"-right?
-When $n$ is high, the cycles are longer, the dynamics are therefore similar to a constant environment, and fixation or extinction is more likely to happen before the next cycle.
-Thus, there will be less cycles, which lowers our approximation precision.
+When $k$ is the number of generations where the invading phenotype is advantageous, and $l$ when the original trait is, we found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}), see \Cref{fig:ch_env_alpha_beta} (C,D).
 
 \begin{figure}[h]
-% TODO
-% See comments on previous figures
-% make x axes as before, with alpha on bottom and Ne on top
-    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var.pdf}
-  \caption{\textbf{Sensitivity of fixation probability approximation in a changing environment to varying success coefficient and bias weight.}
-\textbf{)a)} When the bias weight, or effective population size varies, the approximation (blue; \cref{eq:ch_env}) fits simulation results (orange). 
-\textbf{(b)} When success bias is large ($\beta > 0.1$),  % TODO it was s>0.1, and O changed to beta>0.1 because that's what the x axes says, but I am not sure, as below you say the approximation works for weak selection, and s=1-beta, so large beta should give weak selection...
-please check
+    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env.pdf}
+  \caption{\textbf{Sensitivity of fixation probability approximation in a changing environment to varying success coefficient and bias weight and robustness to varying ratios of cycles.}
+\textbf{(A)} When the bias weight, or effective population size varies, the approximation (blue; \cref{eq:ch_env}) fits simulation results (orange). 
+\textbf{(B)} When success bias is large ($1-\beta > 0.1$),  
 simulation results (orange) are underestimated by the approximation (blue; \cref{eq:ch_env}).
-With even larger success bias ($\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) underestimate simulation results, likely because the diffusion equation approximation assumes weak selection.
-Markers show average of $10,000$ simulations, error bars show are 75\% (a) and 95\% (b) confidence intervals.
-  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$; \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success bias weight is: $\alpha=0.1$. 
-  }
+With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) underestimate simulation results, likely because the diffusion equation approximation assumes weak selection.
+We can also see the robustness of the approximation to changes in cycle ratios (\textbf{C,D}): The approximation (blue) fits the simulations (orange) well for different sizes of the changing environment cycle, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
+When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green). 
+Markers show average of $10,000$ simulations, error bars show are 75\% \textbf{(A,C,D)} and 95\% \textbf{(B)} confidence intervals.
+  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$ (\textbf{A,B}), $A=0.8$ \textbf{(C,D)}; In \textbf{(A)} success bias/selection coefficient is: $1-\beta=s=0.005$; In \textbf{(B,C,D)} success bias weight is: $\alpha=0.1$.}
   \label{fig:ch_env_alpha_beta}
@@
 
-\begin{figure}[h]
-% TODO
-% merge with previous figure and edit the caption accordingly.
-    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_l.pdf}
-  \caption{\textbf{Robustness of approximation in a changing environment to varying sizes of the cycles.} 
-Markers for average values across $10,000$ simulations, error bars are 95\% confidence intervals.
-The approximation (blue) fits the simulations (orange) well for different sizes of the changing environment cycle, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
-   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green). 
- Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.8$; success coefficient, $1-\beta=s=0.02$; success bias weight, $\alpha=0.1$.}
-  \label{fig:ch_env_k_l}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal $\alpha$ value.
-This is the $\alpha$ value that minimizes the mean error in estimation.
-% TODO estimation of what?
-This is computed by minimizing the mean difference between the estimated value of every role-model and the ideal trait value $\hat{A}$. % TODO write the explicit equation
-
-We see in \cref{fig:influence_advantage,fig:const_influence} a comparison between a model where every copier chooses its ideal success bias weight $\alpha_{ij}$, and when $\alpha$ is a constant homogeneous value.
-We find that when copiers adapt their success-bias weight, their success-bias weight decreases with the number of copiers that have already chose a role-model~(\cref{fig:influence_advantage}a).
+This is the $\alpha$ value that minimizes the mean square error of the difference between the estimated and the ideal trait values.
+This $\alpha$ is found by minimizing the following:
+\begin{equation}
+SMSE = \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2
+\end{equation}
+where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose him.
+
+We see in \cref{fig:influence_advantage} a comparison between a model where every copier chooses its ideal success bias weight $\alpha_{ij}$, and when $\alpha$ is a constant homogeneous value.
+We find that when copiers adapt their success-bias weight, their success-bias weight decreases with the number of copiers that have already chose a role-model~(\cref{fig:influence_advantage}).
 Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \cref{fig:influence_advantage}b and c): the estimation error converges to $0.046$ whereas a constant weight gives values $>0.74$ in this example.
@@
     \includegraphics[width=\linewidth]{../figures/influence_advantage/choose_bias.pdf}
-    % TODO
-    % fonts too small
-    % capital letters in labels
-    % add "alpha" to ylabel in panel a
-    % "mean estimation error" in y label of panel b
-	% can you maybe add two more lines with different colors on the same plots for other parameters choices? say larger pop size or larger error?
   \caption{
   \textbf{Advantage of an adaptive success-bias weight.}
-  Both success-bias weight $\alpha$ (\textbf{a}) and estimation error (\textbf{b}) 
-   decrease during the role-model choosing process, demonstrating that influence is becomes more advantageous as more copiers have made their choice.
-   Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
+  Both success-bias weight $\alpha$ (\textbf{a}) and estimation error (\textbf{b}) decrease during the role-model choosing process, demonstrating that influence is becomes more advantageous as more copiers have made their choice.
+However, when $\alpha$ is homogeneous, the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
+The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the adaptive $\alpha$ model.
+     Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$; standard deviation $\eta=0.0001 (blue), 0.001 (orange), 0.01 (green)$, plots are average of $300$ simulations.}
   \label{fig:influence_advantage}
@@
 
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/influence_advantage/const_bias.pdf}
-    % TODO 
-    % merge with previous plot
-  \caption{
-  \textbf{Estimation error when using constant success bias weight.}
-  The mean estimation error doesn't have any significant improvement relative to when every copier chooses a bias for himself.
-  The minimum error is no less than $0.74$, while the mean error of the model where $\alpha$ is chosen is $0.06$, converging to $0.046$, which is a factor of $10$ less than the constant $\alpha$ model, showing the clear advantage of choosing $\alpha$.
-  Here, population size $N=200$, estimation error is normally distributed $e \sim N(0,\eta^2)$, standard deviation $\eta=0.0005$, plots are average of $300$ simulations.}	
-  \label{fig:const_influence}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
 \section*{Discussion}
@@
 
-In addition, we see that the process of choosing itself is necessary, and when using a constant ratio ($\alpha$), the mean estimation error in the population is greater by a factor of $10$, even when using the $\alpha$ the population converged to when being able to choose it (\cref{fig:const_influence}).
+In addition, we see that the process of choosing itself is necessary, and when using a constant ratio ($\alpha$), the mean estimation error in the population is greater by a factor of $10$, even when using the $\alpha$ the population converged to when being able to choose it (\cref{fig:influence_advantage}).
 After we showing that choosing one's success bias weight is beneficial to the copier, we continued to create our models- continuous and dichotomous, that incorporated both success and influence.
@@
 Using the DM approximation, because it is easier to analyze, we found equivalents for Kimura's equations, for our dichotomous model.
-Following \cref{res:selection_coef,res:effective_population} we found an approximation for the fixation probability of the ideal trait, and an approximation for the time of fixation.
+Following \cref{res:selection_coef} we found an approximation for the fixation probability of the ideal trait, and an approximation for the time of fixation.
 These approximations hold only when the equivalent for the selection coefficient, in our model $1-\beta(A)$, is low (0.4 or lower).
@@
 Once we found the equations for a constant environment, we moved on to a cyclic changing environment.
-Based on \cref{res:ch_expected,res:ch_var}, we found the approximations for the fixation probability and time to fixation.
+Based on \cref{res:ch_expected}, we found the approximations for the fixation probability and time to fixation.
 We discovered that as in the constant environment, the effective population size doesn't affect the goodness of fit of the approximation.

### 2022-06-11 ms/PrestigeBias.tex
update

@@
 % title page stuff
-\title{Prestige as a Driving Force in Cultural Transmission}
+\title{Cultural Evolutionary Dynamics with Success and Influence biases}
 
@@
 These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
-It also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
+Influence bias also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
 Our model may provide a good description of cultural transmission, 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Models and Methods}
+\section*{Models and methods}
 
@@
 We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
-
 Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
@@
     \includegraphics[width=\linewidth]{../figures/binary/kimura_var.pdf}
+    % TODO - black line for 2s as well
   \caption{\textbf{Fixation probability and time approximation for varying bias weight and success coefficient.}
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \includegraphics[width=\linewidth]{../figures/changed_env/ch_env.pdf}
@@
 
-We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal $\alpha$ value.
-This is the $\alpha$ value that minimizes the mean square error of the difference between the estimated and the ideal trait values.
-This $\alpha$ is found by minimizing the following:
-\begin{equation}
-SMSE = \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2
-\end{equation}
-where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose him.
-
-We see in \cref{fig:influence_advantage} a comparison between a model where every copier chooses its ideal success bias weight $\alpha_{ij}$, and when $\alpha$ is a constant homogeneous value.
-We find that when copiers adapt their success-bias weight, their success-bias weight decreases with the number of copiers that have already chose a role-model~(\cref{fig:influence_advantage}).
-Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \cref{fig:influence_advantage}b and c): the estimation error converges to $0.046$ whereas a constant weight gives values $>0.74$ in this example.
-
-\begin{figure}[b!]
+We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the estimated and the ideal trait values,
+\begin{equation}
+\alpha^* = \textit{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2 \;,
+\end{equation}
+where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model $j$.
+
+We find that when copiers adapt their success-bias weight, it decreases with the number of copiers that have already chosen a role-model~(\cref{fig:influence_advantage}).
+Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \cref{fig:influence_advantage}b and c): in this example, the adaptive weight estimation error converges to $0.046$, whereas a constant weight gives values $>0.74$.
+
+\begin{figure}[H]
     \includegraphics[width=\linewidth]{../figures/influence_advantage/choose_bias.pdf}
+    % TODO - capital letters for all axis lables
+    % letter follows the description (success-bias weight, \alpha
+    % show plot of error bars and a scatter for the constant bias weight (no trend)
   \caption{
@@
 The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the adaptive $\alpha$ model.
-     Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$; standard deviation $\eta=0.0001 (blue), 0.001 (orange), 0.01 (green)$, plots are average of $300$ simulations.}
+Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}
   \label{fig:influence_advantage}

### 2022-06-12 ms/PrestigeBias.tex
update

@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/chi_square_stats/GBD_validation.pdf}
+    \includegraphics[width=\linewidth]{../figures/final/GBD_validation.pdf}
   \caption{
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/chi_square_stats/DM_validation.pdf}
+    \includegraphics[width=\linewidth]{../figures/final/DM_validation.pdf}
   \caption{
   \textbf{Goodness of fit of Dirichlet-Multinomial approximation to the model.}
-  The difference between the DM approximation distribution to observed model distribution (a) is very small, with the highest difference at 0.5 role-models.
+  The difference between the DM approximation distribution to observed model distribution (a) is very small.
+The DM approximation (orange) and the simulation results (blue) are almost indistinguishable.
   The optimal negative log likelihood (b) is given when using the DM approximation (black vertical line), and is much better when compared to a shuffled vector of the DM distribution (blue bars).
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
+    \includegraphics[width=\linewidth]{../figures/final/num_sims.pdf}
   \caption{
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
+    \includegraphics[width=\linewidth]{../figures/final/full_vs_dm_mutation.pdf}
   \caption{
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
+    \includegraphics[width=\linewidth]{../figures/final/full_vs_dm_changing_alpha.pdf}
    \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/binary/kimura_var.pdf}
-    % TODO - black line for 2s as well
+    \includegraphics[width=\linewidth]{../figures/final/kimura_var.pdf}
   \caption{\textbf{Fixation probability and time approximation for varying bias weight and success coefficient.}
@@
 \begin{figure}[H]
-    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env.pdf}
+    \includegraphics[width=\linewidth]{../figures/final/ch_env.pdf}
   \caption{\textbf{Sensitivity of fixation probability approximation in a changing environment to varying success coefficient and bias weight and robustness to varying ratios of cycles.}
@@
 \begin{figure}[H]
-    \includegraphics[width=\linewidth]{../figures/influence_advantage/choose_bias.pdf}
-    % TODO - capital letters for all axis lables
-    % letter follows the description (success-bias weight, \alpha
-    % show plot of error bars and a scatter for the constant bias weight (no trend)
+    \includegraphics[width=\linewidth]{../figures/final/choose_bias.pdf}
   \caption{

### 2022-06-13 ms/PrestigeBias.tex
update

@@
 \documentclass[12pt]{extarticle}
+
+\makeatletter
+
+\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
+
+\makeatother
+
 \usepackage{geometry}
@@
  \renewcommand\linenumberfont{\normalfont\small\sffamily}
-\linenumbers
+%\linenumbers
 \modulolinenumbers[2]
@@
 
+\begin{document}
+
+\begin{titlepage}
+	\centering
+	\includegraphics[width=0.4\textwidth]{ReichmanLogo}\par\vspace{1cm}
+	{\huge Reichman University \par}
+	{\Large Efi Arazi School of Computer Science \par}
+	{\Large M.Sc. Program - Research Track \par}
+
+	\vspace{1.5cm}
+	{\Huge Cultural Evolutionary Dynamics with Success and Influence biases\par}
+	\vspace{1.5cm}
+	{\large by\par}
+	{\Large\bfseries Saar Egozi\par}
+	\vspace{1cm}
+	{\large Supervised by Dr. Yoav Ram\par}
+	{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel\par}
+	{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel \par}
+
+	\vspace{1cm}
+	{M.Sc. dissertation, submitted in partial fulfillment of the requirements\par}
+	{for the M.Sc. degree, research track, School of Computer Science\par}
+	{Reichman University}
+
+	\vspace{1cm}
+	% Bottom of the page
+	{\large \today \par}
+
+\end{titlepage}
+
 % title page stuff
-\title{Cultural Evolutionary Dynamics with Success and Influence biases}
-
-\renewcommand\Affilfont{\small}
-\author[1]{Saar Egozi}
-\author[2,3,*]{Yoav Ram}
-\affil[1]{School of Computer Science, Reichman University, Herzliya 4610101, Israel}
-\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
-\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel}
-\affil[*]{Corresponding author: yoav@yoavram.com, ORCID 0000-0002-9653-4458}
-
-\date{\today}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
+%\title{Cultural Evolutionary Dynamics with Success and Influence biases}
+
+%\renewcommand\Affilfont{\small}
+%\author[1]{Saar Egozi}
+%\author[2,3,*]{Yoav Ram}
+%\affil[1]{School of Computer Science, Reichman University, Herzliya 4610101, Israel}
+%\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
+%\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel}
+%\affil[*]{Corresponding author: yoav@yoavram.com, ORCID 0000-0002-9653-4458}
+
+%\date{\today}
+
+%\maketitle
+
+This work was carried out under the supervision of Dr. Yoav Ram as part of the M.Sc.
+program of Efi Arazi School of Computer Science, Reichman University.
+
+\pagebreak
+
+\section*{Abstract}
 Copying role-models can be an efficient method for acquiring knowledge.
@@
 Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
-\end{abstract}
+
+\blfootnote{This work is in preparation for submission to a high-impact journal.}
 \pagebreak

### 2022-06-14 ms/PrestigeBias.tex
revised fig captions, added todos, revised start of discussion

@@
 	\vspace{1.5cm}
-	{\Huge Cultural Evolutionary Dynamics with Success and Influence biases\par}
+	{\Huge Cultural Evolutionary Dynamics with Success and Influence Bias\par}
 	\vspace{1.5cm}
@@
 	{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel\par}
-	{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel \par}
+%	{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel \par}
 
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/final/GBD_validation.pdf}
+    \includegraphics[width=0.7\linewidth]{../figures/final/GBD_validation.pdf}
   \caption{
-  \textbf{Numerical validation for the GBD approximation.}
+  % TODO same x and y label as fig 2A ?
+  \textbf{Numerical validation of the GBD approximation.}
   The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
@@
   \caption{
-  \textbf{Goodness of fit of Dirichlet-Multinomial approximation to the model.}
-  The difference between the DM approximation distribution to observed model distribution (a) is very small.
-The DM approximation (orange) and the simulation results (blue) are almost indistinguishable.
-  The optimal negative log likelihood (b) is given when using the DM approximation (black vertical line), and is much better when compared to a shuffled vector of the DM distribution (blue bars).
-  Here, population size, $N=100$; number of distributions averaged, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; homogeneous success bias weight, $\alpha=0.5$.}	
+  \textbf{Numerical validation of the DM approximation.}
+  We performed computational "experiments" of the role-model choice process and compared them to the DM distribution. 
+  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the experiments (blue) is very small. % TODO check this phrasing is correct
+  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (black vertical line) is much higher compared to the log-likelihood of permutations of experiments (blue histogram).
+  Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.}	
   \label{fig:DM_validation}
@@
   \caption{
-  \textbf{Minimum number of simulations required to get a good approximation.}
-  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. The approximated value (black) is given by equation \cref{eq:kimura_p}.
-  Markers for average value across simulations, error bars for 95\% confidence interval.
-  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
+  \textbf{DM Approximation precision as function of number of simulations.}
+  Our DM approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 DM simulations. % TODO right?
+  Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
+  Markers are averages across simulations, error bars are 95\% confidence intervals.
+  Here, population size, $N=1000$; success-bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success-bias value, $\beta(A)=0.956$.}	
   \label{fig:num_sims}
@@
   \caption{
-  \textbf{Robustness of DM approximations to inclusion of estimation error.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high estimation error rate.
-Markers for average across simulations, error bars for 95\% confidence intervals.
-  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,x^2)$ where $x \in [10^{-7},10^{-1}]$.
+  \textbf{Robustness of DM approximations to success estimation error.}
+  Both the DM approximation (orange) and our approximation (black) agree with the stochastic simulations (blue), even with a high estimation error.
+  Markers are averages across simulations, error bars are 95\% confidence intervals.
+  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,x^2)$ where $x \in [10^{-7},10^{-1}]$.
+% TODO what is "x"?
+should it be \eta?
   }	
@@
 
-\begin{result}[Fixation time approximation]
+\begin{result}[Fixation time]
 \begin{equation}
@@
 \end{equation}
-where, given $S=Ne(1-\beta)$ and $x=\frac{1}{N_e}$,
+where, given $S=N_e(1-\beta)$ and $x=\frac{1}{N_e}$,
 \begin{equation}
@@
 \paragraph{Numerical validation.}
-To validate our analysis we performed multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s=1-\beta$ and $N_e=\alpha N + (1-\alpha)$ for the Wright-Fisher simulations.
-
-We find see that the two models have similar dynamics, and both are well approximated the the approximations in \cref{eq:kimura_p,eq:kimura_t}.
+We compare our approximations (\cref{eq:kimura_p,eq:kimura_t}) with results of simulations of our dichotomous model using various $\alpha$ and $\beta$ values, as well as simulations of the Wright-Fisher model, using the effective selection coefficient, $s_e=1-\beta$, and effective population size, $N_e=\alpha N + (1-\alpha)$.
+We find see that the two models have similar dynamics, and both are well approximated our approximations (\Cref{fig:var_alpha}).
 
@@
     \includegraphics[width=\linewidth]{../figures/final/kimura_var.pdf}
-  \caption{\textbf{Fixation probability and time approximation for varying bias weight and success coefficient.}
-  Fixation probability (\textbf{A}) and time (\textbf{B}) for varying bias weight on the bottom x-axis. The corresponds effective population size is on the top x-axis.
-  The approximation (black) fits DM simulations results (green) and Wright-Fisher simulation results (orange) when using \cref{eq:kimura_p}.
-  Fixation probability (\textbf{A}) is limited at approximately $2s$ (blue), as in the classic WF model.
-  Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for (\textbf{A,B}) and 75\% for (\textbf{C,D}).
-   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (\textbf{A,B}), $A=a\cdot \hat{A}, a \in [0.01,0.99]$ (\textbf{C,D}); success coefficient, $1-\beta=s=0.044$ (\textbf{A,B}); bias weight, $\alpha=0.01$ (\textbf{C,D}).}
+  \caption{\textbf{Fixation probability and time in a constant environment.}
+  Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis), or effective population size $N_e$ (top x-axis) in the top row, and as a function of the success coefficient, $1-\beta$, on the bottom row.
+% TODO missing \beta in x labels of C and D ?
+  The approximation (black; \cref{eq:kimura_p}) agrees with both DM simulations (green) and Wright-Fisher simulation (orange).
+  Fixation probability (A) is bounded by $2s_e=2(1-\beta)$ (blue).
+  Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
+   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (A and B), $A=a\cdot \hat{A}, a \in [0.01,0.99]$ (C and D); success coefficient, $1-\beta=s=0.044$ (A and B); success-bias weight, $\alpha=0.01$ (C and D).}
   \label{fig:var_alpha}
@@
 
-After finding a good approximation for our model in a constant environment, when the favorable trait is always $\hat{A}$, we continued to find an approximation for our model in a changing environment.
+\paragraph*{Changing environment}.
+After finding a good approximation in constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a changing environment.
 Following \citet{changeEnv}, we find the following expressions for the expectation and variance of the change in frequency between $t$ generations.\\
@@
 \begin{equation}\label{eq:ch_expected_and_var}
-E[X_t/N - x] \simeq x(1-x) S_t / N \;, 
+E[X_t/N - x] \simeq x(1-x) S_t / N_e \;, 
 \quad
-V(X_t/N-x) = V(X_t/N) \simeq x(1-x) t/N_e \;,
+\text{and}
+\quad
+V(X_t/N-x) \simeq  t x(1-x) / N_e \;,
 \end{equation}
@@
 
-We can now use the induction assumption of $V(\frac{X_t}{N})$ to get
+We can now use the induction assumption of $V\big(\frac{X_t}{N}\big)$ to get
 \begin{equation}
@@
 \end{equation}
-Now we omit $O(\frac{1}{Ne\cdot N})$ and get
+Now we omit $O\big(\frac{1}{Ne\cdot N}\big)$ and get
 \begin{equation}\label{eq:ch_2}
@@
 E\left[\frac{X_t}{N}\right] 
-&\simeq \frac{1}{N} S_t x(1-x)+x \\
+&\simeq \frac{1}{N} S_t x(1-x)+x \;, \\
 1 - E\left[\frac{X_t}{N}\right] 
@@
 \end{equation}
-after again omitting $O(\frac{1}{N^2})$ terms.
+after again omitting $O\big(\frac{1}{N^2}\big)$ terms.
 To conclude the proof, we note that
@@
 
-When $k$ is the number of generations where the invading phenotype is advantageous, and $l$ when the original trait is, we found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}), see \Cref{fig:ch_env_alpha_beta} (C,D).
+When $k$ is the number of generations where the invading phenotype is advantageous, and $l$ when the original trait is, we found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}), see \Cref{fig:ch_env_alpha_beta}C and \Cref{fig:ch_env_alpha_beta}D.
 
 \begin{figure}[H]
+% TODO remove y label of B ? is it all fixation probability? do we have something for fixation time?
+% adds 1-beta to x label 
     \includegraphics[width=\linewidth]{../figures/final/ch_env.pdf}
-  \caption{\textbf{Sensitivity of fixation probability approximation in a changing environment to varying success coefficient and bias weight and robustness to varying ratios of cycles.}
-\textbf{(A)} When the bias weight, or effective population size varies, the approximation (blue; \cref{eq:ch_env}) fits simulation results (orange). 
-\textbf{(B)} When success bias is large ($1-\beta > 0.1$),  
-simulation results (orange) are underestimated by the approximation (blue; \cref{eq:ch_env}).
-With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) underestimate simulation results, likely because the diffusion equation approximation assumes weak selection.
-We can also see the robustness of the approximation to changes in cycle ratios (\textbf{C,D}): The approximation (blue) fits the simulations (orange) well for different sizes of the changing environment cycle, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
-When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green). 
-Markers show average of $10,000$ simulations, error bars show are 75\% \textbf{(A,C,D)} and 95\% \textbf{(B)} confidence intervals.
-  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$ (\textbf{A,B}), $A=0.8$ \textbf{(C,D)}; In \textbf{(A)} success bias/selection coefficient is: $1-\beta=s=0.005$; In \textbf{(B,C,D)} success bias weight is: $\alpha=0.1$.}
+  \caption{\textbf{Fixation probability in a changing environment.}
+\textbf{(A)} Fixation probability decreases with the the success-bias weight (bottom x-axis) and effective population size (top x-axis).
+The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange).
+\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
+When success bias is large ($1-\beta > 0.1$),  
+simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}).
+With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak "selection" .
+(\textbf{C,D}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias.
+% TODO everywhere we say "beneficial" or "advantageous" we need to correct it, because there is no selection, it is under bias or favored by bias or something like that.
+When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green). % TODO because .... one sentence.
+Markers show average of $10,000$ simulations, error bars show 75\% (A, C, and D) and 95\% (B) confidence intervals.
+  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$ (A and B), $A=0.8$ (C and D); In (A), the success coefficient is: $1-\beta=s=0.005$; In (B, C, and D) the success-bias weight is $\alpha=0.1$.}
   \label{fig:ch_env_alpha_beta}
@@
 
-We find that when copiers adapt their success-bias weight, it decreases with the number of copiers that have already chosen a role-model~(\cref{fig:influence_advantage}).
-Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \cref{fig:influence_advantage}b and c): in this example, the adaptive weight estimation error converges to $0.046$, whereas a constant weight gives values $>0.74$.
+We find that when copiers adapt their success-bias weight, it decreases with the number of copiers that have already chosen a role-model~(\Cref{fig:influence_advantage}).
+Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the adaptive weight estimation error converges to $0.046$, whereas a constant weight gives values $>0.74$.
 
@@
 During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
-Some cultural traits or cultural role-models may be more likely to be copied due to transmission biases. 
-A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
-However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful, portrayed by other traits or means.
-
-Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias, which included both success and influence biases, where the latter is a bias towards role-models with many copiers.
-As shown in \cref{fig:influence_advantage}, given the option to choose the ratio of success and influence, copiers will minimize their estimation error, hence will copy the traits that are closer to the ideal phenotype.
-We see that throughout the choosing process, the estimation error decreases, and the success bias rate also decreases.
-This suggests that the later a copier gets to choose, the less he should rely on his own estimation, and more on previous choices.
-This behavior fits the intuitive thought - the more information you have, using others as an information source, the more informative your choice can be, therefore minimizing the distance from your choice of trait to the ideal one.
-
-In addition, we see that the process of choosing itself is necessary, and when using a constant ratio ($\alpha$), the mean estimation error in the population is greater by a factor of $10$, even when using the $\alpha$ the population converged to when being able to choose it (\cref{fig:influence_advantage}).
-After we showing that choosing one's success bias weight is beneficial to the copier, we continued to create our models- continuous and dichotomous, that incorporated both success and influence.
-However, running simulations for a nested iterative model is costly, and analyzing such model mathematically is very hard.
-We therefor found approximations for the role-model choice process: the generalized binomial distribution (\cref{res:GBD}) and the Dirichlet-Multinomial distribution (\cref{cor:dirichlet}).
-To use approximate our model with the GBD distribution, we must assume homogeneous estimation error, $e$, and homogeneous success bias weight, $\alpha$.
-Both assumptions are necessary to this approximation, because it requires all copiers to be identical (order of copiers must not be a factor).
-For the DM approximation we can relax the assumption for $\alpha$, and allow a varying $\alpha_j$ for each role-model $j$.
-This means that a copier is still not able to choose a success bias weight for itself, and instead it is a characteristic of the role-model only.
-Using the DM approximation, because it is easier to analyze, we found equivalents for Kimura's equations, for our dichotomous model.
-Following \cref{res:selection_coef} we found an approximation for the fixation probability of the ideal trait, and an approximation for the time of fixation.
-These approximations hold only when the equivalent for the selection coefficient, in our model $1-\beta(A)$, is low (0.4 or lower).
-We also discovered that changing the success bias weight doesn't hurt the goodness of the approximations, and only affects the effective population size $N_e$.
-Once we found the equations for a constant environment, we moved on to a cyclic changing environment.
-Based on \cref{res:ch_expected}, we found the approximations for the fixation probability and time to fixation.
-We discovered that as in the constant environment, the effective population size doesn't affect the goodness of fit of the approximation.
+Some cultural traits or cultural role-models may be copied more often due to transmission biases. 
+A common bias is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
+However, it has been suggested that because it is hard to estimate success, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{complexityPaper}.
+% TODO change ref to https://royalsocietypublishing.org/doi/10.1098/rstb.2010.0323
+
+Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias that includes both success and influence biases, where the latter is a bias towards role-models with many copiers.
+This is accomplished by a role-model choice process: each copier, in its turn, chooses a role-model, and that choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model.
+% TODO ref to the correct equation
+
+This resulted in a model with two "nested" stochastic process: the role-model choice process within generations, and the cultural-evolutionary process between generations.
+To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the generalized binomial distribution (GBD, \Cref{res:GBD}) and the Dirichlet-Multinomial distribution (DM, \Cref{cor:dirichlet}).
+The latter is especially useful, as it approximated the entire process and only requires us to assume that the relative effect of success and influence is a characteristic of the role-model, rather than the copier.
+% TODO check this is correct
+
+Analyzing the model with the DM approximation, we found approximations for the fixation probability and fixation time of a beneficial cultural trait in a constant environment.
+Our approximations are similar to Kimura's evolutionary-genetic approximations, such that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence bias compared to success bias, $\alpha$, decreases the effective population size, $N_e$.
+% TODO ref to figure/result
+
+We also analyzed a cyclic changing environment in which the identity of the advantageous trait value switches after a fixed amount of generations.
+We found that as in the constant environment, the effective population size doesn't affect the goodness of fit of the approximation.
 The success coefficient however, must be even lower than before for the approximation to fit.
@@
 We showed that the approximation fits well regardless of the ratio, but when the ratio of adaptive generations to maladaptive ones is very high, it is very similar to a constant environment model.
+
+We find that copiers can minimize their estimation error (i.e., copy trait values closer to the ideal value) by correctly balancing between success and influence biases (\Cref{fig:influence_advantage}).
+We find that throughout the role-model choice process, the estimation error decreases, and the success bias rate also decreases.
+This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers and the less it should rely on its own estimation.
+The rationale, then, is that the more information a copier has, e.g. by using others as an information source, the more informative and effective his choice can be.
+
+In addition, we find that the process of choosing itself is necessary, and when using a constant ratio ($\alpha$), the mean estimation error in the population is greater by a factor of $10$, even when using the $\alpha$ the population converged to when being able to choose it (\cref{fig:influence_advantage}).
 

### 2022-06-14 ms/PrestigeBias.tex
finished going over discussion

@@
 \section*{Discussion}
-\paragraph{Summary.}
+%\paragraph{Summary.}
 During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
@@
 
-We also analyzed a cyclic changing environment in which the identity of the advantageous trait value switches after a fixed amount of generations.
+We also analyzed a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations.
+%% TODO move this to results
 We found that as in the constant environment, the effective population size doesn't affect the goodness of fit of the approximation.
@@
 We showed that the approximation fits well regardless of the ratio, but when the ratio of adaptive generations to maladaptive ones is very high, it is very similar to a constant environment model.
-
-We find that copiers can minimize their estimation error (i.e., copy trait values closer to the ideal value) by correctly balancing between success and influence biases (\Cref{fig:influence_advantage}).
-We find that throughout the role-model choice process, the estimation error decreases, and the success bias rate also decreases.
-This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers and the less it should rely on its own estimation.
-The rationale, then, is that the more information a copier has, e.g. by using others as an information source, the more informative and effective his choice can be.
-
-In addition, we find that the process of choosing itself is necessary, and when using a constant ratio ($\alpha$), the mean estimation error in the population is greater by a factor of $10$, even when using the $\alpha$ the population converged to when being able to choose it (\cref{fig:influence_advantage}).
+%%% 
+% instead, write here how the model parameters affect fixation probability
+
+We also examined a scenario in which copiers can adapt their success-weight bias, $\alpha$ to minimize their copying error, i.e., copy trait values closer to the ideal value.
+We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight (adapted by copiers) and the estimation error decrease. 
+The latter is significantly lower compared to a population using a constant, fixed success-bias weight, regardless of the value of the constant weight (\Cref{fig:influence_advantage}).
+This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers, and the less it should rely on its own estimation.
+The rationale, then, is that the more information a copier has, e.g. by using others as an information sources, the more informative and effective his choice can be.
 
@@
 In some species, like the females of \textit{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}. 
-
-In humans, leadership also has its costs and benefits.
-Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion.
-However, wrong decision making that harms the group could result in harm.
-
-In modern society humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure/education from the family.
-
-\citet{dual_leadership} suggest a different view of leadership.
-They note that most discussions assume there is one type of leadership, as seen above, and so they differ in their definitions.
-\citet{dual_leadership} suggest a way to solve said contradiction by defining two types of leaderships: prestige-based and dominance-based.
-They present classical views of leaderships by Confucius and Machiavelli. Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills,
-and (outstanding) personal qualities. This description is very similar to success bias in our model. 
-By contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence.
-They say that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view into the complex and dynamic processes of leadership. 
+% TODO this is a nice paragraph, but it is unclear how it relates to your work.
+does your model results have something to say about leadership?
+or what?
+if this is just an introduction so that you can then present Van Vugt and Smith, then it is too long.
+
+In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. 
+However, wrong decision making that harms the group could result in harm. % TODO you have double harm here, rephrase it.
+In modern society, many humans strive for prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure or education from the family.
+% again, how is this relevant?
+also I would add reference to at least some of your claims -
+
+\citet{dual_leadership} suggest a different view of leadership. They note that most discussions assume there is one type of leadership, 
+as seen above, and so they differ in their definitions. % TODO this sentence (on this line) in unclear
+\citet{dual_leadership} suggest a way to solve said contradiction % TODO what contradiction? I dont understand
+ by defining two types of leaderships: prestige-based and dominance-based.
+They present classical views of leaderships by Confucius and Machiavelli.
+Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
+This fits the success bias in our model.
+In contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence. % TODO but this is different from our influence model right?
+\citet{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic processes of leadership.
 Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style. 
 The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
-
-\citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige based and dominance based leadership types.
-By their definition, the latter is defined by acquiring social status by using aggression, intimidation and violence.
-It is also more common than prestige in non humans.
-Their definition of prestige is somewhat synonymous with ours.
-According to their manuscript, prestige is composed both of estimation in the eyes of people (our success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
-In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
-Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
+% TODO is this paragraph is a suggestion for followup work?
+if so, you could make it shorter - remove the first sentences about contradictions, and directly present Confucius and Machiavelli, and so on.
+Also this should be in a latter part of the Discussion under the name "Future work" or something like that.
+
+% TODO it seems that the next paragraph is the one that really corresponds to ours, so it should be emphasized earlier, I think
+\citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige-based and dominance-based leadership types.
+In the latter, social status is acquired through using aggression, intimidation and violence. It is also more common than prestige in non-human animals.
+Their definition of prestige seems to overlap with ours.
+They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers others people think one has, which they define as \textit{influence}, similar to our influence bias.
+\citet{prestige_evolution} show that prestige evolved via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
+% TODO how do they show this?
+math?
+simulations?
+experiments?
+Simply put, prestige naturally evolves when social learning already exists to save costs of individual learning. % TODO Are you sure ?
 It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the trait copied.
-\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions and results, is consistent with ours.
-
-Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require replication of representations.
-They base their assumption on three claims - mental representations are non-discrete, cultural transmission is highly inaccurate, and mental representations are not replicated, but rather are 'reconstructed' through an inferential process that is strongly affected by cognitive 'attractors.' In their paper they describe three different models to support their points.
+% TODO unclear
+\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions, and results, is consistent with ours. % TODO how so?
+
+Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require replication of representations.% TODO what is "representation"?
+They base their assumption on three claims: mental representations are non-discrete, cultural transmission is highly inaccurate, and mental representations are not replicated, but rather are `reconstructed' through an inferential process that is strongly affected by cognitive `attractors.' They describe three different models to support their points.
 We see a high similarity between their model and ours.
-Like them, we treat the cultural trait as non-discrete (in the main model, before simplifying it to dichotomous in order to analyze it).
-We also assume error in estimation, which the copiers aren't really replicating their role-models, but rather reconstructing them to create a different trait, which is their representation of the role-model's trait.
-In addition, the inferential process that they describe as strongly affected by cognitive attractors match our influence bias, resulting in a very similar base assumptions in our models.
-
-So far we presented the theory behind prestige, and it's appearance in nature. The following will show the appearances of prestige biases in humans, and in recent times.
-
-\citet{prestige_cultural_learning}, for example, tested the existence of prestige in young children.
-\citet{prestige_cultural_learning} report the first direct tests in children that suggest the existence of \textit{prestige bias}, a tendency to learn from individuals to whom others have preferentially attended, learned or deferred.
-Their definition of prestige is similar to our \textit{influence bias}, and brings concrete proof of its existence and effects.
-Their study showed that the odds of 3-4 years-old children learning from an adult model to whom bystanders had previously preferentially attended for 10 seconds were over twice those of their learning from a model whom bystanders ignored.
-In addition to this first study, they also discovered prestige effects are domain-sensitive.
-They saw that prestigious models were listened to by most when demonstrating artifact-use, but not as much as when presenting food preferences.
-It lead \citet{prestige_cultural_learning} to believe that when the trait is costly to learn individually, prestige will have a higher effect.
-It would be interesting to include costs in our model to try and observe these effects and their dynamics in the simulations of a larger population than this study.
-
-\citet{fijian_social_bias} researched Fijian villages, looking for evidence of social learning biases and their origins. They mention that:
-\begin{quote}
-evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
-\end{quote}
-Their goal is to bridge from the laboratory to the field by examining if and how these biases emerge in a small-scale society.
-During their research they found that:
-\begin{quote}
-Fijian villagers (ages 10 and up) are biased to learn from others perceived as more successful/knowledgeable, both within and across domains (prestige effects).
-\end{quote}
-Their research shows promising evidence for our prestige model, suggesting that copying from others who are \textit{perceived} as successful, rather than actually are successful.
-In their paper, they show that the social networks representing copier-role-model relationships are centralized, suggesting:
-\begin{quote}
-This degree of centralization is consistent with the prediction that people substantially share notions about who is a good cultural model (network centrality), but that individuals’ model selections are influenced by multiple factors.
-\end{quote}
-We see here support for both our trait and our influence bias in their data.
-
-Aside from children's learning biases and small villages in a relatively primitive population, we can see prestige in more advanced domains as well, like western medicine.\citet{medical_prestige} present a specific and important effect of prestige - its significance for medical specialties and diseases.
+Like them, we treat the cultural trait as non-discrete (in the main model, before simplifying it to facilitate analysis).
+We also assume error in estimation, such that copiers do not precisely replicate their role-models, but rather reconstruct them to create a different trait, which is their representation of the role-model's trait.
+In addition, the inferential process that they describe as strongly affected by cognitive attractors matches our influence bias.
+
+% TODO maybe this and the following should be grouped under a heading like "empirical evidence of prestige bias"
+\citet{prestige_cultural_learning} tested the existence of prestige in young children. 
+They report the first direct tests in children that suggest the existence of "prestige bias", defined as the tendency to learn from individuals to whom others have preferentially attended, learned or deferred.
+Their definition of prestige is similar to our influence bias.
+They showed that the odds of 3-4 years-old children learning from an adult model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of their learning from a model whom bystanders ignored.
+They also note that prestige effects are domain-sensitive: they found that prestigious models were attended more when demonstrating artifact-use, but not as much as when presenting food preferences.
+% TODO confusing phrasing, try again?
+This lead \citet{prestige_cultural_learning} to suggest that when the trait is costly to learn individually, prestige will have a higher effect. % TODO higher effect? or will be used more often?
+It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.
+
+\citet{fijian_social_bias} wrote that ``evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.''
+Thus, they studied Fijian villages to examine if and how such biases emerge in a small-scale society.
+They found that ``Fijian villagers (ages 10 and up) are biased to learn from others perceived as more successful/knowledgeable, both within and across domains (prestige effects).'' % TODO it's better to rephrase in your words.
+(you can have one quote, but too is a bit much)
+Their research thus suggests that copying from those perceived as successful, rather than actually are successful. % TODO this sentence is not finished?
+They show that the social networks representing copier--role-model relationships are centralized, suggesting that ``this degree of centralization is consistent with the prediction that people substantially share notions about who is a good cultural model (network centrality), but that individuals' model selections are influenced by multiple factors.''
+
+We can also find prestige bias in more modern domains such as western medicine.
+\citet{medical_prestige} present a specific and important effect of prestige: its significance for medical specialties and diseases.
 They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices.
-They discovered that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
-They have concluded that such differences in prestige bear consequences for actual priority setting in healthcare systems.
-They discovered that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
-In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered \textit{easier} are less prestigious.
-Simply put, they found that the advance in technology and research was in accordance with the prestige rankings.
-This means that there may be very important practices that are neglected due to the prestige bias.
-
-As we seen so far, prestige can explain many behaviors and evolution of cultural traits.
-It is a tool to cheaply estimate and acquire knowledge, which helps an individual to survive and breed.
+They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
+% TODO I dont understand - what is accorded prestige here?
+people or ...
+what?
+They have concluded that such differences in prestige may bear consequences for actual priority setting in healthcare systems.
+They found that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
+In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered easier to master are less prestigious.
+This means that there may be very important practices that are neglected due to prestige bias.
+
+Prestige bias can help to cheaply estimate and acquire knowledge, which may help an individual to survive and reproduce.
 However, it is not always the case, and there could be negative repercussions to this bias, such as invasion of maladaptive traits.
-
-\citet{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners’ choice of what to learn and from whom to learn.
-They suggest a best-of-K model where an individual samples k role-models and choose the one he deems most "successful".
+\citet{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
+They suggest a best-of-k model where an individual samples $k$ role-models and chooses the one he deems most "successful".
 They mentioned that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
 In such a case, learners may be selectively disfavored and in the long run replaced by unbiased learners, who simply copy someone chosen at random.
-They develop new mathematical models that are simpler and mathematically tractable.
+They developed new mathematical models that are simpler and mathematically tractable.
 They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff.
-Our model, which includes influence bias, is consistent with that claim.
+Our model, which includes influence bias, is consistent with this claim.
 When a maladaptive trait is "piggybacking" a role-model with high influence, said trait could spread in the population, as mentioned.
 In addition, they show that best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning. 
-Our model is based on copying based learning only, but it could be interesting to combine it with individual learning and see how it affects the dynamics of the population.
-
-We discussed prestige in depth, and provided several proofs for its existence in nature, humans, and even medicine.
-We saw it could aid invasion of maladaptive traits, or neglect of important medicinal specialities.
-But, it can also accelerate reversal of harmful traditions.
-Harmful traditions can be child marriage, open defecation, and domestic violence, to name a few. 
-\citet{harmful_traditions} suggest a mechanism called \textit{spillover}.
-By their definition, a spillover is when an intervention affect a large enough group in a target population, so that others not included in the intervention starts changing their behavior as well.
-In their research, they found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions.
-This is the same concept as our role-models, where a more prestigious individual will be copied more, therefore spreading his trait wider in the population.
-Their research support therefore in our assumption that there are social biases, conformist influence specifically.
+Our model only includes social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics of the population.
+
+Prestige bias can also accelerate reversal of harmful traditions such as child marriage, open defecation, % TODO why "open defecation" ??
+and domestic violence. 
+\citet{harmful_traditions} suggest a \textit{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
+They found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions.
+This is similar to influential role-models in our model, where a prestigious individual will be copied more often, and will therefore spread his trait faster and wider in the population.
 They also suggest a way to use this phenomena to change existing traditions in a population.
-It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for any negative way that comes to mind.
-
-Up until now, we showed that cultural transmission is a process that manifests in many species, with emphasis on humans.
-We also displayed similarities between this process and genetic transmission, while presenting differences between them, specifically selective biases such as influence and prestige.
+It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for starting harmful traditions.
+
+% TODO I think this whole commented thing should be removed...
+%We also displayed similarities between this process and genetic transmission, while presenting differences between them, specifically selective biases such as influence and prestige.
 We also presented examples of good and bad usages of such biases.
 All of these are mainly presented as a parallel process to the natural selection process in regards to physical anatomy, or at least have an indirect effect on it.
-\citet{collective_brains} offer a take on prestige as a factor of human physical evolution directly.
-They present a concept called \textit{cultural brains} | brains that evolved primarily for the acquisition of adaptive knowledge.
-They build on the hypothesis of \citet{social_brains} that shows that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
-\citet{collective_brains} built a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge.
-They later present their \textit{cumulative cultural brain} hypothesis, an approach which proposes that human brains have evolved with an ability and proclivity for selective, high fidelity social learning.
+
+\citet{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
+Following up in this, \citet{collective_brains} offered that prestige can directly affect human physical evolution.
+They present a concept called \textit{cultural brains}--brains that evolved primarily for the acquisition of adaptive knowledge.
+They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge.
+They later present their \textit{cumulative cultural brain} hypothesis, an approach which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
 As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge.
@@
 success and prestige biases).
-In short, they suggest that some of the reasons for the extreme increase in brain size in humans, are the ability to "cheaply" acquire adaptive knowledge, i.e transmission biases, such as prestige.
+They suggest that some of the reasons for the extreme increase in brain size in humans, are the ability to "cheaply" acquire adaptive knowledge, i.e. via transmission biases, such as prestige.
 
 \paragraph{Further work.}
-In this paper we described several models and processes, analyzed them, and discovered some interesting approximations and results.
+% TODO I think this commented out part can be remove: In this paper we described several models and processes, analyzed them, and discovered some interesting approximations and results.
 But even though, there's much more to research in the direction we took, which can help us better model, understand, and maybe even predict, human behavior, specifically in this era where social media is very accessible and informative.
-Specifically, a deeper analysis of the first model, where every copier chooses its $\alpha$, is preferred.
-It would be interesting to see the if the mean error value and the $\alpha$ are converging to specific values, and what they depend on.
-Following that, it is possible to relax some assumptions we took in our main model in order to find approximations for it - like homogeneous estimation error and success bias weight.
-Lastly, it would be interesting to analyze the continuous model, instead of its dichotomous version. As we've discussed it is probably a much more accurate model of cultural evolution.
+
+One path forward is mathematical analysis of the adaptive success-bias weight model, where every copier chooses its $\alpha$.
+It would be interesting to see the if the mean estimation error and the adaptive weight, $\alpha^*$, are converging to specific values, and how they are affected by the model parameters
+It might also possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
+Lastly, it would be interesting to analyze the continuous model and determine how much it differs from the dichotomous model.
+
+% TODO add a 4-5 sentence "Conclusions" paragaph
 
@@
 and 
-John Templeton Foundation (YR 61809).
+the John Templeton Foundation (YR 61809).
 }

### 2022-06-18 ms/PrestigeBias.tex
update

@@
 We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
-We also find approximations to the fixation probability and the fixation time of an invading advantageous cultural trait, in both constant and changing environments, which resemble Kimura's approximations for population-genetic models.
+We also find approximations to the fixation probability and the fixation time of an invading favored (by bias) cultural trait, in both constant and changing environments, which resemble Kimura's approximations for population-genetic models.
 These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
@@
   \caption{
-  % TODO same x and y label as fig 2A ?
   \textbf{Numerical validation of the GBD approximation.}
@@
   We performed computational "experiments" of the role-model choice process and compared them to the DM distribution. 
-  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the experiments (blue) is very small. % TODO check this phrasing is correct
-  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (black vertical line) is much higher compared to the log-likelihood of permutations of experiments (blue histogram).
+  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the experiments (blue) is very small. 
+  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (red vertical line) is much higher compared to the log-likelihood of permutations of experiments (blue histogram).
   Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.}	
@@
 
-Next, we examined the fixation probability and fixation time of an advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
+Next, we examined the fixation probability and fixation time of a favored phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
 We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
@@
   \textbf{DM Approximation precision as function of number of simulations.}
-  Our DM approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 DM simulations. % TODO right?
+  Our DM approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
   Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
@@
   Markers are averages across simulations, error bars are 95\% confidence intervals.
-  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,x^2)$ where $x \in [10^{-7},10^{-1}]$.
-% TODO what is "x"?
-should it be \eta?
+  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,\eta^2)$ where $\eta \in [10^{-7},10^{-1}]$.
   }	
@@
 After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
-We focus on the fixation probability and fixation time of an advantageous phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
+We focus on the fixation probability and fixation time of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
 We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
@@
 \end{equation}
-where $x$ is the initial frequency of the advantageous phenotype $\hat{A}$.
+where $x$ is the initial frequency of the favored phenotype $\hat{A}$.
 \end{result}
@@
   Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis), or effective population size $N_e$ (top x-axis) in the top row, and as a function of the success coefficient, $1-\beta$, on the bottom row.
-% TODO missing \beta in x labels of C and D ?
   The approximation (black; \cref{eq:kimura_p}) agrees with both DM simulations (green) and Wright-Fisher simulation (orange).
@@
 \paragraph{Numerical validation.}
-Comparing our approximation (\cref{eq:ch_env}) to numerical simulations, we find that the approximation fits simulations results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
+Comparing our approximation, \cref{eq:ch_env} to numerical simulations, we find that the approximation fits simulations results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
 
@@
 
-When $k$ is the number of generations where the invading phenotype is advantageous, and $l$ when the original trait is, we found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}), see \Cref{fig:ch_env_alpha_beta}C and \Cref{fig:ch_env_alpha_beta}D.
+When $k$ is the number of generations where the invading phenotype is favored, and $l$ when the original trait is, we found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=100$), the changing environment approximation, \cref{eq:ch_env} converges to the constant environment approximation, \cref{eq:kimura_p}, see \Cref{fig:ch_env_alpha_beta}C and \Cref{fig:ch_env_alpha_beta}D.
+
+\begin{result}
+The effective population size doesn't affect the goodness of fit of the approximation. The success coefficient however, must be even lower than before for the approximation to fit.
+\end{result}
+The proof is seen in \Cref{fig:ch_env_alpha_beta}A,B. The approximation follows the trend of the simulation results for all $\alpha$ values.
+When increasing the success coefficient to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation.
+We believe the reason is the structure of the cycle.
+Our proof and approximation in the changing environment are for a large amount of cycles, and when the success coefficient is too high, there might be very few cycles.
+Either the ideal trait is copied by enough copiers so that the influence is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait gets extinct before there were enough copiers that copied it.
+We then tried to change the ratio between the number of cycles where $\hat{A}$ is favored and disfavored.
+We showed that the approximation fits well regardless of the ratio, but when the ratio of favored generations to disfavored ones is very high, it is very similar to a constant environment model.
 
 \begin{figure}[H]
-% TODO remove y label of B ? is it all fixation probability? do we have something for fixation time?
-% adds 1-beta to x label 
     \includegraphics[width=\linewidth]{../figures/final/ch_env.pdf}
@@
 (\textbf{C,D}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias.
-% TODO everywhere we say "beneficial" or "advantageous" we need to correct it, because there is no selection, it is under bias or favored by bias or something like that.
-When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green). % TODO because .... one sentence.
+When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
 Markers show average of $10,000$ simulations, error bars show 75\% (A, C, and D) and 95\% (B) confidence intervals.
@@
   \textbf{Advantage of an adaptive success-bias weight.}
-  Both success-bias weight $\alpha$ (\textbf{a}) and estimation error (\textbf{b}) decrease during the role-model choosing process, demonstrating that influence is becomes more advantageous as more copiers have made their choice.
-However, when $\alpha$ is homogeneous, the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
+  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process, demonstrating that influence becomes more favored as more copiers have made their choice.
+However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
 The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the adaptive $\alpha$ model.
@@
 \section*{Discussion}
-%\paragraph{Summary.}
 During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
@@
 A common bias is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
-However, it has been suggested that because it is hard to estimate success, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{complexityPaper}.
-% TODO change ref to https://royalsocietypublishing.org/doi/10.1098/rstb.2010.0323
+However, it has been suggested that because it is hard to estimate success, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{fijian_social_bias}.
 
 Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias that includes both success and influence biases, where the latter is a bias towards role-models with many copiers.
-This is accomplished by a role-model choice process: each copier, in its turn, chooses a role-model, and that choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model.
-% TODO ref to the correct equation
+This is accomplished by a role-model choice process: each copier, in its turn, chooses a role-model, and that choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model, \cref{eq:prestige}.
 
@@
 The latter is especially useful, as it approximated the entire process and only requires us to assume that the relative effect of success and influence is a characteristic of the role-model, rather than the copier.
-% TODO check this is correct
-
-Analyzing the model with the DM approximation, we found approximations for the fixation probability and fixation time of a beneficial cultural trait in a constant environment.
-Our approximations are similar to Kimura's evolutionary-genetic approximations, such that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence bias compared to success bias, $\alpha$, decreases the effective population size, $N_e$.
-% TODO ref to figure/result
-
-We also analyzed a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations.
-%% TODO move this to results
-We found that as in the constant environment, the effective population size doesn't affect the goodness of fit of the approximation.
-The success coefficient however, must be even lower than before for the approximation to fit.
-When the success coefficient is higher than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation.
-We believe the reason is the structure of the cycle.
-Our proof and approximation in the changing environment are for a large amount of cycles, and when the success coefficient is too high, there might be very few cycles.
-Either the ideal trait is copied by enough copiers so that the influence is sufficient to negate the success bias when the cycle changes (and the beneficial trait becomes the maladaptive), or the opposite happens, and the ideal trait gets extinct before there were enough copiers that copied it.
-We then tried to change the ratio between the number of cycles where $\hat{A}$ is beneficial and maladaptive.
-We showed that the approximation fits well regardless of the ratio, but when the ratio of adaptive generations to maladaptive ones is very high, it is very similar to a constant environment model.
-%%% 
-% instead, write here how the model parameters affect fixation probability
+
+Analyzing the model with the DM approximation, we found approximations for the fixation probability and fixation time of a favored by bias cultural trait in a constant environment.
+Our approximations are similar to Kimura's evolutionary-genetic approximations, such that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence bias compared to success bias, $\alpha$, decreases the effective population size, $N_e$, \Cref{fig:var_alpha}.
+
+We also analyzed a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations, \Cref{fig:ch_env_alpha_beta}.
+We see that similarly to the constant environment approximation, a change in the success-bias weight has no negative effects on the goodness of fit to the simulation results.
+We also showed that this approximation is more sensitive to the success coefficient value than the approximation of the constant environment, and a lower value is required to have a good fit.
+Changing the ratio between the cycles that have a bias that favors the rare phenotype and the ones that disfavors it, doesn't affect the goodness of fit.
 
@@
 According to \citet{animal_leadership}, there are two main approaches to group decision-making in nature: leadership and consensus.
-Leaders may lead the group when traveling, decide on a nesting site, or choose foraging patches.
-They found that leadership is mostly observed when there are a lot of connections in the social network of the group, and when there are individuals that present leadership behavior.
 Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
-When no individual posseses such traits, or when there are not enough connections and relations in the social network, decisions are more likely to be made by consensus.
-Leaders may carry selection costs, e.g. due to higher predation risk, poisoning when exploring new foraging patches.
-In some cases, the leader may be the hungriest or the weakest individual, while the others would prefer to follow the leader and minimizing their risks and costs.
-However, leadership may also carry selection benefits.
-For example, given the route to the foraging site was successful, the leader and his closest followers would gain most or the best of the food, whereas in consensus decision making, the food would be shared more equally.
-Or, sexual selection may also provide a selection benefit advantage to leaders, who might gain more sexual partners due to their leadership of the group.
 \citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
 In some species, like the females of \textit{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}. 
-% TODO this is a nice paragraph, but it is unclear how it relates to your work.
-does your model results have something to say about leadership?
-or what?
-if this is just an introduction so that you can then present Van Vugt and Smith, then it is too long.
-
 In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. 
-However, wrong decision making that harms the group could result in harm. % TODO you have double harm here, rephrase it.
+However, wrong decision making that harms the group could result in negative effects for the leader. 
 In modern society, many humans strive for prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure or education from the family.
-% again, how is this relevant?
-also I would add reference to at least some of your claims -
-
-\citet{dual_leadership} suggest a different view of leadership. They note that most discussions assume there is one type of leadership, 
-as seen above, and so they differ in their definitions. % TODO this sentence (on this line) in unclear
-\citet{dual_leadership} suggest a way to solve said contradiction % TODO what contradiction? I dont understand
- by defining two types of leaderships: prestige-based and dominance-based.
-They present classical views of leaderships by Confucius and Machiavelli.
-Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
-This fits the success bias in our model.
-In contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence. % TODO but this is different from our influence model right?
-\citet{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic processes of leadership.
-Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style. 
-The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
-% TODO is this paragraph is a suggestion for followup work?
-if so, you could make it shorter - remove the first sentences about contradictions, and directly present Confucius and Machiavelli, and so on.
-Also this should be in a latter part of the Discussion under the name "Future work" or something like that.
-
-% TODO it seems that the next paragraph is the one that really corresponds to ours, so it should be emphasized earlier, I think
-\citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige-based and dominance-based leadership types.
+
+\citet{prestige_evolution} suggest that there are two types of leadership, and also define the two as prestige-based and dominance-based leadership types.
 In the latter, social status is acquired through using aggression, intimidation and violence. It is also more common than prestige in non-human animals.
@@
 \citet{prestige_evolution} show that prestige evolved via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
-% TODO how do they show this?
-math?
-simulations?
-experiments?
-Simply put, prestige naturally evolves when social learning already exists to save costs of individual learning. % TODO Are you sure ?
-It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the trait copied.
-% TODO unclear
-\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions, and results, is consistent with ours. % TODO how so?
-
-Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require replication of representations.% TODO what is "representation"?
+They back up their claims by creating testable predictions and using evidence from the literature and experiments of social sciences.
+Simply put, prestige can naturally evolve when social learning already exists to save costs of individual learning.
+
+Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require accurate replication of viewed cultural traits, addressed as "representations" in their paper.
 They base their assumption on three claims: mental representations are non-discrete, cultural transmission is highly inaccurate, and mental representations are not replicated, but rather are `reconstructed' through an inferential process that is strongly affected by cognitive `attractors.' They describe three different models to support their points.
@@
 
-% TODO maybe this and the following should be grouped under a heading like "empirical evidence of prestige bias"
+\paragraph{Empirical evidence of prestige bias}
 \citet{prestige_cultural_learning} tested the existence of prestige in young children. 
@@
 Their definition of prestige is similar to our influence bias.
-They showed that the odds of 3-4 years-old children learning from an adult model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of their learning from a model whom bystanders ignored.
-They also note that prestige effects are domain-sensitive: they found that prestigious models were attended more when demonstrating artifact-use, but not as much as when presenting food preferences.
-% TODO confusing phrasing, try again?
-This lead \citet{prestige_cultural_learning} to suggest that when the trait is costly to learn individually, prestige will have a higher effect. % TODO higher effect? or will be used more often?
+They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of their learning from a role-models whom bystanders ignored.
+They also note that prestige effects are domain-sensitive: they found that prestigious role-models were attended more when demonstrating artifact-use.
+Meanwhile, role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact-use vs.
+food preference) can affect the attendance, hence the prestige of the role-model.
+This lead \citet{prestige_cultural_learning} to suggest that when the trait is costly to learn individually, prestige will have a stronger bias.
 It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.
 
-\citet{fijian_social_bias} wrote that ``evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.''
+\citet{fijian_social_bias} wrote that evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
 Thus, they studied Fijian villages to examine if and how such biases emerge in a small-scale society.
-They found that ``Fijian villagers (ages 10 and up) are biased to learn from others perceived as more successful/knowledgeable, both within and across domains (prestige effects).'' % TODO it's better to rephrase in your words.
-(you can have one quote, but too is a bit much)
-Their research thus suggests that copying from those perceived as successful, rather than actually are successful. % TODO this sentence is not finished?
-They show that the social networks representing copier--role-model relationships are centralized, suggesting that ``this degree of centralization is consistent with the prediction that people substantially share notions about who is a good cultural model (network centrality), but that individuals' model selections are influenced by multiple factors.''
+They found that Fijian villagers are more likely to learn from role-models perceived as more successful/knowledgeable, both within and across domains.
+Their research thus suggests that copying from those perceived as successful, rather than actually are successful, is a common phenomena. 
+They show that the social networks representing copier--role-model relationships are centralized, suggesting that it is consistent with the prediction that people substantially share notions about who is a good cultural model, but that individuals' role-model selections are influenced by multiple factors.
 
@@
 They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices.
-They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
-% TODO I dont understand - what is accorded prestige here?
-people or ...
-what?
+They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were medicine and practices accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
 They have concluded that such differences in prestige may bear consequences for actual priority setting in healthcare systems.
@@
 
-Prestige bias can also accelerate reversal of harmful traditions such as child marriage, open defecation, % TODO why "open defecation" ??
-and domestic violence. 
+Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
 \citet{harmful_traditions} suggest a \textit{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
@@
 It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for starting harmful traditions.
-
-% TODO I think this whole commented thing should be removed...
-%We also displayed similarities between this process and genetic transmission, while presenting differences between them, specifically selective biases such as influence and prestige.
-We also presented examples of good and bad usages of such biases.
-All of these are mainly presented as a parallel process to the natural selection process in regards to physical anatomy, or at least have an indirect effect on it.
 
@@
 \paragraph{Further work.}
-% TODO I think this commented out part can be remove: In this paper we described several models and processes, analyzed them, and discovered some interesting approximations and results.
-But even though, there's much more to research in the direction we took, which can help us better model, understand, and maybe even predict, human behavior, specifically in this era where social media is very accessible and informative.
-
 One path forward is mathematical analysis of the adaptive success-bias weight model, where every copier chooses its $\alpha$.
@@
 
-% TODO add a 4-5 sentence "Conclusions" paragaph
+Another is to expand our model to account for two types of prestige/leadership, suggested by \citet{dual_leadership}.
+They present classical views of leaderships by Confucius and Machiavelli.
+Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
+This fits the success bias in our model.
+In contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence. 
+\citet{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic processes of leadership.
+Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style. 
+The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
+
+\paragraph{Conclusions.}
+In this paper we presented numerous reasons and sources to support the existence of biases in cultural transmission of traits.
+We presented the most known and addressed bias, the success bias, and added another bias, which is addressed a lot less, the influence bias.
+We believe the combination of these biases is a strong driving force in cultural evolution.
+We see a clear advantage when an individual can choose his ideal ratio between the two biases.
+We also showed that even when this ratio is constant and homogeneous in the population, it is affecting the effective population size.
+The higher the influence bias will be, the smaller the effective population size will become.
 

### 2022-06-25 ms/PrestigeBias.tex
update

@@
 \usepackage{authblk}
+\usepackage[utf8x]{inputenc}
+\usepackage[english]{babel}
+\usepackage{cjhebrew}
 
@@
 
-\section*{Abstract}
+\section{Abstract}
 Copying role-models can be an efficient method for acquiring knowledge.
@@
 
-\section*{Introduction}
+\tableofcontents
+
+\pagebreak
+
+\section{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Models and methods}
+\section{Models and methods}
 
@@
 
-\subsection*{Continuous trait}
+\subsection{Continuous trait}
 We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
@@
 
-\subsection*{Dichotomous trait}
+\subsection{Dichotomous trait}
 To allow for mathematical analysis of the model, we introduce a simplified version where the trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
@@
 
-\subsection*{Generalized binomial distribution}
+\subsection{Generalized binomial distribution}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
@@
 
-\subsection*{Dirichlet-Multinomial distribution}
+\subsection{Dirichlet-Multinomial distribution}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Fixation probability and time}
+\subsection{Fixation probability and time}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Adaptive success-bias weight}
+\subsection{Adaptive success-bias weight}
 
@@
 \clearpage
-\section*{Discussion}
+\section{Discussion}
 During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
@@
 {\small
-\section*{Acknowledgements}
+\section{Acknowledgements}
 We thank Marcus Feldman, Martin Pontz, and Tal Simon for discussions and comments.
@@
 
-\section*{References}
+\section{References}
 \nolinenumbers
@@
 \bibliographystyle{apalike}
+
+\pagebreak
+
+\begin{cjhebrew}
+\section*{תקציר}
+Copying role-models can be an efficient method for acquiring knowledge.
+A common bias when choosing a role-model to copy is success bias: copying whoever appears more successful.
+This bias depends on the performance of the role-model alone, with no other factors.
+We propose an additional bias that may be prevalent in cultural transmission: influence bias, in which role-model choice is affected by the number of individuals that have already copied each potential role-model.
+We combine success and influence bias together to a ``prestige bias'' and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
+We find analytic approximations to our stochastic model, facilitating further mathematical analysis and reducing the computational complexity of simulations.
+We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
+We also find approximations to the fixation probability and the fixation time of an invading favored (by bias) cultural trait, in both constant and changing environments, which resemble Kimura's approximations for population-genetic models.
+These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
+Influence bias also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
+Our model may provide a good description of cultural transmission, 
+especially in human societies where social media is popular. 
+Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
+\end{cjhebrew}
 \end{document}

### 2022-06-26 ms/merge_pdfs.py
update

@@ -1,0 +1,27 @@
+from PyPDF2 import PdfFileMerger
+
+
+def merge(thesis_path, hebrew_cover):
+    merger = PdfFileMerger()
+
+    thesis_file = open(thesis_path, "rb")
+    hebrew_file = open(hebrew_cover, "rb")
+
+    # add all pages of thesis to output
+    merger.append(fileobj=thesis_file)
+
+    # append hebrew cover to the end of the output document
+    merger.append(hebrew_file)
+
+    # Write to an output PDF document
+    output = open(output_path(thesis_path), "wb")
+    merger.write(output)
+
+
+def output_path(thesis_path: str):
+    assert thesis_path.endswith('.pdf')
+    return thesis_path[:-4] + '_with_hebrew_abstract' + '.pdf'
+
+
+if __name__ == '__main__':
+    merge('PrestigeBias.pdf', 'HebrewThesisSaar.pdf')

### 2022-06-27 ms/hebrew_abstract.tex
update

%\title{Hebrew document in WriteLatex - מסמך בעברית}
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[english,hebrew]{babel}
\selectlanguage{hebrew}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
headheight=12pt
}
\begin{document}
\pagestyle{empty}

\section*{תקציר}
העתקה של מודל לחיקוי יכולה להיות שיטה יעילה לרכישת ידע. כאשר נדרשים לבחור מודל לחיקוי, ישנה הטייה ידועה הנקראת הטיה מבוססת הצלחה: כלומר, להעתיק מהמודל לחיקוי שנראה המצליח ביותר. הטיה זאת מבוססת על ביצועיו ויכולותיו של המודל לחיקוי בלבד, ללא גורמים נוספים. אנחנו מציעים הטייה נוספת שייתכן שהינה נפוצה בתהליכי הורשה תרבותית: הטייה מבוססת השפעה, כלומר, הבחירה במודל לחיקוי מושפעת מכמות המעתיקים שכבר בחרו מודל לחיקוי. במודל שלנו אנחנו משלבים את ההטיות לכדי הטייה אחת שאנו קוראים לה "הטיית יוקרה" ואנו מנתחים את ההשפעות של הטייה זו על הדינמיקות של אבולציה תרבותית, באמצעות שימוש באנליזה מתמטית וסימולציות סטוכסטיות.

במחקר זה מצאנו שיערוכים מתמטיים לתהליך הסטוכסטי שלנו, אשר סייעו לנו בפיתוח מתמטיים מורכבים יותר של המודל, ובייעול החישוביות של הסימולציות בסדר גודל. אנו מאששים שיערוכים אלה באמצעות סימולציות, ובודקים את חוסנם כנגד הנחות מקלות שבאמצעותן מצאנו שיערוכים אלו.
בנוסף, מצאנו שיערוכים ל"הסתברות קיבעון" )ההסתברות שאלמנט תרבותי יתפשט באוכלוסיה כולה( ו"זמן לקיבעון", בסביבות קבועות ומשתנות, אשר דומים לשיערוכי קימורה למודלים של אבולוציה גנטית.
שיערוכים אלו מראים שהטייה מבוססת הצלחה דומה לבחירה הטבעית, והטייה מבוססת השפעה מקטינה את גודל האוכלוסייה האפקטיבי.
הטייה מבוססת השפעה גם מאיצה את הדינמיקות של האבולוציה, כמו שניתן לצפות ממודל "עשירים מתעשרים".

המודל שלנו יכול לתאר בצורה טובה תהליכי תורשה תרבותית, במיוחד בתרבויות של בני האדם, בהן רשתות המדיה החברתית פופלריות. עובדה נוספת נדרשת בכדי לבחון אם מודל זה יכול לחזות תופעות כלשהן באבולוציה תרבותית, כאשר מעשירים אותו בהשפעות של בחירה טבעית, ויוזמה אישית.

\pagebreak

עבודה זו בוצעה בהדרכתו של דר' יואב רם מבי"ס לזואולוגיה, הפקולטה למדעי החיים, אוניברסיטת תל אביב.

\end{document}

### 2022-06-27 ms/merge_pdfs.py

@@ -24,4 +24,4 @@ def output_path(thesis_path: str):
 
 
 if __name__ == '__main__':
-    merge('PrestigeBias.pdf', 'HebrewThesisSaar.pdf')
+    merge('PrestigeBias.pdf', 'hebrew_abstract.pdf')

### 2022-09-05 ms/PrestigeBias.tex
update
edited discussion

@@
 Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias that includes both success and influence biases, where the latter is a bias towards role-models with many copiers.
-This is accomplished by a role-model choice process: each copier, in its turn, chooses a role-model, and that choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model, \cref{eq:prestige}.
-
-This resulted in a model with two "nested" stochastic process: the role-model choice process within generations, and the cultural-evolutionary process between generations.
-To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the generalized binomial distribution (GBD, \Cref{res:GBD}) and the Dirichlet-Multinomial distribution (DM, \Cref{cor:dirichlet}).
-The latter is especially useful, as it approximated the entire process and only requires us to assume that the relative effect of success and influence is a characteristic of the role-model, rather than the copier.
-
-Analyzing the model with the DM approximation, we found approximations for the fixation probability and fixation time of a favored by bias cultural trait in a constant environment.
-Our approximations are similar to Kimura's evolutionary-genetic approximations, such that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence bias compared to success bias, $\alpha$, decreases the effective population size, $N_e$, \Cref{fig:var_alpha}.
-
-We also analyzed a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations, \Cref{fig:ch_env_alpha_beta}.
-We see that similarly to the constant environment approximation, a change in the success-bias weight has no negative effects on the goodness of fit to the simulation results.
-We also showed that this approximation is more sensitive to the success coefficient value than the approximation of the constant environment, and a lower value is required to have a good fit.
-Changing the ratio between the cycles that have a bias that favors the rare phenotype and the ones that disfavors it, doesn't affect the goodness of fit.
-
-We also examined a scenario in which copiers can adapt their success-weight bias, $\alpha$ to minimize their copying error, i.e., copy trait values closer to the ideal value.
+This is accomplished by a role-model choice process: each copier, in its turn, chooses a role-model, and that choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-mode (eq.~\ref{eq:prestige}).
+
+This resulted in a model with two "nested" stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
+To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DM, \Cref{cor:dirichlet}).
+The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and influence is a characteristic of the role-model, rather than the copier.
+
+Analyzing the model with the DM distribution, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
+Our approximations are similar to Kimura's evolutionary-genetic approximations, such that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence versus success bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
+
+We also analyzed a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
+We find that, similarly to the constant environment approximation, a change in the success-bias weight % TODO which symbol is that? was that it's name in the model section?
+ has no negative effects on the goodness-of-fit of the approximation to simulation results.
+We also showed that this approximation is more sensitive to changes in the success coefficient value % TODO which symbol is that? was that it's name in the model section?
+than the constant environment approximation, and a lower value is required to have a good fit.
+The ratio between the number of generation in which the rare phenotype is under positive transmission bias and the number of generations in which it is under negative bias does not affect the goodness-of-fit of the approximation.
+
+We also examined a scenario in which copiers can adapt their success-weight bias, $\alpha$, to minimize their copying error, i.e., copy trait values closer to the optimal value.
 We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight (adapted by copiers) and the estimation error decrease. 
@@
 This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers, and the less it should rely on its own estimation.
-The rationale, then, is that the more information a copier has, e.g. by using others as an information sources, the more informative and effective his choice can be.
+The rationale, then, is that the more information a copier has, e.g. by using others as information sources, the more informative and effective his choice can be.
 
@@
 
-According to \citet{animal_leadership}, there are two main approaches to group decision-making in nature: leadership and consensus.
+According to \citet{animal_leadership}, there are two main approaches to group decision making in nature: leadership and consensus.
 Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
@@
 
-\citet{prestige_evolution} suggest that there are two types of leadership, and also define the two as prestige-based and dominance-based leadership types.
-In the latter, social status is acquired through using aggression, intimidation and violence. It is also more common than prestige in non-human animals.
+\citet{prestige_evolution} suggested that there are two types of leadership: prestige-based and dominance-based leadership.
+In the latter, social status is acquired through aggression, intimidation and violence. It is also more common than prestige in non-human animals.
 Their definition of prestige seems to overlap with ours.
-They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers others people think one has, which they define as \textit{influence}, similar to our influence bias.
-\citet{prestige_evolution} show that prestige evolved via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
+They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers other people think one has, which they define as \textit{influence}, similar to our influence bias.
+\citet{prestige_evolution} show that prestige can evolve via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
 They back up their claims by creating testable predictions and using evidence from the literature and experiments of social sciences.
@@
 
-Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require accurate replication of viewed cultural traits, addressed as "representations" in their paper.
+Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require accurate replication of cultural traits, addressed as "representation" in their paper.
 They base their assumption on three claims: mental representations are non-discrete, cultural transmission is highly inaccurate, and mental representations are not replicated, but rather are `reconstructed' through an inferential process that is strongly affected by cognitive `attractors.' They describe three different models to support their points.
@@
 Like them, we treat the cultural trait as non-discrete (in the main model, before simplifying it to facilitate analysis).
-We also assume error in estimation, such that copiers do not precisely replicate their role-models, but rather reconstruct them to create a different trait, which is their representation of the role-model's trait.
-In addition, the inferential process that they describe as strongly affected by cognitive attractors matches our influence bias.
+We also assume error in estimation, such that copiers do not precisely replicate their role-models, but rather reconstruct them to create a potentially different trait, which is their representation of the role-model's trait.
+In addition, the inferential process that they describe as strongly affected by cognitive attractors may include our definition of influence bias.
 
 \paragraph{Empirical evidence of prestige bias}
-\citet{prestige_cultural_learning} tested the existence of prestige in young children. 
-They report the first direct tests in children that suggest the existence of "prestige bias", defined as the tendency to learn from individuals to whom others have preferentially attended, learned or deferred.
+\citet{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
 Their definition of prestige is similar to our influence bias.
 They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of their learning from a role-models whom bystanders ignored.
-They also note that prestige effects are domain-sensitive: they found that prestigious role-models were attended more when demonstrating artifact-use.
-Meanwhile, role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact-use vs.
-food preference) can affect the attendance, hence the prestige of the role-model.
+They also note that prestige effects are domain sensitive: they found that prestigious role-models were attended more when demonstrating artifact use, whereas role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact use vs.
+food preference) can affect the attendance, and hence the prestige of the role-model.
 This lead \citet{prestige_cultural_learning} to suggest that when the trait is costly to learn individually, prestige will have a stronger bias.
@@
 
-\citet{fijian_social_bias} wrote that evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
+According to \citet{fijian_social_bias}, evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
 Thus, they studied Fijian villages to examine if and how such biases emerge in a small-scale society.
@@
 We can also find prestige bias in more modern domains such as western medicine.
-\citet{medical_prestige} present a specific and important effect of prestige: its significance for medical specialties and diseases.
-They examined literature from 1950 to 2005 regarding the effects of prestige on medicinal practices.
-They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were medicine and practices accorded high levels of prestige, while medicine with opposite characteristics had low levels of prestige.
-They have concluded that such differences in prestige may bear consequences for actual priority setting in healthcare systems.
-They found that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
+\citet{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
+They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices with opposite characteristics had low levels of prestige.
+For example, they found that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
 In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered easier to master are less prestigious. 
 This means that there may be very important practices that are neglected due to prestige bias.
-
-Prestige bias can help to cheaply estimate and acquire knowledge, which may help an individual to survive and reproduce.
+They concluded that such differences in prestige may bear consequences for actual priority setting in healthcare systems.
+
+Prestige bias can help to cheaply estimate and acquire knowledge, which may facilitate survival and reproduction.
 However, it is not always the case, and there could be negative repercussions to this bias, such as invasion of maladaptive traits.
@@
 Our model, which includes influence bias, is consistent with this claim.
-When a maladaptive trait is "piggybacking" a role-model with high influence, said trait could spread in the population, as mentioned.
+When a maladaptive trait is "piggybacking" a role-model with high influence, this trait could spread in the population.
 In addition, they show that best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning. 
-Our model only includes social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics of the population.
+Our model only includes social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics.
 
@@
 They also suggest a way to use this phenomena to change existing traditions in a population.
-It is very clear however, that just as it can be used to end harmful traditions, the same agents could be used for starting harmful traditions.
+It is very clear however, that just as it can be used to end harmful traditions, the same agents could start harmful traditions.
 
 \citet{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
-Following up in this, \citet{collective_brains} offered that prestige can directly affect human physical evolution.
-They present a concept called \textit{cultural brains}--brains that evolved primarily for the acquisition of adaptive knowledge.
+Following up on this, \citet{collective_brains} offered that prestige can directly affect human physical evolution.
+They present a concept called \textit{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
 They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. 
-They later present their \textit{cumulative cultural brain} hypothesis, an approach which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
+They also presented the \textit{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
 As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge.
@@
 success and prestige biases).
-They suggest that some of the reasons for the extreme increase in brain size in humans, are the ability to "cheaply" acquire adaptive knowledge, i.e. via transmission biases, such as prestige.
+They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to "cheaply" acquire adaptive knowledge via transmission biases such as prestige.
 
 \paragraph{Further work.}
-One path forward is mathematical analysis of the adaptive success-bias weight model, where every copier chooses its $\alpha$.
-It would be interesting to see the if the mean estimation error and the adaptive weight, $\alpha^*$, are converging to specific values, and how they are affected by the model parameters
-It might also possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
+One path forward is an analysis of the dynamics of the adaptive success-bias weight model, in which every copier chooses its $\alpha$.
+It would be interesting to see the if the mean estimation error and the adaptive weight, $\alpha^*$, are converging to specific values, and how they are affected by the model parameters.
+It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
 Lastly, it would be interesting to analyze the continuous model and determine how much it differs from the dichotomous model.
 
-Another is to expand our model to account for two types of prestige/leadership, suggested by \citet{dual_leadership}.
-They present classical views of leaderships by Confucius and Machiavelli.
-Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
+Another way to expand our model is to account for the two types of prestige or leadership suggested by \citet{dual_leadership} that are attributed to Confucius and Machiavelli.
+Confucius viewed leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
 This fits the success bias in our model.
-In contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence. 
-\citet{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic processes of leadership.
-Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style. 
+In contrast, Machiavelli viewed leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence. 
+\citet{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
+Several adjustments could be made so that our model reflects these leadership styles, such as assuming there is a correlation between phenotype to leadership style. 
 The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
@@
 \paragraph{Conclusions.}
-In this paper we presented numerous reasons and sources to support the existence of biases in cultural transmission of traits.
-We presented the most known and addressed bias, the success bias, and added another bias, which is addressed a lot less, the influence bias.
-We believe the combination of these biases is a strong driving force in cultural evolution.
-We see a clear advantage when an individual can choose his ideal ratio between the two biases.
-We also showed that even when this ratio is constant and homogeneous in the population, it is affecting the effective population size.
-The higher the influence bias will be, the smaller the effective population size will become.
+Here, we presented support for the existence of prestige biases in cultural transmission, including the commonly studied success bias.
+We introduced an influence bias, which has so far received less attention.
+We believe the combination of these biases may be a strong driving force in cultural evolution.
+We show that the relative effect of the two biases changes the effective population size such that the increasing the weight individuals give to influence bias, decreases the effective population size.
+We also find a clear advantage to individuals that can choose the relative weight of the two biases.
 
@@
 \pagebreak
-
-\begin{cjhebrew}
-\section*{תקציר}
-Copying role-models can be an efficient method for acquiring knowledge.
-A common bias when choosing a role-model to copy is success bias: copying whoever appears more successful.
-This bias depends on the performance of the role-model alone, with no other factors.
-We propose an additional bias that may be prevalent in cultural transmission: influence bias, in which role-model choice is affected by the number of individuals that have already copied each potential role-model.
-We combine success and influence bias together to a ``prestige bias'' and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
-We find analytic approximations to our stochastic model, facilitating further mathematical analysis and reducing the computational complexity of simulations.
-We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
-We also find approximations to the fixation probability and the fixation time of an invading favored (by bias) cultural trait, in both constant and changing environments, which resemble Kimura's approximations for population-genetic models.
-These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
-Influence bias also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
-Our model may provide a good description of cultural transmission, 
-especially in human societies where social media is popular. 
-Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
-\end{cjhebrew}
 \end{document}

### 2022-09-05 ms/PrestigeBias.tex
edited fig caption; added question to SE

@@
 
-This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity \citep{kin_selection}, which depend on the frequency of a trait in the population or in a sample of role-models.
+This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity \citep{kin_selection}, % TODO are you sure this is the correct reference?
+maybe change to Denton et al?
+which depend on the frequency of a trait in the population or in a sample of role-models. 
  We define a model of cultural transmission with prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
@@
   Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
-   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (A and B), $A=a\cdot \hat{A}, a \in [0.01,0.99]$ (C and D); success coefficient, $1-\beta=s=0.044$ (A and B); success-bias weight, $\alpha=0.01$ (C and D).}
+   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (A and B), $A = a \cdot \hat{A}$ with $0.01 \le a \le 0.99$ (panels C and D); success coefficient, $1-\beta=s=0.044$ (A and B); success-bias weight, $\alpha=0.01$ (panels C and D).}
   \label{fig:var_alpha}

### 2022-09-14 ms/PrestigeBias.tex
update

@@
 
-This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity \citep{kin_selection}, % TODO are you sure this is the correct reference?
-maybe change to Denton et al?
-which depend on the frequency of a trait in the population or in a sample of role-models. 
+This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity \citep{conformity}, which depend on the frequency of a trait in the population or in a sample of role-models.
  We define a model of cultural transmission with prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
@@
 
-\begin{proof}
-The initial prestige of role-model $j$ based on \cref{eq:prestige} is
-\begin{equation}\label{eq:initial_prob}
-G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
-\end{equation}
-The denominator of \cref{eq:initial_prob} can also be formulated as:
-\begin{equation}\label{eq:denominator}
- \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
-\end{equation}
-where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
-Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
-\begin{equation}
-\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
-\end{equation}
-completing the proof.
+\begin{proof}\cref{append:GBD}
 \end{proof}
@@
 \begin{proof}
-Let $X$ be the number of individuals of type $\hat{A}$ such that $x=X/N$. $X'$ is the number of individuals with $\hat{A}$ in the next generation.
-The expected number of individuals is (due to the DM approximation),
-\begin{equation}
-E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2} \;,
-\end{equation}
-where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
-To use frequencies instead of counts, $E[x'] = E[X'/N] = \frac{1}{N}E[X']$.
-Putting it together,
-\begin{equation}
-\begin{split}
-E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}
-	  = \frac{x}{x + (1-x)\beta} \\
-	  &= \frac{x}{x + (1-x) -(1-x) + (1-x)\beta}
-	  = x \frac{1}{1 -(1-x)(1-\beta)}  \\
-	  &= x \big(1 + (1-x)(1-\beta) + o(\beta)\big)
-	  = x + x(1-x)(1-\beta) + o(\beta) \;,
-\end{split}
-\end{equation}
-following \citet[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
-
-By definition, $x$ is constant, so $E[x] = x$.
-We therefore have
-\begin{equation}\label{eq:expec_freq}
-E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta) \;,
-\end{equation}
-which gives us the drift term of the diffusion equation.
-
-Using the variance of the DM distribution,
-\begin{equation}
-V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}
-\Big(1-\frac{\alpha_1}{\alpha_1+\alpha_2}\Big)
-\Big(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2}\Big) \;.
-\end{equation}
-Again, we want to use frequencies so we have $V(X'/N) = \frac{1}{N^2}V(x')$.
-Putting it together with our model notations,
-\begin{equation}
-V(x') = \frac{1}{N^2}N\frac{x}{x+(1-x)\beta}\Big(1-\frac{x}{x+(1-x)\beta}\Big)
-\Big(\frac{N + \alpha' xN + \alpha' N(1-x)\beta}{1 + \alpha' xN + \alpha' N(1-x)\beta}\Big) \;.
-\end{equation}
-
-Following \citet[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
-\begin{equation}
-\frac{x}{x + (1-x)\beta} \approx x \,
-\end{equation}
-and for the entire variance expression we get
-\begin{equation}
-%\begin{split}
-V(x') \approx  \frac{1}{N} x(1-x)
-\Big(\frac{N + \alpha' xN + \alpha' N - \alpha' xN}{1 + \alpha' xN + \alpha' N - \alpha' xN}\Big)
-= x(1-x)\Big(\frac{1 + \alpha'}{1 + \alpha' N}\Big) \;.
-%\end{split}
-\end{equation}
-Now because $x$ is a constant, $V(x) = 0$, and therefore
-\begin{equation}\label{eq:var_diff_durret}
-V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N}) \;.
-\end{equation}
-$\alpha'$ is the odds ratio of the bias weight, 
-\begin{equation}\label{eq:success_ratio}
-\alpha' = \frac{\alpha}{1-\alpha} \;.
-\end{equation}
-Combining \cref{eq:var_diff_durret} and \cref{eq:success_ratio} we get:
-\begin{equation}\label{eq:const_var}
-\begin{split}
-V(x'-x) \approx x(1-x)\Big(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N}\Big)
-% &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\
-% &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\
-  = x(1-x)(\frac{1}{\alpha N + (1-\alpha)}) \;.
-\end{split}
-\end{equation}
-This gives the diffusion term of the diffusion equation, which completes the proof.
+\cref{append:drift_diff_const}
 \end{proof}
@@
 \begin{proof}
-Let $s_t=N(1-\beta_t)$, and $S_n=\sum\limits_{i=1}^n s_i$, where $\beta_t$ is $\beta(A)$ at generation $t$.
-We prove by induction both terms in \cref{eq:ch_expected_and_var}.
-From \cref{eq:expec_freq} we know that
-\begin{equation}\label{eq:ch_1}
-%\begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] 
-= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) 
-= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1} \;.
-%\end{split}
-\end{equation}
-Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
-\begin{equation}
-\begin{split}
-E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
-&= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] 
-= E\left[\frac{X_t}{N}\right] - E\left[\left(\frac{X_t}{N}\right)^2\right] \\
-&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2 \;.
-\end{split}
-\end{equation}
-
-We can now use the induction assumption of $V\big(\frac{X_t}{N}\big)$ to get
-\begin{equation}
-\begin{split}
-E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
-&\simeq E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x) \;.
-\end{split}
-\end{equation}
-From \cref{eq:ch_1} we know that
-\begin{equation}
-\begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
-&= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
-\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\
-&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x) \;.
-\end{split}
-\end{equation}
-Now we omit $O\big(\frac{1}{Ne\cdot N}\big)$ and get
-\begin{equation}\label{eq:ch_2}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) \;.
-\end{equation}
-
-We now look at the induction assumption to see that
-\begin{equation}
-E\left[\frac{X_t}{N}-x\right]
-= E\left[\frac{X_t}{N}\right]-E[x]
-= E\left[\frac{X_t}{N}\right]-x \;,
-\end{equation}
-so using the assumption we get
-\begin{equation}
-\begin{split}
-E\left[\frac{X_t}{N}\right] 
-&\simeq \frac{1}{N} S_t x(1-x)+x \;, \\
-1 - E\left[\frac{X_t}{N}\right] 
-&\simeq 1- \frac{1}{N} S_t x(1-x)+x \;.
-\end{split}
-\end{equation}
-We use both expressions in \cref{eq:ch_2} and get
-\begin{equation}\label{eq:ch_3}
-\begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
-&\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
-&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x) \;,
-\end{split}
-\end{equation}
-after again omitting $O\big(\frac{1}{N^2}\big)$ terms.
-To conclude the proof, we note that
-\begin{equation}
-E\left[\frac{X_{t+1}}{N}-x\right] 
-= E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right] \;,
-\end{equation}
-so again using the induction assumption, together with \cref{eq:ch_3} we get
-\begin{equation}
-\begin{split}
-E\left[\frac{X_{t+1}}{N}-x\right] \simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
-\simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) 
-\simeq \frac{1}{N} S_{t+1} x(1-x) \;,
-\end{split}
-\end{equation}
-which proves the drift term.
-
-For the diffusion term, we use a property of variance,
-\begin{equation}\label{eq:ch_var}
-V\left(\frac{X_{t+1}}{N}\right) 
-= E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) \;.
-\end{equation}
-
-Using \cref{eq:ch_1} we see that
-\begin{equation}\label{eq:ch_var1}
-\begin{split}
-&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] 
-= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\
-&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] 
-= \frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;.
-\end{split}
-\end{equation}
-
-Using \cref{eq:const_var} we get
-\begin{equation}
-V\left(\frac{X_{t+1}}{N} \bigg|X_t \right) 
-= \frac{1}{N_e}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;,
-\end{equation}
-and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of \cref{eq:ch_var} we get
-\begin{equation}\label{eq:ch_var2}
-E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] 
-= \frac{1}{N_e}E\left[\frac{X_t}{N}\left(1- \frac{X_t}{N}\right) \right] \simeq \frac{1}{N_e} x(1-x) \;.
-\end{equation}
-Moving on to simplify the second part of \cref{eq:ch_var} using \cref{eq:ch_var1},
-\begin{equation}
-V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
-= V\left(\frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \;.\right) \right)
-\end{equation}
-Now, because $\frac{X_t}{N}$ is a frequency, i.e $0 \leq X_t/N \leq 1$, we know that $V\left(\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq\frac{1}{4}$. We therefore find that
-\begin{equation}
-V\left(\frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)
-\leq \frac{1}{4N^2}s^2_{t+1} ;,
-\end{equation}
-and so it can be ignored.
-Combining our equations we get
-\begin{equation}
-V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
-= V\left(\frac{X_t}{N}\right) + O\left(\frac{1}{N^2}\right)\simeq V\left(\frac{X_t}{N}\right) \;.
-\end{equation}
-Using the induction assumption and \cref{eq:ch_var2},
-\begin{equation}
-V\left(\frac{X_{t+1}}{N}\right) 
-\simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1) \,
-\end{equation}
-which proves the diffusion term.
+\cref{append:drift_diff_chang}
 \end{proof}
@@
 We also analyzed a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
-We find that, similarly to the constant environment approximation, a change in the success-bias weight % TODO which symbol is that? was that it's name in the model section?
- has no negative effects on the goodness-of-fit of the approximation to simulation results.
-We also showed that this approximation is more sensitive to changes in the success coefficient value % TODO which symbol is that? was that it's name in the model section?
-than the constant environment approximation, and a lower value is required to have a good fit.
+We find that, similarly to the constant environment approximation, a change in the success-bias weight $\alpha$ has no negative effects on the goodness-of-fit of the approximation to simulation results.
+We also showed that this approximation is more sensitive to changes in the success coefficient $\beta$ than the constant environment approximation, and a lower value is required to have a good fit.
 The ratio between the number of generation in which the rare phenotype is under positive transmission bias and the number of generations in which it is under negative bias does not affect the goodness-of-fit of the approximation.
@@
 \pagebreak
+
+\appendix
+\section{General Binomial Distribution approximation proof}\label{append:GBD}
+\begin{proof}
+The initial prestige of role-model $j$ based on \cref{eq:prestige} is
+\begin{equation}\label{eq:initial_prob}
+G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
+\end{equation}
+The denominator of \cref{eq:initial_prob} can also be formulated as:
+\begin{equation}\label{eq:denominator}
+ \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
+\end{equation}
+where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
+Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
+\begin{equation}
+\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
+\end{equation}
+\end{proof}
+
+\section{Drift and diffusion in a constant environment proof}\label{append:drift_diff_const}
+\begin{proof}
+Let $X$ be the number of individuals of type $\hat{A}$ such that $x=X/N$. $X'$ is the number of individuals with $\hat{A}$ in the next generation.
+The expected number of individuals is (due to the DM approximation),
+\begin{equation}
+E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2} \;,
+\end{equation}
+where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
+To use frequencies instead of counts, $E[x'] = E[X'/N] = \frac{1}{N}E[X']$.
+Putting it together,
+\begin{equation}
+\begin{split}
+E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}
+	  = \frac{x}{x + (1-x)\beta} \\
+	  &= \frac{x}{x + (1-x) -(1-x) + (1-x)\beta}
+	  = x \frac{1}{1 -(1-x)(1-\beta)}  \\
+	  &= x \big(1 + (1-x)(1-\beta) + o(\beta)\big)
+	  = x + x(1-x)(1-\beta) + o(\beta) \;,
+\end{split}
+\end{equation}
+following \citet[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
+
+By definition, $x$ is constant, so $E[x] = x$.
+We therefore have
+\begin{equation}\label{eq:expec_freq}
+E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta) \;,
+\end{equation}
+which gives us the drift term of the diffusion equation.
+
+Using the variance of the DM distribution,
+\begin{equation}
+V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}
+\Big(1-\frac{\alpha_1}{\alpha_1+\alpha_2}\Big)
+\Big(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2}\Big) \;.
+\end{equation}
+Again, we want to use frequencies so we have $V(X'/N) = \frac{1}{N^2}V(x')$.
+Putting it together with our model notations,
+\begin{equation}
+V(x') = \frac{1}{N^2}N\frac{x}{x+(1-x)\beta}\Big(1-\frac{x}{x+(1-x)\beta}\Big)
+\Big(\frac{N + \alpha' xN + \alpha' N(1-x)\beta}{1 + \alpha' xN + \alpha' N(1-x)\beta}\Big) \;.
+\end{equation}
+
+Following \citet[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
+\begin{equation}
+\frac{x}{x + (1-x)\beta} \approx x \,
+\end{equation}
+and for the entire variance expression we get
+\begin{equation}
+%\begin{split}
+V(x') \approx  \frac{1}{N} x(1-x)
+\Big(\frac{N + \alpha' xN + \alpha' N - \alpha' xN}{1 + \alpha' xN + \alpha' N - \alpha' xN}\Big)
+= x(1-x)\Big(\frac{1 + \alpha'}{1 + \alpha' N}\Big) \;.
+%\end{split}
+\end{equation}
+Now because $x$ is a constant, $V(x) = 0$, and therefore
+\begin{equation}\label{eq:var_diff_durret}
+V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N}) \;.
+\end{equation}
+$\alpha'$ is the odds ratio of the bias weight, 
+\begin{equation}\label{eq:success_ratio}
+\alpha' = \frac{\alpha}{1-\alpha} \;.
+\end{equation}
+Combining \cref{eq:var_diff_durret} and \cref{eq:success_ratio} we get:
+\begin{equation}\label{eq:const_var}
+\begin{split}
+V(x'-x) \approx x(1-x)\Big(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N}\Big)
+% &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\
+% &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\
+  = x(1-x)(\frac{1}{\alpha N + (1-\alpha)}) \;.
+\end{split}
+\end{equation}
+This gives the diffusion term of the diffusion equation.
+\end{proof}
+
+\section{Drift and diffusion in a changing environment proof}\label{append:drift_diff_chang}
+\begin{proof}
+Let $s_t=N(1-\beta_t)$, and $S_n=\sum\limits_{i=1}^n s_i$, where $\beta_t$ is $\beta(A)$ at generation $t$.
+We prove by induction both terms in \cref{eq:ch_expected_and_var}.
+From \cref{eq:expec_freq} we know that
+\begin{equation}\label{eq:ch_1}
+%\begin{split}
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] 
+= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) 
+= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1} \;.
+%\end{split}
+\end{equation}
+Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
+\begin{equation}
+\begin{split}
+E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
+&= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] 
+= E\left[\frac{X_t}{N}\right] - E\left[\left(\frac{X_t}{N}\right)^2\right] \\
+&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2 \;.
+\end{split}
+\end{equation}
+
+We can now use the induction assumption of $V\big(\frac{X_t}{N}\big)$ to get
+\begin{equation}
+\begin{split}
+E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
+&\simeq E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x) \;.
+\end{split}
+\end{equation}
+From \cref{eq:ch_1} we know that
+\begin{equation}
+\begin{split}
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
+&= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
+\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\
+&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x) \;.
+\end{split}
+\end{equation}
+Now we omit $O\big(\frac{1}{Ne\cdot N}\big)$ and get
+\begin{equation}\label{eq:ch_2}
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) \;.
+\end{equation}
+
+We now look at the induction assumption to see that
+\begin{equation}
+E\left[\frac{X_t}{N}-x\right]
+= E\left[\frac{X_t}{N}\right]-E[x]
+= E\left[\frac{X_t}{N}\right]-x \;,
+\end{equation}
+so using the assumption we get
+\begin{equation}
+\begin{split}
+E\left[\frac{X_t}{N}\right] 
+&\simeq \frac{1}{N} S_t x(1-x)+x \;, \\
+1 - E\left[\frac{X_t}{N}\right] 
+&\simeq 1- \frac{1}{N} S_t x(1-x)+x \;.
+\end{split}
+\end{equation}
+We use both expressions in \cref{eq:ch_2} and get
+\begin{equation}\label{eq:ch_3}
+\begin{split}
+E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
+&\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
+&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x) \;,
+\end{split}
+\end{equation}
+after again omitting $O\big(\frac{1}{N^2}\big)$ terms.
+To conclude the proof, we note that
+\begin{equation}
+E\left[\frac{X_{t+1}}{N}-x\right] 
+= E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right] \;,
+\end{equation}
+so again using the induction assumption, together with \cref{eq:ch_3} we get
+\begin{equation}
+\begin{split}
+E\left[\frac{X_{t+1}}{N}-x\right] \simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
+\simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) 
+\simeq \frac{1}{N} S_{t+1} x(1-x) \;,
+\end{split}
+\end{equation}
+which proves the drift term.
+
+For the diffusion term, we use a property of variance,
+\begin{equation}\label{eq:ch_var}
+V\left(\frac{X_{t+1}}{N}\right) 
+= E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) \;.
+\end{equation}
+
+Using \cref{eq:ch_1} we see that
+\begin{equation}\label{eq:ch_var1}
+\begin{split}
+&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] 
+= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\
+&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] 
+= \frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;.
+\end{split}
+\end{equation}
+
+Using \cref{eq:const_var} we get
+\begin{equation}
+V\left(\frac{X_{t+1}}{N} \bigg|X_t \right) 
+= \frac{1}{N_e}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;,
+\end{equation}
+and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of \cref{eq:ch_var} we get
+\begin{equation}\label{eq:ch_var2}
+E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] 
+= \frac{1}{N_e}E\left[\frac{X_t}{N}\left(1- \frac{X_t}{N}\right) \right] \simeq \frac{1}{N_e} x(1-x) \;.
+\end{equation}
+Moving on to simplify the second part of \cref{eq:ch_var} using \cref{eq:ch_var1},
+\begin{equation}
+V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
+= V\left(\frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \;.\right) \right)
+\end{equation}
+Now, because $\frac{X_t}{N}$ is a frequency, i.e $0 \leq X_t/N \leq 1$, we know that $V\left(\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq\frac{1}{4}$. We therefore find that
+\begin{equation}
+V\left(\frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)
+\leq \frac{1}{4N^2}s^2_{t+1} ;,
+\end{equation}
+and so it can be ignored.
+Combining our equations we get
+\begin{equation}
+V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
+= V\left(\frac{X_t}{N}\right) + O\left(\frac{1}{N^2}\right)\simeq V\left(\frac{X_t}{N}\right) \;.
+\end{equation}
+Using the induction assumption and \cref{eq:ch_var2},
+\begin{equation}
+V\left(\frac{X_{t+1}}{N}\right) 
+\simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1) \,
+\end{equation}
+which proves the diffusion term.
+\end{proof}
+
 \end{document}

### 2022-09-18 ms/ms.tex
rename

--- 2022-09-14 ms/PrestigeBias.tex
@@
 \section{General Binomial Distribution approximation proof}\label{append:GBD}
+
+\paragraph{Proving $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.}
+
 \begin{proof}
@@
 \section{Drift and diffusion in a constant environment proof}\label{append:drift_diff_const}
+
+\paragraph{Proving drift and diffusion terms in a constant environment.}
+Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ is the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
+Then,
+\begin{equation*}
+E[x'-x] \approx x(1-x)(1-\beta) \;, 
+\quad
+V(x'-x) \approx x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big) \;.
+\end{equation*}
+
 \begin{proof}
@@
 \section{Drift and diffusion in a changing environment proof}\label{append:drift_diff_chang}
+\paragraph{Proving drift and diffusion terms in a changing environment.}
+Let $x$ be the initial frequency of the invading phenotype and $X_t$ is the number of individuals with the phenotype at time $t$.
+Then,
+\begin{equation*}
+E[X_t/N - x] \simeq x(1-x) S_t / N_e \;, 
+\quad
+\text{and}
+\quad
+V(X_t/N-x) \simeq  t x(1-x) / N_e \;,
+\end{equation*}
+where $S_t=\sum\limits_{i=1}^{t} N (1-\beta_t)$.
+
 \begin{proof}

### 2022-09-18 ms/ms.tex
reformat for journals

@@
 \documentclass[12pt]{extarticle}
-
-\makeatletter
-
-\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
-
-\makeatother
-
 \usepackage{geometry}
@@
 \usepackage[english]{babel}
-\usepackage{cjhebrew}
+% appendix
+\usepackage[title,page]{appendix}
+\usepackage{chngcntr}
 
@@
 % Supplementary
+% https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
 \newcommand{\beginsupplement}{%
@@
         \renewcommand{\thefigure}{S\arabic{figure}}%
+		\setcounter{equation}{0}
+        \renewcommand{\theequation}{A\arabic{equation}}%
 }
@@
 
+% line numbers
+\usepackage[displaymath, mathlines]{lineno}
+\renewcommand\linenumberfont{\normalfont\small\sffamily}
+\linenumbers
+\modulolinenumbers[2]
+
+% Title page
+\title{Cultural evolutionary dynamics with prestige bias}
+
+% Authors
+\renewcommand\Affilfont{\small}
+
+\author[1]{Saar Egozi}
+\author[2,3,$\dagger$]{Yoav Ram}
+
+\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
+\affil[3]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
+\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
+%\affil[*]{These authors contributed equally to this work}
+\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}
+
+% Document
 \begin{document}
-
-\begin{titlepage}
-	\centering
-	\includegraphics[width=0.4\textwidth]{ReichmanLogo}\par\vspace{1cm}
-	{\huge Reichman University \par}
-	{\Large Efi Arazi School of Computer Science \par}
-	{\Large M.Sc. Program - Research Track \par}
-
-	\vspace{1.5cm}
-	{\Huge Cultural Evolutionary Dynamics with Success and Influence Bias\par}
-	\vspace{1.5cm}
-	{\large by\par}
-	{\Large\bfseries Saar Egozi\par}
-	\vspace{1cm}
-	{\large Supervised by Dr. Yoav Ram\par}
-	{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel\par}
-%	{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel \par}
-
-	\vspace{1cm}
-	{M.Sc. dissertation, submitted in partial fulfillment of the requirements\par}
-	{for the M.Sc. degree, research track, School of Computer Science\par}
-	{Reichman University}
-
-	\vspace{1cm}
-	% Bottom of the page
-	{\large \today \par}
-
-\end{titlepage}
-
-% title page stuff
-%\title{Cultural Evolutionary Dynamics with Success and Influence biases}
-
-%\renewcommand\Affilfont{\small}
-%\author[1]{Saar Egozi}
-%\author[2,3,*]{Yoav Ram}
-%\affil[1]{School of Computer Science, Reichman University, Herzliya 4610101, Israel}
-%\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
-%\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel}
-%\affil[*]{Corresponding author: yoav@yoavram.com, ORCID 0000-0002-9653-4458}
-
-%\date{\today}
-
-%\maketitle
-
-This work was carried out under the supervision of Dr. Yoav Ram as part of the M.Sc.
-program of Efi Arazi School of Computer Science, Reichman University.
-
-\pagebreak
-
-\section{Abstract}
+\maketitle
+
+\begin{abstract}
 Copying role-models can be an efficient method for acquiring knowledge.
@@
 Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
-
-\blfootnote{This work is in preparation for submission to a high-impact journal.}
+\end{abstract}
+
 \pagebreak
 
-\tableofcontents
-
-\pagebreak
-
-\section{Introduction}
+%% Introduction
+\section*{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Models and methods}
+\section*{Models}
 
@@
 
-\subsection{Continuous trait}
+\subsection*{Continuous trait}
 We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
@@
 
-\subsection{Dichotomous trait}
+\subsection*{Dichotomous trait}
 To allow for mathematical analysis of the model, we introduce a simplified version where the trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\subsection{Approximations}
+\section*{Results}
+
 Our model is defined by two nested stochastic processes.
@@
 The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
-We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$.
-However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
+We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
+
 Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
@@
 In both we assume either $\alpha_j$ is a trait of role-model $j$ only (contrary to $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.
-\begin{enumerate}
-\item 
+\paragraph{Generalized binomial approximation.} 
 The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
-\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
-$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
-\item the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
-\end{enumerate}
-\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
+(i) the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
+$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$); and
+(ii) the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
+
+\paragraph{Dirichlet-Multinomial approximation.}
+The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
 Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
@@
 Note that here $G_{i,j}$ is only a function of the trait values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
-\end{enumerate}
-
-\subsection{Generalized binomial distribution}
+
+%%%%%%%%%%%%%
+\subsection*{Generalized binomial approximation}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
@@
 
-\begin{result}[GBD approximation]\label{res:GBD}
+\begin{result}[Generalized binomial approximation]\label{res:GBD}
 The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$. 
@@
 \end{proof}
+
+This result gives the following two corollaries on the expected number of followers of a given role-model by the end of the role-model choice process.
+The proof of \cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
+\\
 
@@
 
-\begin{proof}\cref{append:GBD}
-\end{proof}
-
 The special case where the bias weight is uniform for all role-models ($\alpha = \alpha_j$ for $j=1,\ldots, N$) is interesting, because we can evaluate the expected number of copiers using a linear equation
@@
   \caption{
-  \textbf{Numerical validation of the GBD approximation.}
+  \textbf{Numerical validation of the GB approximation.}
   The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
@@
 
-Although basic, \cref{fig:GBD} shows good fit of the GBD approximation.
+Although basic, \cref{fig:GBD} shows good fit of the GB approximation.
 This validation is initial, and the more extensive validations we do on the Dirichlet-Multinomial approximation, because it is what we will use in our analysts.
 
-\subsection{Dirichlet-Multinomial distribution}
+%%%%%%%%%%%%%
+\subsection*{Dirichlet-Multinomial distribution approximation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fixation probability and time}
+\subsection*{Fixation probability and time}
 
@@
 
-We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.\\
+We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.
+The proof is in Appendix~\ref{sec:drift_diff_const}.
+\\
 
@@
 \end{result}
-
-\begin{proof}
-\cref{append:drift_diff_const}
-\end{proof}
 
@@
 After finding a good approximation in constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a changing environment.
-Following \citet{changeEnv}, we find the following expressions for the expectation and variance of the change in frequency between $t$ generations.\\
+Following \citet{changeEnv}, we find the following expressions for the expectation and variance of the change in frequency between $t$ generations. 
+The proof is in Appendix~\ref{sec:drift_diff_chang}.
+\\
 
@@
 \end{result}
-
-\begin{proof}
-\cref{append:drift_diff_chang}
-\end{proof}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Adaptive success-bias weight}
+\subsection*{Adaptive success-bias weight}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
     \includegraphics[width=\linewidth]{../figures/final/choose_bias.pdf}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
-\section{Discussion}
+\section*{Discussion}
 During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
@@
 \citet{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
-They suggest a best-of-k model where an individual samples $k$ role-models and chooses the one he deems most "successful".
+They suggest a best-of-k model where an individual samples~$k$ role-models and chooses the one he deems most "successful".
 They mentioned that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
@@
 {\small
-\section{Acknowledgements}
+\section*{Acknowledgements}
 We thank Marcus Feldman, Martin Pontz, and Tal Simon for discussions and comments.
@@
 
-\section{References}
+\pagebreak
+
+\section*{References}
 \nolinenumbers
@@
 
-\appendix
-\section{General Binomial Distribution approximation proof}\label{append:GBD}
+\begin{appendices}
+\renewcommand{\theequation}{\thesection\arabic{equation}}
+\counterwithin*{equation}{section}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{General binomial distribution approximation} \label{sec:GBD}
 
@@
 
-\section{Drift and diffusion in a constant environment proof}\label{append:drift_diff_const}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Drift and diffusion in a constant environment} \label{sec:drift_diff_const}
 
@@
 
-\section{Drift and diffusion in a changing environment proof}\label{append:drift_diff_chang}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Drift and diffusion in a changing environment} \label{sec:drift_diff_chang}
 \paragraph{Proving drift and diffusion terms in a changing environment.}
@@
 
+\end{appendices}
+
+%%%
 \end{document}

### 2022-09-19 ms/ms.tex
continued to edit

@@
 \begin{abstract}
-Copying role-models can be an efficient method for acquiring knowledge.
-A common bias when choosing a role-model to copy is success bias: copying whoever appears more successful.
-This bias depends on the performance of the role-model alone, with no other factors.
-We propose an additional bias that may be prevalent in cultural transmission: influence bias, in which role-model choice is affected by the number of individuals that have already copied each potential role-model.
-We combine success and influence bias together to a ``prestige bias'' and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
-We find analytic approximations to our stochastic model, facilitating further mathematical analysis and reducing the computational complexity of simulations.
+A common bias in cultural transmission is to copy whoever appears more successful. This ``success bias'' only depends on the performance of the role-model.
+Here, we propose an additional transmission bias that may be common in cultural transmission: ``influence bias'', in which the choice of a role-model depends on the number of individuals that have already copied from that role-model.
+We combine success and influence bias together to form a ``prestige bias'', and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
+We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduces the computational complexity of simulations.
 We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
-We also find approximations to the fixation probability and the fixation time of an invading favored (by bias) cultural trait, in both constant and changing environments, which resemble Kimura's approximations for population-genetic models.
-These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
+We also find approximations to the fixation probability and the fixation time of an invading cultural trait, in both constant and changing environments. 
+These approximations are similar to Kimura's approximations for population-genetic models.
+These similarities show that success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
 Influence bias also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
-Our model may provide a good description of cultural transmission, 
-especially in human societies where social media is popular. 
-Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
+Our model extends the literature that attempt to describe of cultural transmission, 
+especially in human societies where social media is popular and thus influence bias may be expected. 
+Further work is needed to test if this model could predict various phenomena in cultural evolution.
 \end{abstract}
@@
 Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations \citep{cultural_traits}. 
-Although cultural transmission is most common in humans, it is also observed in other animals such as chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}.
-In elephants, \citet{elepahntsRepo} showed that once a matriarch is removed from the group, the group's survival instincts are inferior and that ``the possession of enhanced discriminatory abilities by the oldest individual [matriarch] in a group can influence the social knowledge of the group as a whole.''
-By playing audio recordings of African elephants, they showed that groups with a matriarch recognize and react better to hostile or friendly calls than groups without a matriarch.
-\citet{fliesPaper} showed that choice of oviposition site in fruit flies is culturally transmitted: inexperienced flies that spent some time with experienced flies chose the same type of oviposition site even without directly observing this behavior.
-How the information is transmitted is still an open question, but it has been suggested that flies may use olfactory cues like other animals, such as rodents and bees.
-
-\paragraph{Direction of transmission.}
-Similar to genetic transmission, culturally transmitted traits can be transmitted from parents to offspring, and their effects of can be physiological rather than behavioral.
-For example, parents can "teach" their children to be strong or tall, within some biological limits, by instructing them to maintain a specific diet and engage in physical activity.
-Contrary to genetic transmission, cultural transmission can be non-vertical, that is, traits may be transmitted via social learning from non-parental individuals, and even unrelated individuals such as teachers, leaders, media, or any stranger that interacts with the learning individual.
-Thus, cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
+Although cultural transmission is most common in humans, it is also observed in other animals, e.g., chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper}.
+
+Cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults (teachers, leaders, strangers) transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
 Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.
-
-\paragraph{Transmission biases.}
-In social learning, transmission biases cause a trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
-Although more common in cultural transmission, transmission biases do occur in genetic transmission.
+It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{Ram2018}.
+
+%\paragraph{Transmission biases.}
+Cultural transmission biases may cause a trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
+%Although more common in cultural transmission, transmission biases do occur in genetic transmission.
 For example, \textit{wtf genes} in yeast bias their transmission to the gamete by secreting a long life-expectancy poison together with a short life-expectancy antidote, so that a gamete without the gene will perish because the poison will outlive the antidote \citep{wtfGene}.
@@
 279]{evolutionBook}.
-\citet{cooperation} show that cooperative behavior can evolve in an individual due to horizontal transmission bias even when there is no benefit to it, or when it benefits its competitors.
+For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
 
 \paragraph{Success bias.}
-\citet{strategiesPaper} have conducted a tournament between learning strategies.
-Each strategy defines when individuals observe and copy from others, and when they engage in individual learning, in which an individual learns a cultural trait on his own.
-The best strategies had a high frequency of social learning relative to individual learning, even when the transmission error was almost 50\%.
-From these results we understand that all the winning strategies were mostly based on success biased social learning, meaning it contributed more to the general success of the population than individual learning.
-However, all winning strategies included individual learning to some degree, implying that success-biased learning alone isn't the best way to advance, even when success is measured accurately.
-
-\paragraph{Evaluating success.}
-\citet[Ch. 5]{evolutionBook} suggest that the evaluation of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
-A direct bias occurs when a variation of a trait is more attractive than others, and is evaluated by \textit{directly} testing the variation of the trait.
-For example, an individual observing a Ping-Pong match can attempt both of the observed paddle grips to determine which grip is better.
-An indirect bias occurs when an individual uses the value of one trait to determine the attractiveness of another, so it \textit{indirectly} evaluates the attractiveness of the role-model.
-For example, an observer may copy the paddle grip of the Ping-Pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
-A frequency-dependent bias occurs when an individual has a probability to copy a variant of the trait that higher or lower than trait's frequency among demonstrators. 
-For example, when an individual is 80\% likely to copy the common paddle grip even when only 60\% of the population is using it, it is said to be frequency-biased, or in this case, conformist.
-Frequency bias could be negative, i.e., non-conformist bias. 
-Conformity and non-conformity are well-known biases in cultural transmission \citep{conformism}, and its effect on cultural evolution have been studied with both models \citep{conformity,anticonformity} and experiments \citep{negativeFrequency}.
-
+% TODO add definition of success bias and some reference to a study demonstrating it in humans or other animals.
+Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself is not enough, even if success is measured accurately.
+
+\citet[Ch. 5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
+A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \textit{directly} testing the trait.
+For example, an individual observing a ping-pong match can attempt both of the observed paddle grips to determine which grip is better.
+An indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
+For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
+A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
+For example, when the common paddle grip is used by 60\% of the demonstrators, then if the probability to copy this grip is 80\%, then transmission is under positive frequency bias, also called conformity; if the probability is 40\%, then transmission is under negative frequency bias, or non-conformity \citep{conformism}.
+The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{conformity,anticonformity} and experiments \citep{negativeFrequency}.
+
+% YOAV HERE
 \paragraph{Prestige.}

### 2022-09-21 ms/ms.tex
finished intro

@@
 
-% YOAV HERE
 \paragraph{Prestige.}
-Prestige means having a good reputation or high esteem, therefore does not directly signify success (although it may imply it), making it an indirect bias.
-Both \citet[Ch. 8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
+Prestige means having a good reputation or high esteem, therefore does not directly signify success, although it may imply it--making it an indirect bias.
+\citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
 \citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population if indirect biases are strong enough.
@@
 Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making.
-Online social networks such as \textit{Facebook} or \textit{Instagram} are known to affect the influence of individuals \citep{social_influence,influence_analysis,social_media}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
+Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
+
 Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
+% TODO rephrase the next two sentences, they are heard to understand - from here
 In addition to using influence bias as an easy way to approximate role-models worth, it can also be a used to approximate it better than the copier's own estimation.
 This bias can save the copier costs: time, effort etc, and it can also improve its choice of role-model.
-
-This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity \citep{conformity}, which depend on the frequency of a trait in the population or in a sample of role-models.
- We define a model of cultural transmission with prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
+%% to here
+Influence bias is a context-based, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model.
+IT also differs from frequency biases such as conformity \citep{conformity}, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.
+
+Here, we define a model of cultural transmission with prestige bias that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics.
+We find approximations for the probability and time for fixation of a "successful" phenotype (i.e., that is favored by success bias).
+Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.
 
@@
 \section*{Models}
-
+% YOAV HERE
 We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.

### 2022-10-26 ms/PrestigeBias.tex
update

@@
 \end{equation}
+
 Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$, that determines the relative significance of success and influence within the role-model's overall prestige, in the eyes if the copier.
+
+We assume every individual evaluates the importance of success and influence differently.
+Additionally, we assume every role-model displays his influence and success individually, for example - a person with more followers but lack of actual skill may emphasize the number of his followers rather than his actual skill.
+We therefore modeled $\alpha_{ij}$ to be the relation between every copiers intrinsic significance of estimation, and every role-models personal emphasis.
+
 The trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
@@
 \begin{equation}\label{eq:binary-model}
-G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
-\end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.
+G_{i,A} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + C\alpha'\beta(\hat{A})} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + \alpha'C}
+\end{equation}
+where $C$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.
 
@@
 $\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
+This means that there's no actual estimation error in the population, just a fixed bias in every copiers estimation.
 \item the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
@@
   \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (red vertical line) is much higher compared to the log-likelihood of permutations of experiments (blue histogram).
-  Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.}	
+  Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
+  No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
   \label{fig:DM_validation}
@@
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
-We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,x)$ where $x \in [10^{-7},10^{-1}]$.
+We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,q)$ where $q \in [10^{-7},10^{-1}]$.
 We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\cref{fig:hetro_alpha}).
@@
 After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
-We focus on the fixation probability and fixation time of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
+We focus on the conditional fixation probability and conditioned fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
 We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
@@
 Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citet[eq.~8]{kimura}, we get the following result.\\
+It's interesting to notice that when $N>>1$, $N_e \approx \alpha N$, resulting in a very convenient expression.\\
 

### 2022-10-27 ms/ms.tex

--- 2022-09-18 ms/ms.tex
@@
 \usepackage[english]{babel}
-% appendix
-\usepackage[title,page]{appendix}
-\usepackage{chngcntr}
+\usepackage{cjhebrew}
 
@@
  \renewcommand\linenumberfont{\normalfont\small\sffamily}
-%\linenumbers
+%%%%\linenumbers
 \modulolinenumbers[2]
@@
 % Supplementary
-% https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
 \newcommand{\beginsupplement}{%
@@
         \renewcommand{\thefigure}{S\arabic{figure}}%
-		\setcounter{equation}{0}
-        \renewcommand{\theequation}{A\arabic{equation}}%
 }
@@
 
-% line numbers
-\usepackage[displaymath, mathlines]{lineno}
-\renewcommand\linenumberfont{\normalfont\small\sffamily}
-\linenumbers
-\modulolinenumbers[2]
-
-% Title page
-\title{Cultural evolutionary dynamics with prestige bias}
-
-% Authors
-\renewcommand\Affilfont{\small}
-
-\author[1]{Saar Egozi}
-\author[2,3,$\dagger$]{Yoav Ram}
-
-\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
-\affil[3]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
-\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
-%\affil[*]{These authors contributed equally to this work}
-\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}
-
-% Document
 \begin{document}
-\maketitle
-
-\begin{abstract}
+
+\begin{titlepage}
+	\centering
+	\includegraphics[width=0.4\textwidth]{ReichmanLogo}\par\vspace{1cm}
+	{\huge Reichman University \par}
+	{\Large Efi Arazi School of Computer Science \par}
+	{\Large M.Sc. Program - Research Track \par}
+
+	\vspace{1.5cm}
+	{\Huge Cultural Evolutionary Dynamics with Success and Influence Bias\par}
+	\vspace{1.5cm}
+	{\large by\par}
+	{\Large\bfseries Saar Egozi\par}
+	\vspace{1cm}
+	{\large Supervised by Dr. Yoav Ram\par}
+	{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel\par}
+%	{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel \par}
+
+	\vspace{1cm}
+	{M.Sc. dissertation, submitted in partial fulfillment of the requirements\par}
+	{for the M.Sc. degree, research track, School of Computer Science\par}
+	{Reichman University}
+
+	\vspace{1cm}
+	% Bottom of the page
+	{\large \today \par}
+
+\end{titlepage}
+
+% title page stuff
+%\title{Cultural Evolutionary Dynamics with Success and Influence biases}
+
+%\renewcommand\Affilfont{\small}
+%\author[1]{Saar Egozi}
+%\author[2,3,*]{Yoav Ram}
+%\affil[1]{School of Computer Science, Reichman University, Herzliya 4610101, Israel}
+%\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
+%\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel}
+%\affil[*]{Corresponding author: yoav@yoavram.com, ORCID 0000-0002-9653-4458}
+
+%\date{\today}
+
+%\maketitle
+
+This work was carried out under the supervision of Dr. Yoav Ram as part of the M.Sc.
+program of Efi Arazi School of Computer Science, Reichman University.
+
+\pagebreak
+
+\section{Abstract}
 Copying role-models can be an efficient method for acquiring knowledge.
@@
 Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
-\end{abstract}
-
+
+\blfootnote{This work is in preparation for submission to a high-impact journal.}
 \pagebreak
 
-%% Introduction
-\section*{Introduction}
+\tableofcontents
+
+\pagebreak
+
+\section{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Models}
+\section{Models and methods}
 
@@
 \end{equation}
-Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$, that determines the relative significance of success and influence within the role-model's overall prestige, in the eyes if the copier.
+
+Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of success and influence in the role-model's overall prestige in the eyes of the copier.
+
+We assume every individual evaluates the importance of success and influence differently.
+Additionally, we assume every role-model displays his influence and success individually, for example - a person with more followers but lack of actual skill may emphasize the number of his followers rather than his actual skill.
+We therefore modeled $\alpha_{ij}$ to be the relation between every copiers intrinsic significance of estimation, and every role-models personal emphasis.
+
 The trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
 
-\subsection*{Dichotomous trait}
+\subsection{Dichotomous trait}
 To allow for mathematical analysis of the model, we introduce a simplified version where the trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-
+\section{Results}
+\subsection{Approximations}
 Our model is defined by two nested stochastic processes.
@@
 The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
-We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
-
+We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$.
+However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
 Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$.
@@
 In both we assume either $\alpha_j$ is a trait of role-model $j$ only (contrary to $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.
-\paragraph{Generalized binomial approximation.} 
+\begin{enumerate}
+\item 
 The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
-(i) the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
-$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$); and
-(ii) the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
-
-\paragraph{Dirichlet-Multinomial approximation.}
-The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
+\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
+$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
+This means that there's no actual estimation error in the population, just a fixed bias in every copier estimation.
+\item the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
+\end{enumerate}
+\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
 Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
@@
 Note that here $G_{i,j}$ is only a function of the trait values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
-
-%%%%%%%%%%%%%
-\subsection*{Generalized binomial approximation}
+\end{enumerate}
+
+\subsection{Generalized binomial distribution}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
@@
 
-\begin{result}[Generalized binomial approximation]\label{res:GBD}
+\begin{result}[GBD approximation]\label{res:GBD}
 The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$. 
@@
 \end{proof}
-
-This result gives the following two corollaries on the expected number of followers of a given role-model by the end of the role-model choice process.
-The proof of \cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
-\\
 
@@
 
+\begin{proof}\cref{append:GBD}
+\end{proof}
+
 The special case where the bias weight is uniform for all role-models ($\alpha = \alpha_j$ for $j=1,\ldots, N$) is interesting, because we can evaluate the expected number of copiers using a linear equation
@@
   \caption{
-  \textbf{Numerical validation of the GB approximation.}
+  \textbf{Numerical validation of the GBD approximation.}
   The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
@@
 
-Although basic, \cref{fig:GBD} shows good fit of the GB approximation.
+Although basic, \cref{fig:GBD} shows good fit of the GBD approximation.
 This validation is initial, and the more extensive validations we do on the Dirichlet-Multinomial approximation, because it is what we will use in our analysts.
 
-%%%%%%%%%%%%%
-\subsection*{Dirichlet-Multinomial distribution approximation}
+\subsection{Dirichlet-Multinomial distribution}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Fixation probability and time}
+\subsection{Fixation probability and time}
 
 After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
-We focus on the fixation probability and fixation time of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
+We focus on the fixation probability and conditioned fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
 We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
@@
 
-We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.
-The proof is in Appendix~\ref{sec:drift_diff_const}.
-\\
+We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.\\
 
@@
 \end{result}
+
+\begin{proof}
+\cref{append:drift_diff_const}
+\end{proof}
 
@@
 
-Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citet[eq.~8]{kimura}, we get the following result.\\
-
+Note that when $N>>1$, $N_e \approx \alpha N$, resulting in a very convenient expression.\\
+
+Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citet[eq.~8]{kimura}, we get the following result:
 \begin{result}[Fixation probability]
@@
 After finding a good approximation in constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a changing environment.
-Following \citet{changeEnv}, we find the following expressions for the expectation and variance of the change in frequency between $t$ generations. 
-The proof is in Appendix~\ref{sec:drift_diff_chang}.
-\\
+Following \citet{changeEnv}, we find the following expressions for the expectation and variance of the change in frequency between $t$ generations.\\
 
@@
 \end{result}
+
+\begin{proof}
+\cref{append:drift_diff_chang}
+\end{proof}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \includegraphics[width=\linewidth]{../figures/final/choose_bias.pdf}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
+\clearpage
+\section{Discussion}
 During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
@@
 \citet{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
-They suggest a best-of-k model where an individual samples~$k$ role-models and chooses the one he deems most "successful".
+They suggest a best-of-k model where an individual samples $k$ role-models and chooses the one he deems most "successful".
 They mentioned that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
@@
 
-\pagebreak
-
-\section*{References}
+\section{References}
 \nolinenumbers
@@
 
-\begin{appendices}
-\renewcommand{\theequation}{\thesection\arabic{equation}}
-\counterwithin*{equation}{section}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{General binomial distribution approximation} \label{sec:GBD}
+\appendix
+\section{General Binomial Distribution approximation proof}\label{append:GBD}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Drift and diffusion in a constant environment} \label{sec:drift_diff_const}
+\section{Drift and diffusion in a constant environment proof}\label{append:drift_diff_const}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Drift and diffusion in a changing environment} \label{sec:drift_diff_chang}
+\section{Drift and diffusion in a changing environment proof}\label{append:drift_diff_chang}
 \paragraph{Proving drift and diffusion terms in a changing environment.}
@@
 
-\end{appendices}
-
-%%%
 \end{document}

### 2022-10-27 ms/ms.tex
update

@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{ReichmanLogo}\par\vspace{1cm}
+	\includegraphics[width=0.4\textwidth]{ReichmanLogo.png}\par\vspace{1cm}
 	{\huge Reichman University \par}
@@
 	\vspace{1cm}
-	{\large Supervised by Dr. Yoav Ram\par}
-	{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel\par}
+	%{\large Supervised by Dr. Yoav Ram\par}
+	%{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel\par}
 %	{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel \par}
@@
 \paragraph{Prestige.}
-Prestige means having a good reputation or high esteem, therefore does not directly signify success (although it may imply it), making it an indirect bias.
-Both \citet[Ch. 8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
+Prestige means having a good reputation or high esteem, therefore does not directly signify success, although it may imply it--making it an indirect bias.
+\citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
 \citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population if indirect biases are strong enough.
@@
 Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making.
-Online social networks such as \textit{Facebook} or \textit{Instagram} are known to affect the influence of individuals \citep{social_influence,influence_analysis,social_media}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
+Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
 Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
-In addition to using influence bias as an easy way to approximate role-models worth, it can also be a used to approximate it better than the copier's own estimation.
-This bias can save the copier costs: time, effort etc, and it can also improve its choice of role-model.
-
-This bias depends on the state of a role-model rather than on its trait, in contrast to frequency biases such as conformity \citep{conformity}, which depend on the frequency of a trait in the population or in a sample of role-models.
- We define a model of cultural transmission with prestige bias that combines both success and influence biases, provide analytic approximations for this model, and analyze its dynamics.
+Influence can be easily estimated, so costs may be lower than estimating success. In some cases it could be a more accurate estimation as well.
+
+Influence bias is a context-based, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model.
+IT also differs from frequency biases such as conformity \citep{conformity}, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.
+
+Here, we define a model of cultural transmission with prestige bias that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics.
+We find approximations for the probability and time for fixation of a "successful" phenotype (i.e., that is favored by success bias).
+Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.
 

### 2022-10-27 ms/merge.py

@@ -1,0 +1,27 @@
+from PyPDF2 import PdfFileMerger
+
+
+def merge(thesis_path, hebrew_cover):
+    merger = PdfFileMerger()
+
+    thesis_file = open(thesis_path, "rb")
+    hebrew_file = open(hebrew_cover, "rb")
+
+    # add all pages of thesis to output
+    merger.append(fileobj=thesis_file)
+
+    # append hebrew cover to the end of the output document
+    merger.append(hebrew_file)
+
+    # Write to an output PDF document
+    output = open(output_path(thesis_path), "wb")
+    merger.write(output)
+
+
+def output_path(thesis_path: str):
+    assert thesis_path.endswith('.pdf')
+    return thesis_path[:-4] + '_with_hebrew_abstract' + '.pdf'
+
+
+if __name__ == '__main__':
+    merge('ms.pdf', 'HebrewThesisSaar.pdf')

### 2022-11-08 ms/ms.tex
update

@@
 \section{Abstract}
-Copying role-models can be an efficient method for acquiring knowledge.
-A common bias when choosing a role-model to copy is success bias: copying whoever appears more successful.
-This bias depends on the performance of the role-model alone, with no other factors.
-We propose an additional bias that may be prevalent in cultural transmission: influence bias, in which role-model choice is affected by the number of individuals that have already copied each potential role-model.
-We combine success and influence bias together to a ``prestige bias'' and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
-We find analytic approximations to our stochastic model, facilitating further mathematical analysis and reducing the computational complexity of simulations.
+A common bias in cultural transmission is to copy whoever appears more successful. This ``success bias'' only depends on the performance of the role-model.
+Here, we propose an additional transmission bias that may be common in cultural transmission: ``influence bias'', in which the choice of a role-model depends on the number of individuals that have already copied from that role-model.
+We combine success and influence bias together to form a ``prestige bias'', and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
+We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduces the computational complexity of simulations.
 We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
-We also find approximations to the fixation probability and the fixation time of an invading favored (by bias) cultural trait, in both constant and changing environments, which resemble Kimura's approximations for population-genetic models.
-These approximations show that success bias effectively plays the part of natural selection, whereas influence bias effectively reduces the population size.	
+We also find approximations to the fixation probability and the fixation time of an invading cultural trait, in both constant and changing environments. 
+These approximations are similar to Kimura's approximations for population-genetic models.
+These similarities show that success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.
+
 Influence bias also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
-Our model may provide a good description of cultural transmission, 
-especially in human societies where social media is popular. 
-Further work is needed to test if this model could predict various phenomena in cultural evolution when extended with the effects of selection and innovation.
+Our model extends the literature that attempt to describe of cultural transmission, 
+especially in human societies where social media is popular and thus influence bias may be expected. 
+Further work is needed to test if this model could predict various phenomena in cultural evolution.
 
@@
 Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations \citep{cultural_traits}.
-Although cultural transmission is most common in humans, it is also observed in other animals such as chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}.
-In elephants, \citet{elepahntsRepo} showed that once a matriarch is removed from the group, the group's survival instincts are inferior and that ``the possession of enhanced discriminatory abilities by the oldest individual [matriarch] in a group can influence the social knowledge of the group as a whole.''
-By playing audio recordings of African elephants, they showed that groups with a matriarch recognize and react better to hostile or friendly calls than groups without a matriarch.
-\citet{fliesPaper} showed that choice of oviposition site in fruit flies is culturally transmitted: inexperienced flies that spent some time with experienced flies chose the same type of oviposition site even without directly observing this behavior.
-How the information is transmitted is still an open question, but it has been suggested that flies may use olfactory cues like other animals, such as rodents and bees.
-
-\paragraph{Direction of transmission.}
-Similar to genetic transmission, culturally transmitted traits can be transmitted from parents to offspring, and their effects of can be physiological rather than behavioral.
-For example, parents can "teach" their children to be strong or tall, within some biological limits, by instructing them to maintain a specific diet and engage in physical activity.
-Contrary to genetic transmission, cultural transmission can be non-vertical, that is, traits may be transmitted via social learning from non-parental individuals, and even unrelated individuals such as teachers, leaders, media, or any stranger that interacts with the learning individual.
-Thus, cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
+
+Although cultural transmission is most common in humans, it is also observed in other animals, e.g., chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper}.
+
+Cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults (teachers, leaders, strangers) transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
 Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.
-
-\paragraph{Transmission biases.}
-In social learning, transmission biases cause a trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
-Although more common in cultural transmission, transmission biases do occur in genetic transmission.
-For example, \textit{wtf genes} in yeast bias their transmission to the gamete by secreting a long life-expectancy poison together with a short life-expectancy antidote, so that a gamete without the gene will perish because the poison will outlive the antidote \citep{wtfGene}.
+It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{Ram2018}.
+
+Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.
+
+Cultural transmission biases may cause a trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
 Importantly, even when a trait is disfavored by natural selection, it may still spread in a population due to transmission biases that are strong enough to overcome selection \citep[Ch.
@@
 279]{evolutionBook}.
-\citet{cooperation} show that cooperative behavior can evolve in an individual due to horizontal transmission bias even when there is no benefit to it, or when it benefits its competitors.
-
-\paragraph{Success bias.}
-\citet{strategiesPaper} have conducted a tournament between learning strategies.
-Each strategy defines when individuals observe and copy from others, and when they engage in individual learning, in which an individual learns a cultural trait on his own.
-The best strategies had a high frequency of social learning relative to individual learning, even when the transmission error was almost 50\%.
-From these results we understand that all the winning strategies were mostly based on success biased social learning, meaning it contributed more to the general success of the population than individual learning.
-However, all winning strategies included individual learning to some degree, implying that success-biased learning alone isn't the best way to advance, even when success is measured accurately.
-
-\paragraph{Evaluating success.}
-\citet[Ch. 5]{evolutionBook} suggest that the evaluation of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
-A direct bias occurs when a variation of a trait is more attractive than others, and is evaluated by \textit{directly} testing the variation of the trait.
-For example, an individual observing a Ping-Pong match can attempt both of the observed paddle grips to determine which grip is better.
-An indirect bias occurs when an individual uses the value of one trait to determine the attractiveness of another, so it \textit{indirectly} evaluates the attractiveness of the role-model.
-For example, an observer may copy the paddle grip of the Ping-Pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
-A frequency-dependent bias occurs when an individual has a probability to copy a variant of the trait that higher or lower than trait's frequency among demonstrators. 
-For example, when an individual is 80\% likely to copy the common paddle grip even when only 60\% of the population is using it, it is said to be frequency-biased, or in this case, conformist.
-Frequency bias could be negative, i.e., non-conformist bias. 
-Conformity and non-conformity are well-known biases in cultural transmission \citep{conformism}, and its effect on cultural evolution have been studied with both models \citep{conformity,anticonformity} and experiments \citep{negativeFrequency}.
+For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
+
+% TODO add definition of success bias and some reference to a study demonstrating it in humans or other animals.
+Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself is not enough, even if success is measured accurately.
+
+\citet[Ch. 5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
+A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \textit{directly} testing the trait.
+For example, an individual observing a ping-pong match can attempt both of the observed paddle grips to determine which grip is better.
+An indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
+For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
+A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
+For example, when the common paddle grip is used by 60\% of the demonstrators, then if the probability to copy this grip is 80\%, then transmission is under positive frequency bias, also called conformity; if the probability is 40\%, then transmission is under negative frequency bias, or non-conformity \citep{conformism}.
+The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{conformity,anticonformity} and experiments \citep{negativeFrequency}.
 

### 2022-11-08 ms/ms.tex
update

@@
 \documentclass[12pt]{extarticle}
-
-\makeatletter
-
-\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
-
-\makeatother
 
@@
 \usepackage[english]{babel}
-\usepackage{cjhebrew}
-
+% appendix
+\usepackage[title,page]{appendix}
+\usepackage{chngcntr}
 % unbreakable dashes
@@
         \renewcommand{\thefigure}{S\arabic{figure}}%
+        \setcounter{equation}{0}
+        \renewcommand{\theequation}{A\arabic{equation}}%
 }
@@
 
+% line numbers
+\usepackage[displaymath, mathlines]{lineno}
+\renewcommand\linenumberfont{\normalfont\small\sffamily}
+\linenumbers
+\modulolinenumbers[2]
+
+% Title page
+\title{Cultural evolutionary dynamics with prestige bias}
+% Authors
+\renewcommand\Affilfont{\small}
+
+\author[1]{Saar Egozi}
+\author[2,3,$\dagger$]{Yoav Ram}
+
+\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
+\affil[3]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
+\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
+%\affil[*]{These authors contributed equally to this work}
+\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}
+
 \begin{document}
-
-\begin{titlepage}
-	\centering
-	\includegraphics[width=0.4\textwidth]{ReichmanLogo.png}\par\vspace{1cm}
-	{\huge Reichman University \par}
-	{\Large Efi Arazi School of Computer Science \par}
-	{\Large M.Sc. Program - Research Track \par}
-
-	\vspace{1.5cm}
-	{\Huge Cultural Evolutionary Dynamics with Success and Influence Bias\par}
-	\vspace{1.5cm}
-	{\large by\par}
-	{\Large\bfseries Saar Egozi\par}
-	\vspace{1cm}
-	%{\large Supervised by Dr. Yoav Ram\par}
-	%{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel\par}
-%	{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel \par}
-
-	\vspace{1cm}
-	{M.Sc. dissertation, submitted in partial fulfillment of the requirements\par}
-	{for the M.Sc. degree, research track, School of Computer Science\par}
-	{Reichman University}
-
-	\vspace{1cm}
-	% Bottom of the page
-	{\large \today \par}
-
-\end{titlepage}
-
-% title page stuff
-%\title{Cultural Evolutionary Dynamics with Success and Influence biases}
-
-%\renewcommand\Affilfont{\small}
-%\author[1]{Saar Egozi}
-%\author[2,3,*]{Yoav Ram}
-%\affil[1]{School of Computer Science, Reichman University, Herzliya 4610101, Israel}
-%\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv 6997801, Israel}
-%\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv 6997801, Israel}
-%\affil[*]{Corresponding author: yoav@yoavram.com, ORCID 0000-0002-9653-4458}
-
-%\date{\today}
-
-%\maketitle
-
-This work was carried out under the supervision of Dr. Yoav Ram as part of the M.Sc.
-program of Efi Arazi School of Computer Science, Reichman University.
-
-\pagebreak
-
-\section{Abstract}
+\maketitle
+
+\begin{abstract}
 A common bias in cultural transmission is to copy whoever appears more successful. This ``success bias'' only depends on the performance of the role-model.
@@
 Further work is needed to test if this model could predict various phenomena in cultural evolution.
-
-\blfootnote{This work is in preparation for submission to a high-impact journal.}
+\end{abstract}
+
 \pagebreak
 
-\tableofcontents
-
-\pagebreak
-
-\section{Introduction}
+\section*{Introduction}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\subsection{Approximations}
+\section*{Results}
 Our model is defined by two nested stochastic processes.
@@
 The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
-We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$.
-However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
+We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
 Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
@@
 In both we assume either $\alpha_j$ is a trait of role-model $j$ only (contrary to $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.
-\begin{enumerate}
-\item 
+
+\paragraph{Generalized binomial approximation.}  
 The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
-\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
-$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
-This means that there's no actual estimation error in the population, just a fixed bias in every copier estimation.
-\item the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
-\end{enumerate}
-\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
-Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
-$\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
+
+(i) the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
+$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$); and
+(ii) the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
+
+\paragraph{Dirichlet-Multinomial approximation.}
+The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
+
 Note that here $G_{i,j}$ is only a function of the trait values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
-\end{enumerate}
-
-\subsection{Generalized binomial distribution}
+
+\subsection*{Generalized binomial distribution}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
@@
 \end{proof}
+This result gives the following two corollaries on the expected number of followers of a given role-model by the end of the role-model choice process.
+The proof of \cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
+\\
 
@@
 
-Although basic, \cref{fig:GBD} shows good fit of the GBD approximation.
+Although basic, \cref{fig:GBD} shows good fit of the GB approximation.
 This validation is initial, and the more extensive validations we do on the Dirichlet-Multinomial approximation, because it is what we will use in our analysts.
 
-\subsection{Dirichlet-Multinomial distribution}
+\subsection*{Dirichlet-Multinomial distribution approximation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
-\section{Discussion}
+
+\section*{Discussion}
 During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
@@
 
-\section{References}
+\section*{References}
 \nolinenumbers
@@
 
-\section{Drift and diffusion in a constant environment proof}\label{append:drift_diff_const}
+\section{Drift and diffusion in a constant environment} \label{sec:drift_diff_const}
 
@@
 
-\section{Drift and diffusion in a changing environment proof}\label{append:drift_diff_chang}
+\section{Drift and diffusion in a changing environment} \label{sec:drift_diff_chang}
 \paragraph{Proving drift and diffusion terms in a changing environment.}
@@
 \end{proof}
+\end{appendices}
+
+%%%
 

### 2022-11-08 ms/merge.py

@@ -1,27 +1,0 @@
-from PyPDF2 import PdfFileMerger
-
-
-def merge(thesis_path, hebrew_cover):
-    merger = PdfFileMerger()
-
-    thesis_file = open(thesis_path, "rb")
-    hebrew_file = open(hebrew_cover, "rb")
-
-    # add all pages of thesis to output
-    merger.append(fileobj=thesis_file)
-
-    # append hebrew cover to the end of the output document
-    merger.append(hebrew_file)
-
-    # Write to an output PDF document
-    output = open(output_path(thesis_path), "wb")
-    merger.write(output)
-
-
-def output_path(thesis_path: str):
-    assert thesis_path.endswith('.pdf')
-    return thesis_path[:-4] + '_with_hebrew_abstract' + '.pdf'
-
-
-if __name__ == '__main__':
-    merge('ms.pdf', 'HebrewThesisSaar.pdf')

### 2022-12-17 ms/ms.tex
update

@@
 All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
-In addition, we assume homogeneous $\alpha$ for simplicity and for easier mathematical analysis.
+In addition, we assume homogeneous $\alpha$, also called \textit{exchangability}, for simplicity and for easier mathematical analysis.
 Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
@@
 
+So far we examined different variations of our model using a Wright-Fisher model as our basis, mainly because we wanted to base our model on a known one from the literature, namely \citet{evolutionBook} indirect bias model.
+When approximating our model by comparing it to a Polya Urn process, we noticed that our model would be identical to a model where every copier that chose a role-model would copy its trait and join the role-models during the selection process.
+Based on this, we theorize that when using a Moran model as basis instead of a Wright-Fisher mode, we would get very similar, and perhaps identical results.
+It would be interesting to run simulations and analyze that model, to prove or disprove our hypothesis.
+
 \paragraph{Conclusions.}

### 2022-12-29 ms/ms.tex
edit intro

@@
 Here, we propose an additional transmission bias that may be common in cultural transmission: ``influence bias'', in which the choice of a role-model depends on the number of individuals that have already copied from that role-model.
-We combine success and influence bias together to form a ``prestige bias'', and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
-We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduces the computational complexity of simulations.
-We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
+We combine success and influence bias together to a ``prestige bias'', and analyze its effects on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
+We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduce the computational complexity of simulations.
+We validate these approximations and demonstrate their robustness to model assumptions.
 We also find approximations to the fixation probability and the fixation time of an invading cultural trait, in both constant and changing environments. 
@@
 These similarities show that success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
-
-Influence bias also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
-Our model extends the literature that attempt to describe of cultural transmission, 
+Influence bias also accelerates the evolutionary dynamics, as can be expected in a \emph{rich-getting-richer} process.
+Our model extends the literature that describes and analyses cultural transmission, 
 especially in human societies where social media is popular and thus influence bias may be expected. 
-Further work is needed to test if this model could predict various phenomena in cultural evolution.
+Further work is needed to test if this model could explain and predict various phenomena in cultural evolution.
 \end{abstract}
@@
 
-\paragraph{Cultural transmission.}
-In cultural transmission, individuals transmit cultural traits (i.e., behavior, beliefs, norms) to one another, typically via learning and demonstrating \citep{transmissionVectorsBook}.
-Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations \citep{cultural_traits}.
-
-Although cultural transmission is most common in humans, it is also observed in other animals, e.g., chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper}.
-
-Cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults (teachers, leaders, strangers) transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another.
-Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.
-It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{Ram2018}.
-
-Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.
-
-Cultural transmission biases may cause a trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
-Importantly, even when a trait is disfavored by natural selection, it may still spread in a population due to transmission biases that are strong enough to overcome selection \citep[Ch.
-8 pg.
-279]{evolutionBook}.
+%\paragraph{Cultural transmission.}
+In cultural transmission, individuals transmit cultural traits (i.e., behaviors, beliefs, norms) to one another, typically by learning and demonstrating \citep{transmissionVectorsBook}.
+Examples for cultural traits in humans are norms, preferences, tools, ideas, and language, potentially transmitted verbally and/or by observations \citep{transmissionVectors}. 
+Although cultural transmission is common in humans, it is also observed in other animals, e.g.
+chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper} and fish \citep{Truskanov2020}.
+
+Cultural transmission may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, strangers) transmit traits to unrelated offspring; and horizontal transmission, in which peers from the same age cohort transmit to one another \citep{transmissionVectorsBook,transmissionVectors}.
+It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{changeEnv}.
+
+Transmission biases may cause a cultural trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
+Importantly, even when a trait is disfavored by natural selection, it may still spread in a population due to transmission biases that are strong enough to overcome selection \citep[Ch.~8, pg.~279]{evolutionBook}.
 For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
@@
 % TODO add definition of success bias and some reference to a study demonstrating it in humans or other animals.
-Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself is not enough, even if success is measured accurately.
-
-\citet[Ch. 5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
-A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \textit{directly} testing the trait.
-For example, an individual observing a ping-pong match can attempt both of the observed paddle grips to determine which grip is better.
+Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough, % TODO enough for what?
+even if success is measured accurately.
+
+\citet[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
+A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
+For example, an individual observing a ping-pong match can attempt the observed paddle grips to determine which grip is better.
 An indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
 For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
+This, however, may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
 A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
-For example, when the common paddle grip is used by 60\% of the demonstrators, then if the probability to copy this grip is 80\%, then transmission is under positive frequency bias, also called conformity; if the probability is 40\%, then transmission is under negative frequency bias, or non-conformity \citep{conformism}.
-The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{conformity,anticonformity} and experiments \citep{negativeFrequency}.
-
-\paragraph{Prestige.}
-Prestige means having a good reputation or high esteem, therefore does not directly signify success, although it may imply it--making it an indirect bias.
+For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{non-conformity} \citep{conformism}.
+The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
+
+%\paragraph{Prestige.}
+Prestige is defined as the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
+Therefore, prestige does not directly signify success, although it may imply it--making it an indirect bias.
 \citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
@@
 On the other hand, \citet{fijian_social_bias} suggest that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
-Prestige is often mentioned in the cultural-evolution literature, but seldom modeled.
-
-\paragraph{Influence bias.}
+Prestige is often mentioned in the cultural evolution literature, but seldom modeled.
+
+%\paragraph{Influence bias.}
 Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making.
@@
 All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
-In addition, we assume homogeneous $\alpha$, also called \textit{exchangability}, for simplicity and for easier mathematical analysis.
+In addition, we assume homogeneous $\alpha$, also called \emph{exchangability}, for simplicity and for easier mathematical analysis.
 Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
@@
 \begin{result}[P{\'{o}}lya urn model]\label{result:polya}
-The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \textit{P\'{o}lya urn model} if both trait estimation error and bias weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
+The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \emph{P\'{o}lya urn model} if both trait estimation error and bias weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
 \end{result}
@@
 
-\citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
+\citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
 We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
@@
 \begin{corollary}\label{cor:dirichlet}
-The number of copiers of each role-model follows a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \textit{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
+The number of copiers of each role-model follows a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \emph{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
 \end{corollary}
@@
 \begin{equation}
-\alpha^* = \textit{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2 \;,
+\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2 \;,
 \end{equation}
@@
 A common bias is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
-However, it has been suggested that because it is hard to estimate success, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{fijian_social_bias}.
+However, it has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{fijian_social_bias}.
 
@@
 \citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
-In some species, like the females of \textit{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}. 
+In some species, like the females of \emph{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}. 
 In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. 
@@
 Their definition of prestige seems to overlap with ours.
-They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers other people think one has, which they define as \textit{influence}, similar to our influence bias.
+They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers other people think one has, which they define as \emph{influence}, similar to our influence bias.
 \citet{prestige_evolution} show that prestige can evolve via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
@@
 Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
-\citet{harmful_traditions} suggest a \textit{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
-They found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions.
+\citet{harmful_traditions} suggest a \emph{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
+They found that there are individuals who act as \emph{agents}, who are often looked upon, and therefore they are ideal targets for interventions.
 This is similar to influential role-models in our model, where a prestigious individual will be copied more often, and will therefore spread his trait faster and wider in the population.
@@
 Following up on this, \citet{collective_brains} offered that prestige can directly affect human physical evolution.
-They present a concept called \textit{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
+They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
 They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. 
-They also presented the \textit{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
+They also presented the \emph{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
 As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge.

### 2022-12-29 ms/ms.tex
finish to edit intro

@@
 Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
-Influence can be easily estimated, so costs may be lower than estimating success. In some cases it could be a more accurate estimation as well.
-
-Influence bias is a context-based, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model.
-IT also differs from frequency biases such as conformity \citep{conformity}, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.
-
-Here, we define a model of cultural transmission with prestige bias that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics.
-We find approximations for the probability and time for fixation of a "successful" phenotype (i.e., that is favored by success bias).
+Importantly, influence may be easier and more accurate to estimate compared to success.
+
+Influence bias is a context-based bias, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model.
+It also differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.
+
+Here, we define a stochastic model of cultural transmission with prestige bias that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics.
+We find approximations for the probability and time for fixation of a `successful' phenotype (i.e., that is favored by success bias).
 Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.

### 2023-01-02 ms/ms.tex
addressed TODOs

@@
 
-% TODO add definition of success bias and some reference to a study demonstrating it in humans or other animals.
-Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough, % TODO enough for what?
-even if success is measured accurately.
+A very common bias in the literature is \textit{success bias}.
+Success bias refers to the tendency for certain cultural traits or behaviors to spread and become more common in a population simply because they have been successful in the past.
+Success in that regard is defined by each individual trait, for example, a successful manifestation is a ping pong-player who won many games, tournaments, didn't lose much, etc..
+\citet{prestige_cultural_learning} describe a definition for success, as well as skill and prestige bias, and their differences.
+Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
 

### 2023-01-03 ms/ms.tex
revised success-bias and influence-bias paragraphs in introduction; some formatting

@@
 
-A very common bias in the literature is \textit{success bias}.
-Success bias refers to the tendency for certain cultural traits or behaviors to spread and become more common in a population simply because they have been successful in the past.
-Success in that regard is defined by each individual trait, for example, a successful manifestation is a ping pong-player who won many games, tournaments, didn't lose much, etc..
-\citet{prestige_cultural_learning} describe a definition for success, as well as skill and prestige bias, and their differences.
+A common bias in the literature is \textit{success bias}, in which individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, and using medicinal plants \citep{fijian_social_bias}, and hunting \citep{Mesoudi2008}, and it can increase the probability of learning a successful trait or strategy \citep{Borofsky2022}.
 Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
@@
 Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
-Importantly, influence may be easier and more accurate to estimate compared to success.
-
-Influence bias is a context-based bias, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model.
-It also differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.
+Such a bias has been demonstrated by \citet{prestige_cultural_learning} in 3-4 year old children.
+
+Influence bias is a context-based bias, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model, which may be easier and more accurate to estimate compared to success.
+Influence bias differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.
 
@@
 \begin{equation}\label{eq:success_bias}
-\beta(A_{i,j}) = b \cdot \exp{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)},
+\beta(A_{i,j}) = b \cdot \exp{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)} \;,
 \end{equation} 
@@
 \begin{equation}\label{eq:binary-model}
-G_{i,A} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + C\alpha'\beta(\hat{A})} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + \alpha'C}
+G_{i,A} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + C\alpha'\beta(\hat{A})} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + \alpha'C} \;,
 \end{equation}
 where $C$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.
-
 We prove this equation later, based on the proof of the Dirichlet-Multinomial approximation.
@@
 \begin{equation}\label{recursive}
-Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1),
+Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1) \;,
 \end{equation}
@@
 This result gives the following two corollaries on the expected number of followers of a given role-model by the end of the role-model choice process.
-The proof of \cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
+The proof of \Cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
 \\
 
-\begin{corollary}
-$\E[K_{N,j}] = N \cdot G_{1,j}$.
+\begin{corollary} The expected number of copiers of role-model $j$ after all copiers have chosen a role-model is
+$\E[K_{N,j}] = N \cdot G_{1,j}$, where $G_{1,j}$ is the probability of the first copier to copy role-model $j$.
 \end{corollary}
@@
 \begin{corollary}\label{cor:GBD}
-$\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
+$\E[K_{N, j}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
 \end{corollary}
@@
 \end{equation}
-where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution we draw the trait values from, modified by some constant parameters of $\beta$.
+where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution of the trait values, modified by some constant parameters of $\beta$.
 We can then denote $L = 1/\overline{\beta(A+e)}$ and write
@@
 \paragraph{Numerical validation.}
-To validate our results we ran $1,000$ simulations of the full model, and compared the results with \cref{cor:GBD}.
-We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \cref{cor:GBD}.
-We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \cref{fig:GBD}.
+To validate our results we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
+We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \Cref{cor:GBD}.
+We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \Cref{fig:GBD}.
 
@@
 
-Although basic, \cref{fig:GBD} shows good fit of the GB approximation.
+Although basic, \Cref{fig:GBD} shows good fit of the GB approximation.
 This validation is initial, and the more extensive validations we do on the Dirichlet-Multinomial approximation, because it is what we will use in our analysts.
@@
 \paragraph{Numerical validation.}
-To validate our analytical result (\cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
+To validate our analytical result (\Cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
 First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then compared this observed distribution with the expected theoretical DM distribution as can be seen in \cref{fig:DM_validation} (a).
+We then compared this observed distribution with the expected theoretical DM distribution as can be seen in \Cref{fig:DM_validation} (a).
 The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
 The maximum difference is 0.5 role-models, which indicate a very good fit.
-In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself, as seen in \cref{fig:DM_validation} (b).
+In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself, as seen in \Cref{fig:DM_validation} (b).
 We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, supporting our approximation more.
@@
 When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
-Even when the standard deviation is $0.1$, the fixation probability and time is similar~(\cref{fig:hetro_error}). 
+Even when the standard deviation is $0.1$, the fixation probability and time is similar~(\Cref{fig:hetro_error}). 
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
 We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,q)$ where $q \in [10^{-7},10^{-1}]$.
-We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\cref{fig:hetro_alpha}).
+We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).
 
@@
 For simplicity, we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
-As shown above, transmission in our model is approximately DM distributed (\cref{cor:dirichlet} and \cref{eq:copier_choose}).
+As shown above, transmission in our model is approximately DM distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
 
@@
 
-\begin{result}[Fixation time]
+\begin{result}[Fixation time] The fixation time (conditioned on fixation) is approximately
 \begin{equation}

### 2023-01-04 ms/ms.tex
revise introduction for better definitions of succes prestige influence and motivation for these definitions

@@
 
-Cultural transmission may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, strangers) transmit traits to unrelated offspring; and horizontal transmission, in which peers from the same age cohort transmit to one another \citep{transmissionVectorsBook,transmissionVectors}.
+Cultural transmission may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, and even strangers) transmit to unrelated offspring; and horizontal transmission, in which peers from the same age cohort transmit to one another \citep{transmissionVectorsBook,transmissionVectors}.
 It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{changeEnv}.
@@
 Transmission biases may cause a cultural trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
-Importantly, even when a trait is disfavored by natural selection, it may still spread in a population due to transmission biases that are strong enough to overcome selection \citep[Ch.~8, pg.~279]{evolutionBook}.
-For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
-
-A common bias in the literature is \textit{success bias}, in which individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, and using medicinal plants \citep{fijian_social_bias}, and hunting \citep{Mesoudi2008}, and it can increase the probability of learning a successful trait or strategy \citep{Borofsky2022}.
+A common bias in the literature is \textit{success bias}, in which individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, and using medicinal plants \citep{fijian_social_bias}, and hunting \citep{Mesoudi2008}, and it can increase the probability of learning a successful trait \citep{Borofsky2022}.
 Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
@@
 For example, an individual observing a ping-pong match can attempt the observed paddle grips to determine which grip is better.
+A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
+For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{non-conformity} \citep{conformism}.
+The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
 An indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
@@
 This, however, may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
-A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
-For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{non-conformity} \citep{conformism}.
-The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
-
-%\paragraph{Prestige.}
-Prestige is defined as the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
-Therefore, prestige does not directly signify success, although it may imply it--making it an indirect bias.
-\citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
-\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population if indirect biases are strong enough.
-They suggest that such biases could lead to a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
-On the other hand, \citet{fijian_social_bias} suggest that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
-Prestige is often mentioned in the cultural evolution literature, but seldom modeled.
-
-%\paragraph{Influence bias.}
-Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making.
+Furthermore, \citet[Ch.
+8]{evolutionBook} have suggested that maladaptive traits may spread widely in a population if indirect biases are strong enough by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
+For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
+
+\citet{fijian_social_bias} have studied such indirect biases, which they call cross-domain success bias, or in short, \emph{prestige} (e.g.
+great fishermen may be chosen as role-models for growing yams).
+They have suggested that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
+\citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} have suggested that prestige biases are probably more common in humans than success biases, and prestige is often mentioned in the cultural evolution literature, however there are few models of prestige bias.
+
+A broader definition of prestige is the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
+Indeed, \citet{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
+To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
+This is an important distinction, as influence is a context-based bias, rather than a content-based bias: it does not depend on the phenotype itself but rather on the number of copiers that already copied each role-model, which may be easier and more accurate to estimate compared to success.
+Influence bias differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+We model influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model.
+
+In contemporary human society, social media makes it especially easy to estimate the social and cultural influence individuals have over others, and therefore can have an effect on decision making.
 Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
-Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
-Such a bias has been demonstrated by \citet{prestige_cultural_learning} in 3-4 year old children.
-
-Influence bias is a context-based bias, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model, which may be easier and more accurate to estimate compared to success.
-Influence bias differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.
-
-Here, we define a stochastic model of cultural transmission with prestige bias that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics.
+
+In the following, we develop a stochastic model of cultural transmission with that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics.
 We find approximations for the probability and time for fixation of a `successful' phenotype (i.e., that is favored by success bias).
@@
 \paragraph{Conclusions.}
-Here, we presented support for the existence of prestige biases in cultural transmission, including the commonly studied success bias.
-We introduced an influence bias, which has so far received less attention.
-We believe the combination of these biases may be a strong driving force in cultural evolution.
-We show that the relative effect of the two biases changes the effective population size such that the increasing the weight individuals give to influence bias, decreases the effective population size.
+Here, we studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with influence bias, which has so far received less attention.
+We found approximations for this complex dynamics.
+We then showed that success bias affects the evolutionary dynamics much like natural selection does, whereas influence bias has a similar effect to random genetic drift.
 We also find a clear advantage to individuals that can choose the relative weight of the two biases.

### 2023-01-04 ms/ms.tex
revise some of results, left todos for things unresolved

@@
 % Title page
-\title{Cultural evolutionary dynamics with prestige bias}
+\title{Cultural evolutionary dynamics with success and influence bias}
 % Authors
@@
 \end{equation}
-The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased trait value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citet{evolutionBook} with
+The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and influence--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citet{evolutionBook} with
 \begin{equation}\label{eq:prestige}
@@
 
-Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of success and influence in the role-model's overall prestige in the eyes of the copier.
-
-We assume every individual evaluates the importance of success and influence differently.
-Additionally, we assume every role-model displays his influence and success individually, for example - a person with more followers but lack of actual skill may emphasize the number of his followers rather than his actual skill.
-We therefore modeled $\alpha_{ij}$ to be the relation between every copiers intrinsic significance of estimation, and every role-models personal emphasis.
+Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs.
+influence in the role-model's overall prestige in the eyes of the copier.
+
+We assume every individual may evaluate the importance of success and influence differently.
+Additionally, we assume every role-model displays his influence and success individually.
+For example, a person with more followers but lack of actual skill may emphasize the number of his followers rather than his actual skill.
+We therefore defined $\alpha_{i,j}$ to be the relation between every copier's intrinsic significance of estimation, and every role-model's personal emphasis.
 
@@
 All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
-In addition, we assume homogeneous $\alpha$, also called \emph{exchangability}, for simplicity and for easier mathematical analysis.
+In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous, such that we have exchangeability between role-models.
 Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
@@
 \end{equation}
-where $C$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.
-We prove this equation later, based on the proof of the Dirichlet-Multinomial approximation.
-
-Initially, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. The rest of the details follow the continuous trait model.
+where $C$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model.
+$\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.
+We prove this equation later, based on the proof of the Dirichlet-Multinomial approximation. % TODO what do you mean "we prove this later"..?
+The rest of the details follow the continuous trait model.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Dirichlet-Multinomial distribution approximation}
@@
 Next, we examined the fixation probability and fixation time of a favored phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
+Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
 We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
-Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions.
+We examined the robustness of the DM approximation to relaxing the approximation assumptions.
 First, we relaxed our assumption of no estimation error $e$.
@@
 After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
-We focus on the fixation probability and conditioned fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
+We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
 We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
@@
 After finding a good approximation in constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a changing environment.
-Following \citet{changeEnv}, we find the following expressions for the expectation and variance of the change in frequency between $t$ generations. 
+Following \citet{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
+We then proceed to find expressions for the expectation and variance of the change in frequency between $n=k+l$ generations. 
 The proof is in Appendix~\ref{sec:drift_diff_chang}.
@@
 \begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
-Let $x$ be the initial frequency of the invading phenotype and $X_t$ is the number of individuals with the phenotype at time $t$.
+Let $x$ be the initial frequency of the invading phenotype and $X_t$ is the number of individuals with the phenotype after $n$ generation.
 Then,
 \begin{equation}\label{eq:ch_expected_and_var}
-E[X_t/N - x] \simeq x(1-x) S_t / N_e \;, 
+E[X_n/N - x] \simeq x(1-x) S_n / N_e \;, 
 \quad
@@
 \quad
-V(X_t/N-x) \simeq  t x(1-x) / N_e \;,
-\end{equation}
-where $S_t=\sum\limits_{i=1}^{t} N (1-\beta_t)$.
+V(X_n/N-x) \simeq  n x(1-x) / N_e \;,
+\end{equation}
+where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$.
 \end{result}
 
+Note that here, we have the average selection coefficient during a cycle of $n$ generations as the selection coefficient \cref{eq:kimura_p}.
 Using the drift and diffusion terms and following \citet{changeEnv}, we can approximate the fixation probability in a changing environment using
 \begin{equation}\label{eq:ch_env}
-\tilde\pi = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
-\end{equation}
-where $\frac{S_n}{n} = \frac{k-l}{k+l}(1-\beta)$ and $n=k+l$.
-That is, we use the average selection coefficient during a cycle of $k+l$ generations as the selection coefficient \cref{eq:kimura_p}.
+\tilde\pi = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}} \;.
+\end{equation}
 
 \paragraph{Numerical validation.}
-Comparing our approximation, \cref{eq:ch_env} to numerical simulations, we find that the approximation fits simulations results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
+Comparing our approximation (\cref{eq:ch_env}) to simulations, we find that the approximation fits simulation results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
 
@@
 We suspect that when $\beta$ is too small, there will not be many cycles in the simulations, because either the population reaches a high frequency of the fitter phenotype after just a few cycles, or the fitter phenotype becomes extinct very quickly.
-For the $\beta$ values (0.65 and below), the fixation probability exceeds even the constant environment approximation (which is the upper limit).
-However, this is to be expected, because the diffusion-equation approximations assume weak selection (i.e., low selection coefficient $s$).
-
-When $k$ is the number of generations where the invading phenotype is favored, and $l$ when the original trait is, we found that for large $k$-to-$l$ ratio (while keeping constant total cycle length, $n=k+l=100$), the changing environment approximation, \cref{eq:ch_env} converges to the constant environment approximation, \cref{eq:kimura_p}, see \Cref{fig:ch_env_alpha_beta}C and \Cref{fig:ch_env_alpha_beta}D.
-
+For such $\beta$ values (below 0.65), the fixation probability exceeds even the constant environment approximation (which is the upper limit).
+We note that the diffusion-equation approximation assumes weak selection, or in our case, weak success bias.
+
+We found that for a large $k/l$ ratio (with a constant cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}), see \Cref{fig:ch_env_alpha_beta}C and \Cref{fig:ch_env_alpha_beta}D.
+\\
+
+% TODO the next paragraph is strange...
 \begin{result}
@@
 \begin{equation}
-\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2 \;,
+\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l} (\hat{A}-A_j)^2 \;,
 \end{equation}

### 2023-01-05 ms/ms.tex
revise with SE

@@
 % Title page
-\title{Cultural evolutionary dynamics with success and influence bias}
+\title{Prestige bias in cultural evolutionary dynamics}
 % Authors
@@
 
+% TODO edit so that we focus on indirect success - aka prestige - and decompose it to content based - which we call success - and context based - which we call influence
 \citet[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
@@
 \begin{equation}\label{eq:binary-model}
-G_{i,A} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + C\alpha'\beta(\hat{A})} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + \alpha'C} \;,
-\end{equation}
-where $C$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model.
-$\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.
-We prove this equation later, based on the proof of the Dirichlet-Multinomial approximation. % TODO what do you mean "we prove this later"..?
+G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
+\end{equation}
+where $X$ is the number of role-models with trait $\hat{A}$, $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, $\beta(\hat{A})=1$, and $\alpha'= \frac{\alpha}{1-\alpha}$ is the odd ratio of the bias weight.
+Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
 The rest of the details follow the continuous trait model.
@@
 \begin{equation}\label{eq:kimura_p}
-\pi = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
+\pi(x) = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
 \end{equation}
@@
 
-\begin{result}[Fixation time] The fixation time (conditioned on fixation) is approximately
-\begin{equation}
-T = J_1 + \frac{1-u(x)}{u(x)}\cdot J_2,
-\end{equation}
-where, given $S=N_e(1-\beta)$ and $x=\frac{1}{N_e}$,
-\begin{equation}
-u(x)=\frac{1-e^{-2Sx}}{1-e^{2S}}
-\end{equation}
-and,
-\begin{equation}
-J_1 = \frac{2}{(1-\beta)(1-e^{-2S})}\int_x^1 \frac{(e^{2S\xi}-1)(e^{-2S\xi}-e^{-2S})}{\xi(1-\xi)}d\xi,
-\end{equation}
-\begin{equation}
-J_2= \frac{2}{(1-\beta)(1-e^{-2S})}\int_0^p \frac{(e^{2S\xi}-1)(1-e^{-2S\xi})}{\xi(1-\xi)}d\xi
-\end{equation}
-
-\begin{equation}\label{eq:kimura_t}
-T = \frac{1-\pi}{1-\beta}\int_0^x\frac{e^{2(1-\beta) \xi}-1}{\xi(1-\xi)}d\xi+ \frac{\pi}{1-\beta}\int_x^1\frac{1-e^{-2(1-\beta)(1-\xi)}}{\xi(1-\xi)}d\xi
+% TODO SAAR check these equations vs what you have in the source code
+\begin{result}[Fixation time] The fixation time (conditioned on fixation) from an initial frequency $x$ is approximately
+\begin{equation} \label{eq:kimura_t}
+T(x) = J_1(x) + \frac{1-\pi(x)}{\pi(x)}\cdot J_2(x),
+\end{equation}
+where $N_e=\alpha N + (1-\alpha)$, $S=N_e(1-\beta)$, and
+\begin{equation}
+\begin{aligned}
+J_1(x) &= \frac{2}{(1-\beta)(1-e^{-2S})}\int_x^1 \frac{(e^{2S\xi}-1)(e^{-2S\xi}-e^{-2S})}{\xi(1-\xi)}d\xi \;, \\
+J_2 (x) &= \frac{2}{(1-\beta)(1-e^{-2S})}\int_0^x \frac{(e^{2S\xi}-1)(1-e^{-2S\xi})}{\xi(1-\xi)}d\xi \;.
+\end{aligned}
 \end{equation}
@@
 \paragraph{Numerical validation.}
-We compare our approximations (\cref{eq:kimura_p,eq:kimura_t}) with results of simulations of our dichotomous model using various $\alpha$ and $\beta$ values, as well as simulations of the Wright-Fisher model, using the effective selection coefficient, $s_e=1-\beta$, and effective population size, $N_e=\alpha N + (1-\alpha)$.
+We compare our approximations (\cref{eq:kimura_p,eq:kimura_t}) with results of simulations of our dichotomous model using various $\alpha$ and $\beta$ values, as well as simulations of the Wright-Fisher model, using the effective selection coefficient, $1-\beta$, and effective population size, $N_e=\alpha N + (1-\alpha)$.
 We find see that the two models have similar dynamics, and both are well approximated our approximations (\Cref{fig:var_alpha}).
@@
   The approximation (black; \cref{eq:kimura_p}) agrees with both DM simulations (green) and Wright-Fisher simulation (orange).
-  Fixation probability (A) is bounded by $2s_e=2(1-\beta)$ (blue).
+  Fixation probability (A) is bounded by $2(1-\beta)$ (blue).
   Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
@@
 \begin{equation}\label{eq:ch_env}
-\tilde\pi = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}} \;.
+\tilde\pi(x) = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}} \;.
 \end{equation}
@@
 \paragraph{Numerical validation.}
+% TODO SAAR edit this section
 Comparing our approximation (\cref{eq:ch_env}) to simulations, we find that the approximation fits simulation results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
@@
 We found that for a large $k/l$ ratio (with a constant cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}), see \Cref{fig:ch_env_alpha_beta}C and \Cref{fig:ch_env_alpha_beta}D.
-\\
-
-% TODO the next paragraph is strange...
-\begin{result}
-The effective population size doesn't affect the goodness of fit of the approximation. The success coefficient however, must be even lower than before for the approximation to fit.
-\end{result}
-The proof is seen in \Cref{fig:ch_env_alpha_beta}A,B. The approximation follows the trend of the simulation results for all $\alpha$ values.
+
+The approximation follows the trend of the simulation results for all $\alpha$ values.
 When increasing the success coefficient to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+% TODO Edit to follow our latest definition of prestige etc in the introduction
 \section*{Discussion}

### 2023-01-05 ms/ms.tex
revise abstract and last intro par

@@
 \begin{abstract}
-A common bias in cultural transmission is to copy whoever appears more successful. This ``success bias'' only depends on the performance of the role-model.
-Here, we propose an additional transmission bias that may be common in cultural transmission: ``influence bias'', in which the choice of a role-model depends on the number of individuals that have already copied from that role-model.
-We combine success and influence bias together to a ``prestige bias'', and analyze its effects on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
+A common bias in cultural transmission is to copy whoever appears more successful. This success bias only depends on the performance of the role-model.
+Because success may be difficult to estimate, it has been suggested that individuals may indirectly estimate success by using prestige as a proxy for success.
+However, prestige can be defined in different ways: it can reflect performance in another, possibly related, task; but it can also reflect overall influence of the role-model, irrespective of performance.
+Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied from that role-model.
+We analyze the effect of prestige on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
 We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduce the computational complexity of simulations.
@@
 These approximations are similar to Kimura's approximations for population-genetic models.
-These similarities show that success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
+These similarities show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
 Influence bias also accelerates the evolutionary dynamics, as can be expected in a \emph{rich-getting-richer} process.
@@
 Transmission biases may cause a cultural trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
-A common bias in the literature is \textit{success bias}, in which individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, and using medicinal plants \citep{fijian_social_bias}, and hunting \citep{Mesoudi2008}, and it can increase the probability of learning a successful trait \citep{Borofsky2022}.
+\textit{Success bias} occurs when individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, using medicinal plants \citep{fijian_social_bias}, or hunting \citep{Mesoudi2008}, and it can increase the probability of learning a successful trait \citep{Borofsky2022}.
 Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
@@
 % TODO edit so that we focus on indirect success - aka prestige - and decompose it to content based - which we call success - and context based - which we call influence
-\citet[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
+\citet[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
 A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
@@
 
-\citet{fijian_social_bias} have studied such indirect biases, which they call cross-domain success bias, or in short, \emph{prestige} (e.g.
-great fishermen may be chosen as role-models for growing yams).
-They have suggested that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
+\citet{fijian_social_bias} have studied such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
+They have suggested that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
 \citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} have suggested that prestige biases are probably more common in humans than success biases, and prestige is often mentioned in the cultural evolution literature, however there are few models of prestige bias.
@@
 Influence bias differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
-We model influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model.
 
@@
 
-In the following, we develop a stochastic model of cultural transmission with that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics.
+In the following, we develop a stochastic model of cultural transmission with prestige bias. In our model, prestige combines both cross-domain indirect success bias and influence bias.
+We develop analytic approximations for this model and analyze its dynamics.
 We find approximations for the probability and time for fixation of a `successful' phenotype (i.e., that is favored by success bias).

### 2023-01-07 ms/ms.tex
edited discussion

@@
 However, it has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{fijian_social_bias}.
-
-Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias that includes both success and influence biases, where the latter is a bias towards role-models with many copiers.
+This perceived success can be by a manifestation of another trait, i.e indirect success, which we refer to as success in this research.
+Prestige can also be identified as the influence an individual has on others.
+
+Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
 This is accomplished by a role-model choice process: each copier, in its turn, chooses a role-model, and that choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-mode (eq.~\ref{eq:prestige}).

### 2023-01-09 ms/ms.tex
update
minor edits

@@
 Indeed, \citet{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
+\citet{prestige_evolution} give a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provide examples from the anthropological literature.
+
 To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
 This is an important distinction, as influence is a context-based bias, rather than a content-based bias: it does not depend on the phenotype itself but rather on the number of copiers that already copied each role-model, which may be easier and more accurate to estimate compared to success.
-Influence bias differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+Influence bias also differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TODO Edit to follow our latest definition of prestige etc in the introduction
 \section*{Discussion}
@@
 A common bias is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
-However, it has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{fijian_social_bias}.
-This perceived success can be by a manifestation of another trait, i.e indirect success, which we refer to as success in this research.
-Prestige can also be identified as the influence an individual has on others.
+However, it has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
+This perceived success can be determined by performance in another trait, i.e., by indirect success \citet{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citet{prestige_cultural_learning,prestige_evolution}.
 
 Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
-This is accomplished by a role-model choice process: each copier, in its turn, chooses a role-model, and that choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-mode (eq.~\ref{eq:prestige}).
-
-This resulted in a model with two "nested" stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
+We model the these biases using a stochastic role-model choice process: each copier, in its turn, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
+
+Hence, we have a model with two "nested" stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
 To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DM, \Cref{cor:dirichlet}).
@@
 \section*{Acknowledgements}
-We thank Marcus Feldman, Martin Pontz, and Tal Simon for discussions and comments.
+We thank Marcus Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, and Tal Simon for discussions and comments.
 This work was supported in part by 
-the Israel Science Foundation (YR 552/19),
 Minerva Stiftung Center for Lab Evolution (YR),

### 2023-01-22 ms/ms.tex
final revisions

@@
 }
-
 % NatBib
-%\usepackage[super,comma]{natbib}
-\usepackage[round,colon,authoryear]{natbib}
-%\use-package[numbers,super,sort&compress]{natbib}
+\usepackage[numbers,square,comma,sort]{natbib}
 \renewcommand{\bibsection}{}
@@
 Furthermore, \citet[Ch.
-8]{evolutionBook} have suggested that maladaptive traits may spread widely in a population if indirect biases are strong enough by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
-For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
+8]{evolutionBook} have suggested that maladaptive traits may spread widely in a population if indirect biases are strong enough, e.g., by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
+Indeed, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
 
@@
 Indeed, \citet{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
-\citet{prestige_evolution} give a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provide examples from the anthropological literature.
+\citet{prestige_evolution} gave a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature.
 
@@
 We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \Cref{fig:GBD}.
-
-\begin{figure}[h]
-    \includegraphics[width=0.7\linewidth]{../figures/final/GBD_validation.pdf}
-  \caption{
-  \textbf{Numerical validation of the GB approximation.}
-  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
-  Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; idea phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
-  \label{fig:GBD}
-\end{figure}
 
@@
 First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then compared this observed distribution with the expected theoretical DM distribution as can be seen in \Cref{fig:DM_validation} (a).
+We then compared this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A).
 The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
 The maximum difference is 0.5 role-models, which indicate a very good fit.
-In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself, as seen in \Cref{fig:DM_validation} (b).
+In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself (\Cref{fig:DM_validation}B).
 We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, supporting our approximation more.
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/final/DM_validation.pdf}
-  \caption{
-  \textbf{Numerical validation of the DM approximation.}
-  We performed computational "experiments" of the role-model choice process and compared them to the DM distribution. 
-  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the experiments (blue) is very small. 
-  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (red vertical line) is much higher compared to the log-likelihood of permutations of experiments (blue histogram).
-  Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
-  No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
-  \label{fig:DM_validation}
-\end{figure}
 
@@
 
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/final/num_sims.pdf}
-  \caption{
-  \textbf{DM Approximation precision as function of number of simulations.}
-  Our DM approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
-  Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
-  Markers are averages across simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success-bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success-bias value, $\beta(A)=0.956$.}	
-  \label{fig:num_sims}
-\end{figure}
-
 \begin{figure}
@@
   Markers are averages across simulations, error bars are 95\% confidence intervals.
-  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,\eta^2)$ where $\eta \in [10^{-7},10^{-1}]$.
+  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,\eta^2)$ where $\eta^2$ in on the x-axis.
   }	
@@
 However, it has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
-This perceived success can be determined by performance in another trait, i.e., by indirect success \citet{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citet{prestige_cultural_learning,prestige_evolution}.
-
-Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
+This perceived success can be determined by performance in another trait, i.e., by indirect success \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.
+
+We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
 We model the these biases using a stochastic role-model choice process: each copier, in its turn, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
@@
 To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DM, \Cref{cor:dirichlet}).
-The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and influence is a characteristic of the role-model, rather than the copier.
+The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and influence is a characteristic of the role-model and not the copier.
 
@@
 This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers, and the less it should rely on its own estimation.
-The rationale, then, is that the more information a copier has, e.g. by using others as information sources, the more informative and effective his choice can be.
+The rationale, then, is that the more information a copier has, e.g., by using others as information sources, the more informative and effective his choice can be.
 
@@
 
-So far we examined different variations of our model using a Wright-Fisher model as our basis, mainly because we wanted to base our model on a known one from the literature, namely \citet{evolutionBook} indirect bias model.
-When approximating our model by comparing it to a Polya Urn process, we noticed that our model would be identical to a model where every copier that chose a role-model would copy its trait and join the role-models during the selection process.
-Based on this, we theorize that when using a Moran model as basis instead of a Wright-Fisher mode, we would get very similar, and perhaps identical results.
-It would be interesting to run simulations and analyze that model, to prove or disprove our hypothesis.
-
 \paragraph{Conclusions.}
@@
 \section*{Acknowledgements}
-We thank Marcus Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, and Tal Simon for discussions and comments.
+We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, and Tal Simon for discussions and comments.
 This work was supported in part by 
-Minerva Stiftung Center for Lab Evolution (YR),
-and 
-the John Templeton Foundation (YR 61809).
+Minerva Stiftung Center for Lab Evolution (YR) and  the John Templeton Foundation (YR 61809).
 }
@@
 %\bibliographystyle{agsm}
-\bibliographystyle{apalike}
+%\bibliographystyle{apalike}
+\bibliographystyle{unsrtnat}
 
@@
 
+\newpage
+\section*{Supplementary Figures}
+\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
+
+\begin{figure}[h]
+    \includegraphics[width=0.7\linewidth]{../figures/final/GBD_validation.pdf}
+  \caption{
+  \textbf{Numerical validation of the GB approximation.}
+  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
+  Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; idea phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
+  \label{fig:GBD}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/final/DM_validation.pdf}
+  \caption{
+  \textbf{Numerical validation of the DM approximation.}
+  We performed computational "experiments" of the role-model choice process and compared them to the DM distribution. 
+  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the experiments (blue) is very small. 
+  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (red vertical line) is much higher compared to the log-likelihood of permutations of experiments (blue histogram).
+  Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
+  No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
+  \label{fig:DM_validation}
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{../figures/final/num_sims.pdf}
+  \caption{
+  \textbf{DM Approximation precision as function of number of simulations.}
+  Our DM approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
+  Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
+  Markers are averages across simulations, error bars are 95\% confidence intervals.
+  Here, population size, $N=1000$; success-bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success-bias value, $\beta(A)=0.956$.}	
+  \label{fig:num_sims}
+\end{figure}
+
 \end{document}

### 2023-02-06 ms/ms.tex
reduce words to 9.5k

@@
 Because success may be difficult to estimate, it has been suggested that individuals may indirectly estimate success by using prestige as a proxy for success.
-However, prestige can be defined in different ways: it can reflect performance in another, possibly related, task; but it can also reflect overall influence of the role-model, irrespective of performance.
 Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied from that role-model.
@@
 We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduce the computational complexity of simulations.
-We validate these approximations and demonstrate their robustness to model assumptions.
-We also find approximations to the fixation probability and the fixation time of an invading cultural trait, in both constant and changing environments. 
-These approximations are similar to Kimura's approximations for population-genetic models.
-These similarities show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
+We also find approximations to the fixation probability and the fixation time of an invading cultural trait in different environments.
+We show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
 Influence bias also accelerates the evolutionary dynamics, as can be expected in a \emph{rich-getting-richer} process.
-Our model extends the literature that describes and analyses cultural transmission, 
-especially in human societies where social media is popular and thus influence bias may be expected. 
-Further work is needed to test if this model could explain and predict various phenomena in cultural evolution.
+Our model describes and analyses cultural transmission, especially in human societies where social media is popular.
+
 \end{abstract}
@@
 
+\iffalse
 \paragraph{Empirical evidence of prestige bias}
@@
 
+\fi
 \paragraph{Conclusions.}

### 2023-02-07 ms/ms.tex
revise abstract

@@
 \begin{abstract}
-A common bias in cultural transmission is to copy whoever appears more successful. This success bias only depends on the performance of the role-model.
-Because success may be difficult to estimate, it has been suggested that individuals may indirectly estimate success by using prestige as a proxy for success.
+A common bias in cultural transmission is success bias, where more successful individuals are more likely to be copied.
+Because success may be difficult to estimate, individuals may indirectly estimate success by using prestige as a proxy for success.
 Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied from that role-model.
@@
 We show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
-Influence bias also accelerates the evolutionary dynamics, as can be expected in a \emph{rich-getting-richer} process.
-Our model describes and analyses cultural transmission, especially in human societies where social media is popular.
-
+Influence bias also accelerates the evolutionary dynamics, as can be expected in a rich-getting-richer process.
+Our study extends the literature that describes and analyses cultural transmission,
+especially in human societies where social media is popular and thus influence bias may be expected.
 \end{abstract}

### 2023-02-07 ms/ms.tex
revised reduction of words

@@
 
-\paragraph{Prestige in the literature.}
-
-According to \citet{animal_leadership}, there are two main approaches to group decision making in nature: leadership and consensus.
-Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
-\citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
-In some species, like the females of \emph{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}. 
-In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. 
-However, wrong decision making that harms the group could result in negative effects for the leader. 
-In modern society, many humans strive for prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure or education from the family.
-
-\citet{prestige_evolution} suggested that there are two types of leadership: prestige-based and dominance-based leadership.
-In the latter, social status is acquired through aggression, intimidation and violence. It is also more common than prestige in non-human animals.
-Their definition of prestige seems to overlap with ours.
-They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers other people think one has, which they define as \emph{influence}, similar to our influence bias.
-\citet{prestige_evolution} show that prestige can evolve via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information.
-They back up their claims by creating testable predictions and using evidence from the literature and experiments of social sciences.
-Simply put, prestige can naturally evolve when social learning already exists to save costs of individual learning.
-
-Furthermore, according to \citet{no_replication}, the process of cultural evolution doesn't require accurate replication of cultural traits, addressed as "representation" in their paper.
-They base their assumption on three claims: mental representations are non-discrete, cultural transmission is highly inaccurate, and mental representations are not replicated, but rather are `reconstructed' through an inferential process that is strongly affected by cognitive `attractors.' They describe three different models to support their points.
-We see a high similarity between their model and ours.
-Like them, we treat the cultural trait as non-discrete (in the main model, before simplifying it to facilitate analysis).
-We also assume error in estimation, such that copiers do not precisely replicate their role-models, but rather reconstruct them to create a potentially different trait, which is their representation of the role-model's trait.
-In addition, the inferential process that they describe as strongly affected by cognitive attractors may include our definition of influence bias.
-
-\iffalse
-\paragraph{Empirical evidence of prestige bias}
+%\paragraph{Empirical evidence of prestige bias}
 \citet{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
@@
 
-\paragraph{Further work.}
+%\paragraph{Further work.}
 One path forward is an analysis of the dynamics of the adaptive success-bias weight model, in which every copier chooses its $\alpha$.
@@
 
-\fi
 \paragraph{Conclusions.}

### 2023-02-15 ms/ms.tex
move validation figs to SI
remove doulbe lineno declaration
update

@@
 
-% line numbers
-\usepackage[displaymath, mathlines]{lineno}
- \renewcommand\linenumberfont{\normalfont\small\sffamily}
-%%%%\linenumbers
-\modulolinenumbers[2]
-
 % Supplementary
@@
 
-\author[1]{Saar Egozi}
+\author[1,3]{Saar Egozi}
 \author[2,3,$\dagger$]{Yoav Ram}
@@
 \affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
-%\affil[*]{These authors contributed equally to this work}
 \affil[$\dagger$]{Corresponding author: yoav@yoavram.com}
@@
 \textit{Success bias} occurs when individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, using medicinal plants \citep{fijian_social_bias}, or hunting \citep{Mesoudi2008}, and it can increase the probability of learning a successful trait \citep{Borofsky2022}.
-Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
+Indeed, in a tournament between learning strategies conducted by \citep{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
 
 % TODO edit so that we focus on indirect success - aka prestige - and decompose it to content based - which we call success - and context based - which we call influence
-\citet[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
+\citep[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
 A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
@@
 This, however, may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
-Furthermore, \citet[Ch.
+Furthermore, \citep[Ch.
 8]{evolutionBook} have suggested that maladaptive traits may spread widely in a population if indirect biases are strong enough, e.g., by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
-Indeed, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
-
-\citet{fijian_social_bias} have studied such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
+Indeed, \citep{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
+
+\citep{fijian_social_bias} have studied such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
 They have suggested that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
-\citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} have suggested that prestige biases are probably more common in humans than success biases, and prestige is often mentioned in the cultural evolution literature, however there are few models of prestige bias.
+\citep[Ch.~8]{evolutionBook} and \citep{complexityPaper} have suggested that prestige biases are probably more common in humans than success biases, and prestige is often mentioned in the cultural evolution literature, however there are few models of prestige bias.
 
 A broader definition of prestige is the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
-Indeed, \citet{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
-\citet{prestige_evolution} gave a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature.
+Indeed, \citep{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
+\citep{prestige_evolution} gave a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature.
 
@@
 
-We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
+We begin with a continuous trait model with indirect bias suggested by \citep{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
 We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
@@
 \subsection*{Continuous trait}
-We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
+We follow the model of \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
 We consider a population of $N$ individuals, described by a single trait with a continuous value.
@@
 \paragraph{Success bias.}
-\citet[Ch.~8, p.~247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$ as a weighted average of the traits of all role-models, 
+\citep[Ch.~8, p.~247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$ as a weighted average of the traits of all role-models, 
 \begin{equation}\label{eq:boydF}
@@
 
-\citet{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
+\citep{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
 We thus develop a similar stochastic model with transmission from a single random role-model.
@@
 \end{equation}
-The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and influence--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citet{evolutionBook} with
+The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and influence--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citep{evolutionBook} with
 \begin{equation}\label{eq:prestige}
@@
 where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
-\Cref{recursive} is equivalent to eq.~(2.1) by \citet{GBD}, which completes the proof.
+\Cref{recursive} is equivalent to eq.~(2.1) by \citep{GBD}, which completes the proof.
 \end{proof}
@@
 \begin{proof}
-\citet[eq.~(2.3)]{GBD} show that 
+\citep[eq.~(2.3)]{GBD} show that 
 $\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
@@
 
-\citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
+\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
 We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{../figures/final/full_vs_dm_mutation.pdf}
-  \caption{
-  \textbf{Robustness of DM approximations to success estimation error.}
-  Both the DM approximation (orange) and our approximation (black) agree with the stochastic simulations (blue), even with a high estimation error.
-  Markers are averages across simulations, error bars are 95\% confidence intervals.
-  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,\eta^2)$ where $\eta^2$ in on the x-axis.
-  }	
-  \label{fig:hetro_error}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{../figures/final/full_vs_dm_changing_alpha.pdf}
-   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variation in success bias weight.Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$; phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
-  \label{fig:hetro_alpha}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citet[eq.~8]{kimura}, we get the following result:
+Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citep[eq.~8]{kimura}, we get the following result:
 \begin{result}[Fixation probability]
@@
 
-Similarly, we can use $1-\beta$ and $N_e$ in the population-genetics fixation time approximation given by \citet[eq.~17]{kimura_average}.\\
+Similarly, we can use $1-\beta$ and $N_e$ in the population-genetics fixation time approximation given by \citep[eq.~17]{kimura_average}.\\
 
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/final/kimura_var.pdf}
+    \includegraphics[width=\linewidth]{kimura_var.pdf}
   \caption{\textbf{Fixation probability and time in a constant environment.}
@@
 After finding a good approximation in constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a changing environment.
-Following \citet{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
+Following \citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
 We then proceed to find expressions for the expectation and variance of the change in frequency between $n=k+l$ generations. 
@@
 Note that here, we have the average selection coefficient during a cycle of $n$ generations as the selection coefficient \cref{eq:kimura_p}.
-Using the drift and diffusion terms and following \citet{changeEnv}, we can approximate the fixation probability in a changing environment using
+Using the drift and diffusion terms and following \citep{changeEnv}, we can approximate the fixation probability in a changing environment using
 \begin{equation}\label{eq:ch_env}
@@
 \begin{figure}[H]
-    \includegraphics[width=\linewidth]{../figures/final/ch_env.pdf}
+    \includegraphics[width=\linewidth]{ch_env.pdf}
   \caption{\textbf{Fixation probability in a changing environment.}
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/final/choose_bias.pdf}
+    \includegraphics[width=\linewidth]{choose_bias.pdf}
   \caption{
@@
 %\paragraph{Empirical evidence of prestige bias}
-\citet{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
+\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
 Their definition of prestige is similar to our influence bias.
@@
 food preference) can affect the attendance, and hence the prestige of the role-model.
-This lead \citet{prestige_cultural_learning} to suggest that when the trait is costly to learn individually, prestige will have a stronger bias.
+This lead \citep{prestige_cultural_learning} to suggest that when the trait is costly to learn individually, prestige will have a stronger bias.
 It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.
 
-According to \citet{fijian_social_bias}, evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
+According to \citep{fijian_social_bias}, evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
 Thus, they studied Fijian villages to examine if and how such biases emerge in a small-scale society.
@@
 We can also find prestige bias in more modern domains such as western medicine.
-\citet{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
+\citep{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
 They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices with opposite characteristics had low levels of prestige.
@@
 However, it is not always the case, and there could be negative repercussions to this bias, such as invasion of maladaptive traits.
-\citet{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
+\citep{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
 They suggest a best-of-k model where an individual samples~$k$ role-models and chooses the one he deems most "successful".
@@
 Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
-\citet{harmful_traditions} suggest a \emph{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
+\citep{harmful_traditions} suggest a \emph{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
 They found that there are individuals who act as \emph{agents}, who are often looked upon, and therefore they are ideal targets for interventions.
@@
 
-\citet{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
-Following up on this, \citet{collective_brains} offered that prestige can directly affect human physical evolution.
+\citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
+Following up on this, \citep{collective_brains} offered that prestige can directly affect human physical evolution.
 They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
@@
 
-Another way to expand our model is to account for the two types of prestige or leadership suggested by \citet{dual_leadership} that are attributed to Confucius and Machiavelli.
+Another way to expand our model is to account for the two types of prestige or leadership suggested by \citep{dual_leadership} that are attributed to Confucius and Machiavelli.
 Confucius viewed leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
@@
 In contrast, Machiavelli viewed leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence. 
-\citet{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
+\citep{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
 Several adjustments could be made so that our model reflects these leadership styles, such as assuming there is a correlation between phenotype to leadership style. 
@@
 \nolinenumbers
-\bibliography{refs}
-%\bibliographystyle{agsm}
-%\bibliographystyle{apalike}
-\bibliographystyle{unsrtnat}
+\begin{thebibliography}{}
+
+\bibitem{fliesPaper}
+  Battesti, Marine, et al. "Spread of social information and dynamics of social transmission within Drosophila groups." Current biology 22.4 (2012): 309-313.
+
+\bibitem{transmissionVectors}
+Creanza, Nicole, Oren Kolodny, and Marcus W. Feldman. "Cultural evolutionary theory: How culture evolves and why it matters." Proceedings of the National Academy of Sciences 114.30 (2017): 7782-7789.
+
+\bibitem{negativeFrequency}
+Aljadeff, Naama, Luc-Alain Giraldeau, and Arnon Lotem.
+"Competitive advantage of rare behaviours induces adaptive diversity rather than social conformity in skill learning." Proceedings of the Royal Society B 287.1933 (2020): 20201259.
+
+\bibitem{transmissionVectorsBook}
+Cavalli-Sforza, Luigi Luca, and Marcus W. Feldman. Cultural transmission and evolution: A quantitative approach. No. 16. Princeton University Press, 1981.
+
+\bibitem{evolutionBook}
+Boyd, Robert, and Peter J. Richerson. Culture and the evolutionary process. University of Chicago press, 1988.
+
+\bibitem{complexityPaper}
+Fogarty, Laurel, et al. "The driving forces of cultural complexity: neanderthals, modern humans, and the question of population size." Human Nature 28 (2017): 39-52.
+
+\bibitem{strategiesPaper}
+Rendell, Luke, et al. "Why copy others? Insights from the social learning strategies tournament." Science 328.5975 (2010): 208-213.
+
+\bibitem{sexualSelectionBook}
+Andersson, Malte, and Yoh Iwasa. "Sexual selection." Trends in ecology \& evolution 11.2 (1996): 53-58.
+
+\bibitem{chimpsCopy}
+Kendal, Rachel, et al. "Chimpanzees copy dominant and knowledgeable individuals: implications for cultural diversity." Evolution and Human Behavior 36.1 (2015): 65-72.
+
+\bibitem{chimpsPrestige}
+Horner, Victoria, et al. "Prestige affects cultural learning in chimpanzees." PloS one 5.5 (2010): e10625.
+
+\bibitem{dualEvolution}
+Henrich, Joseph, and Richard McElreath. "Dual-inheritance theory: the evolution of human cultural capacities and cultural evolution." (2007).
+
+\bibitem{elepahntsRepo}
+McComb, Karen, et al. "Matriarchs as repositories of social knowledge in African elephants." Science 292.5516 (2001): 491-494.
+
+\bibitem{wtfGene}
+Eickbush, Michael T., Janet M. Young, and Sarah E. Zanders. "Killer meiotic drive and dynamic evolution of the wtf gene family." Molecular Biology and Evolution 36.6 (2019): 1201-1214.
+
+\bibitem{pageRank}
+Xing, Wenpu, and Ali Ghorbani. "Weighted pagerank algorithm." Proceedings. Second Annual Conference on Communication Networks and Services Research, 2004.. IEEE, 2004.
+
+\bibitem{conformism}
+Molleman, Lucas, Ido Pen, and Franz J. Weissing. "Effects of conformism on the cultural evolution of social behaviour." PloS one 8.7 (2013): e68153.
+
+\bibitem{GBD}
+Drezner, Zvi, and Nicholas Farnum. "A generalized binomial distribution." Communications in Statistics-Theory and Methods 22.11 (1993): 3051-3063.
+
+\bibitem{dirichlet}
+Frigyik, Bela A., Amol Kapila, and Maya R.
+Gupta.
+"Introduction to the Dirichlet distribution and related processes." Department of Electrical Engineering, University of Washignton, UWEETR-2010-0006 6 (2010): 1-27.
+
+\bibitem{martingaleBook}
+Durrett, Richard, and R. Durrett. Essentials of stochastic processes. Vol. 1. New York: Springer, 1999.
+
+\bibitem{kimura}
+Kimura, Motoo. "On the probability of fixation of mutant genes in a population." Genetics 47.6 (1962): 713.
+
+\bibitem{durret}
+Durrett, Richard, and Richard Durrett. Probability models for DNA sequence evolution. Vol. 2. New York: Springer, 2008.
+
+\bibitem{changeEnv}
+Ram, Yoav, Uri Liberman, and Marcus W. Feldman. "Evolution of vertical and oblique transmission under fluctuating selection." Proceedings of the National Academy of Sciences 115.6 (2018): E1174-E1183.
+
+\bibitem{animal_leadership}
+King, Andrew J., and Guy Cowlishaw. "Leaders, followers, and group decision-making." Communicative \& integrative biology 2.2 (2009): 147-150.
+
+\bibitem{dual_leadership}
+Van Vugt, Mark, and Jennifer E. Smith. "A dual model of leadership and hierarchy: Evolutionary synthesis." Trends in Cognitive Sciences 23.11 (2019): 952-967.
+
+\bibitem{fijian_social_bias}
+Henrich, Joseph, and James Broesch.
+"On the nature of cultural transmission networks: evidence from Fijian villages for adaptive learning biases." Philosophical Transactions of the Royal Society B: Biological Sciences 366.1567 (2011): 1139-1148.
+
+\bibitem{harmful_traditions}
+Efferson, Charles, Sonja Vogt, and Ernst Fehr. "The promise and the peril of using social influence to reverse harmful traditions." Nature human behaviour 4.1 (2020): 55-68.
+
+\bibitem{prestige_evolution}
+Henrich, Joseph, and Francisco J.
+Gil-White.
+"The evolution of prestige: Freely conferred deference as a mechanism for enhancing the benefits of cultural transmission." Evolution and human behavior 22.3 (2001): 165-196.
+
+\bibitem{best_of_k}
+Takahashi, Takuya, and Yasuo Ihara. "Cultural and evolutionary dynamics with best-of-k learning when payoffs are uncertain." Theoretical Population Biology 128 (2019): 27-38.
+
+\bibitem{medical_prestige}
+Norredam, Marie, and Dag Album. "Prestige and its significance for medical specialties and diseases." Scandinavian journal of public health 35.6 (2007): 655-661.
+
+\bibitem{collective_brains}
+Muthukrishna, Michael, and Joseph Henrich. "Innovation in the collective brain." Philosophical Transactions of the Royal Society B: Biological Sciences 371.1690 (2016): 20150192.
+
+\bibitem{social_brains}
+Dunbar, Robin IM. "The social brain hypothesis and its implications for social evolution." Annals of human biology 36.5 (2009): 562-572.
+
+\bibitem{prestige_cultural_learning}
+Chudek, Maciej, et al. "Prestige-biased cultural learning: Bystander's differential attention to potential models influences children's learning." Evolution and human behavior 33.1 (2012): 46-56.
+
+\bibitem{evolution_of_cultural_evolution}
+Henrich, Joseph, and Richard McElreath. "The evolution of cultural evolution." Evolutionary Anthropology: Issues, News, and Reviews: Issues, News, and Reviews 12.3 (2003): 123-135.
+
+\bibitem{cultural_traits}
+O'Brien, Michael J., et al. "Cultural traits as units of analysis." Philosophical Transactions of the Royal Society B: Biological Sciences 365.1559 (2010): 3797-3806.
+
+\bibitem{dolphins_whales}
+Whitehead, Hal. "Gene–culture coevolution in whales and dolphins." Proceedings of the National Academy of Sciences 114.30 (2017): 7814-7821.
+
+\bibitem{cooperation}
+Cohen, Dor, et al. "Non-vertical cultural transmission, assortment and the evolution of cooperation." Proceedings of the Royal Society B 288.1951 (2021): 20203162.
+
+\bibitem{conformity}
+Denton, Kaleda K., Yoav Ram, and Marcus W. Feldman. "Conformity and content-biased cultural transmission in the evolution of altruism." Theoretical Population Biology 143 (2022): 52-61.
+
+\bibitem{anticonformity}
+Denton, Kaleda Krebs, et al. "Cultural evolution of conformity and anticonformity." Proceedings of the National Academy of Sciences 117.24 (2020): 13603-13614.
+
+\bibitem{facebook_marketing}
+Lee, Woojin, Lina Xiong, and Clark Hu.
+"The effect of Facebook users’ arousal and valence on intention to go to the festival: Applying an extension of the technology acceptance model." International Journal of Hospitality Management 31.3 (2012): 819-827.
+
+\bibitem{social_influence}
+Anagnostopoulos, Aris, Ravi Kumar, and Mohammad Mahdian.
+"Influence and correlation in social networks." Proceedings of the 14th ACM SIGKDD international conference on Knowledge discovery and data mining.
+2008.
+
+\bibitem{influence_analysis}
+Peng, Sancheng, et al. "Influence analysis in social networks: A survey." Journal of Network and Computer Applications 106 (2018): 17-32.
+
+\bibitem{social_media}
+Diga, Marichris, and Tom Kelleher. "Social media use, perceptions of decision-making power, and public relations roles." Public Relations Review 35.4 (2009): 440-442.
+
+\bibitem{python}
+Van Rossum, Guido. "Python Programming Language." USENIX annual technical conference. Vol. 41. No. 1. 2007.
+
+\bibitem{numpy}
+Van Der Walt, Stefan, S. Chris Colbert, and Gael Varoquaux. "The NumPy array: a structure for efficient numerical computation." Computing in science \& engineering 13.2 (2011): 22-30.
+
+\bibitem{mathplotlib}
+Hunter, John D. "Matplotlib: A 2D graphics environment." Computing in science \& engineering 9.03 (2007): 90-95.
+
+\bibitem{kimura_average}
+Kimura, Motoo, and Tomoko Ohta. "The average number of generations until fixation of a mutant gene in a finite population." Genetics 61.3 (1969): 763.
+
+\bibitem{otto_fixation}
+Slatkin, Montgomery. "Fixation probabilities and fixation times in a subdivided population." Evolution (1981): 477-488.
+
+\bibitem{lemurs}
+Erhart, Elizabeth M., and Deborah J. Overdorff. "Female coordination of group travel in wild Propithecus and Eulemur." International Journal of Primatology 20 (1999): 927-940.
+
+\bibitem{no_replication}
+Boyd, Robert, and Joseph Henrich. "On modeling cognition and culture: Why cultural evolution does not require replication of representations." Journal of cognition and culture 2.2 (2002): 87-112.
+
+\bibitem{kin_selection}
+Gardner, Andy, Stuart A. West, and Geoff Wild. "The genetical theory of kin selection." Journal of evolutionary biology 24.5 (2011): 1020-1043.
+
+\bibitem{Truskanov2020}
+Truskanov, Noa, Yasmin Emery, and Redouan Bshary. "Juvenile cleaner fish can socially learn the consequences of cheating." Nature communications 11.1 (2020): 1159.
+
+\bibitem{Kolodny2022}
+Kolodny, Oren, et al. "Differential application of cultural practices at the family and individual levels may alter heritability estimates." Behavioral and Brain Sciences 45 (2022): e167.
+
+\bibitem{Denton2021}
+Denton, Kaleda K., Uri Liberman, and Marcus W. Feldman. "On randomly changing conformity bias in cultural transmission." Proceedings of the National Academy of Sciences 118.34 (2021): e2107204118.
+
+\bibitem{Borofsky2022}
+Borofsky, Talia, and Marcus W. Feldman. "Success-biased social learning in a one-consumer, two-resource model." Theoretical Population Biology 146 (2022): 29-35.
+
+\bibitem{Mesoudi2008}
+The cultural transmission of great basin projectile-point technology II: An agent-based computer simulation
+
+\end{thebibliography}
 
@@
 \end{equation}
-following \citet[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
+following \citep[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
 
@@
 
-Following \citet[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
+Following \citep[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
 \begin{equation}
@@
 \begin{figure}[h]
-    \includegraphics[width=0.7\linewidth]{../figures/final/GBD_validation.pdf}
+    \includegraphics[width=0.7\linewidth]{GBD_validation.pdf}
   \caption{
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/final/DM_validation.pdf}
+    \includegraphics[width=\linewidth]{DM_validation.pdf}
   \caption{
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{../figures/final/num_sims.pdf}
+    \includegraphics[width=\linewidth]{num_sims.pdf}
   \caption{
@@
 
+\begin{figure}
+    \includegraphics[width=\linewidth]{full_vs_dm_mutation.pdf}
+  \caption{
+  \textbf{Robustness of DM approximations to success estimation error.}
+  Both the DM approximation (orange) and our approximation (black) agree with the stochastic simulations (blue), even with a high estimation error.
+  Markers are averages across simulations, error bars are 95\% confidence intervals.
+  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,\eta^2)$ where $\eta^2$ in on the x-axis.
+  }	
+  \label{fig:hetro_error}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{full_vs_dm_changing_alpha.pdf}
+   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
+   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variation in success bias weight.Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
+  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$; phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
+  \label{fig:hetro_alpha}
+\end{figure}
+
 \end{document}

### 2023-03-01 ms/ms.tex
mwf suggestions

@@
 \usepackage[english]{babel}
+\usepackage{xcolor}
 % appendix
@@
 \begin{abstract}
-A common bias in cultural transmission is success bias, where more successful individuals are more likely to be copied.
-Because success may be difficult to estimate, individuals may indirectly estimate success by using prestige as a proxy for success.
-Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied from that role-model.
-We analyze the effect of prestige on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
-We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduce the computational complexity of simulations.
-We also find approximations to the fixation probability and the fixation time of an invading cultural trait in different environments.
+{If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased. Prestige may be used as a proxy for successs.}
+Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied  that role-model.
+{The} effect of prestige on cultural evolutionary dynamics {is analyzed} using mathematical analysis and stochastic simulations.
+{Analytic} approximations to the stochastic role-model choice process {facilitate the} mathematical analysis and reduce the computational complexity of simulations.
+{Approximations are given}  to the fixation probability and the fixation time of an invading cultural trait in different environments.
 We show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
-Influence bias also accelerates the evolutionary dynamics, as can be expected in a rich-getting-richer process.
-Our study extends the literature that describes and analyses cultural transmission,
-especially in human societies where social media is popular and thus influence bias may be expected.
+Influence bias{, which may be strong in communities where social media are prevalent,}  also accelerates the evolutionary dynamics, as can be expected in a rich-{get}-richer process.
 \end{abstract}
@@
 %\paragraph{Cultural transmission.}
-In cultural transmission, individuals transmit cultural traits (i.e., behaviors, beliefs, norms) to one another, typically by learning and demonstrating \citep{transmissionVectorsBook}.
-Examples for cultural traits in humans are norms, preferences, tools, ideas, and language, potentially transmitted verbally and/or by observations \citep{transmissionVectors}. 
-Although cultural transmission is common in humans, it is also observed in other animals, e.g.
+%In cultural transmission, individuals transmit cultural traits (i.e., behaviors, beliefs, norms) to one another, typically by learning and demonstrating \citep{transmissionVectorsBook}.
+%Examples for cultural traits in humans are norms, preferences, tools, ideas, and language, potentially transmitted verbally and/or by observations \citep{transmissionVectors}. 
+%Although cultural transmission is common in humans, it is also observed in other animals, e.g.
 chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper} and fish \citep{Truskanov2020}.
 
-Cultural transmission may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, and even strangers) transmit to unrelated offspring; and horizontal transmission, in which peers from the same age cohort transmit to one another \citep{transmissionVectorsBook,transmissionVectors}.
-It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{changeEnv}.
-
-Transmission biases may cause a cultural trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
-\textit{Success bias} occurs when individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, using medicinal plants \citep{fijian_social_bias}, or hunting \citep{Mesoudi2008}, and it can increase the probability of learning a successful trait \citep{Borofsky2022}.
-Indeed, in a tournament between learning strategies conducted by \citep{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
+Cultural transmission {of attitudes, preferences, beliefs, norms, and behaviors} may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, and even strangers) transmit to unrelated offspring; and horizontal transmission, in which {individuals} from the same age cohort transmit to one another \citep{transmissionVectorsBook}.
+It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{changeEnv,Lehmann2009}.
+
+Transmission biases may cause a cultural trait to have a {higher rate of transmission than} its frequency in the population.
+\textit{Success bias} occurs when individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, using medicinal plants \citep{fijian_social_bias}, or hunting \citep{Mesoudi2008}, and it can increase the probability of learning a {trait that is present in those successful individuals} \citep{Borofsky2022}.
+Indeed, in a tournament between learning strategies  \citep{strategiesPaper}, most {winning} strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
 
 % TODO edit so that we focus on indirect success - aka prestige - and decompose it to content based - which we call success - and context based - which we call influence
-\citep[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
-A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
-For example, an individual observing a ping-pong match can attempt the observed paddle grips to determine which grip is better.
-A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
-For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{non-conformity} \citep{conformism}.
-The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
-An indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
-For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
-This, however, may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
-Furthermore, \citep[Ch.
-8]{evolutionBook} have suggested that maladaptive traits may spread widely in a population if indirect biases are strong enough, e.g., by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
-Indeed, \citep{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.
-
-\citep{fijian_social_bias} have studied such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
-They have suggested that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
-\citep[Ch.~8]{evolutionBook} and \citep{complexityPaper} have suggested that prestige biases are probably more common in humans than success biases, and prestige is often mentioned in the cultural evolution literature, however there are few models of prestige bias.
+{Boyd and Richerson} \citep[Ch.~5]{evolutionBook}  suggested that the {assessment} of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
+{Direct} bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
+For example, an individual observing a ping-pong match can {try} the observed paddle grips to determine which grip is better.
+{Frequency}-dependent bias occurs when the probability {of copying} a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
+For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{{anti}-conformity} \citep{conformism}.
+The effects of conformity and {anti}-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
+{Indirect} bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
+For example, an observer may copy the paddle grip of the {ping}-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
+{However, this} may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
+Furthermore, {Boyd and Richerson} \citep[Ch.
+8]{evolutionBook} {suggest} that maladaptive traits may spread widely in a population if indirect {bias is} strong enough, e.g., by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
+Indeed, helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost \citep{cooperation}.
+
+{Heinrich and Broesch \citep{fijian_social_bias}  studied} such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
+They {suggested} that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits
+\citep[Ch.~8]{evolutionBook}.
+{Prestige bias may be} more common in humans than success {bias} \citep{complexityPaper}, and prestige is often mentioned in the cultural evolution literature, {although} there are few models of {it}.
 
 A broader definition of prestige is the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
-Indeed, \citep{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
-\citep{prestige_evolution} gave a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature.
+Indeed, {Chudek et al.}\ \citep{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
+{Henrich and Gil-White} \citep{prestige_evolution} gave a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature.
 
 To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
-This is an important distinction, as influence is a context-based bias, rather than a content-based bias: it does not depend on the phenotype itself but rather on the number of copiers that already copied each role-model, which may be easier and more accurate to estimate compared to success.
-Influence bias also differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
-
-In contemporary human society, social media makes it especially easy to estimate the social and cultural influence individuals have over others, and therefore can have an effect on decision making.
-Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
-
-In the following, we develop a stochastic model of cultural transmission with prestige bias. In our model, prestige combines both cross-domain indirect success bias and influence bias.
+This is an important distinction, as influence is a context-{dependent} bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that {have} already copied each role-model, which may be easier and more accurate to estimate {than} success.
+Influence bias also differs from {conformity}, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+
+In contemporary human society, social media {make} it especially easy to estimate the social and cultural influence individuals have over others, {which} can have an effect on decision making.
+Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices {have been} invented to capitalize on this effect \citep{facebook_marketing}.
+
+In the following, we develop a stochastic model of cultural transmission with prestige bias {that} combines both cross-domain indirect success bias and influence bias.
 We develop analytic approximations for this model and analyze its dynamics.
-We find approximations for the probability and time for fixation of a `successful' phenotype (i.e., that is favored by success bias).
+We {also} find approximations for the probability and time {to} fixation of a `successful' phenotype (i.e., that is {subject to} success bias).
 Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.
@@
 
-We begin with a continuous trait model with indirect bias suggested by \citep{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
-We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
+We begin with a continuous trait model with indirect bias suggested by {Boyd and Richerson} \citep{evolutionBook}, {propose} an extension with influence bias, and then develop a model with a dichotomous trait.
+We {implement} our stochastic models and approximations, {perform} statistical analyses, and {produce} figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
 Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
@@
 \subsection*{Continuous trait}
-We follow the model of \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
-We consider a population of $N$ individuals, described by a single trait with a continuous value.
+We follow the {Boyd and Richerson model} \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
+{Consider} a population of $N$ individuals, described by a single trait {that takes continuous values}.
 Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait.
-Similar to a Wright-Fisher model, we assume non-overlapping generations such that the entire population is replaced in each generation.
-The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t$.
-We assume the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
+Similar to a Wright-Fisher model, {generations are non-overlapping, and}  the entire population is replaced in each generation.
+The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t${, and}  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
 Cultural transmission is modeled by a function $F$ such that 
@@
 \paragraph{Success bias.}
-\citep[Ch.~8, p.~247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$ as a weighted average of the traits of all role-models, 
+{Boyd and Richerson} \citep[Ch.~8, p.~247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$,  a weighted average of the traits of all role-models, {as}
 \begin{equation}\label{eq:boydF}
@@
 \end{equation}
-$A_{i,j}$ is the absolute trait value copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
+$A_{i,j}$ is the absolute trait value {that} copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
 \begin{equation}\label{eq:relativeTrait}
@@
 with $\hat{A}$ as the arbitrary optimal trait value, and $J$ and $b$ as parameters that control the bias strength.
-Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$, equivalent to relative fitness in evolutionary-genetic transmission models.
-
-\citep{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
-We thus develop a similar stochastic model with transmission from a single random role-model.
-Instead of \cref{eq:boydF}, we define the transmission function $F$ as a random variable with its distribution given by
+Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$.
+
+{Boyd and Richerson} \citep{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
+We {can} develop a similar stochastic model with transmission from a single random role-model{\ where instead} of \cref{eq:boydF}, we define the transmission function $F$ as a random variable with its distribution given by
 \begin{equation}\label{eq:ourF}
-\Pr\big(F_i(\vec{A}) = A_{j}\big) = G_{i,j} \;,
-\end{equation}
-such that $G_{i,j}$ gives the probability of copier $i$ to choose to copy the trait of role-model $j$.
+\Pr\big(F_i(\vec{A}) = A_{j}\big) = G_{i,j} \;;
+\end{equation}
+{here $G_{i,j}$ is} the probability {that copier $i$ chooses} to copy the trait of role-model $j$.
 
 \paragraph{Influence bias.}
-Here we introduce a new element to the model.
-We assume that in each generation, copiers choose their role-models one by one.
-We denote $K_{i,j}$ as the number of copiers that chose role-model $j$ after copier $i$ chose a role-model.
-Thus, $i$ out of $N$ copiers already chose a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
+Here we introduce a new element to the model {by assuming} that in each generation, copiers choose their role-models one by one.
+{Denote by} $K_{i,j}$  the number of copiers that {choose} role-model $j$ after copier $i$ chose a role-model.
+Thus, $i$ out of $N$ copiers {had} already {chosen} a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
 The stochastic process of role-model choice, 
@@
 \end{equation}
-The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and influence--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} of \citep{evolutionBook} with
+The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and influence--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} with
 \begin{equation}\label{eq:prestige}
@@
 
-We assume every individual may evaluate the importance of success and influence differently.
-Additionally, we assume every role-model displays his influence and success individually.
-For example, a person with more followers but lack of actual skill may emphasize the number of his followers rather than his actual skill.
-We therefore defined $\alpha_{i,j}$ to be the relation between every copier's intrinsic significance of estimation, and every role-model's personal emphasis.
+{Different individuals} may evaluate the importance of success and influence differently.
+Additionally, we assume {each} role-model displays {its} influence and success individually.
+For example, {individuals} with more followers but {lacking} skill may emphasize the number of {their} followers rather than {their} skill.
+%We therefore defined $\alpha_{i,j}$ to be the relation between every copier's intrinsic significance of estimation, and every role-model's personal emphasis.
 
@@
 \subsection*{Dichotomous trait}
-To allow for mathematical analysis of the model, we introduce a simplified version where the trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
-All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
-In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous, such that we have exchangeability between role-models.
-Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
+{We} introduce a simplified version where the trait {has only} two phenotypes: {an} optimal phenotype $\hat{A}$ and {a} sub-optimal phenotype $A$. 
+All role-models with the same phenotype will contribute to the probability {that} that phenotype {is} transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
+In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous, {which entails} exchangeability between role-models.
+Therefore, the probability {that} the $i$-th copier {copies} phenotype $A$ is
 \begin{equation}\label{eq:binary-model}
@@
 \end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$, $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, $\beta(\hat{A})=1$, and $\alpha'= \frac{\alpha}{1-\alpha}$ is the odd ratio of the bias weight.
+where $X$ is the number of role-models with trait $\hat{A}$, $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, $\beta(\hat{A})=1$, and $\alpha'= \frac{\alpha}{1-\alpha}$ is the {odds} ratio of the bias weight.
 Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
@@
 Our model is defined by two nested stochastic processes.
-Change over multiple generations is described by the phenotype distribution at each generation, $\{\vec{A}(t)\}_t$.
+Change over multiple generations is described by the {dynamics of the} phenotype distribution at each generation, $\{\vec{A}(t)\}_t$.
 The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
@@
 We found two such approximations, summarized here and explained in detail below.
-In both we assume either $\alpha_j$ is a trait of role-model $j$ only (contrary to $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.
+In both we assume either $\alpha_j$ is a trait of role-model $j$ only ({different from} $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.
 
@@
 \subsection*{Generalized binomial distribution}
-The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
+The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is {denoted}  by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
 \\
@@
 \begin{proof}
-We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$. 
+{Let} $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ {be} the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ {out} of $i-1$ copiers chose role-model $j$. 
 Using conditional probability and \cref{eq:recurrence},
@@
 \begin{proof}
-\citep[eq.~(2.3)]{GBD} show that 
+{Drezner and Farnum} \citep[eq.~(2.3)]{GBD} show that 
 $\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
@@
 where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution of the trait values, modified by some constant parameters of $\beta$.
-We can then denote $L = 1/\overline{\beta(A+e)}$ and write
+We can then {write} $L = 1/\overline{\beta(A+e)}$ and
 \begin{equation}\label{eq:linearEq}
@@
 Although basic, \Cref{fig:GBD} shows good fit of the GB approximation.
-This validation is initial, and the more extensive validations we do on the Dirichlet-Multinomial approximation, because it is what we will use in our analysts.
+This validation is initial, and {we do} more extensive validations on the Dirichlet-Multinomial approximation, because {that} is what we will use in our {analysis}.
 
@@
 \paragraph{P\'{o}lya urn model.}
-This stochastic process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors.
+This stochastic process consists of $N$ draws from an urn with an initial {number} of colored balls of $M$ colors.
 When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same color.
@@
 \end{equation}
-where $o_j$ is the initial number of balls of the color $j$ in the urn, and $w_{i,j}$ is the cumulative number of new balls that were added to the urn after $i$ draws of the color $j$.
+where $o_j$ is the initial number of balls of color $j$ in the urn, and $w_{i,j}$ is the cumulative number of new balls that were added to the urn after $i$ draws of color $j$.
 \\
@@
 \begin{proof} 
-Denote $\alpha'=\frac{\alpha}{1-\alpha}$ as the bias weight ratio, and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
+{Write} $\alpha'=\frac{\alpha}{1-\alpha}$ as the bias weight ratio, and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
 \begin{equation}\label{eq:copier_choose}
 G_{i,j} = 
-\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}
+\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N}{\left[ \alpha'\beta(A'_m) + K_{i-1,m}\right]}}
  =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N}\alpha'\beta(A'_m)} \;.
@@
 
-\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
+{Frigyik et al.}\ \citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
 We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
-Thus, choosing the role-models for all copiers is equivalent to drawing from a Multinomial distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
+Thus, choosing the role-models for all copiers is equivalent to drawing from a {multinomial} distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
 \\
@@
 \begin{corollary}\label{cor:dirichlet}
-The number of copiers of each role-model follows a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \emph{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
+The number of copiers of each role-model {approximates} a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \emph{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
 \end{corollary}
@@
 To validate our analytical result (\Cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
-First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then compared this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A).
+First, we {compute} an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
+We then {compare} this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A).
 The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
-The maximum difference is 0.5 role-models, which indicate a very good fit.
+The maximum difference is 0.5 role-models, which {indicates} a very good fit.
 In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself (\Cref{fig:DM_validation}B).
-We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, supporting our approximation more.
+We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, {strongly} supporting our approximation.
 
@@
 Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
-We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
+{That} the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
 We examined the robustness of the DM approximation to relaxing the approximation assumptions.
@@
 When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
-Even when the standard deviation is $0.1$, the fixation probability and time is similar~(\Cref{fig:hetro_error}). 
+Even when the standard deviation is $0.1$, the fixation probability and time {are} similar~(\Cref{fig:hetro_error}). 
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
@@
 \begin{result}[Drift and diffusion terms in a constant environment]
-Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ is the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
+Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
 Then,
@@
 the selection coefficient $s$, a measure of the effect of natural selection on the change in frequency of genotypes, and the effective population size, $N_e$, a measure of the effect of random genetic drift on the change in frequency of genotypes.
-In a diffusion-equation approximation of the classical Wright-Fisher model, the expectation and variance of the change in frequency are $E[x'-x]=x+x(1-x)s+o(s)$ and $V[x'-x]=x(1-x)/N_e$ \citep[eq.~7]{kimura}.
+In a diffusion-equation approximation of the classical Wright-Fisher model, the expectation and variance of the change in frequency are $E[x'-x]=x+x(1-x)s+o(s)$ and $V[x'-x]=x(1-x)/N_e$ \citep[eq.~7]{kimura}{, respectively}.
 Therefore, we have the following result.\\
@@
 
-Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citep[eq.~8]{kimura}, we get the following result:
+Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citep[eq.~8]{kimura}, we {obtain}:
 \begin{result}[Fixation probability]
@@
 \begin{equation}\label{eq:kimura_p}
-\pi(x) = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
+\pi(x) = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}},
 \end{equation}
@@
 % TODO SAAR check these equations vs what you have in the source code
-\begin{result}[Fixation time] The fixation time (conditioned on fixation) from an initial frequency $x$ is approximately
+\begin{result}[Fixation time] The {expected} fixation time (conditioned on fixation) from an initial frequency $x$ is approximately
 \begin{equation} \label{eq:kimura_t}
@@
 \end{result}
-Note that these integrals cannot be solved in closed form, so we can only estimate them numerically.
+Note that these integrals cannot be solved in closed form, {and are estimated} numerically.
 
@@
 We compare our approximations (\cref{eq:kimura_p,eq:kimura_t}) with results of simulations of our dichotomous model using various $\alpha$ and $\beta$ values, as well as simulations of the Wright-Fisher model, using the effective selection coefficient, $1-\beta$, and effective population size, $N_e=\alpha N + (1-\alpha)$.
-We find see that the two models have similar dynamics, and both are well approximated our approximations (\Cref{fig:var_alpha}).
+We find see that the two models have similar dynamics, and both are well approximated {by} our approximations (\Cref{fig:var_alpha}).
 
@@
 \paragraph*{Changing environment}.
-After finding a good approximation in constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a changing environment.
+After finding a good approximation in {a} constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for {when the environment changes}.
 Following \citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
@@
 \begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
-Let $x$ be the initial frequency of the invading phenotype and $X_t$ is the number of individuals with the phenotype after $n$ generation.
+Let $x$ be the initial frequency of the invading phenotype and $X_t$ {the} number of individuals with {that} phenotype after $n$ generation.
 Then,
@@
 
-Note that here, we have the average selection coefficient during a cycle of $n$ generations as the selection coefficient \cref{eq:kimura_p}.
+Note that here, we have the average selection coefficient during a cycle of $n$ generations as the selection coefficient {in} \cref{eq:kimura_p}.
 Using the drift and diffusion terms and following \citep{changeEnv}, we can approximate the fixation probability in a changing environment using
@@
 However, the approximation is more sensitive to the value of the success bias coefficient $\beta$ (\Cref{fig:ch_env_alpha_beta}B).
-We suspect that when $\beta$ is too small, there will not be many cycles in the simulations, because either the population reaches a high frequency of the fitter phenotype after just a few cycles, or the fitter phenotype becomes extinct very quickly.
+We suspect that when $\beta$ is too small, there will not be many cycles in the simulations, because either the population reaches a high frequency of the fitter phenotype after just a few cycles, or the fitter phenotype {goes} extinct very quickly.
 For such $\beta$ values (below 0.65), the fixation probability exceeds even the constant environment approximation (which is the upper limit).
@@
 The approximation follows the trend of the simulation results for all $\alpha$ values.
-When increasing the success coefficient to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation.
+{On} increasing the success coefficient {$\alpha$} to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation.
 We believe the reason is the structure of the cycle.
-Our proof and approximation in the changing environment are for a large amount of cycles, and when the success coefficient is too high, there might be very few cycles.
-Either the ideal trait is copied by enough copiers so that the influence is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait gets extinct before there were enough copiers that copied it.
+Our proof and approximation in the changing environment are for a large {number} of cycles, and when the success coefficient {$\alpha$} is too high, there might be very few cycles.
+Either the ideal trait is copied by enough copiers so that the influence is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait {goes} extinct before there {are} enough copiers that copied it.
 We then tried to change the ratio between the number of cycles where $\hat{A}$ is favored and disfavored.
@@
   \caption{\textbf{Fixation probability in a changing environment.}
-\textbf{(A)} Fixation probability decreases with the the success-bias weight (bottom x-axis) and effective population size (top x-axis).
+\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis).
 The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange).
@@
 
-We find that when copiers adapt their success-bias weight, it decreases with the number of copiers that have already chosen a role-model~(\Cref{fig:influence_advantage}).
+We find that when copiers {choose} their success-bias weight, it decreases with the number of copiers that have already chosen a role-model~(\Cref{fig:influence_advantage}).
 Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the adaptive weight estimation error converges to $0.046$, whereas a constant weight gives values $>0.74$.
@@
 \section*{Discussion}
-During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
-Some cultural traits or cultural role-models may be copied more often due to transmission biases. 
-A common bias is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
-However, it has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
-This perceived success can be determined by performance in another trait, i.e., by indirect success \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.
-
-We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
-We model the these biases using a stochastic role-model choice process: each copier, in its turn, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
-
-Hence, we have a model with two "nested" stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
+%During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
+{Some} cultural traits or cultural role-models may be copied more often {than others} due to transmission biases. 
+{One such} bias is success bias, in which copiers are more likely to copy a successful role-model.
+{Although many} models assume that success can be accurately estimated{, it} has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
+This perceived success can be determined by performance {with respect to another trait (indirect)} \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.
+
+We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers {and hence is the same as conformity bias}.
+We model the these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
+
+Hence, {our model has} two ``nested'' stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
 To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DM, \Cref{cor:dirichlet}).
@@
 Analyzing the model with the DM distribution, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
-Our approximations are similar to Kimura's evolutionary-genetic approximations, such that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence versus success bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
+Our approximations are similar to Kimura's evolutionary-genetic approximations, {in} that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence versus success bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
 
@@
 We also showed that this approximation is more sensitive to changes in the success coefficient $\beta$ than the constant environment approximation, and a lower value is required to have a good fit.
-The ratio between the number of generation in which the rare phenotype is under positive transmission bias and the number of generations in which it is under negative bias does not affect the goodness-of-fit of the approximation.
+The ratio between the number of {generations} in which the rare phenotype is under positive transmission bias and the number of generations in which it is under negative bias does not affect the goodness-of-fit of the approximation.
 
 We also examined a scenario in which copiers can adapt their success-weight bias, $\alpha$, to minimize their copying error, i.e., copy trait values closer to the optimal value.
-We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight (adapted by copiers) and the estimation error decrease. 
-The latter is significantly lower compared to a population using a constant, fixed success-bias weight, regardless of the value of the constant weight (\Cref{fig:influence_advantage}).
+We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight ({chosen} by copiers) and the estimation error decrease. 
+The latter is significantly lower {than in} a population using a constant, fixed success-bias weight, regardless of the value of the constant weight (\Cref{fig:influence_advantage}).
 This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers, and the less it should rely on its own estimation.
@@
 %\paragraph{Empirical evidence of prestige bias}
-\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
+{Chudek et al.}\ \citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
 Their definition of prestige is similar to our influence bias.
-They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of their learning from a role-models whom bystanders ignored.
+They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of {learning from a role model} whom bystanders ignored.
 They also note that prestige effects are domain sensitive: they found that prestigious role-models were attended more when demonstrating artifact use, whereas role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact use vs.
 food preference) can affect the attendance, and hence the prestige of the role-model.
-This lead \citep{prestige_cultural_learning} to suggest that when the trait is costly to learn individually, prestige will have a stronger bias.
+This {led to the suggestion} that when the trait is costly to learn individually, prestige will have a stronger bias \citep{prestige_cultural_learning}.
 It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.
 
-According to \citep{fijian_social_bias}, evolutionary theorists propose that natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
-Thus, they studied Fijian villages to examine if and how such biases emerge in a small-scale society.
+According to \citep{fijian_social_bias}, {natural} selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information. 
+{They} studied Fijian villages to examine if and how such biases emerge in a small-scale society.
 They found that Fijian villagers are more likely to learn from role-models perceived as more successful/knowledgeable, both within and across domains.
-Their research thus suggests that copying from those perceived as successful, rather than actually are successful, is a common phenomena. 
+Their research thus suggests that copying from those perceived as successful, rather than {who are actually} successful, is a common {phenomenon}. 
 They show that the social networks representing copier--role-model relationships are centralized, suggesting that it is consistent with the prediction that people substantially share notions about who is a good cultural model, but that individuals' role-model selections are influenced by multiple factors.
 
-We can also find prestige bias in more modern domains such as western medicine.
-\citep{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
+{Prestige bias also occurs} in more modern domains such as western medicine.
+{Norredam and Album} \citep{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
 They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices with opposite characteristics had low levels of prestige.
-For example, they found that surgery counts as the most prestigious specialty, while psychiatry is the less prestigious.
+For example, they found that surgery counts as the most prestigious specialty, while psychiatry is the {least} prestigious.
 In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered easier to master are less prestigious. 
 This means that there may be very important practices that are neglected due to prestige bias.
-They concluded that such differences in prestige may bear consequences for actual priority setting in healthcare systems.
+They concluded that such differences in prestige may {affect} for actual priority setting in healthcare systems.
 
@@
 However, it is not always the case, and there could be negative repercussions to this bias, such as invasion of maladaptive traits.
-\citep{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
+{Takahashi and Ihara} \citep{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
 They suggest a best-of-k model where an individual samples~$k$ role-models and chooses the one he deems most "successful".
-They mentioned that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
+They {mention} that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
 In such a case, learners may be selectively disfavored and in the long run replaced by unbiased learners, who simply copy someone chosen at random.
 They developed new mathematical models that are simpler and mathematically tractable.
-They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff.
+They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff {(see Fogarty et al.\ \citep{Fogarty2017} and references there)}.
 Our model, which includes influence bias, is consistent with this claim.
-When a maladaptive trait is "piggybacking" a role-model with high influence, this trait could spread in the population.
-In addition, they show that best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning. 
-Our model only includes social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics.
+When a maladaptive trait is ``piggybacking'' {on} a role-model with high influence, {the former} could spread in the population.
+In addition, {best}-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning \citep{best_of_k}. 
+Our model {includes only} social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics.
 
 Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
-\citep{harmful_traditions} suggest a \emph{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
-They found that there are individuals who act as \emph{agents}, who are often looked upon, and therefore they are ideal targets for interventions.
-This is similar to influential role-models in our model, where a prestigious individual will be copied more often, and will therefore spread his trait faster and wider in the population.
-They also suggest a way to use this phenomena to change existing traditions in a population.
+{Efferson et al.}\ \citep{harmful_traditions} suggest a \emph{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
+They {find} that there are individuals who act as \emph{agents}, who are often {observed}, and therefore they are ideal targets for interventions.
+This is similar to influential role-models in our model, where a prestigious individual will be copied more often, and will therefore spread {their} trait faster and wider in the population.
+They also suggest a way to use this {phenomenon} to change existing traditions in a population.
 It is very clear however, that just as it can be used to end harmful traditions, the same agents could start harmful traditions.
 
-\citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
-Following up on this, \citep{collective_brains} offered that prestige can directly affect human physical evolution.
+{Dunbar} \citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
+Following {this, Muthukrishnan and Henrich \citep{collective_brains} suggested} that prestige can directly affect human physical evolution.
 They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
@@
 One path forward is an analysis of the dynamics of the adaptive success-bias weight model, in which every copier chooses its $\alpha$.
-It would be interesting to see the if the mean estimation error and the adaptive weight, $\alpha^*$, are converging to specific values, and how they are affected by the model parameters.
+It would be interesting to see the if the mean estimation error and the adaptive weight, $\alpha^*$, {converge} to specific values, and how they are affected by the model parameters.
 It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
@@
 
-Another way to expand our model is to account for the two types of prestige or leadership suggested by \citep{dual_leadership} that are attributed to Confucius and Machiavelli.
+Another way to expand our model is to account for the two types of prestige or leadership suggested by {Van Vugt and Smith} \citep{dual_leadership} that are attributed to Confucius and Machiavelli.
 Confucius viewed leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
@@
 In contrast, Machiavelli viewed leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence. 
-\citep{dual_leadership} suggest that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
-Several adjustments could be made so that our model reflects these leadership styles, such as assuming there is a correlation between phenotype to leadership style. 
-The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
+{Van Vugt and Smith suggest} that these opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
+Several adjustments could be made so that our model reflects these leadership styles, such as assuming there is a correlation between phenotype {and} leadership style. 
+The {resulting} cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
 
 \paragraph{Conclusions.}
-Here, we studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with influence bias, which has so far received less attention.
+{We} studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with influence bias, which has so far received less attention.
 We found approximations for this complex dynamics.
@@
 
+\bibitem{Lehmann2009}
+Lehmann, L., and M.W. Feldman. Coevolution of adaptive technology, maladaptive culture, and population size in a producer-scrounger game. Proc.\ Roy.\ Soc.\ B 276 (2009): 3853-3862.
+
+\bibitem{Fogarty2017}Fogarty, L., J.
+Y.
+Wakano, M.
+W.
+Feldman, and K.
+Aoki.
+The driving forces of cultural complexity: Neanderthals, modern humans, and the question of population size.
+Hum.\ Nat.\ (2017): 28: 39-52.
+
 \end{thebibliography}
@@
 
-\paragraph{Proving $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.}
+\paragraph{Proving $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the {average} in the denominator is over the role-models index, $j$.}
 
@@
 \end{equation}
-where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
+where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$.
 Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
@@
 \paragraph{Proving drift and diffusion terms in a constant environment.}
-Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ is the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
+Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
 Then,
@@
 
-By definition, $x$ is constant, so $E[x] = x$.
-We therefore have
+%By definition, $x$ is constant, so $E[x] = x$.
+{We} therefore have
 \begin{equation}\label{eq:expec_freq}
@@
   The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
-  Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; idea phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
+  Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; {ideal} phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
   \label{fig:GBD}
@@
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the experiments (blue) is very small. 
-  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (red vertical line) is much higher compared to the log-likelihood of permutations of experiments (blue histogram).
+  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (red vertical line) is much higher {than} the log-likelihood of permutations of experiments (blue histogram).
   Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.

### 2023-03-09 ms/ms.tex
added todos from MWF

@@
 Influence bias also differs from {conformity}, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+% TODO check this - is influence frequency dependent?
 
@@
 
-We begin with a continuous trait model with indirect bias suggested by {Boyd and Richerson} \citep{evolutionBook}, {propose} an extension with influence bias, and then develop a model with a dichotomous trait.
-We {implement} our stochastic models and approximations, {perform} statistical analyses, and {produce} figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
+We begin with a continuous trait model with indirect bias suggested by {Boyd and Richerson} \citep{evolutionBook}, propose an extension with influence bias, and then develop a model with a dichotomous trait.
+We implement our stochastic models and approximations, {perform} statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
 Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
@@
 We follow the {Boyd and Richerson model} \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity.
+% TODO If you omit the indirect trait, it is no longer indirect transmission.
 {Consider} a population of $N$ individuals, described by a single trait {that takes continuous values}.
 Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait.
+% We need to mention that each copier chooses one role model out of the entire population; this is different from other models studied by Feldman and colleagues in which the population is infinite and each copier samples n role models, and uses those n role models to determine its trait:
+%  Denton, Kaleda K, Yoav Ram, and Marcus W.
+Feldman.
+2023.
+“Conditions That Favour Cumulative Cultural Evolution.” Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
+https://doi.org/10.1098/rstb.2021.0400.
+% Denton, Kaleda Krebs, Yoav Ram, Uri Liberman, and Marcus W.
+Feldman.
+2020.
+“Cultural Evolution of Conformity and Anticonformity.” Proceedings of the National Academy of Sciences 117 (24): 13603–14.
+https://doi.org/10.1073/pnas.2004102117.
+% Boyd & Richerson book
 Similar to a Wright-Fisher model, {generations are non-overlapping, and}  the entire population is replaced in each generation.
@@
 \paragraph{Success bias.}
-{Boyd and Richerson} \citep[Ch.~8, p.~247-249]{evolutionBook} describe a blended transmission algorithm by defining $F$,  a weighted average of the traits of all role-models, {as}
+{Boyd and Richerson} \citep[Ch.~8, p.~247-249]{evolutionBook} describe a  transmission algorithm by defining $F$, a weighted average of the traits of all role-models, as
 \begin{equation}\label{eq:boydF}
@@
 \end{equation}
-and $\beta(\cdot)$ is the bias function that quantifies the success bias of a role-model,
+and $\beta(\cdot)$ is the bias function that quantifies the success bias of a role-model \citep[eq.~5.11]{evolutionBook},
 \begin{equation}\label{eq:success_bias}
@@
 
-Here, the bias weight $\alpha_{ij}$ is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs.
+Here, the bias weight $\alpha_{ij}$ determines the relative weighting of success and influence bias.
+It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs.
 influence in the role-model's overall prestige in the eyes of the copier.
@@
 \end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$, $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, $\beta(\hat{A})=1$, and $\alpha'= \frac{\alpha}{1-\alpha}$ is the {odds} ratio of the bias weight.
+where $X$ is the number of role-models with trait $\hat{A}$; $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model; assuming (without loss of generality) that $\beta(\hat{A})=1$; and defining $\alpha'= \frac{\alpha}{1-\alpha}$ as the odds ratio of the bias weight.
 Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
@@
 \section*{Results}
-Our model is defined by two nested stochastic processes.
-Change over multiple generations is described by the {dynamics of the} phenotype distribution at each generation, $\{\vec{A}(t)\}_t$.
-The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
-We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
+Our models are defined by two nested stochastic processes.
+Change over multiple generations is described by the {dynamics of the} phenotype distribution at each generation, $\{\vec{A}(t)\}_t$, see \cref{eq:transmission}.
+The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$, see \cref{eq:process}.
+We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$, where $K_{N,j}$ is the number of copiers that chose role-model $j$ after all copiers chose a role model.
+However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
 Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
-We found two such approximations, summarized here and explained in detail below.
-In both we assume either $\alpha_j$ is a trait of role-model $j$ only ({different from} $\alpha_{ij}$ that included the relation with copier $i$), or a completely homogeneous $\alpha$.
+We found two approximations for the distribution of $\vec{K}_{N}$, summarized here and explained in detail below.
+In both we assume that the bias weight is completely homogeneous, $\alpha_{i,j}=\alpha$ (it is also enough to assume that $\alpha_j$ is a bias of role-model $j$ only, that is, it does not vary between copiers).
+% TODO but result 1 has alpha_i
+Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.
 
@@
 \paragraph{Dirichlet-Multinomial approximation.}
-The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning there's no meaning for the order of copiers.
-
-Note that here $G_{i,j}$ is only a function of the trait values $A_j$ and the bias weights $\alpha_j$, as the estimation error is uniform, meaning all copiers are identical.
+The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning that the order of copiers does not matter.
 
@@
 \end{proof}
-This result gives the following two corollaries on the expected number of followers of a given role-model by the end of the role-model choice process.
+This result gives the following two corollaries on the expected number of followers of a given role-model $j$ by the end of the role-model choice process, $K_{N,j}$.
 The proof of \Cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
@@
 {Drezner and Farnum} \citep[eq.~(2.3)]{GBD} show that 
-$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
+$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation). % TODO what is E[k]?
 $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
@@
 
-\begin{corollary}\label{cor:GBD}
+\begin{corollary}\label{cor:GBD} % TODO merge with the previous corollary
 $\E[K_{N, j}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
@@
 \paragraph{Numerical validation.}
-To validate our results we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
+To validate our results  % TODO be more explicit - what exactly are you validating?
+we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
 We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \Cref{cor:GBD}.
-We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \Cref{fig:GBD}.
+We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \Cref{fig:GBD}. % TODO what are drift errors? not clear.
 
@@
 
-{Frigyik et al.}\ \citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
+Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, % TODO is the "number of draws" equal to our parameter N?
+if so, did we check the sensitivity of this approximation to small N?
+based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
 We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
@@
 \paragraph{Numerical validation.}
-To validate our analytical result (\Cref{cor:dirichlet}) and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
-First, we {compute} an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
+To validate our analytical result (\Cref{cor:dirichlet}) % TODO again be more explicit what it is you are validating
+and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
+% Also not clear what is the "full model" - ref to equation, and explain - you are comparing the DM approximation (result 2?
+corollary 3?
+eq 16?
+what?) to results of simulations of the model (not full), eq 10?
+First, we compute an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
 We then {compare} this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A).
@@
 Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
-{That} the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
+That the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
 We examined the robustness of the DM approximation to relaxing the approximation assumptions.
+% TODO which assumptions?
+those given in result 2?
+if so, refer to them directly and repeat them (e=ej, alpha=alpha_j).
 First, we relaxed our assumption of no estimation error $e$.
 Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
-When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
+When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance). % TODO Not clear what “varying scale (variance)” means
 Even when the standard deviation is $0.1$, the fixation probability and time {are} similar~(\Cref{fig:hetro_error}). 
@@
 \subsection*{Fixation probability and time}
-
+% TODO check that is its clear we are using the dichotomous model here
 After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
@@
 
+% TODO I'm not sure this needs to be a "Results" - I think we can write it here as apart of the analysis, which gives Result 4. Also, where is the actual proof of the equation in this result?
 \begin{result}[Drift and diffusion terms in a constant environment]
 Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
+% TODO can we say beta=beta(A)/beta(hat A) ? then we dont force beta(hat A)=1
 Then,
-\begin{equation}
+\begin{equation} % TODO remove \approx and instead add big-O notation
 E[x'-x] \approx x(1-x)(1-\beta) \;, 
@@
   Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
-   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (A and B), $A = a \cdot \hat{A}$ with $0.01 \le a \le 0.99$ (panels C and D); success coefficient, $1-\beta=s=0.044$ (A and B); success-bias weight, $\alpha=0.01$ (panels C and D).}
+   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (panels A and B), 
+   $A = a \cdot \hat{A}$ with $0.01 \le a \le 0.99$ (panels C and D); % TODO this is not clear
+   success coefficient, $1-\beta=s=0.044$ (panels A and B); 
+   success-bias weight, $\alpha=0.01$ (panels C and D).
+   }
   \label{fig:var_alpha}
@@
 \end{equation}
-where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$.
+where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$. % TODO beta_t is note defined - maybe in the appendix? needs. to be defined above, before the reference to the appendix
 \end{result}
@@
 When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
-Markers show average of $10,000$ simulations, error bars show 75\% (A, C, and D) and 95\% (B) confidence intervals.
-  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$ (A and B), $A=0.8$ (C and D); In (A), the success coefficient is: $1-\beta=s=0.005$; In (B, C, and D) the success-bias weight is $\alpha=0.1$.}
+Markers show average of $10,000$ simulations, error bars show 75\% (panels A, C, and D) and 95\% (panel B) confidence intervals.
+  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$ (panels A and B) and $A=0.8$ (panels C and D); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B, C, and D, the success-bias weight is $\alpha=0.1$.
+  }
   \label{fig:ch_env_alpha_beta}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% TODO MWF thinks the paper is better without this paragraph; if we remove, we should also remove references to it from abstac/intro/discussion
 \subsection*{Adaptive success-bias weight}
@@
 {Although many} models assume that success can be accurately estimated{, it} has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
-This perceived success can be determined by performance {with respect to another trait (indirect)} \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.
+This perceived success can be determined by performance with respect to another trait (indirect) \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.
 
@@
 They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices with opposite characteristics had low levels of prestige.
+% TODO what is "opposite"?
+change this
 For example, they found that surgery counts as the most prestigious specialty, while psychiatry is the {least} prestigious.
@@
 	  = x \frac{1}{1 -(1-x)(1-\beta)}  \\
-	  &= x \big(1 + (1-x)(1-\beta) + o(\beta)\big)
-	  = x + x(1-x)(1-\beta) + o(\beta) \;,
+	  &= x \big(1 + (1-x)(1-\beta) + o(1-\beta)\big)
+	  = x + x(1-x)(1-\beta) + o(1-\beta) \;, 
 \end{split}
 \end{equation}
-following \citep[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
+following Durrett~\citep[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
 
@@
 
-Following \citep[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
+Following Durrett~\citep[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
 \begin{equation}
@@
 \end{equation}
-Now because $x$ is a constant, $V(x) = 0$, and therefore
+Now because $x$ is a constant, $V(x) = 0$, % TODO x is not a constant, go back to Durrett and check how to go from the previous equation to the next one
+and therefore
 \begin{equation}\label{eq:var_diff_durret}
@@
   \textbf{Numerical validation of the GB approximation.}
-  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models.
+  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. % TODO which two models?
   Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; {ideal} phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
@@
   \textbf{Numerical validation of the DM approximation.}
-  We performed computational "experiments" of the role-model choice process and compared them to the DM distribution. 
-  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the experiments (blue) is very small. 
-  \textbf{(B)} The log-likelihood of the DM distribution for results of the experiments (red vertical line) is much higher {than} the log-likelihood of permutations of experiments (blue histogram).
-  Here, population size, $N=100$; number of experiments, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
+  We performed computational simulations of the role-model choice process and compared them to the DM distribution. % TODO it is not clear what's being compared here
+  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
+  \textbf{(B)} The log-likelihood of the DM distribution for results of the simulations (red vertical line) is much higher {than} the log-likelihood of permutations of simulations (blue histogram).
+  Here, population size, $N=100$; number of simulations, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
   No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
@@
    \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variation in success bias weight.Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$; phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
+   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variation in success bias weight.
+Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
+  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$; % TODO what is x here?
+  phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
   \label{fig:hetro_alpha}

### 2023-03-25 ms/ms.tex
update

@@
 Influence bias also differs from {conformity}, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
-% TODO check this - is influence frequency dependent?
 
@@
 We follow the {Boyd and Richerson model} \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
-% TODO If you omit the indirect trait, it is no longer indirect transmission.
 {Consider} a population of $N$ individuals, described by a single trait {that takes continuous values}.
-Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait.
-% We need to mention that each copier chooses one role model out of the entire population; this is different from other models studied by Feldman and colleagues in which the population is infinite and each copier samples n role models, and uses those n role models to determine its trait:
-%  Denton, Kaleda K, Yoav Ram, and Marcus W.
-Feldman.
-2023.
-“Conditions That Favour Cumulative Cultural Evolution.” Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
-https://doi.org/10.1098/rstb.2021.0400.
-% Denton, Kaleda Krebs, Yoav Ram, Uri Liberman, and Marcus W.
-Feldman.
-2020.
-“Cultural Evolution of Conformity and Anticonformity.” Proceedings of the National Academy of Sciences 117 (24): 13603–14.
-https://doi.org/10.1073/pnas.2004102117.
-% Boyd & Richerson book
+Each generation, $N$ naive individuals, or copiers, choose a single individual from the entire previous generation, or role-models, from which they will copy their trait.
+This is different than the usual models studied by Feldman et al \citep{cumul_culture,anticonformity} or Boyd \& Richerson \citep{evolutionBook}, where the population is infinite and each copier samples $n$ role-models, and copies the trait from them.
 Similar to a Wright-Fisher model, {generations are non-overlapping, and}  the entire population is replaced in each generation.
@@
 We found two approximations for the distribution of $\vec{K}_{N}$, summarized here and explained in detail below.
-In both we assume that the bias weight is completely homogeneous, $\alpha_{i,j}=\alpha$ (it is also enough to assume that $\alpha_j$ is a bias of role-model $j$ only, that is, it does not vary between copiers).
-% TODO but result 1 has alpha_i
+In both we assume that the bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_j$ is a bias of role-model $j$ only, meaning it does not vary between copiers.
 Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.
@@
 
-\begin{corollary} The expected number of copiers of role-model $j$ after all copiers have chosen a role-model is
+\begin{corollary}\label{cor:GBD} The expected number of copiers of role-model $j$ after all copiers have chosen a role-model is
 $\E[K_{N,j}] = N \cdot G_{1,j}$, where $G_{1,j}$ is the probability of the first copier to copy role-model $j$.
+In addition, $\E[K_{N, j}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
 \end{corollary}
@@
 \begin{proof}
-{Drezner and Farnum} \citep[eq.~(2.3)]{GBD} show that 
-$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation). % TODO what is E[k]?
+{Drezner and Farnum} \citep[eq.~(2.3)]{GBD} show that the expected number of successful trials, 
+$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
 $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
@@
 \end{proof}
-
-\begin{corollary}\label{cor:GBD} % TODO merge with the previous corollary
-$\E[K_{N, j}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
-\end{corollary}
 
@@
 \paragraph{Numerical validation.}
-To validate our results  % TODO be more explicit - what exactly are you validating?
+To validate that our approximation is correct
 we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
 We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \Cref{cor:GBD}.
-We used the average of the $1,000$ simulations to eliminate drift errors, as can be seen in \Cref{fig:GBD}. % TODO what are drift errors? not clear.
 
@@
 
-Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, % TODO is the "number of draws" equal to our parameter N?
-if so, did we check the sensitivity of this approximation to small N?
+Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, $N$ in our model,
 based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
@@
 \paragraph{Numerical validation.}
-To validate our analytical result (\Cref{cor:dirichlet}) % TODO again be more explicit what it is you are validating
-and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the full model.
-% Also not clear what is the "full model" - ref to equation, and explain - you are comparing the DM approximation (result 2?
-corollary 3?
-eq 16?
-what?) to results of simulations of the model (not full), eq 10?
+To validate our model can be approximated by the Dirichlet distribution properly, i.e  (\Cref{cor:dirichlet}),
+and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the model, meaning we compare \Cref{cor:dirichlet} to  \Cref{eq:binary-model}.
 First, we compute an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
@@
 That the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
-We examined the robustness of the DM approximation to relaxing the approximation assumptions.
-% TODO which assumptions?
-those given in result 2?
-if so, refer to them directly and repeat them (e=ej, alpha=alpha_j).
+We examined the robustness of the DM approximation to relaxing the following assumptions.
 First, we relaxed our assumption of no estimation error $e$.
 Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
-When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance). % TODO Not clear what “varying scale (variance)” means
+When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution.
 Even when the standard deviation is $0.1$, the fixation probability and time {are} similar~(\Cref{fig:hetro_error}). 
@@
 \subsection*{Fixation probability and time}
-% TODO check that is its clear we are using the dichotomous model here
 After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
@@
 We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
-For simplicity, we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
+For simplicity, we use the dichotomous model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
 As shown above, transmission in our model is approximately DM distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
@@
 
-% TODO I'm not sure this needs to be a "Results" - I think we can write it here as apart of the analysis, which gives Result 4. Also, where is the actual proof of the equation in this result?
 \begin{result}[Drift and diffusion terms in a constant environment]
 Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
-% TODO can we say beta=beta(A)/beta(hat A) ? then we dont force beta(hat A)=1
+
 Then,
-\begin{equation} % TODO remove \approx and instead add big-O notation
-E[x'-x] \approx x(1-x)(1-\beta) \;, 
+\begin{equation} 
+E[x'-x] = \mathcal{O} (x(1-x)(1-\beta)) \;, 
 \quad
-V(x'-x) \approx x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big) \;.
+V(x'-x) = \mathcal{O} (x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big)) \;.
 \end{equation} 
@@
 
-% TODO SAAR check these equations vs what you have in the source code
 \begin{result}[Fixation time] The {expected} fixation time (conditioned on fixation) from an initial frequency $x$ is approximately
@@
 \begin{aligned}
-J_1(x) &= \frac{2}{(1-\beta)(1-e^{-2S})}\int_x^1 \frac{(e^{2S\xi}-1)(e^{-2S\xi}-e^{-2S})}{\xi(1-\xi)}d\xi \;, \\
-J_2 (x) &= \frac{2}{(1-\beta)(1-e^{-2S})}\int_0^x \frac{(e^{2S\xi}-1)(1-e^{-2S\xi})}{\xi(1-\xi)}d\xi \;.
+J_1(x) &= \frac{-1}{(1-\beta)(e^{-2S}-1)}\int_x^1 \frac{1-e^{2S\xi}-e^{-2S(1-\xi)}+e^{-2S}}{\xi(1-\xi)}d\xi \;, \\
+J_2(x) &= \frac{-1}{(1-\beta)(e^{-2S}-1)}\int_0^x \frac{(1-e^{2S\xi})(e^{-2S\xi}-1)}{\xi(1-\xi)}d\xi \;.
 \end{aligned}
@@
    Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (panels A and B), 
-   $A = a \cdot \hat{A}$ with $0.01 \le a \le 0.99$ (panels C and D); % TODO this is not clear
+   $A = a \cdot \hat{A}$ , where $a$ is a modifier such that $0.01 \le a \le 0.99$ (panels C and D);
    success coefficient, $1-\beta=s=0.044$ (panels A and B); 
@@
 \end{equation}
-where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$. % TODO beta_t is note defined - maybe in the appendix? needs. to be defined above, before the reference to the appendix
+where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$.
 \end{result}
@@
 \paragraph{Numerical validation.}
-% TODO SAAR edit this section
-Comparing our approximation (\cref{eq:ch_env}) to simulations, we find that the approximation fits simulation results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
+To validate that \Cref{eq:ch_env} can approximate our dichotomous model, we compared the results of this equation against simulations using \Cref{cor:dirichlet}.
+We find that the approximation fits the simulation results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
 
@@
 {Norredam and Album} \citep{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
-They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices with opposite characteristics had low levels of prestige.
-% TODO what is "opposite"?
-change this
+They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices that weren't of these types had low levels of prestige.
 For example, they found that surgery counts as the most prestigious specialty, while psychiatry is the {least} prestigious.
@@
 
+\bibitem{cumul_culture}Denton, Kaleda K, Yoav Ram, and Marcus W.
+Feldman.
+2023.
+“Conditions That Favour Cumulative Cultural Evolution.” Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
+https://doi.org/10.1098/rstb.2021.0400.
+
 \end{thebibliography}
@@
 \end{equation}
-Now because $x$ is a constant, $V(x) = 0$, % TODO x is not a constant, go back to Durrett and check how to go from the previous equation to the next one
+Now because $x$, the initial frequency, is a constant, $V(x) = 0$,
 and therefore
@@
   \textbf{Numerical validation of the GB approximation.}
-  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. % TODO which two models?
+  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. 
   Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; {ideal} phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
@@
   \textbf{Numerical validation of the DM approximation.}
-  We performed computational simulations of the role-model choice process and compared them to the DM distribution. % TODO it is not clear what's being compared here
+  We performed computational simulations of the role-model choice process, i.e the fully iterative process, and compared them to the results of simulations using the DM distribution approximation.
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
@@
 Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$; % TODO what is x here?
+  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$ where $e^{-7}\le x \le e^{-1}$; 
   phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	

### 2023-03-28 ms/ms.tex
reviewed changes by SE, added comments

@@
 
-% TODO edit so that we focus on indirect success - aka prestige - and decompose it to content based - which we call success - and context based - which we call influence
 {Boyd and Richerson} \citep[Ch.~5]{evolutionBook} suggested that the {assessment} of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
@@
 A broader definition of prestige is the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
-Indeed, {Chudek et al.}\ \citep{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
+Indeed, Chudek et al.~\citep{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
 {Henrich and Gil-White} \citep{prestige_evolution} gave a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature.
@@
 To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
-This is an important distinction, as influence is a context-{dependent} bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that {have} already copied each role-model, which may be easier and more accurate to estimate {than} success.
-Influence bias also differs from {conformity}, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
-
-In contemporary human society, social media {make} it especially easy to estimate the social and cultural influence individuals have over others, {which} can have an effect on decision making.
-Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices {have been} invented to capitalize on this effect \citep{facebook_marketing}.
-
-In the following, we develop a stochastic model of cultural transmission with prestige bias {that} combines both cross-domain indirect success bias and influence bias.
+This is an important distinction, as influence is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
+%TODO check this - is influence frequency dependent?
+Influence bias also differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+
+In contemporary human society, social media make it especially easy to estimate the social and cultural influence individuals have over others, which can have an effect on decision making.
+Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices have been invented to capitalize on this effect \citep{facebook_marketing}.
+
+In the following, we develop a stochastic model of cultural transmission with prestige bias that combines both cross-domain indirect success bias and influence bias.
 We develop analytic approximations for this model and analyze its dynamics.
-We {also} find approximations for the probability and time {to} fixation of a `successful' phenotype (i.e., that is {subject to} success bias).
+We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is {subject to} success bias).
 Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.
@@
 
-We begin with a continuous trait model with indirect bias suggested by {Boyd and Richerson} \citep{evolutionBook}, propose an extension with influence bias, and then develop a model with a dichotomous trait.
-We implement our stochastic models and approximations, {perform} statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
+We begin with a continuous trait model with indirect bias suggested by Boyd and Richerson~\citep{evolutionBook}, propose an extension with influence bias, and then develop a model with a dichotomous trait.
+We implement our stochastic models and approximations, perform statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
 Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
@@
 \subsection*{Continuous trait}
-We follow the {Boyd and Richerson model} \citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
-{Consider} a population of $N$ individuals, described by a single trait {that takes continuous values}.
-Each generation, $N$ naive individuals, or copiers, choose a single individual from the entire previous generation, or role-models, from which they will copy their trait.
-This is different than the usual models studied by Feldman et al \citep{cumul_culture,anticonformity} or Boyd \& Richerson \citep{evolutionBook}, where the population is infinite and each copier samples $n$ role-models, and copies the trait from them.
-Similar to a Wright-Fisher model, {generations are non-overlapping, and}  the entire population is replaced in each generation.
-The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t${, and}  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
+%TODO If you omit the indirect trait, it is no longer indirect transmission.
+We follow the Boyd and Richerson model~\citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
+Consider a population of $N$ individuals, described by a single trait that takes continuous values.
+Each generation, $N$ naive individuals, or copiers, each chooses a single role-model from the entire previous generation. The copier than copies its trait value from the chosen role-model.
+Note that our transmission models is slightly different than previous those modeled before, e.g.
+\citep{cumul_culture,anticonformity,evolutionBook}, in which the population is infinite and each copier samples $n$ role-models and then copies its trait from one or more of the sampled role-models.
+
+Similar to a Wright-Fisher model, generations are non-overlapping, and the entire population is replaced in each generation.
+The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t$, and  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
 Cultural transmission is modeled by a function $F$ such that 
@@
 \paragraph{Success bias.}
-{Boyd and Richerson} \citep[Ch.~8, p.~247-249]{evolutionBook} describe a  transmission algorithm by defining $F$, a weighted average of the traits of all role-models, as
+Boyd and Richerson~\citep[Ch.~8, p.~247-249]{evolutionBook} describe a  transmission algorithm by defining $F$, a weighted average of the traits of all role-models, as
 \begin{equation}\label{eq:boydF}
@@
 
-{Boyd and Richerson} \citep{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
-We {can} develop a similar stochastic model with transmission from a single random role-model{\ where instead} of \cref{eq:boydF}, we define the transmission function $F$ as a random variable with its distribution given by
+Boyd and Richerson~\citep{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
+We {can} develop a similar stochastic model with transmission from a single random role-model where instead of \cref{eq:boydF}, we define the transmission function $F$ as a random variable with its distribution given by
 \begin{equation}\label{eq:ourF}
@@
 \paragraph{Influence bias.}
-Here we introduce a new element to the model {by assuming} that in each generation, copiers choose their role-models one by one.
+Here we introduce a new element to the model by assuming that in each generation, copiers choose their role-models one by one.
 {Denote by} $K_{i,j}$  the number of copiers that {choose} role-model $j$ after copier $i$ chose a role-model.
@@
 We found two approximations for the distribution of $\vec{K}_{N}$, summarized here and explained in detail below.
-In both we assume that the bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_j$ is a bias of role-model $j$ only, meaning it does not vary between copiers.
+In both we assume that the bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_j$ is a bias of role-model $j$ only, meaning it does not vary between copiers.% TODO but result 1 has alpha_i
 Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.
@@
 where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
-\Cref{recursive} is equivalent to eq.~(2.1) by \citep{GBD}, which completes the proof.
+\Cref{recursive} is equivalent to eq.~(2.1) in \citep{GBD}, which completes the proof.
 \end{proof}
-This result gives the following two corollaries on the expected number of followers of a given role-model $j$ by the end of the role-model choice process, $K_{N,j}$.
+
+This result gives the following corollary on the expected number of followers of a given role-model $j$ by the end of the role-model choice process, $K_{N,j}$.
 The proof of \Cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
@@
 \begin{proof}
-{Drezner and Farnum} \citep[eq.~(2.3)]{GBD} show that the expected number of successful trials, 
-$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
+Drezner and Farnum~\citep[eq.~(2.3)]{GBD} show that the expected number of successful trials, 
+$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation). % TODO what is k? not defined.
 $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
 $Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
+% TODO where is the proof for the second part of the corollary??
 \end{proof}
@@
 \begin{equation}\label{eq:linearEq}
-\E[K_{Nj}] = L\cdot \beta(A_j+e) \;.
+\E[K_{N,j}] = L\cdot \beta(A_j+e) \;.
 \end{equation}
@@
 \paragraph{Numerical validation.}
-To validate that our approximation is correct
+To validate that our approximation is correct, % TODO which approximation?? be explicit. refer to an equation. tell us what you are approximating.
 we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
@@
 
-Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, $N$ in our model,
+Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity (the population size, $N$, in our model), % TODO did we check sensitivity of the approximation to small values of N?
+if so, refer to it here.
 based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
@@
 \paragraph{Numerical validation.}
-To validate our model can be approximated by the Dirichlet distribution properly, i.e  (\Cref{cor:dirichlet}),
-and test its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) we compare it to results of stochastic simulations of the model, meaning we compare \Cref{cor:dirichlet} to  \Cref{eq:binary-model}.
-First, we compute an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then {compare} this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A).
+We next validated the DM approximation of our model
+and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DM approximation (\Cref{cor:dirichlet}).
+First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
+We then compared this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A).
 The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
-The maximum difference is 0.5 role-models, which {indicates} a very good fit.
+The maximum difference is 0.5 role-models, which indicates a very good fit.
 In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself (\Cref{fig:DM_validation}B).
-We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, {strongly} supporting our approximation.
+We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, strongly supporting our approximation.
 
@@
 Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
-When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution.
-Even when the standard deviation is $0.1$, the fixation probability and time {are} similar~(\Cref{fig:hetro_error}). 
+When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$. % TODO J_i? e_i?
+Even when the estimation error variance is $0.1$, both the fixation probability and fixation time approximations are accurate~(\Cref{fig:hetro_error}). 
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
@@
 
+% TODO I'm not sure this needs to be a "Results" - I think we can write it here as apart of the analysis, which gives Result 4. Also, where is the actual proof of the equation in this result?
 \begin{result}[Drift and diffusion terms in a constant environment]
-Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
-
+Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ be the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
+% TODO can we say beta=beta(A)/beta(hat A) ? then we dont force beta(hat A)=1
 Then,
 \begin{equation} 
+% TODO the use of big O is incorrect... 
 E[x'-x] = \mathcal{O} (x(1-x)(1-\beta)) \;, 
@@
 
-\begin{result}[Fixation time] The {expected} fixation time (conditioned on fixation) from an initial frequency $x$ is approximately
+\begin{result}[Fixation time] The expected fixation time (conditioned on fixation) from an initial frequency $x$ is approximately
 \begin{equation} \label{eq:kimura_t}
@@
    Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (panels A and B), 
-   $A = a \cdot \hat{A}$ , where $a$ is a modifier such that $0.01 \le a \le 0.99$ (panels C and D);
+   $A/\hat{A}$, is between 0.01 and 0.99 (panels C and D); % TODO not clear, because x label suggest you modify beta, but caption says you modify A/hatA
    success coefficient, $1-\beta=s=0.044$ (panels A and B); 
@@
 \paragraph*{Changing environment}.
-After finding a good approximation in {a} constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for {when the environment changes}.
+After finding a good approximation in a constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for when the environment changes.
 Following \citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
@@
 \begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
-Let $x$ be the initial frequency of the invading phenotype and $X_t$ {the} number of individuals with {that} phenotype after $n$ generation.
+Let $x$ be the initial frequency of the invading phenotype and $X_t$ the number of individuals with that phenotype after $n$ generation.
 Then,
@@
 where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$.
+% TODO define more explicitly - connect it to the paragraph above that explains that the environment changes
 \end{result}
@@
 \paragraph{Numerical validation.}
-To validate that \Cref{eq:ch_env} can approximate our dichotomous model, we compared the results of this equation against simulations using \Cref{cor:dirichlet}.
+To validate the the approximation for the fixation probability in a changing environment (\cref{eq:ch_env}), we compare it to results of simulations that use the DM approximation (\Cref{cor:dirichlet}).
 We find that the approximation fits the simulation results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
@@
 {Prestige bias also occurs} in more modern domains such as western medicine.
-{Norredam and Album} \citep{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
-They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices that weren't of these types had low levels of prestige.
+Norredam and Album~\citep{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
+They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices that were not of these types had low levels of prestige.
 For example, they found that surgery counts as the most prestigious specialty, while psychiatry is the {least} prestigious.
@@
 \end{equation}
-Now because $x$, the initial frequency, is a constant, $V(x) = 0$,
+The current frequency $x$ is a given, such that $V(x) = 0$,
 and therefore
@@
   \textbf{Numerical validation of the DM approximation.}
-  We performed computational simulations of the role-model choice process, i.e the fully iterative process, and compared them to the results of simulations using the DM distribution approximation.
+  We performed computational simulations of the role-model choice process and compared them to the results of simulations using the DM distribution approximation.
+  % TODO but what are these "results"?
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
@@
    Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variation in success bias weight.
+% TODO variation between...
+copiers?
+role-models?
    Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha\sim N(0.5,x^2)$ where $e^{-7}\le x \le e^{-1}$; 
+  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha \sim N(0.5,\epsilon^2)$ where $e^{-7}\le \epsilon \le e^{-1}$; % TODO not clear to me: the x axes shows alpha, so how can alpha also be normally distributed ?
   phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	

### 2023-03-28 ms/ms.tex
todos during discussion with SE

@@
 For example, an individual observing a ping-pong match can {try} the observed paddle grips to determine which grip is better.
-{Frequency}-dependent bias occurs when the probability {of copying} a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
+Frequency-dependent bias occurs when the probability {of copying} a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
 For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{{anti}-conformity} \citep{conformism}.
 The effects of conformity and {anti}-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
-{Indirect} bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
+Indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
+% TODO change this to indirect evaluation instead of two phenotypes because we dont have two phenotypes
 For example, an observer may copy the paddle grip of the {ping}-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
-{However, this} may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
+However, this may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
 Furthermore, {Boyd and Richerson} \citep[Ch.
@@
 This is an important distinction, as influence is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
-%TODO check this - is influence frequency dependent?
-Influence bias also differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+Influence bias is also frequency independent (see \cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
 
@@
 \section*{Models}
-
+% TODO explain indirect bias as indirect evaluation
 We begin with a continuous trait model with indirect bias suggested by Boyd and Richerson~\citep{evolutionBook}, propose an extension with influence bias, and then develop a model with a dichotomous trait.
@@
 \subsection*{Continuous trait}
-%TODO If you omit the indirect trait, it is no longer indirect transmission.
-We follow the Boyd and Richerson model~\citep{evolutionBook}, assuming only oblique transmission of the trait and omitting the indirect trait in order to reduce model complexity. 
+We follow the Boyd and Richerson model~\citep{evolutionBook}, assuming only oblique transmission of a single trait. 
 Consider a population of $N$ individuals, described by a single trait that takes continuous values.
@@
 \begin{equation}\label{eq:prestige}
-G_{i,j} = \frac{\alpha_{ij} \cdot \beta(A_{i,j}) + (1-\alpha_{ij}) \cdot K_{i-1,j}}{W_i} \;.
-\end{equation}
-
-Here, the bias weight $\alpha_{ij}$ determines the relative weighting of success and influence bias.
+G_{i,j} = \frac{\alpha_{ij} \cdot \beta(A_{i,j}) + (1-\alpha_{ij}) \cdot K_{i-1,j}}{W_i} \;,
+\end{equation}
+where $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
+
+Here, the bias weight $\alpha_{i,j}$ determines the relative weighting of success and influence bias.
 It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs.
 influence in the role-model's overall prestige in the eyes of the copier.
-
-{Different individuals} may evaluate the importance of success and influence differently.
-Additionally, we assume {each} role-model displays {its} influence and success individually.
-For example, {individuals} with more followers but {lacking} skill may emphasize the number of {their} followers rather than {their} skill.
-%We therefore defined $\alpha_{i,j}$ to be the relation between every copier's intrinsic significance of estimation, and every role-model's personal emphasis.
-
-The trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}, and $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
+Different individuals may evaluate the importance of success and influence differently.
+Additionally, we assume each role-model displays its influence and success individually.
+For example, individuals with more followers but lacking skill may emphasize the number of their followers rather than their skill.
+Finally, the trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}.
 
@@
 We found two approximations for the distribution of $\vec{K}_{N}$, summarized here and explained in detail below.
-In both we assume that the bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_j$ is a bias of role-model $j$ only, meaning it does not vary between copiers.% TODO but result 1 has alpha_i
+In both we assume that the bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_{i,j}=\alpha_j$ is a bias of role-model $j$ only, meaning it does not vary between copiers.
+%TODO but result 1 has alpha_i
 Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.
@@
 The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$.
+% TODO what about theta?
 \end{result}
@@
 This result gives the following corollary on the expected number of followers of a given role-model $j$ by the end of the role-model choice process, $K_{N,j}$.
-The proof of \Cref{cor:GBD} is in Appendix~\ref{sec:GBD}.
 \\
@@
 Drezner and Farnum~\citep[eq.~(2.3)]{GBD} show that the expected number of successful trials, 
-$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation). % TODO what is k? not defined.
-$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
-$Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
-% TODO where is the proof for the second part of the corollary??
+$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation). %TODO what is k? not defined.
+Here, $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
+$Q_j(1,1) = G_{1,j}$ by definition.
+The rest of the proof is in Appendix~\ref{sec:GBD}.
 \end{proof}
 
+%% TODO two sentences - influence bias is not frequency dependent
+
 The special case where the bias weight is uniform for all role-models ($\alpha = \alpha_j$ for $j=1,\ldots, N$) is interesting, because we can evaluate the expected number of copiers using a linear equation
-\begin{equation}
-\E[K_{Nj}]= N\cdot\frac{\alpha\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N}\alpha\cdot\beta(A_m+e)} =\beta(A_j+e) \bigg/ \overline{\beta(A+e)} \;,
+\begin{equation}\label{eq:GBDsamelalpha}
+\E[K_{N,j}]= N\cdot\frac{\alpha\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N}\alpha\cdot\beta(A_m+e)} =\beta(A_j+e) \bigg/ \overline{\beta(A+e)} \;,
 \end{equation}
 where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution of the trait values, modified by some constant parameters of $\beta$.
-We can then {write} $L = 1/\overline{\beta(A+e)}$ and
+We can then write $L = 1/\overline{\beta(A+e)}$ and
 \begin{equation}\label{eq:linearEq}
@@
 \paragraph{Numerical validation.}
-To validate that our approximation is correct, % TODO which approximation?? be explicit. refer to an equation. tell us what you are approximating.
+To validate that GBD approximation for the number of copiers of a role-model is correct (\cref{eq:GBDsamelalpha}), %TODO check that this is the correct equation reference
 we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
@@
 
-Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity (the population size, $N$, in our model), % TODO did we check sensitivity of the approximation to small values of N?
-if so, refer to it here.
-based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
+Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws  (the population size, $N$, in our model) approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
 We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
@@
 \paragraph{Numerical validation.}
+% TODO add something about small N
 We next validated the DM approximation of our model
@@
 First, we relaxed our assumption of no estimation error $e$.
-Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
-When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$. % TODO J_i? e_i?
+Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{i,j} = A_j + e_i$).
+When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$. % TODO should e_i?
 Even when the estimation error variance is $0.1$, both the fixation probability and fixation time approximations are accurate~(\Cref{fig:hetro_error}). 
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
-We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,q)$ where $q \in [10^{-7},10^{-1}]$.
+We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,q)$ where $\epsilon$ is between $10^{-7}$ and $10^{-1}$.
 We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).
@@
 
+\paragraph{Drift and diffusion terms in a constant environment.}
 We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.
-The proof is in Appendix~\ref{sec:drift_diff_const}.
+Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ be the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
+% TODO can we say beta=beta(A)/beta(hat A) ? because beta(A hat)=b and not 1.
+Then (see Appendix~\ref{sec:drift_diff_const} for derivation),
+\begin{equation}\begin{aligned}
+E[x'-x] &= (x(1-x)(1-\beta) + o(1-\beta)  \;, 
 \\
-
-% TODO I'm not sure this needs to be a "Results" - I think we can write it here as apart of the analysis, which gives Result 4. Also, where is the actual proof of the equation in this result?
-\begin{result}[Drift and diffusion terms in a constant environment]
-Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ be the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
-% TODO can we say beta=beta(A)/beta(hat A) ? then we dont force beta(hat A)=1
-Then,
-\begin{equation} 
-% TODO the use of big O is incorrect... 
-E[x'-x] = \mathcal{O} (x(1-x)(1-\beta)) \;, 
-\quad
-V(x'-x) = \mathcal{O} (x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big)) \;.
-\end{equation} 
-\end{result}
+V(x'-x) &= x(1-x)\left(\frac{1}{\alpha N + (1-\alpha)}\right) + o\left(\frac{1}{\alpha N + (1-\alpha)}\right) \;.
+\end{aligned}\end{equation}
 
@@
 \begin{equation}
-s=1-\beta(A), \quad N_e=\alpha N + (1-\alpha) \;.
+s=1-\beta, \quad N_e=\alpha N + (1-\alpha) \;.
 \end{equation}
@@
   Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
-   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$ (panels A and B), 
-   $A/\hat{A}$, is between 0.01 and 0.99 (panels C and D); % TODO not clear, because x label suggest you modify beta, but caption says you modify A/hatA
+   Here, Population size, $N=1,000$; phenotype values, $A=0.7$ (panels A and B), 
+   $A/\hat{A}$ is between 0.01 and 0.99 (panels C and D), and $\hat{A}=1$; % TODO not clear, because x label suggest you modify beta, but caption says you modify A/hatA.
+remind us that beta is given from A - refer to equation
    success coefficient, $1-\beta=s=0.044$ (panels A and B); 
@@
 
+% TODO same as above, the derivation of drift and diffusion doesnt have to be a result of its own, but rather the fixation prob can be a result
 \begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
@@
 \end{equation}
-where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$.
-% TODO define more explicitly - connect it to the paragraph above that explains that the environment changes
+where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$. % TODO define more explicitly how environmental change affects A and beta. define it before the result!
 \end{result}
@@
 \begin{equation}
-\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
+\E[K_{N,j}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
 \end{equation}

### 2023-03-30 ms/ms.tex
update

@@
 The effects of conformity and {anti}-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
-Indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
-% TODO change this to indirect evaluation instead of two phenotypes because we dont have two phenotypes
+Indirect bias occurs when an individual uses a phenotype to evaluate the attractiveness of another individual. 
 For example, an observer may copy the paddle grip of the {ping}-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
@@
 This is an important distinction, as influence is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
-Influence bias is also frequency independent (see \cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+Influence bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
 
@@
 \section*{Models}
-% TODO explain indirect bias as indirect evaluation
 We begin with a continuous trait model with indirect bias suggested by Boyd and Richerson~\citep{evolutionBook}, propose an extension with influence bias, and then develop a model with a dichotomous trait.
+The indirect bias is due to an indirect evaluation, using a certain trait to determine success of others.
+
 We implement our stochastic models and approximations, perform statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
@@
 In both we assume that the bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_{i,j}=\alpha_j$ is a bias of role-model $j$ only, meaning it does not vary between copiers.
-%TODO but result 1 has alpha_i
 Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.
@@
 \subsection*{Generalized binomial distribution}
-The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is {denoted}  by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).
+The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is {denoted}  by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials.
+$\theta$ can be calculated from data using maximum likelihood estimation, but its value is irrelevant for our proof.
+Note that $\theta=0$ gives the standard binomial distribution.
 \\
@@
 \begin{result}[Generalized binomial approximation]\label{res:GBD}
-The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$.
-% TODO what about theta?
+The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_j\cdot\beta(A_j+e),\theta)$ if $e_i=e$ for all role-models $i=1, \ldots, N$, and $\theta$ is a model parameter.
 \end{result}
@@
 Drezner and Farnum~\citep[eq.~(2.3)]{GBD} show that the expected number of successful trials, 
-$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation). %TODO what is k? not defined.
+$\E[k] = N \cdot Q_j(1,1)$, where $k$ is the number of copiers that chose role model $j$ (i.e successful trials).
 Here, $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
@@
 
-%% TODO two sentences - influence bias is not frequency dependent
+From \Cref{cor:GBD} we see that if there is no success bias, meaning $Q_j(1,1)=q$ for $j$ in $1,...,N$, then the expected number of copiers will be Binomial distributed.
+This proves that influence bias is not frequency dependent.
 
@@
 \paragraph{Numerical validation.}
-To validate that GBD approximation for the number of copiers of a role-model is correct (\cref{eq:GBDsamelalpha}), %TODO check that this is the correct equation reference
+To validate that GBD approximation for the number of copiers of a role-model is correct (\cref{eq:GBDsamelalpha}), % check that this is the correct equation reference. It is
 we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
@@
 \paragraph{Numerical validation.}
-% TODO add something about small N
 We next validated the DM approximation of our model
 and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DM approximation (\Cref{cor:dirichlet}).
+We did our validation on a relatively small population size $N=100$, showing that the approximation is very good for small $N$ as well, even though the Martingales proof requires $N$ to be very large.
 First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
@@
 Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{i,j} = A_j + e_i$).
-When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$. % TODO should e_i?
+When estimation error is applied, we sample $e_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$.
 Even when the estimation error variance is $0.1$, both the fixation probability and fixation time approximations are accurate~(\Cref{fig:hetro_error}). 
@@
 We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.
-Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ be the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
-% TODO can we say beta=beta(A)/beta(hat A) ? because beta(A hat)=b and not 1.
+Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ be the success coefficient of phenotype $A$, $\beta = \frac{\beta(A)}{\beta(\hat{A})} < 1$.
 Then (see Appendix~\ref{sec:drift_diff_const} for derivation),
-\begin{equation}\begin{aligned}
+\begin{equation}\label{eq:drift_diff}
+\begin{aligned}
 E[x'-x] &= (x(1-x)(1-\beta) + o(1-\beta)  \;, 
@@
    Here, Population size, $N=1,000$; phenotype values, $A=0.7$ (panels A and B), 
-   $A/\hat{A}$ is between 0.01 and 0.99 (panels C and D), and $\hat{A}=1$; % TODO not clear, because x label suggest you modify beta, but caption says you modify A/hatA.
-remind us that beta is given from A - refer to equation
+   $A/\hat{A}$ varies between 0.01 and 0.99 (panels C and D), and $\hat{A}=1$, which affects $\beta$ given in \Cref{eq:drift_diff};
    success coefficient, $1-\beta=s=0.044$ (panels A and B); 
@@
 Following \citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
+This means that during the $k$ generations of the cycle, $\beta=\frac{\beta(A)}{\beta(\hat{A})}$, where $\hat{A}$ is the invading phenotype.
+During the following $l$ generations of the cycle, the favored phenotype is switched, so that $\frac{\beta(A)}{\beta(\hat{A})}>1$.
 We then proceed to find expressions for the expectation and variance of the change in frequency between $n=k+l$ generations. 
@@
 
-% TODO same as above, the derivation of drift and diffusion doesnt have to be a result of its own, but rather the fixation prob can be a result
-\begin{result} [Drift and diffusion terms in a changing environment]\label{res:ch_expected}
+\paragraph{Drift and diffusion terms in a changing environment.}
 Let $x$ be the initial frequency of the invading phenotype and $X_t$ the number of individuals with that phenotype after $n$ generation.
@@
 \end{equation}
-where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$. % TODO define more explicitly how environmental change affects A and beta. define it before the result!
-\end{result}
+where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$.
+% define more explicitly how environmental change affects A and beta.
+define it before the result!
+(above)
 
 Note that here, we have the average selection coefficient during a cycle of $n$ generations as the selection coefficient {in} \cref{eq:kimura_p}.
-Using the drift and diffusion terms and following \citep{changeEnv}, we can approximate the fixation probability in a changing environment using
+Using the drift and diffusion terms and following \citep{changeEnv}, we can approximate the fixation probability in a changing environment.
+
+\begin{result}[Fixation probability in changing environment]\label{res:ch_expected}
 \begin{equation}\label{eq:ch_env}
@@
 \end{equation}
+\end{result}
 
@@
   \textbf{Numerical validation of the DM approximation.}
-  We performed computational simulations of the role-model choice process and compared them to the results of simulations using the DM distribution approximation.
-  % TODO but what are these "results"?
+  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared them to simulations when using the DM distribution approximation (\Cref{cor:dirichlet}).
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
@@
    \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variation in success bias weight.
-% TODO variation between...
-copiers?
-role-models?
+   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variance in success bias weight.
    Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success bias weight normally distributed, $\alpha \sim N(0.5,\epsilon^2)$ where $e^{-7}\le \epsilon \le e^{-1}$; % TODO not clear to me: the x axes shows alpha, so how can alpha also be normally distributed ?
+  Here, population size, $N=1000$; success bias weight is not homogeneous, but instead normally distributed, $\alpha \sim N(0.5,\epsilon^2)$ where $e^{-7}\le \epsilon \le e^{-1}$; 
   phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	

### 2023-04-16 ms/ms.tex
went over latest changes

@@
 The effects of conformity and {anti}-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
-Indirect bias occurs when an individual uses a phenotype to evaluate the attractiveness of another individual. 
-For example, an observer may copy the paddle grip of the {ping}-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
+Indirect bias occurs when a copier uses some observed phenotype to evaluate the attractiveness of a potential role-model. 
+For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
 However, this may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
@@
 \section*{Models}
-We begin with a continuous trait model with indirect bias suggested by Boyd and Richerson~\citep{evolutionBook}, propose an extension with influence bias, and then develop a model with a dichotomous trait.
-The indirect bias is due to an indirect evaluation, using a certain trait to determine success of others.
+We begin with a continuous trait model with indirect bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}.
+We extend this model to include influence bias.
+We then develop a dichotomous trait model.
+Note that the indirect bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
 
@@
 \subsection*{Generalized binomial distribution}
-The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is {denoted}  by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials.
-$\theta$ can be calculated from data using maximum likelihood estimation, but its value is irrelevant for our proof.
+The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is {denoted}  by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials (the latter can be estimated from data, but its value is insignificant for our approximation).
 Note that $\theta=0$ gives the standard binomial distribution.
@@
 \begin{result}[Generalized binomial approximation]\label{res:GBD}
-The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_j\cdot\beta(A_j+e),\theta)$ if $e_i=e$ for all role-models $i=1, \ldots, N$, and $\theta$ is a model parameter.
+The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the generalized binomial distribution, $K_{i,j} \sim GBD(i,\alpha_j\cdot\beta(A_j+e),\theta)$ if $e_i=e$ for all role-models $i=1, \ldots, N$, and $\theta$ is the correlation between successive role-model choices.
 \end{result}
@@
 \begin{proof}
-Drezner and Farnum~\citep[eq.~(2.3)]{GBD} show that the expected number of successful trials, 
-$\E[k] = N \cdot Q_j(1,1)$, where $k$ is the number of copiers that chose role model $j$ (i.e successful trials).
-Here, $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
-$Q_j(1,1) = G_{1,j}$ by definition.
+The expected value of the GBD is
+$\E[K_{N,j}] = N \cdot Q_j(1,1)$, see Drezner and Farnum~\citep[eq.~(2.3)]{GBD}.
+Here, $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made, such that $Q_j(1,1) = G_{1,j}$ by definition.
 The rest of the proof is in Appendix~\ref{sec:GBD}.
@@
 and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DM approximation (\Cref{cor:dirichlet}).
-We did our validation on a relatively small population size $N=100$, showing that the approximation is very good for small $N$ as well, even though the Martingales proof requires $N$ to be very large.
+We used a relatively small population size, $N=100$, thus validating that the approximation is in good agreement even for small $N$, despite the assumption of large $N$ in the proof by Frigyik et al.~\citep[section 2]{dirichlet}.
 First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
@@
 We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.
-Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ be the success coefficient of phenotype $A$, $\beta = \frac{\beta(A)}{\beta(\hat{A})} < 1$.
+Let $x$ and $x'$ be the frequency of phenotype $\hat{A}$ in a population with $N$ individuals in the current and next generation, respectively.
+We set $\beta$ to be the success bias of phenotype $A$ relative to phenotype $\hat{A}$, such that $\beta = \beta(A)/\beta(\hat{A}) < 1$.
 Then (see Appendix~\ref{sec:drift_diff_const} for derivation),
@@
 \begin{aligned}
-E[x'-x] &= (x(1-x)(1-\beta) + o(1-\beta)  \;, 
+E[x'-x] &= x(1-x)(1-\beta) + o(1-\beta)  \;, 
 \\
@@
 \begin{equation}
-s=1-\beta, \quad N_e=\alpha N + (1-\alpha) \;.
+s=1-\beta=\frac{\beta(\hat{A})-\beta(A)}{\beta(\hat{A})}, \quad N_e=\alpha N + (1-\alpha) \;.
 \end{equation}
@@
 
-Using our effective selection coefficient, $1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by \citep[eq.~8]{kimura}, we {obtain}:
+Using our effective selection coefficient, $s=1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by Kimura and Ohta~\citep[eq.~8]{kimura}, we obtain:
 \begin{result}[Fixation probability]
-The fixation probability is approximately
+The fixation probability of an invading phenotype favored by success bias is approximately 
 \begin{equation}\label{eq:kimura_p}
@@
 \end{equation}
-where $x$ is the initial frequency of the favored phenotype $\hat{A}$.
+where $x$ is the initial frequency of the invading phenotype.
 \end{result}
@@
    Here, Population size, $N=1,000$; phenotype values, $A=0.7$ (panels A and B), 
-   $A/\hat{A}$ varies between 0.01 and 0.99 (panels C and D), and $\hat{A}=1$, which affects $\beta$ given in \Cref{eq:drift_diff};
+   $A/\hat{A}$ varies between 0.01 and 0.99 (panels C and D), and $\hat{A}=1$, which affects $\beta$ via \cref{eq:drift_diff};
    success coefficient, $1-\beta=s=0.044$ (panels A and B); 
@@
 \paragraph*{Changing environment}.
-After finding a good approximation in a constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for when the environment changes.
+After finding a good approximation in a constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a periodically changing environment.
 Following \citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
-This means that during the $k$ generations of the cycle, $\beta=\frac{\beta(A)}{\beta(\hat{A})}$, where $\hat{A}$ is the invading phenotype.
-During the following $l$ generations of the cycle, the favored phenotype is switched, so that $\frac{\beta(A)}{\beta(\hat{A})}>1$.
-We then proceed to find expressions for the expectation and variance of the change in frequency between $n=k+l$ generations. 
+Thus, during the first $k$ generations of the environmental cycle, $\beta=\frac{\beta(A)}{\beta(\hat{A})}$<1, where $\hat{A}$ is the invading phenotype.
+During the following $l$ generations of the environmental cycle, the phenotype favored by success bias is switched, such that $\frac{\beta(A)}{\beta(\hat{A})}>1$.
+We then proceed to find expressions for the expectation and variance of the change in the frequency of phenotype $\hat{A}$ after $n=k+l$ generations. 
 The proof is in Appendix~\ref{sec:drift_diff_chang}.
@@
 \paragraph{Drift and diffusion terms in a changing environment.}
-Let $x$ be the initial frequency of the invading phenotype and $X_t$ the number of individuals with that phenotype after $n$ generation.
+Let $x$ be the initial frequency of the invading phenotype and $X_t$ the number of individuals with that phenotype after $n$ generations.
 Then,
@@
 where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$.
-% define more explicitly how environmental change affects A and beta.
-define it before the result!
-(above)
 
@@
 Using the drift and diffusion terms and following \citep{changeEnv}, we can approximate the fixation probability in a changing environment.
-
-\begin{result}[Fixation probability in changing environment]\label{res:ch_expected}
+\\
+
+\begin{result}[Fixation probability in a changing environment]\label{res:ch_expected}
+
+The fixation probability of an invading phenotype under periodical environmental changes is approximately
 \begin{equation}\label{eq:ch_env}
@@
 \end{equation}
+where $x$ is the initial frequency of the invading phenotype.
 \end{result}
@@
   We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared them to simulations when using the DM distribution approximation (\Cref{cor:dirichlet}).
+% TODO what is "them"??
+where is being compared??
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
@@
    \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high variance in success bias weight.
+   Fixation probability does not seem to be effected by variation in success bias weight between individuals. % TODO copiers? or role-models?
+    Thus, both the DM approximation (orange) and Kimura's equation (black line) have a good fit to results of stochastic simulations (blue).
    Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success bias weight is not homogeneous, but instead normally distributed, $\alpha \sim N(0.5,\epsilon^2)$ where $e^{-7}\le \epsilon \le e^{-1}$; 
+  Here, population size, $N=1000$; 
+  success bias weight is normally distributed, $\alpha \sim N(0.5,\epsilon^2)$ where $10^{-7}\le \epsilon \le 10^{-1}$;  % TODO alpha_j ? alpha_i?
+  % TODO not clear if epsilon or epsilon^2 should be written in the inequality: x label says variance but epsilon is standard variation.
   phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	

### 2023-04-30 ms/ms.tex
remove mwf comment
update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TODO MWF thinks the paper is better without this paragraph; if we remove, we should also remove references to it from abstac/intro/discussion
 \subsection*{Adaptive success-bias weight}
@@
   \textbf{Numerical validation of the DM approximation.}
-  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared them to simulations when using the DM distribution approximation (\Cref{cor:dirichlet}).
-% TODO what is "them"??
-where is being compared??
+  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared the distribution of the number of copiers to simulations when using the DM distribution approximation (\Cref{cor:dirichlet}).
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
@@
    \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   Fixation probability does not seem to be effected by variation in success bias weight between individuals. % TODO copiers? or role-models?
+   Fixation probability does not seem to be affected by variation in success bias weight between role-models.
     Thus, both the DM approximation (orange) and Kimura's equation (black line) have a good fit to results of stochastic simulations (blue).
@@
   Here, population size, $N=1000$; 
-  success bias weight is normally distributed, $\alpha \sim N(0.5,\epsilon^2)$ where $10^{-7}\le \epsilon \le 10^{-1}$;  % TODO alpha_j ? alpha_i?
-  % TODO not clear if epsilon or epsilon^2 should be written in the inequality: x label says variance but epsilon is standard variation.
+  success bias weight is normally distributed, $\alpha_j \sim N(0.5,\epsilon^2)$ where $10^{-7}\le \epsilon^2 \le 10^{-1}$; 
   phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	

### 2023-05-07 ms/ms.tex
update

@@
 \begin{abstract}
-{If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased. Prestige may be used as a proxy for successs.}
+{If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased. Prestige may be used as a proxy for success.}
 Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied  that role-model.

### 2023-10-25 ms/ms.tex
started response to reviewers

@@
 \usepackage[numbers,square,comma,sort]{natbib}
+\bibliographystyle{vancouver}
+\setcitestyle{numbers}
 \renewcommand{\bibsection}{}
@@
 
-{Heinrich and Broesch \citep{fijian_social_bias}  studied} such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
+Henrich and Broesch \citep{fijian_social_bias}  studied such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
 They {suggested} that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits
@@
 Consider a population of $N$ individuals, described by a single trait that takes continuous values.
-Each generation, $N$ naive individuals, or copiers, each chooses a single role-model from the entire previous generation. The copier than copies its trait value from the chosen role-model.
-Note that our transmission models is slightly different than previous those modeled before, e.g.
+Each generation, $N$ naive individuals, or copiers, each chooses a single role-model from the entire previous generation. The copier then copies its trait value from the chosen role-model.
+Note that our transmission models are slightly different from those modeled before, e.g.
 \citep{cumul_culture,anticonformity,evolutionBook}, in which the population is infinite and each copier samples $n$ role-models and then copies its trait from one or more of the sampled role-models.
@@
 Here we introduce a new element to the model by assuming that in each generation, copiers choose their role-models one by one.
+We formulate this assumption in the following.
 {Denote by} $K_{i,j}$  the number of copiers that {choose} role-model $j$ after copier $i$ chose a role-model.
@@
 \subsection*{Dichotomous trait}
-{We} introduce a simplified version where the trait {has only} two phenotypes: {an} optimal phenotype $\hat{A}$ and {a} sub-optimal phenotype $A$. 
-All role-models with the same phenotype will contribute to the probability {that} that phenotype {is} transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
+We introduce a simplified version of the above model where the trait has only two phenotypes: an optimal phenotype $\hat{A}$ and a sub-optimal phenotype $A$. 
+All role-models with the same phenotype will contribute to the probability that that phenotype is transmitted and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
 In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous, {which entails} exchangeability between role-models.
@@
 \begin{equation}\label{eq:binary-model}
-G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
-\end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$; $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model; assuming (without loss of generality) that $\beta(\hat{A})=1$; and defining $\alpha'= \frac{\alpha}{1-\alpha}$ as the odds ratio of the bias weight.
+G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i-1,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
+\end{equation}
+where $X$ is the number of role-models with trait $\hat{A}$; $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model; assuming that $\beta(\hat{A})=1$; and defining $\alpha'= \frac{\alpha}{1-\alpha}$ as the odds ratio of the bias weight.
 Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
-The rest of the details follow the continuous trait model.
 
@@
 \paragraph{Dirichlet-Multinomial approximation.}
-The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$), meaning that the order of copiers does not matter.
+The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$).
 
@@
 Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
-That the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
+We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
 We examined the robustness of the DM approximation to relaxing the following assumptions.
@@
 
-This analysis gives a surprising result relating the parameters $\alpha$ and $\beta$ to parameters of the classical Wright-Fisher model from population genetics:
+This analysis gives an interesting result relating the parameters $\alpha$ and $\beta$ to parameters of the classical Wright-Fisher model from population genetics:
 the selection coefficient $s$, a measure of the effect of natural selection on the change in frequency of genotypes, and the effective population size, $N_e$, a measure of the effect of random genetic drift on the change in frequency of genotypes.
-In a diffusion-equation approximation of the classical Wright-Fisher model, the expectation and variance of the change in frequency are $E[x'-x]=x+x(1-x)s+o(s)$ and $V[x'-x]=x(1-x)/N_e$ \citep[eq.~7]{kimura}{, respectively}.
+In a diffusion-equation approximation of the classical Wright-Fisher model, the expectation and variance of the change in frequency are $E[x'-x]=sx(1-x)+o(s)$ and $V[x'-x]=x(1-x)/N_e$ \citep[eq.~7]{kimura}{, respectively}.
 Therefore, we have the following result.\\
@@
 
-Using our effective selection coefficient, $s=1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by Kimura and Ohta~\citep[eq.~8]{kimura}, we obtain:
+Using our effective selection coefficient, $s=1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by Kimura~\citep[eq.~8]{kimura}, we obtain the following result.\\
+
 \begin{result}[Fixation probability]
@@
   The approximation (black; \cref{eq:kimura_p}) agrees with both DM simulations (green) and Wright-Fisher simulation (orange).
-  Fixation probability (A) is bounded by $2(1-\beta)$ (blue).
+  Fixation probability (A) is bounded by $2(1-\beta)$ (dashed line).
   Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
@@
 We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers {and hence is the same as conformity bias}.
-We model the these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
-
-Hence, {our model has} two ``nested'' stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
+We model these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
+
+Hence, our model has two ``nested'' stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
 To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DM, \Cref{cor:dirichlet}).
@@
 %\paragraph{Empirical evidence of prestige bias}
-{Chudek et al.}\ \citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
+Chudek et al.~\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
 Their definition of prestige is similar to our influence bias.
-They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of {learning from a role model} whom bystanders ignored.
+They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of learning from a role model whom bystanders ignored.
 They also note that prestige effects are domain sensitive: they found that prestigious role-models were attended more when demonstrating artifact use, whereas role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact use vs.
 food preference) can affect the attendance, and hence the prestige of the role-model.
-This {led to the suggestion} that when the trait is costly to learn individually, prestige will have a stronger bias \citep{prestige_cultural_learning}.
+This led to the suggestion that when the trait is costly to learn individually, prestige will have a stronger bias \citep{prestige_cultural_learning}.
 It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.
 
-According to \citep{fijian_social_bias}, {natural} selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information. 
-{They} studied Fijian villages to examine if and how such biases emerge in a small-scale society.
+According to Henrich and Broesch~\citep{fijian_social_bias}, natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
+They authors studied Fijian villages to examine if and how such biases emerge in a small-scale society.
 They found that Fijian villagers are more likely to learn from role-models perceived as more successful/knowledgeable, both within and across domains.
-Their research thus suggests that copying from those perceived as successful, rather than {who are actually} successful, is a common {phenomenon}. 
-They show that the social networks representing copier--role-model relationships are centralized, suggesting that it is consistent with the prediction that people substantially share notions about who is a good cultural model, but that individuals' role-model selections are influenced by multiple factors.
+Their research thus suggests that copying from those perceived as successful, rather than who are actually successful, is a common phenomenon. 
+They show that the social networks representing copier--role-model relationships are centralized, which is consistent with the prediction that people substantially share notions about who is a good cultural model, but that individuals' role-model selections are influenced by multiple factors.
 
@@
 “Conditions That Favour Cumulative Cultural Evolution.” Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
-https://doi.org/10.1098/rstb.2021.0400.
 

### 2023-10-29 ms/ms.tex
continued revision with SE

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Adaptive success-bias weight}
-
-We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the estimated and the ideal trait values,
-\begin{equation}
+\subsection*{Optimal	 success-bias weight}
+
+We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
+\begin{equation}\label{eq:optimal_alpha}
 \alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l} (\hat{A}-A_j)^2 \;,
 \end{equation}
-where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model $j$.
-
-We find that when copiers {choose} their success-bias weight, it decreases with the number of copiers that have already chosen a role-model~(\Cref{fig:influence_advantage}).
-Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the adaptive weight estimation error converges to $0.046$, whereas a constant weight gives values $>0.74$.
+where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
+% TODO statement about fitness
+
+We find that when copiers choose their success-bias weight according to \cref{eq:optimal_alpha}, it decreases with the number of copiers that have already chosen a role-model~(\Cref{fig:influence_advantage}).
+Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the optimal success-bias weight gives an estimation error (difference between the chosen and optimal trait) converges to $0.046$, whereas a constant success-bias weight gives values $>0.74$.
 
@@
   \caption{
-  \textbf{Advantage of an adaptive success-bias weight.}
-  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process, demonstrating that influence becomes more favored as more copiers have made their choice.
+  \textbf{Advantage of an optimal success-bias weight.}
+  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that influence becomes more favored by copiers as more copiers have made their choice.
 However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
-The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the adaptive $\alpha$ model.
+The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
 Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}
@@
 
-We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers {and hence is the same as conformity bias}.
+We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
 We model these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
@@
 They show that the social networks representing copier--role-model relationships are centralized, which is consistent with the prediction that people substantially share notions about who is a good cultural model, but that individuals' role-model selections are influenced by multiple factors.
-
-{Prestige bias also occurs} in more modern domains such as western medicine.
-Norredam and Album~\citep{medical_prestige} examined literature from 1950 to 2005 on the effects of prestige on medicinal practices.
-They found that active, specialized, biomedical, and high-technological types of medicine on organs in the upper part of the bodies of young and middle-aged people were accorded high levels of prestige, whereas medicine and practices that were not of these types had low levels of prestige.
-For example, they found that surgery counts as the most prestigious specialty, while psychiatry is the {least} prestigious.
-In addition, doctors tend to rank practices that require more time to master as more prestigious, while other procedures that are considered easier to master are less prestigious. 
-This means that there may be very important practices that are neglected due to prestige bias.
-They concluded that such differences in prestige may {affect} for actual priority setting in healthcare systems.
 
@@
 
-\bibitem{medical_prestige}
-Norredam, Marie, and Dag Album. "Prestige and its significance for medical specialties and diseases." Scandinavian journal of public health 35.6 (2007): 655-661.
-
 \bibitem{collective_brains}

### 2023-11-05 ms/ms.tex
update

@@
 % Title page
-\title{Prestige bias in cultural evolutionary dynamics}
+\title{Influence bias in cultural evolutionary dynamics}
 % Authors
@@
 {If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased. Prestige may be used as a proxy for success.}
-Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied  that role-model.
+Here, we model influence bias as a combination of indirect success bias and prestige bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied  that role-model.
 {The} effect of prestige on cultural evolutionary dynamics {is analyzed} using mathematical analysis and stochastic simulations.
@@
 {Approximations are given}  to the fixation probability and the fixation time of an invading cultural trait in different environments.
-We show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
+We show that indirect success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.	
 Influence bias{, which may be strong in communities where social media are prevalent,}  also accelerates the evolutionary dynamics, as can be expected in a rich-{get}-richer process.
@@
 \section*{Introduction}
-
-%\paragraph{Cultural transmission.}
-%In cultural transmission, individuals transmit cultural traits (i.e., behaviors, beliefs, norms) to one another, typically by learning and demonstrating \citep{transmissionVectorsBook}.
-%Examples for cultural traits in humans are norms, preferences, tools, ideas, and language, potentially transmitted verbally and/or by observations \citep{transmissionVectors}. 
-%Although cultural transmission is common in humans, it is also observed in other animals, e.g.
-chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper} and fish \citep{Truskanov2020}.
 
@@
 
-To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
-This is an important distinction, as influence is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
-Influence bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+{Jimenez \& Mesoudi} (2019) \citep{prestigeSocialLearn} suggest that cultural evolution theory is a major factor in human ecological success.
+They mention that a way to acquire adaptive social information is by preferentially copying competent individuals within a valuable domain, and they call it success bias as we do in this paper.
+They also mention that competence within a domain is often difficult or impossible to directly asses, therefore people tend to use indirect cues of success, as suggested by {Henrich and Gil-White}.
+
+In our paper, we examine the effect of both success and prestige biases, and their relationship in contribution to the cultural evolution of populations.
+We call the joint contribution of both biases \emph{Influence bias}.
+This is an important distinction, as prestige is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
+Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
 
@@
 
-In the following, we develop a stochastic model of cultural transmission with prestige bias that combines both cross-domain indirect success bias and influence bias.
+In the following, we develop a stochastic model of cultural transmission with influence bias that combines both cross-domain indirect success bias and prestige bias.
 We develop analytic approximations for this model and analyze its dynamics.
@@
 
-\paragraph{Influence bias.}
+\paragraph{Prestige bias.}
 Here we introduce a new element to the model by assuming that in each generation, copiers choose their role-models one by one.
@@
 
-Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the prestige of role-model $j$ in the eyes of copier $i$,
+Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the influence of role-model $j$ in the eyes of copier $i$,
 \begin{equation}\label{eq:recPrestige}
@@
 \end{equation}
-The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and influence--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} with
+The influence $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and prestige--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} with
 \begin{equation}\label{eq:prestige}
@@
 
-Here, the bias weight $\alpha_{i,j}$ determines the relative weighting of success and influence bias.
+Here, the bias weight $\alpha_{i,j}$ determines the relative weighting of success and prestige bias.
 It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs.
-influence in the role-model's overall prestige in the eyes of the copier.
-Different individuals may evaluate the importance of success and influence differently.
-Additionally, we assume each role-model displays its influence and success individually.
+prestige in the role-model's overall influence in the eyes of the copier.
+Different individuals may evaluate the importance of success and prestige differently.
+Additionally, we assume each role-model displays its prestige and success individually.
 For example, individuals with more followers but lacking skill may emphasize the number of their followers rather than their skill.
@@
 
-(i) the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
+(i) the expected number of copiers of role-model~$j$ equals its influence in the eyes of the first copier, multiplied by the total number of copiers, that is,
 $\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$); and
@@
 From \Cref{cor:GBD} we see that if there is no success bias, meaning $Q_j(1,1)=q$ for $j$ in $1,...,N$, then the expected number of copiers will be Binomial distributed.
-This proves that influence bias is not frequency dependent.
+This proves that prestige bias is not frequency dependent.
 
@@
 Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws  (the population size, $N$, in our model) approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
-We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers.
+We therefore have an approximation for the relative influence each role-model has when evaluated by copiers.
 Thus, choosing the role-models for all copiers is equivalent to drawing from a {multinomial} distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
@@
 We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
-We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
+We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and prestige on influence bias, given by \cref{eq:prestige}.
 For simplicity, we use the dichotomous model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
@@
 Our proof and approximation in the changing environment are for a large {number} of cycles, and when the success coefficient {$\alpha$} is too high, there might be very few cycles.
-Either the ideal trait is copied by enough copiers so that the influence is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait {goes} extinct before there {are} enough copiers that copied it.
+Either the ideal trait is copied by enough copiers so that the prestige is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait {goes} extinct before there {are} enough copiers that copied it.
 We then tried to change the ratio between the number of cycles where $\hat{A}$ is favored and disfavored.
@@
 where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
-% TODO statement about fitness
+Indeed, if the trait value would have been correlated with fitness, the optimal success-bias weight would increase fitness. However in here we don't include natural selection.
 
@@
   \textbf{Advantage of an optimal success-bias weight.}
-  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that influence becomes more favored by copiers as more copiers have made their choice.
+  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
 However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
@@
 
-We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
+We developed a cultural-evolution model with influence bias that includes both indirect success and prestige biases, where the latter is a bias towards role-models with many copiers.
 We model these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
@@
 Chudek et al.~\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
-Their definition of prestige is similar to our influence bias.
+Their definition of prestige is similar to ours.
 They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of learning from a role model whom bystanders ignored.
@@
 %\paragraph{Further work.}
-One path forward is an analysis of the dynamics of the adaptive success-bias weight model, in which every copier chooses its $\alpha$.
-It would be interesting to see the if the mean estimation error and the adaptive weight, $\alpha^*$, {converge} to specific values, and how they are affected by the model parameters.
+One path forward is an analysis of the dynamics of the optimal success-bias weight model, in which every copier chooses its $\alpha$.
+It would be interesting to see the if the mean estimation error and the varying weight, $\alpha^*$, {converge} to specific values, and how they are affected by the model parameters.
 It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
@@
 \begin{thebibliography}{}
+
+\bibitem{prestigeSocialLearn}
+Jiménez, Ángel V., and Alex Mesoudi. "Prestige-biased social learning: Current evidence and outstanding questions." Palgrave Communications 5.1 (2019).
+
+\bibitem{rethinkPrestige}
+Chellappoo, Azita. "Rethinking prestige bias." Synthese 198.9 (2021): 8191-8212.
 
@@
 \begin{proof}
-The initial prestige of role-model $j$ based on \cref{eq:prestige} is
+The initial influence of role-model $j$ based on \cref{eq:prestige} is
 \begin{equation}\label{eq:initial_prob}

### 2023-11-06 ms/ms.tex
update

@@
 
+Similarly to {Henrich and Gil-White} \citep{prestige_evolution}, we believe that the most skilled/knowledgeable models will, on-average, end up with the biggest and most lavish clienteles, so the clientele size provides a convenient and reliable proxy for that person's "worth.
+Therefore, we predict that skilled individuals have higher status, people preferentially copy them more than others, therefore prestigious individuals are influential, even beyond their domain of expertise.
+
 In our paper, we examine the effect of both success and prestige biases, and their relationship in contribution to the cultural evolution of populations.
@@
 where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
+
+Simply put, each copier estimates what success-bias weight $\alpha^*$ will result in copying the closet trait to the ideal one $\hat{A}$.
 Indeed, if the trait value would have been correlated with fitness, the optimal success-bias weight would increase fitness. However in here we don't include natural selection.
@@
 The rationale, then, is that the more information a copier has, e.g., by using others as information sources, the more informative and effective his choice can be.
+
+Our decision to research and analyze a multi-bias model is preceded by several others.
+{Ze Hong} (2020) \citep{payoff}, for example, present a model that combines both frequency dependent bias (including conformist bias) and payoff bias in a single decision-making calculus.
+He shows that an integrated learning strategy may be superior to relying on either bias alone.
+He also show that both are likely to contribute to the spread of variants with high payoff, and the magnitude of conformist bias affects the evolutionary dynamics.
 
@@
 
+\bibitem{payoff} Hong, Ze. "Combining Conformist and Payoff Bias in Cultural Evolution: An Integrated Model for Human Decision-Making." Human Nature 33.4 (2022): 463-484.
+
 \end{thebibliography}

### 2023-11-06 ms/ms.tex
some revisions with SE

--- 2023-11-05 ms/ms.tex
@@
 Henrich and Broesch \citep{fijian_social_bias} studied such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
-They {suggested} that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits
+They suggested that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits
 \citep[Ch.~8]{evolutionBook}.
-{Prestige bias may be} more common in humans than success {bias} \citep{complexityPaper}, and prestige is often mentioned in the cultural evolution literature, {although} there are few models of {it}.
+Prestige bias may be more common in humans than success bias \citep{complexityPaper}, and prestige is often mentioned in the cultural evolution literature, although there are few models of it; see Chellappoo (2021) for a philosophical critique of the concept of prestige itself.
+% TODO convert to reference; add this sentence to response letter.
 
@@
 
-{Jimenez \& Mesoudi} (2019) \citep{prestigeSocialLearn} suggest that cultural evolution theory is a major factor in human ecological success.
+Jimenez \& Mesoudi~\citep{prestigeSocialLearn} suggest that cultural evolution theory is a major factor in human ecological success.
 They mention that a way to acquire adaptive social information is by preferentially copying competent individuals within a valuable domain, and they call it success bias as we do in this paper.
-They also mention that competence within a domain is often difficult or impossible to directly asses, therefore people tend to use indirect cues of success, as suggested by {Henrich and Gil-White}.
-
-In our paper, we examine the effect of both success and prestige biases, and their relationship in contribution to the cultural evolution of populations.
-We call the joint contribution of both biases \emph{Influence bias}.
-This is an important distinction, as prestige is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
+They also mention that competence within a domain is often difficult or impossible to directly asses, therefore people tend to use indirect cues of success, as suggested by Henrich and Gil-White~\citep{prestige_evolution}.
+
+Henrich and Gil-White~\citep{prestige_evolution} noted that ``the most skilled/knowledgeable role-models will, on average, end up with the biggest and most lavish clienteles, so the size and lavishness of a given model's clientele size (the \emph{prestige}) provides a convenient and reliable proxy for that person's information quality''.
+Therefore, they predicted that skilled individuals have higher status, people preferentially copy them more than others, and therefore prestigious individuals may be influential even beyond their domain of expertise.
+
+Here, we examine the effect of both success and prestige biases, and their relationship in contribution to the cultural evolution of populations.
+We call the joint contribution of both biases \emph{influence bias}.
+This is an important distinction, as prestige is a context-dependent bias, rather than a content-dependent bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
 Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
@@
 \subsection*{Optimal success-bias weight}
-
+% TODO edit the next sentence.
 We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
@@
 where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
-Indeed, if the trait value would have been correlated with fitness, the optimal success-bias weight would increase fitness. However in here we don't include natural selection.
+Simply put, each copier estimates what success-bias weight $\alpha^*$ will result in copying a trait that is most similar to the ideal trait value $\hat{A}$.
+Indeed, if the trait value is correlated with fitness, the optimal success-bias weight would increase the fitness of individuals.
+However, here we ignore the effects of natural selection, focusing instead on selectively neutral traits.
 
@@
 The rationale, then, is that the more information a copier has, e.g., by using others as information sources, the more informative and effective his choice can be.
+
+Our decision to research and analyze a multi-bias model is preceded by several others.
+Ze Hong~\citep{payoff}, for example, presented a model that combines both frequency-dependent bias (including conformist bias) and payoff bias.
+He has shown that an integrated learning strategy may be superior to relying on either bias alone.
+Moreover, both are likely to contribute to the spread of variants with high payoff, and the magnitude of conformist bias affects the evolutionary dynamics.
+% TODO add Denton; others
 

### 2023-11-07 ms/ms.tex
revised introduction and discussion following rev1; fixed bibitems

--- 2023-11-05 ms/ms.tex
@@
 
-% Title page
-\title{Influence bias in cultural evolutionary dynamics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Title 
+\title{Prestige bias in cultural evolutionary dynamics}
+
 % Authors
@@
 
-\author[1,3]{Saar Egozi}
+\author[1,2]{Saar Egozi}
 \author[2,3,$\dagger$]{Yoav Ram}
@@
 \affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
-\affil[3]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
+\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
 \affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 \begin{abstract}
-{If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased. Prestige may be used as a proxy for success.}
-Here, we model influence bias as a combination of indirect success bias and prestige bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied  that role-model.
-{The} effect of prestige on cultural evolutionary dynamics {is analyzed} using mathematical analysis and stochastic simulations.
-{Analytic} approximations to the stochastic role-model choice process {facilitate the} mathematical analysis and reduce the computational complexity of simulations.
-{Approximations are given}  to the fixation probability and the fixation time of an invading cultural trait in different environments.
-We show that indirect success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.	
-Influence bias{, which may be strong in communities where social media are prevalent,}  also accelerates the evolutionary dynamics, as can be expected in a rich-{get}-richer process.
+If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased.
+In contrast, if the traits of `prestigious' individuals--those individuals that have already been copied many times--are more likely to be adopted, this is described as prestige-biased cultural transmission.
+In this case prestige can be used as a convenient proxy for success.
+Here, we study the the joint effect of success and prestige bias on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
+Analytic approximations to the stochastic role-model choice process facilitate the mathematical analysis and reduce the computational complexity of simulations.
+Approximations are given to the fixation probability and the fixation time of an invading cultural trait in different environments.
+We show that success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.	Prestige bias, which may be strong in highly social communities, also accelerates the evolutionary dynamics, as can be expected in a rich-get-richer process.
 \end{abstract}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Introduction}
 
-Cultural transmission {of attitudes, preferences, beliefs, norms, and behaviors} may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, and even strangers) transmit to unrelated offspring; and horizontal transmission, in which {individuals} from the same age cohort transmit to one another \citep{transmissionVectorsBook}.
+Cultural transmission of attitudes, preferences, beliefs, norms, and behaviors may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, and even strangers) transmit to unrelated offspring; and horizontal transmission, in which individuals from the same age cohort transmit to one another \citep{transmissionVectorsBook}.
 It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{changeEnv,Lehmann2009}.
 
-Transmission biases may cause a cultural trait to have a {higher rate of transmission than} its frequency in the population.
-\textit{Success bias} occurs when individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, using medicinal plants \citep{fijian_social_bias}, or hunting \citep{Mesoudi2008}, and it can increase the probability of learning a {trait that is present in those successful individuals} \citep{Borofsky2022}.
-Indeed, in a tournament between learning strategies  \citep{strategiesPaper}, most {winning} strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
-
-{Boyd and Richerson} \citep[Ch.~5]{evolutionBook} suggested that the {assessment} of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
-{Direct} bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
-For example, an individual observing a ping-pong match can {try} the observed paddle grips to determine which grip is better.
-Frequency-dependent bias occurs when the probability {of copying} a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
-For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{{anti}-conformity} \citep{conformism}.
-The effects of conformity and {anti}-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
+Transmission biases may cause a cultural trait to have a higher rate of transmission than its frequency in the population.
+\textit{Success bias} occurs when individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, using medicinal plants \citep{fijian_social_bias}, or hunting \citep{Mesoudi2008}, and it can increase the probability of learning a trait that is present in those successful individuals \citep{Borofsky2022}.
+Indeed, in a tournament between learning strategies  \citep{strategiesPaper}, most winning strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
+Jimenez and Mesoudi~\citep{prestigeSocialLearn} also note that a way to acquire adaptive social information is by preferentially copying competent individuals within a valuable domain (which they also call success bias).
+However, they claim that competence within a domain is often difficult or impossible to directly asses, and therefore people tend to use indirect cues of success.
+Henrich and Broesch \citep{fijian_social_bias} have also suggested that direct assessment of success may be ``noisy, unreliable or unavailable'' and therefore copiers should also take into account indirect measures of perceived success (e.g., ``great fishermen may be chosen as role-models for growing yams''.)
+
+Boyd and Richerson~\citep[Ch.~5]{evolutionBook} suggested that the assessment of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
+Direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
+For example, an individual observing a ping-pong match can try the observed paddle grips to determine which grip is better.
+Frequency-dependent bias occurs when the probability of copying a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
+For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{anti-conformity} \citep{conformism}.
+The effects of conformity and anti-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
 Indirect bias occurs when a copier uses some observed phenotype to evaluate the attractiveness of a potential role-model. 
@@
 However, this may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
-Furthermore, {Boyd and Richerson} \citep[Ch.
-8]{evolutionBook} {suggest} that maladaptive traits may spread widely in a population if indirect {bias is} strong enough, e.g., by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
-Indeed, helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost \citep{cooperation}.
-
-Henrich and Broesch \citep{fijian_social_bias}  studied such indirect success biases, which they call cross-domain success bias or \emph{prestige bias} (e.g., great fishermen may be chosen as role-models for growing yams).
-They {suggested} that such biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits
-\citep[Ch.~8]{evolutionBook}.
-{Prestige bias may be} more common in humans than success {bias} \citep{complexityPaper}, and prestige is often mentioned in the cultural evolution literature, {although} there are few models of {it}.
-
-A broader definition of prestige is the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
-Indeed, Chudek et al.~\citep{prestige_cultural_learning} have defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'', and demonstrated its occurrence in in 3-4 year old children.
-{Henrich and Gil-White} \citep{prestige_evolution} gave a similar definition of prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature.
-
-{Jimenez \& Mesoudi} (2019) \citep{prestigeSocialLearn} suggest that cultural evolution theory is a major factor in human ecological success.
-They mention that a way to acquire adaptive social information is by preferentially copying competent individuals within a valuable domain, and they call it success bias as we do in this paper.
-They also mention that competence within a domain is often difficult or impossible to directly asses, therefore people tend to use indirect cues of success, as suggested by {Henrich and Gil-White}.
-
-In our paper, we examine the effect of both success and prestige biases, and their relationship in contribution to the cultural evolution of populations.
-We call the joint contribution of both biases \emph{Influence bias}.
-This is an important distinction, as prestige is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
-Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
-
+Furthermore, Boyd and Richerson~\citep[Ch.
+8]{evolutionBook} suggest that maladaptive traits may spread widely in a population if indirect bias is strong enough, e.g., by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
+Indeed, helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient~\citep{cooperation}.
+
+Henrich and Gil-White~\citep{prestige_evolution} noted that ``the most skilled/knowledgeable role-models will, on average, end up with the biggest and most lavish clienteles, so the size and lavishness of a given model's clientele size (the \emph{prestige}) provides a convenient and reliable proxy for that person's information quality''.
+Therefore, they predicted that skilled individuals have higher status, that people preferentially copy high-status individuals, and therefore that prestigious individuals may be influential even beyond their domain of expertise.
+They defined prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature \citep{prestige_evolution} .
+Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality''.
+Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in in 3-4 year old children.
+Henrich and Broesch \citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
+
+The distinction between success and prestige bias is important, as prestige is a context-dependent bias, rather than a content-dependent bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
+Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity \citep{anticonformity,Denton2021,conformity}, which depends on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+
+Prestige bias may be more common in humans than success bias \citep{complexityPaper}.
 In contemporary human society, social media make it especially easy to estimate the social and cultural influence individuals have over others, which can have an effect on decision making.
 Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices have been invented to capitalize on this effect \citep{facebook_marketing}.
-
-In the following, we develop a stochastic model of cultural transmission with influence bias that combines both cross-domain indirect success bias and prestige bias.
-We develop analytic approximations for this model and analyze its dynamics.
-We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is {subject to} success bias).
-Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.
+However, despite many mentions of prestige in the cultural evolution literature, there are few models of prestige bias.
+
+Here, we develop a stochastic model of cultural transmission with both cross-domain indirect success bias and prestige bias to examine their relationship in contribution to the cultural evolution of populations.
+We find analytic approximations for this model and analyze its dynamics.
+We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is subject to success bias).
+Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and prestige bias play the role of natural selection and genetic drift, respectively.
 
@@
 \section*{Models}
-We begin with a continuous trait model with indirect bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}.
-We extend this model to include influence bias.
+We begin with a continuous trait model with indirect success bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}.
+We extend this model to include prestige bias.
 We then develop a dichotomous trait model.
-Note that the indirect bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
+Note that the indirect success bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
 
@@
 We formulate this assumption in the following.
-{Denote by} $K_{i,j}$  the number of copiers that {choose} role-model $j$ after copier $i$ chose a role-model.
-Thus, $i$ out of $N$ copiers {had} already {chosen} a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
+Denote by $K_{i,j}$  the number of copiers that choose role-model $j$ after copier $i$ chose a role-model.
+Thus, $i$ out of $N$ copiers had already chosen a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
 The stochastic process of role-model choice, 
@@
 
-Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the influence of role-model $j$ in the eyes of copier $i$,
+Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the \emph{influence} of role-model $j$ in the eyes of copier $i$,
 \begin{equation}\label{eq:recPrestige}
@@
 Additionally, we assume each role-model displays its prestige and success individually.
-For example, individuals with more followers but lacking skill may emphasize the number of their followers rather than their skill.
+For example, individuals with more followers but lacking skill may emphasize the number of their followers rather than their skill (i.e., have lower $\alpha_{i,j}$ value).
 Finally, the trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}.
@@
 We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
-We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and prestige on influence bias, given by \cref{eq:prestige}.
+We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and prestige bias, given by \cref{eq:prestige}.
 For simplicity, we use the dichotomous model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
@@
 \section*{Discussion}
-%During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
-{Some} cultural traits or cultural role-models may be copied more often {than others} due to transmission biases. 
-{One such} bias is success bias, in which copiers are more likely to copy a successful role-model.
-{Although many} models assume that success can be accurately estimated{, it} has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful.
-This perceived success can be determined by performance with respect to another trait (indirect) \citep{evolutionBook,fijian_social_bias}, or by the influence an individual has on others \citep{prestige_cultural_learning,prestige_evolution}.
-
-We developed a cultural-evolution model with influence bias that includes both indirect success and prestige biases, where the latter is a bias towards role-models with many copiers.
-We model these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
+Some cultural traits or cultural role-models may be copied more often than others due to transmission biases. 
+One such bias is success bias, in which copiers are more likely to copy a successful role-model. 
+It has been suggested that because it is hard to estimate success, a more common bias is a bias towards role-models \emph{perceived} to be successful.
+This perceived success can be determined by performance with respect to another trait, i.e., \emph{indirect success} \citep{evolutionBook,fijian_social_bias}, or by ``the amount of voluntary deference and attention received by models'' \citep{prestigeSocialLearn}, i.e., \emph{prestige} \citep{prestige_cultural_learning,prestige_evolution} (but see Chellappoo~\citep{rethinkPrestige} for a critical examination of the concept of prestige).
+
+We developed a cultural-evolutionary model that includes both indirect success and prestige biases, where the latter is a bias towards role-models with many copiers.
+We model these biases using a stochastic role-model choice process: each copier, in turn, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
 
@@
 Analyzing the model with the DM distribution, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
-Our approximations are similar to Kimura's evolutionary-genetic approximations, {in} that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence versus success bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
+Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence versus success bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
 
@@
 
-We also examined a scenario in which copiers can adapt their success-weight bias, $\alpha$, to minimize their copying error, i.e., copy trait values closer to the optimal value.
-We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight ({chosen} by copiers) and the estimation error decrease. 
-The latter is significantly lower {than in} a population using a constant, fixed success-bias weight, regardless of the value of the constant weight (\Cref{fig:influence_advantage}).
-This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers, and the less it should rely on its own estimation.
+Lastly, we examined a scenario in which copiers can adjust their success-weight bias, $\alpha$, to minimize their copying error, i.e., copy trait values closer to the optimal value.
+We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight (adjusted by copiers) and the estimation error decrease. 
+The latter is significantly lower than in a population using a constant, fixed success-bias weight, regardless of the value of the constant weight (\Cref{fig:influence_advantage}).
+This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers (prestige), and the less it should rely on its own estimation of the success of role-models.
 The rationale, then, is that the more information a copier has, e.g., by using others as information sources, the more informative and effective his choice can be.
 
-%\paragraph{Empirical evidence of prestige bias}
+Others have analyzed models with interactions between different transmission biases.
+Ze Hong~\citep{payoff} studied a model with both frequency-dependent bias (including conformist bias) and payoff bias.
+The analysis demonstrates that an integrated learning strategy may be superior to relying on either bias alone.
+Moreover, both biases are likely to contribute to the spread of variants with high payoff, and the magnitude of conformist bias affects the evolutionary dynamics.
+% TODO add: 
+% Ammar, Madeleine, Laurel Fogarty, and Anne Kandler.
+2023.
+“Social Learning and Memory.” Proceedings of the National Academy of Sciences 120 (33): e2310033120.
+https://doi.org/10.1073/pnas.2310033120.
+% Enquist, Magnus, and Stefano Ghirlanda.
+2007.
+“Evolution of Social Learning Does Not Explain the Origin of Human Cumulative Culture.” Journal of Theoretical Biology 246 (1): 129–35.
+https://doi.org/10.1016/j.jtbi.2006.12.022.
+% Denton, Kaleda K., Yoav Ram, and Marcus W.
+Feldman.
+2022.
+“Conformity and Content-Biased Cultural Transmission in the Evolution of Altruism.” Theoretical Population Biology 143 (February): 52–61.
+https://doi.org/10.1016/j.tpb.2021.10.004.
+
 Chudek et al.~\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
@@
 However, it is not always the case, and there could be negative repercussions to this bias, such as invasion of maladaptive traits.
-{Takahashi and Ihara} \citep{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
+Takahashi and Ihara~\citep{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
 They suggest a best-of-k model where an individual samples~$k$ role-models and chooses the one he deems most "successful".
-They {mention} that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
+They mention that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
 In such a case, learners may be selectively disfavored and in the long run replaced by unbiased learners, who simply copy someone chosen at random.
 They developed new mathematical models that are simpler and mathematically tractable.
-They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff {(see Fogarty et al.\ \citep{Fogarty2017} and references there)}.
-Our model, which includes influence bias, is consistent with this claim.
-When a maladaptive trait is ``piggybacking'' {on} a role-model with high influence, {the former} could spread in the population.
-In addition, {best}-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning \citep{best_of_k}. 
-Our model {includes only} social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics.
+They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff (see Fogarty et al.\ \citep{Fogarty2017} and references there).
+Our model, which includes both success and prestige bias, is consistent with this claim.
+When a maladaptive trait is `piggybacking' on a role-model with high influence (joint effect of success and prestige), the former could spread in the population.
+In addition, best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning \citep{best_of_k}. 
+Our model includes only social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics.
 
 Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
-{Efferson et al.}\ \citep{harmful_traditions} suggest a \emph{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
-They {find} that there are individuals who act as \emph{agents}, who are often {observed}, and therefore they are ideal targets for interventions.
-This is similar to influential role-models in our model, where a prestigious individual will be copied more often, and will therefore spread {their} trait faster and wider in the population.
-They also suggest a way to use this {phenomenon} to change existing traditions in a population.
+Efferson et al.~\citep{harmful_traditions} suggest a \emph{spillover} mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
+They find that there are individuals who act as \emph{agents}, who are often observed, and therefore they are ideal targets for interventions.
+This is similar to prestigious role-models in our model, which are copied more often, and will therefore spread their trait faster and wider in the population.
+They also suggest a way to use this phenomenon to change existing traditions in a population.
 It is very clear however, that just as it can be used to end harmful traditions, the same agents could start harmful traditions.
 
-{Dunbar} \citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
-Following {this, Muthukrishnan and Henrich \citep{collective_brains} suggested} that prestige can directly affect human physical evolution.
+Dunbar~\citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
+Following this, Muthukrishnan and Henrich \citep{collective_brains} suggested that prestige can directly affect human physical evolution.
 They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
@@
 success and prestige biases).
-They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to "cheaply" acquire adaptive knowledge via transmission biases such as prestige.
-
-%\paragraph{Further work.}
+They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to `cheaply' acquire adaptive knowledge via transmission biases such as prestige.
+
 One path forward is an analysis of the dynamics of the optimal success-bias weight model, in which every copier chooses its $\alpha$.
-It would be interesting to see the if the mean estimation error and the varying weight, $\alpha^*$, {converge} to specific values, and how they are affected by the model parameters.
+It would be interesting to see the if the mean estimation error and the varying weight, $\alpha^*$, converge to specific values, and how they are affected by the model parameters.
 It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
@@
 
-Another way to expand our model is to account for the two types of prestige or leadership suggested by {Van Vugt and Smith} \citep{dual_leadership} that are attributed to Confucius and Machiavelli.
+Another way to expand our model is to account for the two types of prestige or leadership suggested by Van Vugt and Smith~\citep{dual_leadership} that are attributed to Confucius and Machiavelli.
 Confucius viewed leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
@@
 In contrast, Machiavelli viewed leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence.
-{Van Vugt and Smith suggest} that these opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
-Several adjustments could be made so that our model reflects these leadership styles, such as assuming there is a correlation between phenotype {and} leadership style. 
-The {resulting} cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
+Van Vugt and Smith suggest that these opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
+Henrich and Gil-White~\citep{prestige_evolution} have suggested a similar distinction between `prestige and `dominance', or between `persuasion' and `force'.
+Several adjustments could be made so that our model reflects these leadership styles, such as assuming there is a correlation between phenotype and leadership style.
+The resulting cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
 
 \paragraph{Conclusions.}
-{We} studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with influence bias, which has so far received less attention.
+We studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with prestige bias, which has so far received less attention.
 We found approximations for this complex dynamics.
-We then showed that success bias affects the evolutionary dynamics much like natural selection does, whereas influence bias has a similar effect to random genetic drift.
+We then showed that success bias affects the evolutionary dynamics much like natural selection does, whereas prestige bias has a similar effect to random genetic drift.
 We also find a clear advantage to individuals that can choose the relative weight of the two biases.
@@
 \section*{Acknowledgements}
-We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, and Tal Simon for discussions and comments.
+We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, Tal Simon and two anonymous reviewers for discussions and comments.
 This work was supported in part by 
@@
 \bibitem{prestigeSocialLearn}
-Jiménez, Ángel V., and Alex Mesoudi. "Prestige-biased social learning: Current evidence and outstanding questions." Palgrave Communications 5.1 (2019).
+Jiménez, Ángel V., and Alex Mesoudi. (2019) "Prestige-biased social learning: Current evidence and outstanding questions." Palgrave Communications 5.1 (2019).
 
 \bibitem{rethinkPrestige}
-Chellappoo, Azita. "Rethinking prestige bias." Synthese 198.9 (2021): 8191-8212.
+Chellappoo, Azita. (2021) "Rethinking prestige bias." Synthese 198.9: 8191-8212.
 
 \bibitem{fliesPaper}
-  Battesti, Marine, et al. "Spread of social information and dynamics of social transmission within Drosophila groups." Current biology 22.4 (2012): 309-313.
+Battesti, Marine, Celine Moreno, Dominique Joly, and Frederic Mery. (2012) "Spread of Social Information and Dynamics of Social Transmission within Drosophila Groups." Current Biology 22 (4): 309–13.
 
 \bibitem{transmissionVectors}
-Creanza, Nicole, Oren Kolodny, and Marcus W. Feldman. "Cultural evolutionary theory: How culture evolves and why it matters." Proceedings of the National Academy of Sciences 114.30 (2017): 7782-7789.
+Creanza, Nicole, Oren Kolodny, and Marcus W. Feldman. (2017) "Cultural evolutionary theory: How culture evolves and why it matters." Proceedings of the National Academy of Sciences 114.30: 7782-7789.
 
@@
 Aljadeff, Naama, Luc-Alain Giraldeau, and Arnon Lotem.
-"Competitive advantage of rare behaviours induces adaptive diversity rather than social conformity in skill learning." Proceedings of the Royal Society B 287.1933 (2020): 20201259.
+(2020) "Competitive advantage of rare behaviours induces adaptive diversity rather than social conformity in skill learning." Proceedings of the Royal Society B: Biological Sciences 287.1933: 20201259.
 
 \bibitem{transmissionVectorsBook}
-Cavalli-Sforza, Luigi Luca, and Marcus W. Feldman. Cultural transmission and evolution: A quantitative approach. No. 16. Princeton University Press, 1981.
+Cavalli-Sforza, Luigi Luca, and Marcus W. Feldman. (1981) :Cultural transmission and evolution: A quantitative approach." No. 16. Princeton University Press.
 
 \bibitem{evolutionBook}
-Boyd, Robert, and Peter J. Richerson. Culture and the evolutionary process. University of Chicago press, 1988.
+Boyd, Robert, and Peter J. Richerson. (1985) "Culture and the Evolutionary Process". University of Chicago Press.
 
 \bibitem{complexityPaper}
-Fogarty, Laurel, et al. "The driving forces of cultural complexity: neanderthals, modern humans, and the question of population size." Human Nature 28 (2017): 39-52.
+Fogarty, Laurel, Joe Yuichiro Wakano, Marcus W.
+Feldman, and Kenichi Aoki.
+(2017) "The Driving Forces of Cultural Complexity: Neanderthals, Modern Humans, and the Question of Population Size." Human Nature 28 (1): 39–52.
 
 \bibitem{strategiesPaper}
-Rendell, Luke, et al. "Why copy others? Insights from the social learning strategies tournament." Science 328.5975 (2010): 208-213.
+Rendell, Luke E., Robert Boyd, D.
+Cownden, M.
+Enquist, K.
+Eriksson, Marcus W.
+Feldman, Laurel Fogarty, S.
+Ghirlanda, T.
+Lillicrap, and Kevin N.
+Laland.
+(2010) "Why Copy Others?
+Insights from the Social Learning Strategies Tournament." Science 328 (5975): 208–13.
 
 \bibitem{sexualSelectionBook}
-Andersson, Malte, and Yoh Iwasa. "Sexual selection." Trends in ecology \& evolution 11.2 (1996): 53-58.
+Andersson, Malte, and Yoh Iwasa. (1996) "Sexual selection." Trends in ecology \& evolution 11.2: 53-58.
 
 \bibitem{chimpsCopy}
-Kendal, Rachel, et al. "Chimpanzees copy dominant and knowledgeable individuals: implications for cultural diversity." Evolution and Human Behavior 36.1 (2015): 65-72.
+Kendal, Rachel L., Lydia M.
+Hopper, Andrew Whiten, Sarah F.
+Brosnan, Susan P.
+Lambeth, Steven J.
+Schapiro, and William J.E.
+Hoppitt.
+(2015) "Chimpanzees Copy Dominant and Knowledgeable Individuals: Implications for Cultural Diversity." Evolution and Human Behaviour 36 (1): 65–72.
 
 \bibitem{chimpsPrestige}
-Horner, Victoria, et al. "Prestige affects cultural learning in chimpanzees." PloS one 5.5 (2010): e10625.
+Horner, Victoria, Darby Proctor, Kristin E. Bonnie, Andrew Whiten, and Frans B.M. de Waal. (2010) "Prestige Affects Cultural Learning in Chimpanzees." PLoS ONE 5 (5): 1–5.
 
 \bibitem{dualEvolution}
-Henrich, Joseph, and Richard McElreath. "Dual-inheritance theory: the evolution of human cultural capacities and cultural evolution." (2007).
+Henrich, Joseph, and Richard McElreath.
+(2012) "Dual-Inheritance Theory: The Evolution of Human Cultural Capacities and Cultural Evolution." In Oxford Handbook of Evolutionary Psychology, edited by Louise Barrett and Robin Dunbar, 1st ed., 555–70.
+Oxford University Press.
 
 \bibitem{elepahntsRepo}
-McComb, Karen, et al. "Matriarchs as repositories of social knowledge in African elephants." Science 292.5516 (2001): 491-494.
+McComb, K., C. Moss, Sarah M. Durant, L. Baker, and S. Sayialel. (2001) "Matriarchs As Repositories of Social Knowledge in African Elephants." Science 292 (5516): 491–94.
 
 \bibitem{wtfGene}
-Eickbush, Michael T., Janet M. Young, and Sarah E. Zanders. "Killer meiotic drive and dynamic evolution of the wtf gene family." Molecular Biology and Evolution 36.6 (2019): 1201-1214.
+Eickbush, Michael T., Janet M. Young, and Sarah E. Zanders. (2019) "Killer meiotic drive and dynamic evolution of the wtf gene family." Molecular Biology and Evolution 36.6: 1201-1214.
 
 \bibitem{pageRank}
-Xing, Wenpu, and Ali Ghorbani. "Weighted pagerank algorithm." Proceedings. Second Annual Conference on Communication Networks and Services Research, 2004.. IEEE, 2004.
+Xing, Wenpu, and Ali Ghorbani. (2004) "Weighted pagerank algorithm." Proceedings. Second Annual Conference on Communication Networks and Services Research, IEEE.
 
@@
 \bibitem{changeEnv}
-Ram, Yoav, Uri Liberman, and Marcus W. Feldman. "Evolution of vertical and oblique transmission under fluctuating selection." Proceedings of the National Academy of Sciences 115.6 (2018): E1174-E1183.
+Ram, Yoav, Uri Liberman, and Marcus W. Feldman. (2018) "Evolution of vertical and oblique transmission under fluctuating selection." Proceedings of the National Academy of Sciences 115.6: E1174-E1183.
 
 \bibitem{animal_leadership}
-King, Andrew J., and Guy Cowlishaw. "Leaders, followers, and group decision-making." Communicative \& integrative biology 2.2 (2009): 147-150.
+King, Andrew J., and Guy Cowlishaw. (2009) "Leaders, followers, and group decision-making." Communicative \& integrative biology 2.2: 147-150.
 
 \bibitem{dual_leadership}
-Van Vugt, Mark, and Jennifer E. Smith. "A dual model of leadership and hierarchy: Evolutionary synthesis." Trends in Cognitive Sciences 23.11 (2019): 952-967.
+Van Vugt, Mark, and Jennifer E. Smith. (2019) "A dual model of leadership and hierarchy: Evolutionary synthesis." Trends in Cognitive Sciences 23.11: 952-967.
 
@@
 Henrich, Joseph, and James Broesch.
-"On the nature of cultural transmission networks: evidence from Fijian villages for adaptive learning biases." Philosophical Transactions of the Royal Society B: Biological Sciences 366.1567 (2011): 1139-1148.
+(2011) "On the nature of cultural transmission networks: evidence from Fijian villages for adaptive learning biases." Philosophical Transactions of the Royal Society B: Biological Sciences 366.1567: 1139-1148.
 
 \bibitem{harmful_traditions}
-Efferson, Charles, Sonja Vogt, and Ernst Fehr. "The promise and the peril of using social influence to reverse harmful traditions." Nature human behaviour 4.1 (2020): 55-68.
+Efferson, Charles, Sonja Vogt, and Ernst Fehr. (2020) "The promise and the peril of using social influence to reverse harmful traditions." Nature human behaviour 4.1: 55-68.
 
@@
 Gil-White.
-"The evolution of prestige: Freely conferred deference as a mechanism for enhancing the benefits of cultural transmission." Evolution and human behavior 22.3 (2001): 165-196.
+(2001) "The evolution of prestige: Freely conferred deference as a mechanism for enhancing the benefits of cultural transmission." Evolution and human behavior 22.3: 165-196.
 
 \bibitem{best_of_k}
-Takahashi, Takuya, and Yasuo Ihara. "Cultural and evolutionary dynamics with best-of-k learning when payoffs are uncertain." Theoretical Population Biology 128 (2019): 27-38.
+Takahashi, Takuya, and Yasuo Ihara. (2019) "Cultural and evolutionary dynamics with best-of-k learning when payoffs are uncertain." Theoretical Population Biology 128: 27-38.
 
 \bibitem{collective_brains}
-Muthukrishna, Michael, and Joseph Henrich. "Innovation in the collective brain." Philosophical Transactions of the Royal Society B: Biological Sciences 371.1690 (2016): 20150192.
+Muthukrishna, Michael, and Joseph Henrich. (2016) "Innovation in the collective brain." Philosophical Transactions of the Royal Society B: Biological Sciences 371.1690: 20150192.
 
 \bibitem{social_brains}
-Dunbar, Robin IM. "The social brain hypothesis and its implications for social evolution." Annals of human biology 36.5 (2009): 562-572.
+Dunbar, Robin IM. (2009) "The social brain hypothesis and its implications for social evolution." Annals of human biology 36.5: 562-572.
 
 \bibitem{prestige_cultural_learning}
-Chudek, Maciej, et al. "Prestige-biased cultural learning: Bystander's differential attention to potential models influences children's learning." Evolution and human behavior 33.1 (2012): 46-56.
+Chudek, Maciej, Sarah Heller, Susan Birch, and Joseph Henrich.
+(2012) "Prestige-Biased Cultural Learning: Bystander’s Differential Attention to Potential Models Influences Children’s Learning." Evolution and Human Behavior 33 (1): 46–56.
 
 \bibitem{evolution_of_cultural_evolution}
-Henrich, Joseph, and Richard McElreath. "The evolution of cultural evolution." Evolutionary Anthropology: Issues, News, and Reviews: Issues, News, and Reviews 12.3 (2003): 123-135.
+Henrich, Joseph, and Richard McElreath. (2003) "The evolution of cultural evolution." Evolutionary Anthropology: Issues, News, and Reviews 12.3: 123-135.
 
 \bibitem{cultural_traits}
-O'Brien, Michael J., et al. "Cultural traits as units of analysis." Philosophical Transactions of the Royal Society B: Biological Sciences 365.1559 (2010): 3797-3806.
+O’Brien, Michael J., R.
+Lee Lyman, Alex Mesoudi, and Todd L.
+Van Pool.
+(2010) "Cultural Traits as Units of Analysis." Philosophical Transactions of the Royal Society B: Biological Sciences 365 (1559): 3797–3806.
 
 \bibitem{dolphins_whales}
-Whitehead, Hal. "Gene–culture coevolution in whales and dolphins." Proceedings of the National Academy of Sciences 114.30 (2017): 7814-7821.
+Whitehead, Hal. (2017) "Gene–culture coevolution in whales and dolphins." Proceedings of the National Academy of Sciences 114.30: 7814-7821.
 
 \bibitem{cooperation}
-Cohen, Dor, et al. "Non-vertical cultural transmission, assortment and the evolution of cooperation." Proceedings of the Royal Society B 288.1951 (2021): 20203162.
+Cohen, Dor, Ohad Lewin-Epstein, Marcus W.
+Feldman, and Yoav Ram.
+(2021) "Non-Vertical Cultural Transmission, Assortment and the Evolution of Cooperation." Proceedings of the Royal Society B: Biological Sciences 288 (1951): 20203162.
+https://doi.org/10.1098/rspb.2020.3162.
 
 \bibitem{conformity}
-Denton, Kaleda K., Yoav Ram, and Marcus W. Feldman. "Conformity and content-biased cultural transmission in the evolution of altruism." Theoretical Population Biology 143 (2022): 52-61.
+Denton, Kaleda K., Yoav Ram, and Marcus W. Feldman. (2022) "Conformity and content-biased cultural transmission in the evolution of altruism." Theoretical Population Biology 143: 52-61.
 
 \bibitem{anticonformity}
-Denton, Kaleda Krebs, et al. "Cultural evolution of conformity and anticonformity." Proceedings of the National Academy of Sciences 117.24 (2020): 13603-13614.
+Denton, Kaleda Krebs, Yoav Ram, Uri Liberman, and Marcus W. Feldman. (2020) "Cultural Evolution of Conformity and Anticonformity." Proceedings of the National Academy of Sciences 117 (24): 13603–14.
 
@@
 Lee, Woojin, Lina Xiong, and Clark Hu.
-"The effect of Facebook users’ arousal and valence on intention to go to the festival: Applying an extension of the technology acceptance model." International Journal of Hospitality Management 31.3 (2012): 819-827.
+(2012) "The effect of Facebook users’ arousal and valence on intention to go to the festival: Applying an extension of the technology acceptance model." International Journal of Hospitality Management 31.3: 819-827.
 
@@
 Anagnostopoulos, Aris, Ravi Kumar, and Mohammad Mahdian.
-"Influence and correlation in social networks." Proceedings of the 14th ACM SIGKDD international conference on Knowledge discovery and data mining.
-2008.
+(2008) "Influence and correlation in social networks." Proceedings of the 14th ACM SIGKDD international conference on Knowledge discovery and data mining.
 
 \bibitem{influence_analysis}
-Peng, Sancheng, et al. "Influence analysis in social networks: A survey." Journal of Network and Computer Applications 106 (2018): 17-32.
+Peng, Sancheng, Yongmei Zhou, Lihong Cao, Shui Yu, Jianwei Niu, and Weijia Jia.
+(2018) "Influence Analysis in Social Networks: A Survey." Journal of Network and Computer Applications 106 (March): 17–32.
 
 \bibitem{social_media}
-Diga, Marichris, and Tom Kelleher. "Social media use, perceptions of decision-making power, and public relations roles." Public Relations Review 35.4 (2009): 440-442.
+Diga, Marichris, and Tom Kelleher. (2009) "Social media use, perceptions of decision-making power, and public relations roles." Public Relations Review 35.4: 440-442.
 
 \bibitem{python}
-Van Rossum, Guido. "Python Programming Language." USENIX annual technical conference. Vol. 41. No. 1. 2007.
+Van Rossum, Guido. (2007) "Python Programming Language." USENIX annual technical conference. Vol. 41. No. 1.
 
 \bibitem{numpy}
-Van Der Walt, Stefan, S. Chris Colbert, and Gael Varoquaux. "The NumPy array: a structure for efficient numerical computation." Computing in science \& engineering 13.2 (2011): 22-30.
+Van Der Walt, Stefan, S. Chris Colbert, and Gael Varoquaux. (2011) "The NumPy array: a structure for efficient numerical computation." Computing in Science \& Engineering 13.2: 22-30.
 
 \bibitem{mathplotlib}
-Hunter, John D. "Matplotlib: A 2D graphics environment." Computing in science \& engineering 9.03 (2007): 90-95.
+Hunter, John D. (2007) "Matplotlib: A 2D graphics environment." Computing in Science \& Engineering 9.03: 90-95.
 
 \bibitem{kimura_average}
-Kimura, Motoo, and Tomoko Ohta. "The average number of generations until fixation of a mutant gene in a finite population." Genetics 61.3 (1969): 763.
+Kimura, Motoo, and Tomoko Ohta. (1969) "The average number of generations until fixation of a mutant gene in a finite population." Genetics 61.3: 763.
 
 \bibitem{otto_fixation}
-Slatkin, Montgomery. "Fixation probabilities and fixation times in a subdivided population." Evolution (1981): 477-488.
+Slatkin, Montgomery. (1981) "Fixation probabilities and fixation times in a subdivided population." Evolution: 477-488.
 
 \bibitem{lemurs}
-Erhart, Elizabeth M., and Deborah J. Overdorff. "Female coordination of group travel in wild Propithecus and Eulemur." International Journal of Primatology 20 (1999): 927-940.
+Erhart, Elizabeth M., and Deborah J. Overdorff. (1999) "Female coordination of group travel in wild Propithecus and Eulemur." International Journal of Primatology 20: 927-940.
 
 \bibitem{no_replication}
-Boyd, Robert, and Joseph Henrich. "On modeling cognition and culture: Why cultural evolution does not require replication of representations." Journal of cognition and culture 2.2 (2002): 87-112.
+Boyd, Robert, and Joseph Henrich. (2002) "On modeling cognition and culture: Why cultural evolution does not require replication of representations." Journal of cognition and culture 2.2: 87-112.
 
 \bibitem{kin_selection}
-Gardner, Andy, Stuart A. West, and Geoff Wild. "The genetical theory of kin selection." Journal of evolutionary biology 24.5 (2011): 1020-1043.
+Gardner, Andy, Stuart A. West, and Geoff Wild. (2011) "The genetical theory of kin selection." Journal of evolutionary biology 24.5: 1020-1043.
 
 \bibitem{Truskanov2020}
-Truskanov, Noa, Yasmin Emery, and Redouan Bshary. "Juvenile cleaner fish can socially learn the consequences of cheating." Nature communications 11.1 (2020): 1159.
+Truskanov, Noa, Yasmin Emery, and Redouan Bshary. (2020) "Juvenile cleaner fish can socially learn the consequences of cheating." Nature communications 11.1: 1159.
 
 \bibitem{Kolodny2022}
-Kolodny, Oren, et al. "Differential application of cultural practices at the family and individual levels may alter heritability estimates." Behavioral and Brain Sciences 45 (2022): e167.
+Kolodny, Oren, Marcus W.
+Feldman, Arnon Lotem, and Yoav Ram.
+(2022) "Differential Application of Cultural Practices at the Family and Individual Levels May Alter Heritability Estimates." Behavioral and Brain Sciences 45 (September): e167.
 
 \bibitem{Denton2021}
-Denton, Kaleda K., Uri Liberman, and Marcus W. Feldman. "On randomly changing conformity bias in cultural transmission." Proceedings of the National Academy of Sciences 118.34 (2021): e2107204118.
+Denton, Kaleda K., Uri Liberman, and Marcus W. Feldman. (2021) "On randomly changing conformity bias in cultural transmission." Proceedings of the National Academy of Sciences 118.34: e2107204118.
 
 \bibitem{Borofsky2022}
-Borofsky, Talia, and Marcus W. Feldman. "Success-biased social learning in a one-consumer, two-resource model." Theoretical Population Biology 146 (2022): 29-35.
+Borofsky, Talia, and Marcus W. Feldman. (2022) "Success-biased social learning in a one-consumer, two-resource model." Theoretical Population Biology 146: 29-35.
 
 \bibitem{Mesoudi2008}
-The cultural transmission of great basin projectile-point technology II: An agent-based computer simulation
+Mesoudi, Alex, and Michael J. O’Brien. (2008) "The Cultural Transmission of Great Basin Projectile-Point Technology II: An Agent-Based Computer Simulation." American Antiquity 73 (4): 627–44.
 
 \bibitem{Lehmann2009}
-Lehmann, L., and M.W. Feldman. Coevolution of adaptive technology, maladaptive culture, and population size in a producer-scrounger game. Proc.\ Roy.\ Soc.\ B 276 (2009): 3853-3862.
+Lehmann, L., and M.W.
+Feldman.
+(2009) Coevolution of adaptive technology, maladaptive culture, and population size in a producer-scrounger game.
+Proceedings of the Royal Society B: Biological Sciences 276: 3853-3862.
 
@@
 Aoki.
-The driving forces of cultural complexity: Neanderthals, modern humans, and the question of population size.
-Hum.\ Nat.\ (2017): 28: 39-52.
+(2017) The driving forces of cultural complexity: Neanderthals, modern humans, and the question of population size.
+Human Nature : 28: 39-52.
 
@@
 Feldman.
-2023.
-“Conditions That Favour Cumulative Cultural Evolution.” Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
+(2023) "Conditions That Favour Cumulative Cultural Evolution." Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
+
+\bibitem{payoff} Hong, Ze. (2022) "Combining Conformist and Payoff Bias in Cultural Evolution: An Integrated Model for Human Decision-Making." Human Nature 33.4: 463-484.
 

### 2023-11-08 ms/ms.tex
finished with rev1 revisions

@@
 For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{anti-conformity} \citep{conformism}.
-The effects of conformity and anti-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.
+The effects of conformity and anti-conformity on cultural evolution have been studied with both models \citep{Denton2020,Denton2021,Denton2022} and experiments \citep{negativeFrequency}.
 Indirect bias occurs when a copier uses some observed phenotype to evaluate the attractiveness of a potential role-model. 
@@
 The distinction between success and prestige bias is important, as prestige is a context-dependent bias, rather than a content-dependent bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
-Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity \citep{anticonformity,Denton2021,conformity}, which depends on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
+Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity \citep{Denton2020,Denton2021,Denton2022}, which depends on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
 
@@
 Note that our transmission models are slightly different from those modeled before, e.g.
-\citep{cumul_culture,anticonformity,evolutionBook}, in which the population is infinite and each copier samples $n$ role-models and then copies its trait from one or more of the sampled role-models.
+\citep{cumul_culture,Denton2021,evolutionBook}, in which the population is infinite and each copier samples $n$ role-models and then copies its trait from one or more of the sampled role-models.
 
@@
 To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DM, \Cref{cor:dirichlet}).
-The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and influence is a characteristic of the role-model and not the copier.
+The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and prestige is a characteristic of the role-model and not the copier.
 
 Analyzing the model with the DM distribution, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
-Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the difference between the resident and invading cultural trait values, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) increasing the relative weight of influence versus success bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
+Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the strength of success bias towards the invading cultural trait, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) decreasing the relative weight of success versus prestige bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
 
@@
 
-Lastly, we examined a scenario in which copiers can adjust their success-weight bias, $\alpha$, to minimize their copying error, i.e., copy trait values closer to the optimal value.
+Lastly, we examined a scenario in which copiers can adjust their success-bias weight, $\alpha$, to minimize their copying error, i.e., copy trait values closer to the optimal value.
 We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight (adjusted by copiers) and the estimation error decrease. 
@@
 The rationale, then, is that the more information a copier has, e.g., by using others as information sources, the more informative and effective his choice can be.
-
-Others have analyzed models with interactions between different transmission biases.
-Ze Hong~\citep{payoff} studied a model with both frequency-dependent bias (including conformist bias) and payoff bias.
-The analysis demonstrates that an integrated learning strategy may be superior to relying on either bias alone.
-Moreover, both biases are likely to contribute to the spread of variants with high payoff, and the magnitude of conformist bias affects the evolutionary dynamics.
-% TODO add: 
-% Ammar, Madeleine, Laurel Fogarty, and Anne Kandler.
-2023.
-“Social Learning and Memory.” Proceedings of the National Academy of Sciences 120 (33): e2310033120.
-https://doi.org/10.1073/pnas.2310033120.
-% Enquist, Magnus, and Stefano Ghirlanda.
-2007.
-“Evolution of Social Learning Does Not Explain the Origin of Human Cumulative Culture.” Journal of Theoretical Biology 246 (1): 129–35.
-https://doi.org/10.1016/j.jtbi.2006.12.022.
-% Denton, Kaleda K., Yoav Ram, and Marcus W.
-Feldman.
-2022.
-“Conformity and Content-Biased Cultural Transmission in the Evolution of Altruism.” Theoretical Population Biology 143 (February): 52–61.
-https://doi.org/10.1016/j.tpb.2021.10.004.
 
@@
 According to Henrich and Broesch~\citep{fijian_social_bias}, natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
-They authors studied Fijian villages to examine if and how such biases emerge in a small-scale society.
+The authors studied Fijian villages to examine if and how such biases emerge in a small-scale society.
 They found that Fijian villagers are more likely to learn from role-models perceived as more successful/knowledgeable, both within and across domains.
@@
 
+Others have analyzed models with interactions between different transmission biases.
+Hong~\citep{payoff} studied a model with both conformity and success bias (which he calls `payoff bias'). 
+He showed that an intermediate level of conformity bias--not too little but not too much--can be adaptive and evolve to prevent invasion of low-success traits while allowing the invasion of high-success traits (for another example of adaptive filtering, see~\citep{adaptive_filtering}).
+Similar to our model (\cref{eq:prestige}), Hong~\citep{payoff} also additively combined the two transmission biases (his eq.~1). However, transmission biases can be combined in many ways. 
+For example, Denton et al.~\citep{Denton2022} combined frequency-dependent bias and genetically determined content bias multiplicatively (their eq.~1). 
+Ammar et al.~\citep{Ammar2023} studied a model in which individuals have a repertoire of cultural variants to choose from, and both variant choice and transmission via social learning are success-biased.
+Moreover, they also included the possibility to `forget' infrequently used variants; therefore, because usage is success-biased, memory is also success-biased.
+It remains to be seen how different assumptions on the mechanisms of learning and forgetting affect the evolutionary dynamics under different and interacting transmission biases.
+
 Another way to expand our model is to account for the two types of prestige or leadership suggested by Van Vugt and Smith~\citep{dual_leadership} that are attributed to Confucius and Machiavelli.
@@
 \paragraph{Conclusions.}
-We studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with prestige bias, which has so far received less attention.
+We studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with prestige bias, which has so far received less attention by modelers.
 We found approximations for this complex dynamics.
@@
 This work was supported in part by 
-Minerva Stiftung Center for Lab Evolution (YR) and  the John Templeton Foundation (YR 61809).
+Minerva Stiftung Center for Lab Evolution~(YR) and  the John Templeton Foundation~(YR 61809).
 }
+
+\newpage
 
@@
 
-\bibitem{conformity}
+\bibitem{Denton2022}
 Denton, Kaleda K., Yoav Ram, and Marcus W. Feldman. (2022) "Conformity and content-biased cultural transmission in the evolution of altruism." Theoretical Population Biology 143: 52-61.
 
-\bibitem{anticonformity}
-Denton, Kaleda Krebs, Yoav Ram, Uri Liberman, and Marcus W. Feldman. (2020) "Cultural Evolution of Conformity and Anticonformity." Proceedings of the National Academy of Sciences 117 (24): 13603–14.
+\bibitem{Denton2021}
+Denton, Kaleda K., Uri Liberman, and Marcus W. Feldman. (2021) "On randomly changing conformity bias in cultural transmission." Proceedings of the National Academy of Sciences 118.34: e2107204118.
+
+\bibitem{Denton2020}
+Denton, Kaleda Krebs, Yoav Ram, Uri Liberman, and Marcus W. Feldman. (2020) "Cultural evolution of conformity and anticonformity." Proceedings of the National Academy of Sciences 117 (24): 13603–14.
 
@@
 (2022) "Differential Application of Cultural Practices at the Family and Individual Levels May Alter Heritability Estimates." Behavioral and Brain Sciences 45 (September): e167.
-
-\bibitem{Denton2021}
-Denton, Kaleda K., Uri Liberman, and Marcus W. Feldman. (2021) "On randomly changing conformity bias in cultural transmission." Proceedings of the National Academy of Sciences 118.34: e2107204118.
 
@@
 
-\bibitem{Fogarty2017}Fogarty, L., J.
-Y.
-Wakano, M.
-W.
-Feldman, and K.
-Aoki.
-(2017) The driving forces of cultural complexity: Neanderthals, modern humans, and the question of population size.
-Human Nature : 28: 39-52.
-
-\bibitem{cumul_culture}Denton, Kaleda K, Yoav Ram, and Marcus W.
-Feldman.
-(2023) "Conditions That Favour Cumulative Cultural Evolution." Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
-
-\bibitem{payoff} Hong, Ze. (2022) "Combining Conformist and Payoff Bias in Cultural Evolution: An Integrated Model for Human Decision-Making." Human Nature 33.4: 463-484.
+\bibitem{Fogarty2017} 
+Fogarty, L., J. Y. Wakano, M. W. Feldman, and K. Aoki. (2017) The driving forces of cultural complexity: Neanderthals, modern humans, and the question of population size. Human Nature : 28: 39-52.
+
+\bibitem{cumul_culture}
+Denton, Kaleda K, Yoav Ram, and Marcus W. Feldman. (2023) "Conditions That Favour Cumulative Cultural Evolution." Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
+
+\bibitem{payoff}
+Hong, Ze. (2022) "Combining Conformist and Payoff Bias in Cultural Evolution: An Integrated Model for Human Decision-Making." Human Nature 33.4: 463-484.
+
+\bibitem{adaptive_filtering}
+ Enquist, Magnus, and Stefano Ghirlanda. (2007) "Evolution of Social Learning Does Not Explain the Origin of Human Cumulative Culture." Journal of Theoretical Biology 246 (1): 129–35.
+
+\bibitem{Ammar2023}
+Ammar, Madeleine, Laurel Fogarty, and Anne Kandler. (2023) "Social Learning and Memory." Proceedings of the National Academy of Sciences 120 (33): e2310033120.
 

### 2023-11-09 ms/ms.tex
statements on the different models used; DM->DMD

@@
 
-Here, we develop a stochastic model of cultural transmission with both cross-domain indirect success bias and prestige bias to examine their relationship in contribution to the cultural evolution of populations.
+Here, we develop a stochastic model of cultural transmission with both indirect success bias and prestige bias to examine their relationship in contribution to the cultural evolution of populations.
 We find analytic approximations for this model and analyze its dynamics.
-We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is subject to success bias).
+We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is subject to success bias) in both a constant and a cyclic changing environment.
 Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and prestige bias play the role of natural selection and genetic drift, respectively.
@@
 \section*{Models}
-We begin with a continuous trait model with indirect success bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}.
-We extend this model to include prestige bias.
-We then develop a dichotomous trait model.
+We begin with a continuous-trait model with indirect success bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}.
 Note that the indirect success bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
+We extend this model to include prestige bias and then develop a version of the model with a dichotomous trait to facilitate mathematical analysis.
 
@@
 
-\paragraph{Generalized binomial approximation.}  
+\paragraph{Generalized binomial distribution approximation.}  
 The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore, 
-
 (i) the expected number of copiers of role-model~$j$ equals its influence in the eyes of the first copier, multiplied by the total number of copiers, that is,
@@
 
-\paragraph{Dirichlet-Multinomial approximation.}
+\paragraph{Dirichlet-Multinomial distribution approximation.}
 The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$). 
-
-\subsection*{Generalized binomial distribution}
+% TODO missing summary like GBD?
+
+After finding these approximations for the role-model choice process, we focus on the dichotomous-trait model, in which mathematical analysis is simpler, and studied the fixation probability and time in both a constant and a periodically changing environment.
+
+\subsection*{Generalized binomial distribution (GBD) approximation}
 The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is {denoted}  by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials (the latter can be estimated from data, but its value is insignificant for our approximation).
@@
 
-\begin{result}[Generalized binomial approximation]\label{res:GBD}
-The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the generalized binomial distribution, $K_{i,j} \sim GBD(i,\alpha_j\cdot\beta(A_j+e),\theta)$ if $e_i=e$ for all role-models $i=1, \ldots, N$, and $\theta$ is the correlation between successive role-model choices.
+\begin{result}[Generalized binomial distribution approximation]\label{res:GBD}
+The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the generalized binomial distribution, $$K_{i,j} \sim \textit{GenBin}(i,\alpha_j\cdot\beta(A_j+e),\theta)$$ if $e_i=e$ for all role-models $i=1, \ldots, N$, and $\theta$ is the correlation between successive role-model choices.
 \end{result}
@@
 
-Although basic, \Cref{fig:GBD} shows good fit of the GB approximation.
-This validation is initial, and {we do} more extensive validations on the Dirichlet-Multinomial approximation, because {that} is what we will use in our {analysis}.
+Although basic, \Cref{fig:GBD} shows good fit of the GBD approximation.
+We perform more extensive validations on the Dirichlet-Multinomial approximation (see below), because that is what we will use in our analysis.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Dirichlet-Multinomial distribution approximation}
+\subsection*{Dirichlet-Multinomial distribution (DMD) approximation}
 
@@
 
-\begin{corollary}\label{cor:dirichlet}
-The number of copiers of each role-model {approximates} a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \emph{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
+\begin{corollary}[Dirichlet-Multinomial distribution approximation]\label{cor:dirichlet}
+The number of copiers of each role-model approximates a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \textit{DirMul}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
 \end{corollary}
@@
 \paragraph{Numerical validation.}
-We next validated the DM approximation of our model
-and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DM approximation (\Cref{cor:dirichlet}).
+We next validated the DMD approximation of our model
+and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DMD approximation (\Cref{cor:dirichlet}).
 We used a relatively small population size, $N=100$, thus validating that the approximation is in good agreement even for small $N$, despite the assumption of large $N$ in the proof by Frigyik et al.~\citep[section 2]{dirichlet}.
 First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then compared this observed distribution with the expected theoretical DM distribution (\Cref{fig:DM_validation}A).
+We then compared this observed distribution with the expected theoretical DMD (\Cref{fig:DM_validation}A).
 The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
 The maximum difference is 0.5 role-models, which indicates a very good fit.
-In addition, we tested the likelihood of the observed data to be drawn from the DM distribution, against a shuffle of the parameters vector of the DM distribution itself (\Cref{fig:DM_validation}B).
+In addition, we tested the likelihood of the observed data to be drawn from the DMD, against a shuffle of the parameters vector of the DMD itself (\Cref{fig:DM_validation}B).
 We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, strongly supporting our approximation.
 
-Next, we examined the fixation probability and fixation time of a favored phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
+Next, we examined the fixation probability and fixation time of a favored phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DMD approximation.
 Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
-We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
-We examined the robustness of the DM approximation to relaxing the following assumptions.
+We find that the number of simulations needed to sufficiently approximate our model with the DMD approximation is roughly $1,000$ (\Cref{fig:num_sims}).
+We examined the robustness of the DMD approximation to relaxing the following assumptions.
 First, we relaxed our assumption of no estimation error $e$.
@@
 \subsection*{Fixation probability and time}
-After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
+After finding that the DMD is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
 We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
 We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and prestige bias, given by \cref{eq:prestige}.
-For simplicity, we use the dichotomous model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
-As shown above, transmission in our model is approximately DM distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
+
+For simplicity, we use the dichotomous-trait model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
+As shown above, transmission in our model is approximately Dirichlet-Multinomial distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
 
@@
   Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis), or effective population size $N_e$ (top x-axis) in the top row, and as a function of the success coefficient, $1-\beta$, on the bottom row.
-  The approximation (black; \cref{eq:kimura_p}) agrees with both DM simulations (green) and Wright-Fisher simulation (orange).
+  The approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulation (orange).
   Fixation probability (A) is bounded by $2(1-\beta)$ (dashed line).
@@
 \paragraph*{Changing environment}.
-After finding a good approximation in a constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a periodically changing environment.
+After finding a good approximation in a constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a cyclic changing environment.
 Following \citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
@@
 \paragraph{Numerical validation.}
-To validate the the approximation for the fixation probability in a changing environment (\cref{eq:ch_env}), we compare it to results of simulations that use the DM approximation (\Cref{cor:dirichlet}).
+To validate the the approximation for the fixation probability in a changing environment (\cref{eq:ch_env}), we compare it to results of simulations that use the DMD approximation (\Cref{cor:dirichlet}).
 We find that the approximation fits the simulation results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
@@
 
-We developed a cultural-evolutionary model that includes both indirect success and prestige biases, where the latter is a bias towards role-models with many copiers.
+We developed two cultural-evolutionary models, one with continuous and one with dichotomous trait values.
+Our models include both indirect success and prestige biases, where the latter is a bias towards role-models with many copiers.
 We model these biases using a stochastic role-model choice process: each copier, in turn, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
-
-Hence, our model has two ``nested'' stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
-To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DM, \Cref{cor:dirichlet}).
+Hence, our models have two ``nested'' stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
+To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DMD, \Cref{cor:dirichlet}).
 The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and prestige is a characteristic of the role-model and not the copier.
 
-Analyzing the model with the DM distribution, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
+Analyzing the dichotomous-trait model using the the DMD approximation, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
 Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the strength of success bias towards the invading cultural trait, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) decreasing the relative weight of success versus prestige bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
 
-We also analyzed a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
+We also analyzed the dichotomous--trait model in a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
 We find that, similarly to the constant environment approximation, a change in the success-bias weight $\alpha$ has no negative effects on the goodness-of-fit of the approximation to simulation results.
@@
 
-Using the variance of the DM distribution,
+Using the variance of the DMD,
 \begin{equation}
@@
   \textbf{Numerical validation of the DM approximation.}
-  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared the distribution of the number of copiers to simulations when using the DM distribution approximation (\Cref{cor:dirichlet}).
+  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared the distribution of the number of copiers to simulations when using the DMD approximation (\Cref{cor:dirichlet}).
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
-  \textbf{(B)} The log-likelihood of the DM distribution for results of the simulations (red vertical line) is much higher {than} the log-likelihood of permutations of simulations (blue histogram).
+  \textbf{(B)} The log-likelihood of the DMD for results of the simulations (red vertical line) is much higher {than} the log-likelihood of permutations of simulations (blue histogram).
   Here, population size, $N=100$; number of simulations, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
@@
   \caption{
-  \textbf{DM Approximation precision as function of number of simulations.}
-  Our DM approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
+  \textbf{DMD approximation precision as function of number of simulations.}
+  Our DMD approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
   Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
@@
   \caption{
-  \textbf{Robustness of DM approximations to success estimation error.}
-  Both the DM approximation (orange) and our approximation (black) agree with the stochastic simulations (blue), even with a high estimation error.
+  \textbf{Robustness of DMD approximations to success estimation error.}
+  Both the DMD approximation (orange) and our approximation (black) agree with the stochastic simulations (blue), even with a high estimation error.
   Markers are averages across simulations, error bars are 95\% confidence intervals.

### 2023-11-12 ms/ms.tex
update

@@
 Markers show average of $10,000$ simulations, error bars show 75\% (panels A, C, and D) and 95\% (panel B) confidence intervals.
-  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$ (panels A and B) and $A=0.8$ (panels C and D); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B, C, and D, the success-bias weight is $\alpha=0.1$.
+  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$, $k=20$, $l=80$ (panels A and B) and $A=0.8$ (panels C and D); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B, C, and D, the success-bias weight is $\alpha=0.1$.
   }
@@
 The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
-Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}
+Here "Copier" of the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}
   \label{fig:influence_advantage}

### 2023-11-12 ms/ms.tex
continue revision..

--- 2023-11-09 ms/ms.tex
@@
 \subsection*{Optimal success-bias weight}
-% TODO edit the next sentence.
+% TODO edit the next sentence -- mention this is in the continous trait model
+In the above, we assumed that $\alpha$ is homogeneous in the population. 
+Next
 We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
@@
 They show that the social networks representing copier--role-model relationships are centralized, which is consistent with the prediction that people substantially share notions about who is a good cultural model, but that individuals' role-model selections are influenced by multiple factors.
+
+Dunbar~\citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
+Following this, Muthukrishnan and Henrich \citep{collective_brains} suggested that prestige can directly affect human physical evolution.
+They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
+They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. 
+They also presented the \emph{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
+As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge.
+These strategies and biases include direct and indirect cues of the popularity of cultural traits (e.g.
+success and prestige biases).
+They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to `cheaply' acquire adaptive knowledge via transmission biases such as prestige.
 
@@
 
-Dunbar~\citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
-Following this, Muthukrishnan and Henrich \citep{collective_brains} suggested that prestige can directly affect human physical evolution.
-They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
-They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. 
-They also presented the \emph{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
-As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge.
-These strategies and biases include direct and indirect cues of the popularity of cultural traits (e.g.
-success and prestige biases).
-They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to `cheaply' acquire adaptive knowledge via transmission biases such as prestige.
-
-One path forward is an analysis of the dynamics of the optimal success-bias weight model, in which every copier chooses its $\alpha$.
-It would be interesting to see the if the mean estimation error and the varying weight, $\alpha^*$, converge to specific values, and how they are affected by the model parameters.
-It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
-Lastly, it would be interesting to analyze the continuous model and determine how much it differs from the dichotomous model.
-
 Others have analyzed models with interactions between different transmission biases.
@@
 It remains to be seen how different assumptions on the mechanisms of learning and forgetting affect the evolutionary dynamics under different and interacting transmission biases.
+
+One path forward is an analysis of the dynamics of the optimal success-bias weight model, in which every copier chooses its $\alpha$.
+It would be interesting to see the if the mean estimation error and the varying weight, $\alpha^*$, converge to specific values, and how they are affected by the model parameters.
+It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
+Lastly, it would be interesting to analyze the continuous model and determine how much it differs from the dichotomous model.
 

### 2023-11-12 ms/ms.tex
continue revision for rev2

--- 2023-11-12 ms/ms.tex
@@
 where $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
-
-Here, the bias weight $\alpha_{i,j}$ determines the relative weighting of success and prestige bias.
+Here, the success-bias weight $\alpha_{i,j}$ determines the relative weighting of success and prestige bias.
 It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs.
@@
 All role-models with the same phenotype will contribute to the probability that that phenotype is transmitted and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
-In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous, {which entails} exchangeability between role-models.
-Therefore, the probability {that} the $i$-th copier {copies} phenotype $A$ is
+In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous and constant ($\alpha_{i,j}=\alpha$), which entails exchangeability between role-models.
+Therefore, the probability that the $i$-th copier {copies} phenotype $A$ is
 \begin{equation}\label{eq:binary-model}
-G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i-1,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
-\end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$; $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model; assuming that $\beta(\hat{A})=1$; and defining $\alpha'= \frac{\alpha}{1-\alpha}$ as the odds ratio of the bias weight.
+%G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i-1,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
+G_{i,A} = \frac{\alpha \cdot (N-X) \beta(A) + (1-\alpha) \cdot K_{i-1,A}}{\alpha \cdot (N-X) \beta(A) + \alpha \cdot X + (1-\alpha)\cdot(i-1)} \;,
+\end{equation}
+where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i-1,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, and assuming that $\beta(\hat{A})=1$ (thus the term $\alpha X$ in the denominator).
 Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
@@
 We found two approximations for the distribution of $\vec{K}_{N}$, summarized here and explained in detail below.
-In both we assume that the bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_{i,j}=\alpha_j$ is a bias of role-model $j$ only, meaning it does not vary between copiers.
+In both approximations we assume that the success-bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_{i,j}=\alpha_j$ is a characteristic of role-model $j$ that does not vary between copiers.
 Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.
@@
 \begin{result}[Generalized binomial distribution approximation]\label{res:GBD}
-The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the generalized binomial distribution, $$K_{i,j} \sim \textit{GenBin}(i,\alpha_j\cdot\beta(A_j+e),\theta)$$ if $e_i=e$ for all role-models $i=1, \ldots, N$, and $\theta$ is the correlation between successive role-model choices.
+The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the generalized binomial distribution, 
+$$
+K_{i,j} \sim \textit{GenBin}(i,\alpha_j\cdot\beta(A_j+e),\theta)
+$$
+if $e_i=e$ for all copiers $i=1, \ldots, N$; the success-bias weight only depends on the role-model and not the copier, i.e., $\alpha_{i,j}=\alpha_j$  for all $i=1, \ldots, N$; and $\theta$ is the correlation between successive role-model choices.
 \end{result}
@@
 \begin{result}[P{\'{o}}lya urn model]\label{result:polya}
-The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \emph{P\'{o}lya urn model} if both trait estimation error and bias weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
+The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \emph{P\'{o}lya urn model} if both the trait estimation error and the success-bias weight are constant in the population, $e_i=e$ for all $i=1, \ldots, N$ and $\alpha_{i,j}=\alpha$  for all $i,j=1, \ldots, N$.
 \end{result}
@@
 \begin{proof} 
-{Write} $\alpha'=\frac{\alpha}{1-\alpha}$ as the bias weight ratio, and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
+{Write} $\alpha'=\frac{\alpha}{1-\alpha}$ as the success-bias weight ratio, and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
 \begin{equation}\label{eq:copier_choose}
@@
 
-For simplicity, we use the dichotomous-trait model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
+For simplicity, we use the dichotomous-trait model, which also assumes a constant success-bias weight $\alpha_{i,j}=\alpha$, and we do not include trait estimation error in this analysis, i.e., $e_i=0$.
 As shown above, transmission in our model is approximately Dirichlet-Multinomial distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
@@
 With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak "selection" .
-(\textbf{C,D}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias.
+(\textbf{C}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias.
 When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
-Markers show average of $10,000$ simulations, error bars show 75\% (panels A, C, and D) and 95\% (panel B) confidence intervals.
-  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$, $k=20$, $l=80$ (panels A and B) and $A=0.8$ (panels C and D); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B, C, and D, the success-bias weight is $\alpha=0.1$.
+Markers show average of $10,000$ simulations, error bars show 75\% (panels A and C) and 95\% (panel B) confidence intervals.
+Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$, $k=20$, $l=80$ (panels A and B) and $A=0.8$ (panel C); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B and C, the success-bias weight is $\alpha=0.1$.
   }
@@
 \subsection*{Optimal success-bias weight}
-% TODO edit the next sentence.
-We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
+In results 2-6, we assumed that $\alpha$ is homogeneous in the population and constant, that is, it does not depend on any specific context.
+Next, we examined what happens in the continuous-trait model if the $i$-th copier evaluates its own optimal success-bias weight, $\alpha^*_i$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
 \begin{equation}\label{eq:optimal_alpha}
-\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l} (\hat{A}-A_j)^2 \;,
-\end{equation}
-where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
-Simply put, each copier estimates what success-bias weight $\alpha^*$ will result in copying a trait that is most similar to the ideal trait value $\hat{A}$.
+\alpha^*_i = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_{i-1,j}}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_{i-1,l}} (\hat{A}-A_j)^2 \;,
+\end{equation}
+where $A_j$ is the trait of role-model $j$ and $K_{i-1,j}$ is the number of copiers that already chose role-model~$j$ by the time the $i$-the copier chooses a role-model.
+Simply put, each copier $i$ estimates what success-bias weight $\alpha^*_i$ will result in copying a trait that is most similar to the ideal trait value $\hat{A}$.
 Indeed, if the trait value is correlated with fitness, the optimal success-bias weight would increase the fitness of individuals.
@@
 
-We find that when copiers choose their success-bias weight according to \cref{eq:optimal_alpha}, it decreases with the number of copiers that have already chosen a role-model~(\Cref{fig:influence_advantage}).
+We find that when copiers choose their success-bias weight according to \cref{eq:optimal_alpha}, it quickly decreases with the number of copiers that have already chosen a role-model and then stays at what appears to be an equilibrium~(\Cref{fig:influence_advantage}).
 Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the optimal success-bias weight gives an estimation error (difference between the chosen and optimal trait) converges to $0.046$, whereas a constant success-bias weight gives values $>0.74$.
@@
   Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
-However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
+However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error does not decrease, regardless of $\alpha$ or $\eta$.
 The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
-Here "Copier" of the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}
+Here "Copier" of the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
+% lines are also 300 simulations? why not markers? 
+% what are error bars in C? CI 99%
+% C x axis should say "Constant success-bias weight"
+% A B x axis should say "Copier $i$; A y axis should be "Optimal success-bias weight, \alpha^*_i$.
+}	
   \label{fig:influence_advantage}

### 2023-11-14 ms/ms.tex
update
fix fig 1 caption

@@
 \end{equation} 
-with $\hat{A}$ as the arbitrary optimal trait value, and $J$ and $b$ as parameters that control the bias strength.
+with $\hat{A}$ as the arbitrary optimal trait value, and $J$ and $b$ as parameters that control the bias strength; unless otherwise mentioned, we set $b=J=1$.
 Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$.
@@
   \caption{\textbf{Fixation probability and time in a constant environment.}
-  Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis), or effective population size $N_e$ (top x-axis) in the top row, and as a function of the success coefficient, $1-\beta$, on the bottom row.
-  The approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulation (orange).
-  Fixation probability (A) is bounded by $2(1-\beta)$ (dashed line).
+  Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) in panels A and B, and as a function of the effective selection coefficient, $1-\beta$, in panels C and D.
+  The approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
+  The fixation probability in panel A is bounded by $2(1-\beta)$ (dashed line).
   Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
-   Here, Population size, $N=1,000$; phenotype values, $A=0.7$ (panels A and B), 
-   $A/\hat{A}$ varies between 0.01 and 0.99 (panels C and D), and $\hat{A}=1$, which affects $\beta$ via \cref{eq:drift_diff};
-   success coefficient, $1-\beta=s=0.044$ (panels A and B); 
-   success-bias weight, $\alpha=0.01$ (panels C and D).
+   Here, population size is $N=1,000$; in panels A and B, $A=0.7$, $\hat{A}=1$, and $1-\beta=0.044$; in panels C and D, $\alpha=0.01$, $\hat{A}=1$, and $0.01 < A< 0.99$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}.
    }
@@
 \begin{figure}[H]
-    \includegraphics[width=\linewidth]{ch_env.pdf}
+	\centering
+    \includegraphics[width=0.6\linewidth, height=0.7\textheight,keepaspectratio]{ch_env.pdf}
   \caption{\textbf{Fixation probability in a changing environment.}
@@
 Markers show average of $10,000$ simulations, error bars show 75\% (panels A and C) and 95\% (panel B) confidence intervals.
-Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$ with $A=0.9$, $k=20$, $l=80$ (panels A and B) and $A=0.8$ (panel C); In panel A, the success coefficient is $1-\beta=s=0.005$; In panels B and C, the success-bias weight is $\alpha=0.1$.
+Here, population size $N=1,000$; $\hat{A}=1$, $A=0.9$, $k=20$ and $l=80$ (panels A and B); $A=0.8$, (panel C); in panel A, the success coefficient is $1-\beta=s=0.005$; in panels B and C, the success-bias weight is $\alpha=0.1$.
   }

### 2023-11-15 ms/ms.tex
more revising for rev2

@@
 Note that the indirect success bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
-We extend this model to include prestige bias and then develop a version of the model with a dichotomous trait to facilitate mathematical analysis.
+We extend this model to include prestige bias, which introduces a within-generation model-choice process.
+To facilitate mathematical analysis, we also develop a simpler version of the model with a dichotomous trait.
 
@@
 As shown above, transmission in our model is approximately Dirichlet-Multinomial distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
+We focus on two scenarios: the first scenario is of a `constant environment' in which the same phenotype, $\hat{A}$, is always favored by success bias; the second scenario is of a `changing environment' in which the phenotype favored by success bias cycles between the invading phenotype $\hat{A}$ and the resident phenotype $A$ (i.e., $\hat{A}$ starts as the rare phenotype).
 

### 2023-11-15 ms/ms.tex
typos and small mistakes

@@
 Henrich and Gil-White~\citep{prestige_evolution} noted that ``the most skilled/knowledgeable role-models will, on average, end up with the biggest and most lavish clienteles, so the size and lavishness of a given model's clientele size (the \emph{prestige}) provides a convenient and reliable proxy for that person's information quality''.
-Therefore, they predicted that skilled individuals have higher status, that people preferentially copy high-status individuals, and therefore that prestigious individuals may be influential even beyond their domain of expertise.
+Thus, they predicted that skilled individuals have higher status, that people preferentially copy high-status individuals, and therefore that prestigious individuals may be influential even beyond their domain of expertise.
 They defined prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature \citep{prestige_evolution} .
@@
 Here, we develop a stochastic model of cultural transmission with both indirect success bias and prestige bias to examine their relationship in contribution to the cultural evolution of populations.
-We find analytic approximations for this model and analyze its dynamics.
+We find analytic approximations for this model.
 We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is subject to success bias) in both a constant and a cyclic changing environment.
@@
 Consider a population of $N$ individuals, described by a single trait that takes continuous values.
-Each generation, $N$ naive individuals, or copiers, each chooses a single role-model from the entire previous generation. The copier then copies its trait value from the chosen role-model.
+At each generation, $N$ naive individuals, or copiers, each choose a single role-model from the entire previous generation. Each copier then copies its trait value from the chosen role-model.
 Note that our transmission models are slightly different from those modeled before, e.g.
@@
 Similar to a Wright-Fisher model, generations are non-overlapping, and the entire population is replaced in each generation.
-The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t$, and  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
+The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is the trait value of individual $i$ at time $t$, and  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
 Cultural transmission is modeled by a function $F$ such that 
@@
 \end{equation}
-$A_{i,j}$ is the absolute trait value {that} copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
+$A_{i,j}$ is the absolute trait value that copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
 \begin{equation}\label{eq:relativeTrait}
@@
 Boyd and Richerson~\citep{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
-We {can} develop a similar stochastic model with transmission from a single random role-model where instead of \cref{eq:boydF}, we define the transmission function $F$ as a random variable with its distribution given by
+We develop a similar stochastic model with transmission from a single random role-model where instead of \cref{eq:boydF} we define the transmission function $F$ as a random variable with its distribution given by
 \begin{equation}\label{eq:ourF}
@@
 \paragraph{Prestige bias.}
-Here we introduce a new element to the model by assuming that in each generation, copiers choose their role-models one by one.
+We introduce a new element to the model by assuming that in each generation copiers choose their role-models one by one so that the choice of one copier can affect the choice of other copiers.
 We formulate this assumption in the following.
@@
 Here, the success-bias weight $\alpha_{i,j}$ determines the relative weighting of success and prestige bias.
-It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs.
-prestige in the role-model's overall influence in the eyes of the copier.
+It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of  success vs.
+prestige bias in the role-model's overall influence in the eyes of the copier.
 Different individuals may evaluate the importance of success and prestige differently.
@@
 We introduce a simplified version of the above model where the trait has only two phenotypes: an optimal phenotype $\hat{A}$ and a sub-optimal phenotype $A$. 
-All role-models with the same phenotype will contribute to the probability that that phenotype is transmitted and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
+All role-models with the same phenotype will contribute to the probability that that phenotype is transmitted and thus prestige is determined by the number of copiers that have already chosen a role-model with either phenotype.
 In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous and constant ($\alpha_{i,j}=\alpha$), which entails exchangeability between role-models.
@@
 The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$). 
-% TODO missing summary like GBD?
-
-After finding these approximations for the role-model choice process, we focus on the dichotomous-trait model, in which mathematical analysis is simpler, and studied the fixation probability and time in both a constant and a periodically changing environment.
+Hence, the number of copiers of each role-model $\vec{K_{N}}$ at the end of the role-model choice process follows the Dirichelet-Multinomial distribution.
+
+After finding these approximations for the role-model choice process, we focus on the dichotomous-trait model, in which mathematical analysis is simpler, and studied the fixation probability and time in both a constant and a changing environment.
 
@@
 
-From \Cref{cor:GBD} we see that if there is no success bias, meaning $Q_j(1,1)=q$ for $j$ in $1,...,N$, then the expected number of copiers will be Binomial distributed.
-This proves that prestige bias is not frequency dependent.
+% TODO this is wierd
+From \Cref{cor:GBD} we see that without success bias ($\alpha=0$), the expected number of copiers of each role-model is one. Hence, prestige bias is not frequency dependent.
 
@@
 \paragraph{Numerical validation.}
-To validate that GBD approximation for the number of copiers of a role-model is correct (\cref{eq:GBDsamelalpha}), % check that this is the correct equation reference. It is
+To validate that the GBD approximation for the number of copiers of a role-model is correct (\cref{eq:GBDsamelalpha}), 
 we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
-We compare the distribution of number of copiers by plotting the histograms of both our simulations results and the expected values based on \Cref{cor:GBD}.
-
-Although basic, \Cref{fig:GBD} shows good fit of the GBD approximation.
+We compare the distribution of the number of copiers by plotting the histograms of both our simulation results and the expected values based on \Cref{cor:GBD}.
+
+Although basic, \Cref{fig:GBD} shows a good fit of the GBD approximation.
 We perform more extensive validations on the Dirichlet-Multinomial approximation (see below), because that is what we will use in our analysis.
@@
 \begin{corollary}[Dirichlet-Multinomial distribution approximation]\label{cor:dirichlet}
-The number of copiers of each role-model approximates a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \textit{DirMul}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
+The number of copiers of each role-model approximates a Dirichlet-Multinomial distribution, $\vec{K_N} \sim \textit{DirMul}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
 \end{corollary}
@@
 	\centering
-    \includegraphics[width=0.6\linewidth, height=0.7\textheight,keepaspectratio]{ch_env.pdf}
+    \includegraphics[width=\linewidth]{ch_env.pdf}
   \caption{\textbf{Fixation probability in a changing environment.}
@@
 It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
-Lastly, it would be interesting to analyze the continuous model and determine how much it differs from the dichotomous model.
+Another possibility is to model prestige bias in a different way.
+For example, using a Moran model \citep{Moran1958}, one could build model with overlapping generations, which would mix the within-generation model role-model choice process and the between-generation evolutionary dynamics.
+Lastly, it would be interesting to analyze the fixation probability and time in the continuous model and determine how the results compare to those from the dichotomous model.
 
@@
 Ammar, Madeleine, Laurel Fogarty, and Anne Kandler. (2023) "Social Learning and Memory." Proceedings of the National Academy of Sciences 120 (33): e2310033120.
+
+\bibitem{Moran1958}
+Moran, P. A. P. (1958) "Random Processes in Genetics." Mathematical Proceedings of the Cambridge Philosophical Society 54 (1): 60–71.
 

### 2023-11-16 ms/ms.tex
continue editing results

@@
 In this case prestige can be used as a convenient proxy for success.
-Here, we study the the joint effect of success and prestige bias on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
+Here, we study the joint effect of success and prestige bias on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
 Analytic approximations to the stochastic role-model choice process facilitate the mathematical analysis and reduce the computational complexity of simulations.
@@
 We find analytic approximations for this model.
-We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is subject to success bias) in both a constant and a cyclic changing environment.
+We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is subject to success bias) in both a constant and a periodically changing environment.
 Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and prestige bias play the role of natural selection and genetic drift, respectively.
@@
 
-Next, we examined the fixation probability and fixation time of a favored phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DMD approximation.
+Next, we examined the fixation probability and fixation time of a `successful' phenotype $\hat{A}$ (i.e., that is favored by success bias) when invading a population of phenotype $A$ and compared results from the full model and the DMD approximation.
 Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
@@
 First, we relaxed our assumption of no estimation error $e$.
-Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{i,j} = A_j + e_i$).
+Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the success `bias ($A_{i,j} = A_j + e_i$).
 When estimation error is applied, we sample $e_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$.
-Even when the estimation error variance is $0.1$, both the fixation probability and fixation time approximations are accurate~(\Cref{fig:hetro_error}). 
+Even when the estimation error variance is $0.1$, both the fixation probability and fixation time DMD approximations are accurate~(\Cref{fig:hetro_error}). 
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
-We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5,q)$ where $\epsilon$ is between $10^{-7}$ and $10^{-1}$.
-We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).
+We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5, \epsilon)$ where $\epsilon$ is between $10^{-7}$ and $10^{-1}$.
+We found again that results of the DMD approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).
 
@@
 After finding that the DMD is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
-We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
-We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and prestige bias, given by \cref{eq:prestige}.
+We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a `successful' phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
+We are mainly interested in the effect of the success-bias weight, $\alpha$, which determines the relative effect of success and prestige bias, given by \cref{eq:prestige}.
 
@@
 \begin{result}[Effective selection coefficient and population size]\label{res:selection_coef}
-The effective selection coefficient $s$ and effective population size $N_e$ can be written in terms of the success coefficient $\beta$ (\cref{eq:success_bias}), the bias weight $\alpha$ (\cref{eq:prestige}), and the population size $N$ as
+The effective selection coefficient $s$ and effective population size $N_e$ can be written in terms of the success coefficient $\beta$ (\cref{eq:success_bias}), the success-bias weight $\alpha$ (\cref{eq:prestige}), and the population size $N$ as
 \begin{equation}
@@
 We compare our approximations (\cref{eq:kimura_p,eq:kimura_t}) with results of simulations of our dichotomous model using various $\alpha$ and $\beta$ values, as well as simulations of the Wright-Fisher model, using the effective selection coefficient, $1-\beta$, and effective population size, $N_e=\alpha N + (1-\alpha)$.
-We find see that the two models have similar dynamics, and both are well approximated {by} our approximations (\Cref{fig:var_alpha}).
+We find that the two models have similar dynamics, and both are well approximated {by} our approximations (\Cref{fig:var_alpha}).
 
@@
 \paragraph*{Changing environment}.
-After finding a good approximation in a constant environment, where the favorable trait is always $\hat{A}$, we proceeded to find an approximation for a cyclic changing environment.
-Following \citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
+After finding a good approximation in a constant environment, where the `successful' trait is always $\hat{A}$, we proceeded to find an approximation for a periodically changing environment.
+Following Ram et al.~\citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
 Thus, during the first $k$ generations of the environmental cycle, $\beta=\frac{\beta(A)}{\beta(\hat{A})}$<1, where $\hat{A}$ is the invading phenotype.
@@
 
-Note that here, we have the average selection coefficient during a cycle of $n$ generations as the selection coefficient {in} \cref{eq:kimura_p}.
-Using the drift and diffusion terms and following \citep{changeEnv}, we can approximate the fixation probability in a changing environment.
+Note that here, we have the `average selection coefficient' during a cycle of $n$ generations, $S_n/n$ as the selection coefficient {in} \cref{eq:kimura_p}.
+Using the drift and diffusion terms and following Ram et al.~\citep{changeEnv}, we can approximate the fixation probability in a changing environment.
 \\
 
-\begin{result}[Fixation probability in a changing environment]\label{res:ch_expected}
+\begin{result}[Fixation probability in a periodically changing environment]\label{res:ch_expected}
 
@@
 
+Importantly, the average selection coefficient, $S_n/n$, has the same sign as $k-l$.
+Therefore, when $k>l$, the fixation probability will increase with the success-bias weight $\alpha$ (similar to a constant environment, \Cref{fig:var_alpha}A), and when $k<l$, the fixation probability will decrease with the success-bias weight $\alpha$ (\Cref{fig:ch_env_alpha_beta}A).
+Similarly, when the success coefficient $1-\beta$ is large, the approximation can break, as the fixation time can be lower then the number of generations in the cycle, $n$ (see \Cref{fig:var_alpha}D), and again the average selection coefficient, $S_n/n$ is not a good estimate of the effective selection coefficient.
+
 \paragraph{Numerical validation.}
-To validate the the approximation for the fixation probability in a changing environment (\cref{eq:ch_env}), we compare it to results of simulations that use the DMD approximation (\Cref{cor:dirichlet}).
-We find that the approximation fits the simulation results well for variable bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
-
+To validate the approximation for the fixation probability in a changing environment (\cref{eq:ch_env}), we compare it to results of simulations that use the DMD approximation (\Cref{cor:dirichlet}).
+We find that the approximation fits the simulation results well for variable success-bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
 However, the approximation is more sensitive to the value of the success bias coefficient $\beta$ (\Cref{fig:ch_env_alpha_beta}B).
-We suspect that when $\beta$ is too small, there will not be many cycles in the simulations, because either the population reaches a high frequency of the fitter phenotype after just a few cycles, or the fitter phenotype {goes} extinct very quickly.
-For such $\beta$ values (below 0.65), the fixation probability exceeds even the constant environment approximation (which is the upper limit).
-We note that the diffusion-equation approximation assumes weak selection, or in our case, weak success bias.
-
-We found that for a large $k/l$ ratio (with a constant cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}), see \Cref{fig:ch_env_alpha_beta}C and \Cref{fig:ch_env_alpha_beta}D.
-
-The approximation follows the trend of the simulation results for all $\alpha$ values.
-{On} increasing the success coefficient {$\alpha$} to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation.
-We believe the reason is the structure of the cycle.
-Our proof and approximation in the changing environment are for a large {number} of cycles, and when the success coefficient {$\alpha$} is too high, there might be very few cycles.
-Either the ideal trait is copied by enough copiers so that the prestige is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait {goes} extinct before there {are} enough copiers that copied it.
-We then tried to change the ratio between the number of cycles where $\hat{A}$ is favored and disfavored.
-We showed that the approximation fits well regardless of the ratio, but when the ratio of favored generations to disfavored ones is very high, it is very similar to a constant environment model.
+On increasing the success coefficient $1-\beta$ to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation (\Cref{fig:ch_env_alpha_beta}B).
+This is probably because when the success coefficient is high, the number of generations may be less than $n$, the number of generations in a full cycle, and thus $S_n/n$ is not a good estimator for the `average selection coefficient'.
+With even higher success coefficient values, the fixation probability exceeds even the constant environment approximation, possibly because the diffusion-equation approximation assumes weak selection, or in our case, weak success bias.
+We also changed the ratio between the number of cycles where $\hat{A}$ is favored and disfavored.
+We found that the approximation fits well regardless of the ratio, and that for a large $k-l$ difference (with a constant cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}; \Cref{fig:ch_env_alpha_beta}C).
+This makes sense as a constant environment can be viewed as an environment in which the cycle length is longer than the fixation time.
 
@@
 simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}).
-With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak "selection" .
+With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
 (\textbf{C}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias.
@@
 In results 2-6, we assumed that $\alpha$ is homogeneous in the population and constant, that is, it does not depend on any specific context.
-Next, we examined what happens in the continuous-trait model if the $i$-th copier evaluates its own optimal success-bias weight, $\alpha^*_i$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
+Next, we examined what happens in the continuous-trait model if the $i$-th copier evaluates its own optimal success-bias weight, $\alpha^*_i$, which minimizes the expected squared error between the chosen trait value and the `successful' trait value $\hat{A}$,
 \begin{equation}\label{eq:optimal_alpha}
@@
 where $A_j$ is the trait of role-model $j$ and $K_{i-1,j}$ is the number of copiers that already chose role-model~$j$ by the time the $i$-the copier chooses a role-model.
-Simply put, each copier $i$ estimates what success-bias weight $\alpha^*_i$ will result in copying a trait that is most similar to the ideal trait value $\hat{A}$.
+Simply put, each copier $i$ estimates what success-bias weight $\alpha^*_i$ will result in copying a trait that is most similar to the `successful' trait value $\hat{A}$.
 Indeed, if the trait value is correlated with fitness, the optimal success-bias weight would increase the fitness of individuals.
@@
 We find that when copiers choose their success-bias weight according to \cref{eq:optimal_alpha}, it quickly decreases with the number of copiers that have already chosen a role-model and then stays at what appears to be an equilibrium~(\Cref{fig:influence_advantage}).
-Moreover, their estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the optimal success-bias weight gives an estimation error (difference between the chosen and optimal trait) converges to $0.046$, whereas a constant success-bias weight gives values $>0.74$.
+Moreover, the estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the optimal success-bias weight gives an estimation error (difference between the chosen and `successful' trait) that converges to $0.046$, whereas a constant success-bias weight gives values greater than 0.74.
 
@@
 Hence, our models have two ``nested'' stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
-To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DMD, \Cref{cor:dirichlet}).
+To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DMD, \Cref{cor:dirichlet}).
 The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and prestige is a characteristic of the role-model and not the copier.
 
-Analyzing the dichotomous-trait model using the the DMD approximation, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
+Analyzing the dichotomous-trait model using the DMD approximation, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
 Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the strength of success bias towards the invading cultural trait, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) decreasing the relative weight of success versus prestige bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
 
-We also analyzed the dichotomous--trait model in a cyclic changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
+We also analyzed the dichotomous--trait model in a periodically changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
 We find that, similarly to the constant environment approximation, a change in the success-bias weight $\alpha$ has no negative effects on the goodness-of-fit of the approximation to simulation results.

### 2023-11-16 ms/ms.tex
continue editing...

@@
 \end{result}
-Note that these integrals cannot be solved in closed form, {and are estimated} numerically.
+Note that these integrals cannot be solved in closed form, and are estimated numerically.
+
+Results 4-5 lead to the following observations. 
+First, the the fixation probability increases (\Cref{fig:var_alpha}B) and the fixation time decreases (\Cref{fig:var_alpha}D) as a function of the success coefficient $1-\beta$, which acts as an effective selection coefficient.
+Second, the fixation probability increases with the success-bias weight $\alpha$ ({fig:var_alpha}A), reaching a maximum at $2(1-\beta)=2s$ when there is no prestige bias ($\alpha=1$).
+However, conditional on fixation, the fixation time is actually \emph{shorter} with low values of $\alpha$, that is, when prestige bias is strong.
+This is because prestige bias accelerates the evolutionary dynamics due to a \emph{rich-get-richer} process  (\Cref{fig:var_alpha}D)
 
@@
 We compare our approximations (\cref{eq:kimura_p,eq:kimura_t}) with results of simulations of our dichotomous model using various $\alpha$ and $\beta$ values, as well as simulations of the Wright-Fisher model, using the effective selection coefficient, $1-\beta$, and effective population size, $N_e=\alpha N + (1-\alpha)$.
-We find that the two models have similar dynamics, and both are well approximated {by} our approximations (\Cref{fig:var_alpha}).
+We find that the two models have similar dynamics, and both are well approximated by our approximations (\Cref{fig:var_alpha}).
 
@@
 Therefore, when $k>l$, the fixation probability will increase with the success-bias weight $\alpha$ (similar to a constant environment, \Cref{fig:var_alpha}A), and when $k<l$, the fixation probability will decrease with the success-bias weight $\alpha$ (\Cref{fig:ch_env_alpha_beta}A).
-Similarly, when the success coefficient $1-\beta$ is large, the approximation can break, as the fixation time can be lower then the number of generations in the cycle, $n$ (see \Cref{fig:var_alpha}D), and again the average selection coefficient, $S_n/n$ is not a good estimate of the effective selection coefficient.
+Otherwise, fixation probability increases with the success coefficient ($1-\beta$, \Cref{fig:ch_env_alpha_beta}B) and becomes larger as $k-l$ increases, i.e., as the number of generations in which the invading phenotype is favored increases (\Cref{fig:ch_env_alpha_beta}C).
 
@@
 However, the approximation is more sensitive to the value of the success bias coefficient $\beta$ (\Cref{fig:ch_env_alpha_beta}B).
-On increasing the success coefficient $1-\beta$ to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation (\Cref{fig:ch_env_alpha_beta}B).
-This is probably because when the success coefficient is high, the number of generations may be less than $n$, the number of generations in a full cycle, and thus $S_n/n$ is not a good estimator for the `average selection coefficient'.
-With even higher success coefficient values, the fixation probability exceeds even the constant environment approximation, possibly because the diffusion-equation approximation assumes weak selection, or in our case, weak success bias.
+When the success coefficient $1-\beta$ is large, the approximation can break, as the fixation time can be lower then the number of generations in the cycle, $n$ (see \Cref{fig:var_alpha}D), and therefore the average selection coefficient, $S_n/n$ is not a good estimate of the effective selection coefficient.
 We also changed the ratio between the number of cycles where $\hat{A}$ is favored and disfavored.

### 2023-11-16 ms/ms.tex
fig 1 update + results described

@@
 The effective selection coefficient $s$ and effective population size $N_e$ can be written in terms of the success coefficient $\beta$ (\cref{eq:success_bias}), the success-bias weight $\alpha$ (\cref{eq:prestige}), and the population size $N$ as
-\begin{equation}
+\begin{equation}\label{eq:effective}
 s=1-\beta=\frac{\beta(\hat{A})-\beta(A)}{\beta(\hat{A})}, \quad N_e=\alpha N + (1-\alpha) \;.
@@
 First, the the fixation probability increases (\Cref{fig:var_alpha}B) and the fixation time decreases (\Cref{fig:var_alpha}D) as a function of the success coefficient $1-\beta$, which acts as an effective selection coefficient.
-Second, the fixation probability increases with the success-bias weight $\alpha$ ({fig:var_alpha}A), reaching a maximum at $2(1-\beta)=2s$ when there is no prestige bias ($\alpha=1$).
-However, conditional on fixation, the fixation time is actually \emph{shorter} with low values of $\alpha$, that is, when prestige bias is strong.
-This is because prestige bias accelerates the evolutionary dynamics due to a \emph{rich-get-richer} process  (\Cref{fig:var_alpha}D)
+Second, the fixation probability increases with the success-bias weight $\alpha$ (\Cref{fig:var_alpha}A), reaching a maximum at $2(1-\beta)=2s$ when there is no prestige bias ($\alpha=1$), in which case the effective population size equals the actual population size (\cref{eq:effective})
+Third, and in contrast, the fixation time conditional on fixation is actually \emph{shorter} with low values of $\alpha$, that is, when prestige bias is strong (\Cref{fig:var_alpha}D).
+This is because prestige bias accelerates the evolutionary dynamics due to a \emph{rich-get-richer} process.
+Thus, when fixation occurs with strong prestige bias, it occurs faster than it does with strong success bias.
 
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{kimura_var.pdf}
+    \includegraphics[width=0.9\linewidth]{kimura_var.pdf}
   \caption{\textbf{Fixation probability and time in a constant environment.}
-  Fixation probability and time (in generations) as a function of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) in panels A and B, and as a function of the effective selection coefficient, $1-\beta$, in panels C and D.
-  The approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
-  The fixation probability in panel A is bounded by $2(1-\beta)$ (dashed line).
+	The effect of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) on the fixation probability (\textbf{A}) and the conditional fixation time (\textbf{B}), and the effect of the success coefficient, or effective selection coefficient, $1-\beta$, on the fixation probability (\textbf{B}) and the conditional fixation time (\textbf{D}).
+	Our approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
+	Panel A shows a dashed line at $2(1-\beta)$, which is reached by our approximation when $\alpha=1$.
+	Panel B has three lines: solid for  also shows our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
 	Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
-   Here, population size is $N=1,000$; in panels A and B, $A=0.7$, $\hat{A}=1$, and $1-\beta=0.044$; in panels C and D, $\alpha=0.01$, $\hat{A}=1$, and $0.01 < A< 0.99$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}.
+   	Here, population size is $N=1,000$; In panels A and B, $A=0.7$, $\hat{A}=1$, and $1-\beta=0.044$; In panels C and D, $\alpha=0.01$, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}.
    }

### 2023-11-16 ms/ms.tex
finished editing for rev2 :)

@@
 Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in in 3-4 year old children.
-Henrich and Broesch \citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
+Henrich and Broesch~\citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
 
@@
 
-% TODO this is wierd
-From \Cref{cor:GBD} we see that without success bias ($\alpha=0$), the expected number of copiers of each role-model is one. Hence, prestige bias is not frequency dependent.
+Note that $G_{1,j} = \alpha_{i,j} \beta(A_{i,j}) / \sum_{i=1}^{N}{\alpha_{i,j} \beta(A_{i,j})}$ (see \cref{eq:prestige} with $K_{0,j}=0$).
+In the limit of $\alpha_{i,j} \to 0$, that is with only prestige bias, we get $G_{1,j} = 1/N$, and from \Cref{cor:GBD}, the expected number of copiers of role-model $j$ is 1.
+Therefore, prestige bias is frequency independent, in contrast to conformity bias.
 
@@
 Results 4-5 lead to the following observations. 
-First, the the fixation probability increases (\Cref{fig:var_alpha}B) and the fixation time decreases (\Cref{fig:var_alpha}D) as a function of the success coefficient $1-\beta$, which acts as an effective selection coefficient.
+First, the fixation probability increases (\Cref{fig:var_alpha}B) and the fixation time decreases (\Cref{fig:var_alpha}D) as a function of the success coefficient $1-\beta$, which acts as an effective selection coefficient.
 Second, the fixation probability increases with the success-bias weight $\alpha$ (\Cref{fig:var_alpha}A), reaching a maximum at $2(1-\beta)=2s$ when there is no prestige bias ($\alpha=1$), in which case the effective population size equals the actual population size (\cref{eq:effective})
@@
 	Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
-   	Here, population size is $N=1,000$; In panels A and B, $A=0.7$, $\hat{A}=1$, and $1-\beta=0.044$; In panels C and D, $\alpha=0.01$, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}.
+   	Here, population size is $N=1,000$; 
+	In panels A and B, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$);
+	In panels C and D, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $\alpha=0.01$.
    }
@@
 \end{figure}
+
+Here, population size is $N=1,000$;
+In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
+In panel B, $A=0.9$, $\hat{A}=1$ and $A$ varies, $k=20$, and $l=80$, $\alpha=0.1$; 
+In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.005$), $\alpha=0.1$.
 
@@
 Therefore, when $k>l$, the fixation probability will increase with the success-bias weight $\alpha$ (similar to a constant environment, \Cref{fig:var_alpha}A), and when $k<l$, the fixation probability will decrease with the success-bias weight $\alpha$ (\Cref{fig:ch_env_alpha_beta}A).
-Otherwise, fixation probability increases with the success coefficient ($1-\beta$, \Cref{fig:ch_env_alpha_beta}B) and becomes larger as $k-l$ increases, i.e., as the number of generations in which the invading phenotype is favored increases (\Cref{fig:ch_env_alpha_beta}C).
+Furthermore, the fixation probability increases with the success coefficient ($1-\beta$, \Cref{fig:ch_env_alpha_beta}B; see below for how simulation results compare to the constant environment and changing environment approximations) and becomes larger as $k-l$ increases, i.e., as the number of generations in which the invading phenotype is favored increases (\Cref{fig:ch_env_alpha_beta}C).
 
@@
     \includegraphics[width=\linewidth]{ch_env.pdf}
-  \caption{\textbf{Fixation probability in a changing environment.}
+  \caption{\textbf{Fixation probability in a changing environment, $k<l$.}
 \textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis).
@@
 Markers show average of $10,000$ simulations, error bars show 75\% (panels A and C) and 95\% (panel B) confidence intervals.
-Here, population size $N=1,000$; $\hat{A}=1$, $A=0.9$, $k=20$ and $l=80$ (panels A and B); $A=0.8$, (panel C); in panel A, the success coefficient is $1-\beta=s=0.005$; in panels B and C, the success-bias weight is $\alpha=0.1$.
+See \Cref{fig:ch_env_alpha_beta_k_large} for the scenario where $k>l$.
+Here, population size is $N=1,000$;
+In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
+In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=20$, and $l=80$, $\alpha=0.1$; 
+In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.0198$), $\alpha=0.1$.
 }
@@
 Analyzing the dichotomous-trait model using the DMD approximation, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
-Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the strength of success bias towards the invading cultural trait, $1-\beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) decreasing the relative weight of success versus prestige bias, $\alpha$, decreases the effective population size, $N_e$~(\Cref{fig:var_alpha}).
+Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the strength of success bias towards the invading cultural trait, $\beta=\beta(\hat{A}) / \beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) decreasing the relative weight of success versus prestige bias, $\alpha$, decreases the effective population size, $N_e$.
+Therefore, when either $\alpha$ or $1-\beta$ increases, the fixation probability increases~(\Cref{fig:var_alpha}A and \Cref{fig:var_alpha}B).
+However, while increasing the $s=1-\beta$ decreases the  fixation time, as `selection' is stronger (\Cref{fig:var_alpha}D), increasing the success-bias weight $\alpha$ increases the conditional fixation time (\Cref{fig:var_alpha}C).
+This is because, when the invading phenotype manages to fix in a population with strong prestige bias, it will do so faster compared to a population with weak prestige bias, as strong prestige leads to a \emph{rich-getting-richer} process.
 
 We also analyzed the dichotomous--trait model in a periodically changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
-We find that, similarly to the constant environment approximation, a change in the success-bias weight $\alpha$ has no negative effects on the goodness-of-fit of the approximation to simulation results.
-We also showed that this approximation is more sensitive to changes in the success coefficient $\beta$ than the constant environment approximation, and a lower value is required to have a good fit.
-The ratio between the number of {generations} in which the rare phenotype is under positive transmission bias and the number of generations in which it is under negative bias does not affect the goodness-of-fit of the approximation.
+We again derive an approximation for the fixation probability, which works well when the success coefficient $1-\beta$ is low. 
+In the case of a changing environment, two key values are the number of generations $k$ and $l$  in which the invading and resident traits are favored by success bias, respectively.
+When $k>l$, strong success (high $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta_k_large}),
+but when $k<l$, strong prestige (low $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}A).
+This is because prestige accelerates the evolutionary dynamics, which allows the invading trait to fix before the environment changes to favor the resident trait.
+In all cases increasing the success coefficient $1-\beta$, which is equivalent to increasing the strength of selection, will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}B).
 
@@
 
+\begin{figure}
+	\centering
+    \includegraphics[width=\linewidth]{ch_env_k_large.pdf}
+  \caption{\textbf{Fixation probability in a changing environment, $k>l$.}
+\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis).
+The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange).
+\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
+When success bias is large ($1-\beta > 0.1$),  
+simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}).
+With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
+Markers show average of $10,000$ simulations, error bars show 75\% (panel A) and 95\% (panel B) confidence intervals.
+Here, population size is $N=1,000$;
+In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=80$, and $l=20$;
+In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=80$, and $l=20$, $\alpha=0.1$; 
+}
+\label{fig:ch_env_alpha_beta_k_large}
+\end{figure}
+
 \end{document}

### 2024-05-06 ms/ms.tex
revising

@@
 \affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
-\affil[$\dagger$]{Corresponding author: yoav@yoavram.com}
+\affil[$\dagger$]{Corresponding author: yoavram@tauex.tau.ac.il}
 
@@
 In contrast, if the traits of `prestigious' individuals--those individuals that have already been copied many times--are more likely to be adopted, this is described as prestige-biased cultural transmission.
-In this case prestige can be used as a convenient proxy for success.
-Here, we study the joint effect of success and prestige bias on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
-Analytic approximations to the stochastic role-model choice process facilitate the mathematical analysis and reduce the computational complexity of simulations.
+In this case, prestige can be used as a convenient proxy for success.
+However, it is unclear how success and prestige biases interact to determine the outcome of cultural evolutionary dynamics.
+Here, we aim to clarify this using mathematical analysis and stochastic simulations.
+We find analytic approximations to the stochastic role-model choice process that facilitate the mathematical analysis and reduce the computational complexity of simulations.
 Approximations are given to the fixation probability and the fixation time of an invading cultural trait in different environments.
-We show that success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.	Prestige bias, which may be strong in highly social communities, also accelerates the evolutionary dynamics, as can be expected in a rich-get-richer process.
+Our results show that success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.	Prestige bias, which may be strong in highly social communities, also accelerates the evolutionary dynamics, as can be expected in a rich-get-richer process.
+These results signify a step forward in understanding how different cultural transmission biases interact.
 \end{abstract}
@@
 They defined prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature \citep{prestige_evolution} .
-Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality''.
-Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in in 3-4 year old children.
-Henrich and Broesch~\citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
+Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality.''.
+Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in 3-4 year old children.
+Nakata et al.~\citep{Nakata2024} define such a bias as a ``prestige bias based on second-order cues,'' in which ``Social learners can use the extent of attention and the amount copied from others as cues for prestige.''
+Henrich and Broesch~\citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
 
@@
 We follow the Boyd and Richerson model~\citep{evolutionBook}, assuming only oblique transmission of a single trait. 
-Consider a population of $N$ individuals, described by a single trait that takes continuous values.
+This focus on oblique transmission (copying from non-parental adults) means that we can neglect fitness differences between trait values since there is no correlation between the traits of parents and offspring.
+We consider a population of $N$ individuals, described by a single trait that takes continuous values.
 At each generation, $N$ naive individuals, or copiers, each choose a single role-model from the entire previous generation. Each copier then copies its trait value from the chosen role-model.
@@
 Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
+\Cref{fig:timeseries} shows some examples of model dynamics for various values of $\alpha$.
 
@@
 	Panel A shows a dashed line at $2(1-\beta)$, which is reached by our approximation when $\alpha=1$.
-	Panel B has three lines: solid for  also shows our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
-	Markers are averages of $10,000$ simulations, error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
+	Panel B has three lines: solid for our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
+	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
    	Here, population size is $N=1,000$; 
@@
 
-Here, population size is $N=1,000$;
-In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
-In panel B, $A=0.9$, $\hat{A}=1$ and $A$ varies, $k=20$, and $l=80$, $\alpha=0.1$; 
-In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.005$), $\alpha=0.1$.
+%Here, population size is $N=1,000$;
+%In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
+%In panel B, $A=0.9$, $\hat{A}=1$ and $A$ varies, $k=20$, and $l=80$, $\alpha=0.1$; 
+%In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.005$), $\alpha=0.1$.
 
@@
 \subsection*{Optimal success-bias weight}
-In results 2-6, we assumed that $\alpha$ is homogeneous in the population and constant, that is, it does not depend on any specific context.
-Next, we examined what happens in the continuous-trait model if the $i$-th copier evaluates its own optimal success-bias weight, $\alpha^*_i$, which minimizes the expected squared error between the chosen trait value and the `successful' trait value $\hat{A}$,
+In results 2-6, we assumed that the bias weight $\alpha$ is homogeneous in the population and constant, that is, it does not depend on any specific context.
+However, rational individuals could potentially adjust their bias weight to balance between success and prestige bias depending on their context, such as the number of individuals who have already chosen a role model.
+Therefore, we examined what happens in the continuous-trait model if the $i$-th copier evaluates its own optimal success-bias weight, $\alpha^*_i$, which minimizes the expected squared error between the chosen trait value and the `successful' trait value $\hat{A}$,
 \begin{equation}\label{eq:optimal_alpha}
@@
 It has been suggested that because it is hard to estimate success, a more common bias is a bias towards role-models \emph{perceived} to be successful.
-This perceived success can be determined by performance with respect to another trait, i.e., \emph{indirect success} \citep{evolutionBook,fijian_social_bias}, or by ``the amount of voluntary deference and attention received by models'' \citep{prestigeSocialLearn}, i.e., \emph{prestige} \citep{prestige_cultural_learning,prestige_evolution} (but see Chellappoo~\citep{rethinkPrestige} for a critical examination of the concept of prestige).
+This perceived success can be determined by performance with respect to another trait, i.e., \emph{indirect success} \citep{evolutionBook,fijian_social_bias}, or by ``the amount of voluntary deference and attention received by models'' \citep{prestigeSocialLearn}, i.e., \emph{prestige} \citep{prestige_cultural_learning,prestige_evolution,Nakata2024} (but see Chellappoo~\citep{rethinkPrestige} for a critical examination of the concept of prestige).
 
@@
 
+\bibitem{Nakata2024}
+Nakata, Seiya, Akira Masumi, and Genta Toya. (2024) "Formalising Prestige Bias: Differences between Models with First-Order and Second-Order Cues." Evolutionary Human Sciences 6: e21.
+
 \end{thebibliography}
@@
 \beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
+
+\begin{figure}[h]
+    \includegraphics[width=1\linewidth]{timeseries.pdf}
+  \caption{
+  \textbf{Example dynamics of the dichotomous model with varying bias weight.}
+  The dichotomous model is defined in \cref{eq:binary-model}. Shown are full dynamics without DM or GBD approximations.
+  Here, population size, $N=1,000$; ideal phenotype value, $\hat{A}=1$; success bias value, $\beta(A)=0.99$; initial phenotype frequencies are 50\%-50\%.
+  }	
+  \label{fig:timeseries}
+\end{figure}
 

### 2024-05-06 ms/ms.tex
finished revision

@@
 	Panel B has three lines: solid for our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
-	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals for panels A and B and 75\% for panels C and D.
+	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals.
 	Here, population size is $N=1,000$; 
@@
 \section*{Acknowledgements}
-We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, Tal Simon and two anonymous reviewers for discussions and comments.
+We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, Tal Simon and three anonymous reviewers for discussions and comments.
 This work was supported in part by 

### 2024-05-07 ms/ms.tex
typo

@@
 They defined prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature \citep{prestige_evolution} .
-Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality.''.
+Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality.''
 Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in 3-4 year old children.

### 2024-05-08 ms/ms.tex
abstract grammarly

@@
 \begin{abstract}
-If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased.
-In contrast, if the traits of `prestigious' individuals--those individuals that have already been copied many times--are more likely to be adopted, this is described as prestige-biased cultural transmission.
-In this case, prestige can be used as a convenient proxy for success.
+If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as success-biased.
+In contrast, if the traits of ‘prestigious’ individuals–those who have already been copied many times–are more likely to be adopted, this is described as prestige-biased cultural transmission.
+In this case, prestige can be a convenient proxy for success.
 However, it is unclear how success and prestige biases interact to determine the outcome of cultural evolutionary dynamics.
@@
 Approximations are given to the fixation probability and the fixation time of an invading cultural trait in different environments.
-Our results show that success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.	Prestige bias, which may be strong in highly social communities, also accelerates the evolutionary dynamics, as can be expected in a rich-get-richer process.
+Our results show that success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.
+Prestige bias, which may be strong in highly social communities, also accelerates the evolutionary dynamics, as expected in a rich-get-richer process.
 These results signify a step forward in understanding how different cultural transmission biases interact.

### 2024-05-08 ms/ms.tex
remove comments

@@
 The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
-Here "Copier" of the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
-% lines are also 300 simulations? why not markers? 
-% what are error bars in C? CI 99%
-% C x axis should say "Constant success-bias weight"
-% A B x axis should say "Copier $i$; A y axis should be "Optimal success-bias weight, \alpha^*_i$.
+Here, the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
 }	

### 2024-06-02 ms/si.tex
refactor si figures from ms

--- 2024-05-08 ms/ms.tex
@@
 % Title 
-\title{Prestige bias in cultural evolutionary dynamics}
+\title{Supplementary Figures for \\ Prestige bias in cultural evolutionary dynamics}
 
@@
 
-\begin{abstract}
-If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as success-biased.
-In contrast, if the traits of ‘prestigious’ individuals–those who have already been copied many times–are more likely to be adopted, this is described as prestige-biased cultural transmission.
-In this case, prestige can be a convenient proxy for success.
-However, it is unclear how success and prestige biases interact to determine the outcome of cultural evolutionary dynamics.
-Here, we aim to clarify this using mathematical analysis and stochastic simulations.
-We find analytic approximations to the stochastic role-model choice process that facilitate the mathematical analysis and reduce the computational complexity of simulations.
-Approximations are given to the fixation probability and the fixation time of an invading cultural trait in different environments.
-Our results show that success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.
-Prestige bias, which may be strong in highly social communities, also accelerates the evolutionary dynamics, as expected in a rich-get-richer process.
-These results signify a step forward in understanding how different cultural transmission biases interact.
-\end{abstract}
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Introduction}
-
-Cultural transmission of attitudes, preferences, beliefs, norms, and behaviors may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, and even strangers) transmit to unrelated offspring; and horizontal transmission, in which individuals from the same age cohort transmit to one another \citep{transmissionVectorsBook}.
-It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{changeEnv,Lehmann2009}.
-
-Transmission biases may cause a cultural trait to have a higher rate of transmission than its frequency in the population.
-\textit{Success bias} occurs when individuals prefer to copy from role models that demonstrate success in some activity, such as fishing, growing yams, using medicinal plants \citep{fijian_social_bias}, or hunting \citep{Mesoudi2008}, and it can increase the probability of learning a trait that is present in those successful individuals \citep{Borofsky2022}.
-Indeed, in a tournament between learning strategies  \citep{strategiesPaper}, most winning strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
-Jimenez and Mesoudi~\citep{prestigeSocialLearn} also note that a way to acquire adaptive social information is by preferentially copying competent individuals within a valuable domain (which they also call success bias).
-However, they claim that competence within a domain is often difficult or impossible to directly asses, and therefore people tend to use indirect cues of success.
-Henrich and Broesch \citep{fijian_social_bias} have also suggested that direct assessment of success may be ``noisy, unreliable or unavailable'' and therefore copiers should also take into account indirect measures of perceived success (e.g., ``great fishermen may be chosen as role-models for growing yams''.)
-
-Boyd and Richerson~\citep[Ch.~5]{evolutionBook} suggested that the assessment of success can be divided to three categories: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
-Direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
-For example, an individual observing a ping-pong match can try the observed paddle grips to determine which grip is better.
-Frequency-dependent bias occurs when the probability of copying a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
-For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{anti-conformity} \citep{conformism}.
-The effects of conformity and anti-conformity on cultural evolution have been studied with both models \citep{Denton2020,Denton2021,Denton2022} and experiments \citep{negativeFrequency}.
-Indirect bias occurs when a copier uses some observed phenotype to evaluate the attractiveness of a potential role-model. 
-For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
-However, this may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
-Furthermore, Boyd and Richerson~\citep[Ch.
-8]{evolutionBook} suggest that maladaptive traits may spread widely in a population if indirect bias is strong enough, e.g., by a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
-Indeed, helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient~\citep{cooperation}.
-
-Henrich and Gil-White~\citep{prestige_evolution} noted that ``the most skilled/knowledgeable role-models will, on average, end up with the biggest and most lavish clienteles, so the size and lavishness of a given model's clientele size (the \emph{prestige}) provides a convenient and reliable proxy for that person's information quality''.
-Thus, they predicted that skilled individuals have higher status, that people preferentially copy high-status individuals, and therefore that prestigious individuals may be influential even beyond their domain of expertise.
-They defined prestige as ``freely conferred deference'', in contrast to \emph{dominance}, and provided examples from the anthropological literature \citep{prestige_evolution} .
-Similarly, the New Oxford American Dictionary defines prestige as the ``widespread respect and admiration felt for someone or something on the basis of a \emph{perception} of their achievements or quality.''
-Chudek et al.~\citep{prestige_cultural_learning} have also defined prestige bias as ``a tendency to learn from individuals to whom others have preferentially attended, learned or deferred'' and demonstrated its occurrence in 3-4 year old children.
-Nakata et al.~\citep{Nakata2024} define such a bias as a ``prestige bias based on second-order cues,'' in which ``Social learners can use the extent of attention and the amount copied from others as cues for prestige.''
-Henrich and Broesch~\citep{fijian_social_bias} have further suggested that prestige bias can, over generations, lead to cultural adaptations and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
-
-The distinction between success and prestige bias is important, as prestige is a context-dependent bias, rather than a content-dependent bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success.
-Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity \citep{Denton2020,Denton2021,Denton2022}, which depends on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.
-
-Prestige bias may be more common in humans than success bias \citep{complexityPaper}.
-In contemporary human society, social media make it especially easy to estimate the social and cultural influence individuals have over others, which can have an effect on decision making.
-Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices have been invented to capitalize on this effect \citep{facebook_marketing}.
-However, despite many mentions of prestige in the cultural evolution literature, there are few models of prestige bias.
-
-Here, we develop a stochastic model of cultural transmission with both indirect success bias and prestige bias to examine their relationship in contribution to the cultural evolution of populations.
-We find analytic approximations for this model.
-We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is subject to success bias) in both a constant and a periodically changing environment.
-Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and prestige bias play the role of natural selection and genetic drift, respectively.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Models}
-We begin with a continuous-trait model with indirect success bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}.
-Note that the indirect success bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
-We extend this model to include prestige bias, which introduces a within-generation model-choice process.
-To facilitate mathematical analysis, we also develop a simpler version of the model with a dichotomous trait.
-
-We implement our stochastic models and approximations, perform statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
-Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
-
-\subsection*{Continuous trait}
-We follow the Boyd and Richerson model~\citep{evolutionBook}, assuming only oblique transmission of a single trait. 
-This focus on oblique transmission (copying from non-parental adults) means that we can neglect fitness differences between trait values since there is no correlation between the traits of parents and offspring.
-We consider a population of $N$ individuals, described by a single trait that takes continuous values.
-At each generation, $N$ naive individuals, or copiers, each choose a single role-model from the entire previous generation. Each copier then copies its trait value from the chosen role-model.
-Note that our transmission models are slightly different from those modeled before, e.g.
-\citep{cumul_culture,Denton2021,evolutionBook}, in which the population is infinite and each copier samples $n$ role-models and then copies its trait from one or more of the sampled role-models.
-
-Similar to a Wright-Fisher model, generations are non-overlapping, and the entire population is replaced in each generation.
-The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is the trait value of individual $i$ at time $t$, and  the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
-Cultural transmission is modeled by a function $F$ such that 
-\begin{equation}\label{eq:transmission}
-A_{i}(t+1) = F_i(\vec{A}(t)) \;.
-\end{equation}
-
-\paragraph{Success bias.}
-Boyd and Richerson~\citep[Ch.~8, p.~247-249]{evolutionBook} describe a  transmission algorithm by defining $F$, a weighted average of the traits of all role-models, as
-\begin{equation}\label{eq:boydF}
-F_i(\vec{A}) = \sum_{j=1}^N G_{i,j}\cdot A_{i,j} \;, 
-\end{equation}
-where $G_{i,j}$ is the success bias of role-model $j$ in the eyes of copier $i$,
-\begin{equation}\label{eq:boydG}
-G_{i,j} = \frac{\beta(A_{i,j})}{\sum_{k=1}^{N} \beta(A_{i,k})} \;,
-\end{equation}
-$A_{i,j}$ is the absolute trait value that copier $i$ estimates for role-model $j$ with some error $e_i \sim N(0,\eta^2)$,
-\begin{equation}\label{eq:relativeTrait}
-A_{i,j} = A_j + e_i,
-\end{equation}
-and $\beta(\cdot)$ is the bias function that quantifies the success bias of a role-model \citep[eq.~5.11]{evolutionBook},
-\begin{equation}\label{eq:success_bias}
-\beta(A_{i,j}) = b \cdot \exp{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)} \;,
-\end{equation} 
-with $\hat{A}$ as the arbitrary optimal trait value, and $J$ and $b$ as parameters that control the bias strength; unless otherwise mentioned, we set $b=J=1$.
-Therefore, $G_{i,j}$ is a relative success score that copier $i$ assigns to role-model $j$.
-
-Boyd and Richerson~\citep{evolutionBook} note that the deterministic blended transmission algorithm they use has alternatives.
-We develop a similar stochastic model with transmission from a single random role-model where instead of \cref{eq:boydF} we define the transmission function $F$ as a random variable with its distribution given by
-\begin{equation}\label{eq:ourF}
-\Pr\big(F_i(\vec{A}) = A_{j}\big) = G_{i,j} \;;
-\end{equation}
-{here $G_{i,j}$ is} the probability {that copier $i$ chooses} to copy the trait of role-model $j$.
-
-\paragraph{Prestige bias.}
-We introduce a new element to the model by assuming that in each generation copiers choose their role-models one by one so that the choice of one copier can affect the choice of other copiers.
-We formulate this assumption in the following.
-Denote by $K_{i,j}$  the number of copiers that choose role-model $j$ after copier $i$ chose a role-model.
-Thus, $i$ out of $N$ copiers had already chosen a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
-The stochastic process of role-model choice, 
-\begin{equation} \label{eq:process}
-\big\{\vec{K}_i = (K_{i,1}, \ldots, K_{i,N}) \big\}_{i=1}^N \;,
-\end{equation}
-is described by the recurrence equation
-\begin{equation} \label{eq:recurrence}
-K_{i,j} = K_{i-1,j} + S_{i,j}, \quad i,j=1,2,\ldots,N \;,
-\end{equation}
-where $S_{i,j}=1$ if the $i$-th copier chose role-model~$j$ and 0 otherwise, and the initial state is $K_{0,j}=0$.
-
-Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the \emph{influence} of role-model $j$ in the eyes of copier $i$,
-\begin{equation}\label{eq:recPrestige}
-Pr(S_{i,j}=1 \mid S_{1,j},S_{2,j},...,S_{i-1,j}) = G_{i,j} \;.
-\end{equation}
-The influence $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and prestige--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} with
-\begin{equation}\label{eq:prestige}
-G_{i,j} = \frac{\alpha_{ij} \cdot \beta(A_{i,j}) + (1-\alpha_{ij}) \cdot K_{i-1,j}}{W_i} \;,
-\end{equation}
-where $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.
-Here, the success-bias weight $\alpha_{i,j}$ determines the relative weighting of success and prestige bias.
-It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of  success vs.
-prestige bias in the role-model's overall influence in the eyes of the copier.
-Different individuals may evaluate the importance of success and prestige differently.
-Additionally, we assume each role-model displays its prestige and success individually.
-For example, individuals with more followers but lacking skill may emphasize the number of their followers rather than their skill (i.e., have lower $\alpha_{i,j}$ value).
-Finally, the trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}.
-
-\subsection*{Dichotomous trait}
-We introduce a simplified version of the above model where the trait has only two phenotypes: an optimal phenotype $\hat{A}$ and a sub-optimal phenotype $A$. 
-All role-models with the same phenotype will contribute to the probability that that phenotype is transmitted and thus prestige is determined by the number of copiers that have already chosen a role-model with either phenotype.
-In addition, for simplicity and for easier mathematical analysis, we assume $\alpha$ is homogeneous and constant ($\alpha_{i,j}=\alpha$), which entails exchangeability between role-models.
-Therefore, the probability that the $i$-th copier {copies} phenotype $A$ is
-\begin{equation}\label{eq:binary-model}
-%G_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i-1,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} \;,
-G_{i,A} = \frac{\alpha \cdot (N-X) \beta(A) + (1-\alpha) \cdot K_{i-1,A}}{\alpha \cdot (N-X) \beta(A) + \alpha \cdot X + (1-\alpha)\cdot(i-1)} \;,
-\end{equation}
-where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i-1,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model, and assuming that $\beta(\hat{A})=1$ (thus the term $\alpha X$ in the denominator).
-Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
-\Cref{fig:timeseries} shows some examples of model dynamics for various values of $\alpha$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-Our models are defined by two nested stochastic processes.
-Change over multiple generations is described by the {dynamics of the} phenotype distribution at each generation, $\{\vec{A}(t)\}_t$, see \cref{eq:transmission}.
-The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$, see \cref{eq:process}.
-We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$, where $K_{N,j}$ is the number of copiers that chose role-model $j$ after all copiers chose a role model.
-However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}.
-Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
-We found two approximations for the distribution of $\vec{K}_{N}$, summarized here and explained in detail below.
-In both approximations we assume that the success-bias weight is either completely homogeneous, $\alpha_{i,j}=\alpha$, or that $\alpha_{i,j}=\alpha_j$ is a characteristic of role-model $j$ that does not vary between copiers.
-Note that these approximations apply for both the and the continuous trait (\cref{eq:prestige}) and the dichotomous trait (\cref{eq:binary-model}) models.
-
-\paragraph{Generalized binomial distribution approximation.}  
-The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore, 
-(i) the expected number of copiers of role-model~$j$ equals its influence in the eyes of the first copier, multiplied by the total number of copiers, that is,
-$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$); and
-(ii) the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.
-
-\paragraph{Dirichlet-Multinomial distribution approximation.}
-The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$). 
-Hence, the number of copiers of each role-model $\vec{K_{N}}$ at the end of the role-model choice process follows the Dirichelet-Multinomial distribution.
-
-After finding these approximations for the role-model choice process, we focus on the dichotomous-trait model, in which mathematical analysis is simpler, and studied the fixation probability and time in both a constant and a changing environment.
-
-\subsection*{Generalized binomial distribution (GBD) approximation}
-The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is {denoted}  by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials (the latter can be estimated from data, but its value is insignificant for our approximation).
-Note that $\theta=0$ gives the standard binomial distribution.
-\\
-
-\begin{result}[Generalized binomial distribution approximation]\label{res:GBD}
-The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the generalized binomial distribution, 
-$$
-K_{i,j} \sim \textit{GenBin}(i,\alpha_j\cdot\beta(A_j+e),\theta)
-$$
-if $e_i=e$ for all copiers $i=1, \ldots, N$; the success-bias weight only depends on the role-model and not the copier, i.e., $\alpha_{i,j}=\alpha_j$  for all $i=1, \ldots, N$; and $\theta$ is the correlation between successive role-model choices.
-\end{result}
-
-\begin{proof}
-{Let} $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ {be} the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ {out} of $i-1$ copiers chose role-model $j$. 
-Using conditional probability and \cref{eq:recurrence},
-\begin{equation}\label{recursive}
-Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1) \;,
-\end{equation}
-where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
-\Cref{recursive} is equivalent to eq.~(2.1) in \citep{GBD}, which completes the proof.
-\end{proof}
-
-This result gives the following corollary on the expected number of followers of a given role-model $j$ by the end of the role-model choice process, $K_{N,j}$.
-\\
-
-\begin{corollary}\label{cor:GBD} The expected number of copiers of role-model $j$ after all copiers have chosen a role-model is
-$\E[K_{N,j}] = N \cdot G_{1,j}$, where $G_{1,j}$ is the probability of the first copier to copy role-model $j$.
-In addition, $\E[K_{N, j}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
-\end{corollary}
-
-\begin{proof}
-The expected value of the GBD is
-$\E[K_{N,j}] = N \cdot Q_j(1,1)$, see Drezner and Farnum~\citep[eq.~(2.3)]{GBD}.
-Here, $Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made, such that $Q_j(1,1) = G_{1,j}$ by definition.
-The rest of the proof is in Appendix~\ref{sec:GBD}.
-\end{proof}
-
-Note that $G_{1,j} = \alpha_{i,j} \beta(A_{i,j}) / \sum_{i=1}^{N}{\alpha_{i,j} \beta(A_{i,j})}$ (see \cref{eq:prestige} with $K_{0,j}=0$).
-In the limit of $\alpha_{i,j} \to 0$, that is with only prestige bias, we get $G_{1,j} = 1/N$, and from \Cref{cor:GBD}, the expected number of copiers of role-model $j$ is 1.
-Therefore, prestige bias is frequency independent, in contrast to conformity bias.
-
-The special case where the bias weight is uniform for all role-models ($\alpha = \alpha_j$ for $j=1,\ldots, N$) is interesting, because we can evaluate the expected number of copiers using a linear equation
-\begin{equation}\label{eq:GBDsamelalpha}
-\E[K_{N,j}]= N\cdot\frac{\alpha\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N}\alpha\cdot\beta(A_m+e)} =\beta(A_j+e) \bigg/ \overline{\beta(A+e)} \;,
-\end{equation}
-where the only variable is $A_j+e$, because $\overline{\beta(A+e)}$ is the mean of the distribution of the trait values, modified by some constant parameters of $\beta$.
-We can then write $L = 1/\overline{\beta(A+e)}$ and
-\begin{equation}\label{eq:linearEq}
-\E[K_{N,j}] = L\cdot \beta(A_j+e) \;.
-\end{equation}
-
-\paragraph{Numerical validation.}
-To validate that the GBD approximation for the number of copiers of a role-model is correct (\cref{eq:GBDsamelalpha}), 
-we ran $1,000$ simulations of the full model, and compared the results with \Cref{cor:GBD}.
-We compare the distribution of the number of copiers by plotting the histograms of both our simulation results and the expected values based on \Cref{cor:GBD}.
-
-Although basic, \Cref{fig:GBD} shows a good fit of the GBD approximation.
-We perform more extensive validations on the Dirichlet-Multinomial approximation (see below), because that is what we will use in our analysis.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Dirichlet-Multinomial distribution (DMD) approximation}
-
-\paragraph{P\'{o}lya urn model.}
-This stochastic process consists of $N$ draws from an urn with an initial {number} of colored balls of $M$ colors.
-When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same color.
-Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
-Let $S_{i,j}=1$ when drawing a $j$-colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is
-\begin{equation}\label{eq:polya}
-\begin{split}
-P(S_{i,j} = 1 \mid \vec{U_{i-1}}) = 
-\frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = 
-\frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}} = 
-\frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m} \;,
-\end{split}
-\end{equation}
-where $o_j$ is the initial number of balls of color $j$ in the urn, and $w_{i,j}$ is the cumulative number of new balls that were added to the urn after $i$ draws of color $j$.
-\\
-
-\begin{result}[P{\'{o}}lya urn model]\label{result:polya}
-The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \emph{P\'{o}lya urn model} if both the trait estimation error and the success-bias weight are constant in the population, $e_i=e$ for all $i=1, \ldots, N$ and $\alpha_{i,j}=\alpha$  for all $i,j=1, \ldots, N$.
-\end{result}
-
-\begin{proof} 
-{Write} $\alpha'=\frac{\alpha}{1-\alpha}$ as the success-bias weight ratio, and $A'_j=A_j+e$. From \cref{eq:prestige} and because $\sum_{j=1}^{N}{K_{i,j}}=i$, we have
-\begin{equation}\label{eq:copier_choose}
-G_{i,j} = 
-\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N}{\left[ \alpha'\beta(A'_m) + K_{i-1,m}\right]}}
- =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N}\alpha'\beta(A'_m)} \;.
-\end{equation}
-Substituting $M=N$, $o_j = \alpha'\beta(A'_j)$, and $w_{i,j} = K_{i,j}$ in \cref{eq:polya} gives \cref{eq:copier_choose}, thus completing the proof.
-\end{proof}
-
-Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws  (the population size, $N$, in our model) approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
-We therefore have an approximation for the relative influence each role-model has when evaluated by copiers.
-Thus, choosing the role-models for all copiers is equivalent to drawing from a {multinomial} distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
-\\
-
-\begin{corollary}[Dirichlet-Multinomial distribution approximation]\label{cor:dirichlet}
-The number of copiers of each role-model approximates a Dirichlet-Multinomial distribution, $\vec{K_N} \sim \textit{DirMul}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
-\end{corollary}
-
-\paragraph{Numerical validation.}
-We next validated the DMD approximation of our model
-and tested its sensitivity to the assumptions ($e_i=e$ and $\alpha_i=\alpha$ for $i=1,\ldots,N$) by comparing results of stochastic simulations of our model (\cref{eq:binary-model}) with the DMD approximation (\Cref{cor:dirichlet}).
-We used a relatively small population size, $N=100$, thus validating that the approximation is in good agreement even for small $N$, despite the assumption of large $N$ in the proof by Frigyik et al.~\citep[section 2]{dirichlet}.
-First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then compared this observed distribution with the expected theoretical DMD (\Cref{fig:DM_validation}A).
-The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
-The maximum difference is 0.5 role-models, which indicates a very good fit.
-In addition, we tested the likelihood of the observed data to be drawn from the DMD, against a shuffle of the parameters vector of the DMD itself (\Cref{fig:DM_validation}B).
-We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, strongly supporting our approximation.
-
-Next, we examined the fixation probability and fixation time of a `successful' phenotype $\hat{A}$ (i.e., that is favored by success bias) when invading a population of phenotype $A$ and compared results from the full model and the DMD approximation.
-Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
-We find that the number of simulations needed to sufficiently approximate our model with the DMD approximation is roughly $1,000$ (\Cref{fig:num_sims}).
-We examined the robustness of the DMD approximation to relaxing the following assumptions.
-First, we relaxed our assumption of no estimation error $e$.
-Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the success `bias ($A_{i,j} = A_j + e_i$).
-When estimation error is applied, we sample $e_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$.
-Even when the estimation error variance is $0.1$, both the fixation probability and fixation time DMD approximations are accurate~(\Cref{fig:hetro_error}). 
-We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
-We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5, \epsilon)$ where $\epsilon$ is between $10^{-7}$ and $10^{-1}$.
-We found again that results of the DMD approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Fixation probability and time}
-After finding that the DMD is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
-We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a `successful' phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
-We are mainly interested in the effect of the success-bias weight, $\alpha$, which determines the relative effect of success and prestige bias, given by \cref{eq:prestige}.
-
-For simplicity, we use the dichotomous-trait model, which also assumes a constant success-bias weight $\alpha_{i,j}=\alpha$, and we do not include trait estimation error in this analysis, i.e., $e_i=0$.
-As shown above, transmission in our model is approximately Dirichlet-Multinomial distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
-We focus on two scenarios: the first scenario is of a `constant environment' in which the same phenotype, $\hat{A}$, is always favored by success bias; the second scenario is of a `changing environment' in which the phenotype favored by success bias cycles between the invading phenotype $\hat{A}$ and the resident phenotype $A$ (i.e., $\hat{A}$ starts as the rare phenotype).
-
-\paragraph{Drift and diffusion terms in a constant environment.}
-We start by finding the expectation and variance of the change in frequency from one generation to the next, which are the drift and diffusion terms of the diffusion equation.
-Let $x$ and $x'$ be the frequency of phenotype $\hat{A}$ in a population with $N$ individuals in the current and next generation, respectively.
-We set $\beta$ to be the success bias of phenotype $A$ relative to phenotype $\hat{A}$, such that $\beta = \beta(A)/\beta(\hat{A}) < 1$.
-Then (see Appendix~\ref{sec:drift_diff_const} for derivation),
-\begin{equation}\label{eq:drift_diff}
-\begin{aligned}
-E[x'-x] &= x(1-x)(1-\beta) + o(1-\beta)  \;, 
-\\
-V(x'-x) &= x(1-x)\left(\frac{1}{\alpha N + (1-\alpha)}\right) + o\left(\frac{1}{\alpha N + (1-\alpha)}\right) \;.
-\end{aligned}\end{equation}
-
-This analysis gives an interesting result relating the parameters $\alpha$ and $\beta$ to parameters of the classical Wright-Fisher model from population genetics:
-the selection coefficient $s$, a measure of the effect of natural selection on the change in frequency of genotypes, and the effective population size, $N_e$, a measure of the effect of random genetic drift on the change in frequency of genotypes.
-In a diffusion-equation approximation of the classical Wright-Fisher model, the expectation and variance of the change in frequency are $E[x'-x]=sx(1-x)+o(s)$ and $V[x'-x]=x(1-x)/N_e$ \citep[eq.~7]{kimura}{, respectively}.
-Therefore, we have the following result.\\
-
-\begin{result}[Effective selection coefficient and population size]\label{res:selection_coef}
-The effective selection coefficient $s$ and effective population size $N_e$ can be written in terms of the success coefficient $\beta$ (\cref{eq:success_bias}), the success-bias weight $\alpha$ (\cref{eq:prestige}), and the population size $N$ as
-\begin{equation}\label{eq:effective}
-s=1-\beta=\frac{\beta(\hat{A})-\beta(A)}{\beta(\hat{A})}, \quad N_e=\alpha N + (1-\alpha) \;.
-\end{equation}
-\end{result}
-
-Note that when $N>>1$, $N_e \approx \alpha N$, resulting in a very convenient expression.\\
-
-Using our effective selection coefficient, $s=1-\beta$, and effective population size, $N_e$, with the population-genetics fixation probability approximation given by Kimura~\citep[eq.~8]{kimura}, we obtain the following result.\\
-
-\begin{result}[Fixation probability]
-The fixation probability of an invading phenotype favored by success bias is approximately 
-\begin{equation}\label{eq:kimura_p}
-\pi(x) = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}},
-\end{equation}
-where $x$ is the initial frequency of the invading phenotype.
-\end{result}
-
-Similarly, we can use $1-\beta$ and $N_e$ in the population-genetics fixation time approximation given by \citep[eq.~17]{kimura_average}.\\
-
-\begin{result}[Fixation time] The expected fixation time (conditioned on fixation) from an initial frequency $x$ is approximately
-\begin{equation} \label{eq:kimura_t}
-T(x) = J_1(x) + \frac{1-\pi(x)}{\pi(x)}\cdot J_2(x),
-\end{equation}
-where $N_e=\alpha N + (1-\alpha)$, $S=N_e(1-\beta)$, and
-\begin{equation}
-\begin{aligned}
-J_1(x) &= \frac{-1}{(1-\beta)(e^{-2S}-1)}\int_x^1 \frac{1-e^{2S\xi}-e^{-2S(1-\xi)}+e^{-2S}}{\xi(1-\xi)}d\xi \;, \\
-J_2(x) &= \frac{-1}{(1-\beta)(e^{-2S}-1)}\int_0^x \frac{(1-e^{2S\xi})(e^{-2S\xi}-1)}{\xi(1-\xi)}d\xi \;.
-\end{aligned}
-\end{equation}
-\end{result}
-Note that these integrals cannot be solved in closed form, and are estimated numerically.
-
-Results 4-5 lead to the following observations. 
-First, the fixation probability increases (\Cref{fig:var_alpha}B) and the fixation time decreases (\Cref{fig:var_alpha}D) as a function of the success coefficient $1-\beta$, which acts as an effective selection coefficient.
-Second, the fixation probability increases with the success-bias weight $\alpha$ (\Cref{fig:var_alpha}A), reaching a maximum at $2(1-\beta)=2s$ when there is no prestige bias ($\alpha=1$), in which case the effective population size equals the actual population size (\cref{eq:effective})
-Third, and in contrast, the fixation time conditional on fixation is actually \emph{shorter} with low values of $\alpha$, that is, when prestige bias is strong (\Cref{fig:var_alpha}D).
-This is because prestige bias accelerates the evolutionary dynamics due to a \emph{rich-get-richer} process.
-Thus, when fixation occurs with strong prestige bias, it occurs faster than it does with strong success bias.
-
-\paragraph{Numerical validation.}
-We compare our approximations (\cref{eq:kimura_p,eq:kimura_t}) with results of simulations of our dichotomous model using various $\alpha$ and $\beta$ values, as well as simulations of the Wright-Fisher model, using the effective selection coefficient, $1-\beta$, and effective population size, $N_e=\alpha N + (1-\alpha)$.
-We find that the two models have similar dynamics, and both are well approximated by our approximations (\Cref{fig:var_alpha}).
-
-\begin{figure}[h]
-    \includegraphics[width=0.9\linewidth]{kimura_var.pdf}
-  \caption{\textbf{Fixation probability and time in a constant environment.}
-	The effect of the success-bias weight $\alpha$ (bottom x-axis) and effective population size, $N_e$, (top x-axis) on the fixation probability (\textbf{A}) and the conditional fixation time (\textbf{B}), and the effect of the success coefficient, or effective selection coefficient, $1-\beta$, on the fixation probability (\textbf{B}) and the conditional fixation time (\textbf{D}).
-	Our approximation (black; \cref{eq:kimura_p}) agrees with both DMD simulations (green) and Wright-Fisher simulations (orange).
-	Panel A shows a dashed line at $2(1-\beta)$, which is reached by our approximation when $\alpha=1$.
-	Panel B has three lines: solid for our approximation for $\alpha=0.01$, and dashed for $\alpha=0$ (bottom) and $\alpha=0.02$ (top).
-	Markers are averages of $10,000$ simulations. Error bars show 95\% confidence intervals.
-	Here, population size is $N=1,000$; 
-	In panels A and B, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$);
-	In panels C and D, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $\alpha=0.01$.
-   }
-  \label{fig:var_alpha}
-\end{figure}
-
-%Here, population size is $N=1,000$;
-%In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
-%In panel B, $A=0.9$, $\hat{A}=1$ and $A$ varies, $k=20$, and $l=80$, $\alpha=0.1$; 
-%In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.005$), $\alpha=0.1$.
-
-\paragraph*{Changing environment}.
-After finding a good approximation in a constant environment, where the `successful' trait is always $\hat{A}$, we proceeded to find an approximation for a periodically changing environment.
-Following Ram et al.~\citep{changeEnv}, we denote $k$ as the number of generations in which the invading phenotype is favored by success bias, and $l$ as the number of generations in which the resident phenotype is favored by success bias.
-Thus, during the first $k$ generations of the environmental cycle, $\beta=\frac{\beta(A)}{\beta(\hat{A})}$<1, where $\hat{A}$ is the invading phenotype.
-During the following $l$ generations of the environmental cycle, the phenotype favored by success bias is switched, such that $\frac{\beta(A)}{\beta(\hat{A})}>1$.
-We then proceed to find expressions for the expectation and variance of the change in the frequency of phenotype $\hat{A}$ after $n=k+l$ generations. 
-The proof is in Appendix~\ref{sec:drift_diff_chang}.
-\\
-
-\paragraph{Drift and diffusion terms in a changing environment.}
-Let $x$ be the initial frequency of the invading phenotype and $X_t$ the number of individuals with that phenotype after $n$ generations.
-Then,
-\begin{equation}\label{eq:ch_expected_and_var}
-E[X_n/N - x] \simeq x(1-x) S_n / N_e \;, 
-\quad
-\text{and}
-\quad
-V(X_n/N-x) \simeq  n x(1-x) / N_e \;,
-\end{equation}
-where $S_n=\sum\limits_{t=1}^{n} N (1-\beta_t)$ and $\beta_t$ is $\beta(A)$ at generation $t$.
-
-Note that here, we have the `average selection coefficient' during a cycle of $n$ generations, $S_n/n$ as the selection coefficient {in} \cref{eq:kimura_p}.
-Using the drift and diffusion terms and following Ram et al.~\citep{changeEnv}, we can approximate the fixation probability in a changing environment.
-\\
-
-\begin{result}[Fixation probability in a periodically changing environment]\label{res:ch_expected}
-
-The fixation probability of an invading phenotype under periodical environmental changes is approximately
-\begin{equation}\label{eq:ch_env}
-\tilde\pi(x) = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}} \;.
-\end{equation}
-where $x$ is the initial frequency of the invading phenotype.
-\end{result}
-
-Importantly, the average selection coefficient, $S_n/n$, has the same sign as $k-l$.
-Therefore, when $k>l$, the fixation probability will increase with the success-bias weight $\alpha$ (similar to a constant environment, \Cref{fig:var_alpha}A), and when $k<l$, the fixation probability will decrease with the success-bias weight $\alpha$ (\Cref{fig:ch_env_alpha_beta}A).
-Furthermore, the fixation probability increases with the success coefficient ($1-\beta$, \Cref{fig:ch_env_alpha_beta}B; see below for how simulation results compare to the constant environment and changing environment approximations) and becomes larger as $k-l$ increases, i.e., as the number of generations in which the invading phenotype is favored increases (\Cref{fig:ch_env_alpha_beta}C).
-
-\paragraph{Numerical validation.}
-To validate the approximation for the fixation probability in a changing environment (\cref{eq:ch_env}), we compare it to results of simulations that use the DMD approximation (\Cref{cor:dirichlet}).
-We find that the approximation fits the simulation results well for variable success-bias weights, $\alpha$, which corresponds to the effective population size (\Cref{fig:ch_env_alpha_beta}A).
-However, the approximation is more sensitive to the value of the success bias coefficient $\beta$ (\Cref{fig:ch_env_alpha_beta}B).
-When the success coefficient $1-\beta$ is large, the approximation can break, as the fixation time can be lower then the number of generations in the cycle, $n$ (see \Cref{fig:var_alpha}D), and therefore the average selection coefficient, $S_n/n$ is not a good estimate of the effective selection coefficient.
-We also changed the ratio between the number of cycles where $\hat{A}$ is favored and disfavored.
-We found that the approximation fits well regardless of the ratio, and that for a large $k-l$ difference (with a constant cycle length, $n=k+l=100$), the changing environment approximation (\cref{eq:ch_env}) converges to the constant environment approximation (\cref{eq:kimura_p}; \Cref{fig:ch_env_alpha_beta}C).
-This makes sense as a constant environment can be viewed as an environment in which the cycle length is longer than the fixation time.
-
-\begin{figure}[H]
-	\centering
-    \includegraphics[width=\linewidth]{ch_env.pdf}
-  \caption{\textbf{Fixation probability in a changing environment, $k<l$.}
-\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis).
-The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange).
-\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
-When success bias is large ($1-\beta > 0.1$),  
-simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}).
-With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
-(\textbf{C}) The approximation (blue) is robust to changes in environmental cycle length, as it agrees with simulations (orange) for different sizes of the changing environment cycle, where $k$ and $l$ are the number of generations each trait value is under success bias.
-When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green), because the more generations the rare phenotype is favored, the more similar it is to the constant environment model, where it is always favored by the success bias.
-Markers show average of $10,000$ simulations, error bars show 75\% (panels A and C) and 95\% (panel B) confidence intervals.
-See \Cref{fig:ch_env_alpha_beta_k_large} for the scenario where $k>l$.
-Here, population size is $N=1,000$;
-In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=20$, and $l=80$;
-In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=20$, and $l=80$, $\alpha=0.1$; 
-In panel C, $A=0.8$, $\hat{A}=1$ ($1-\beta=s=0.0198$), $\alpha=0.1$.
-}
-\label{fig:ch_env_alpha_beta}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Optimal success-bias weight}
-In results 2-6, we assumed that the bias weight $\alpha$ is homogeneous in the population and constant, that is, it does not depend on any specific context.
-However, rational individuals could potentially adjust their bias weight to balance between success and prestige bias depending on their context, such as the number of individuals who have already chosen a role model.
-Therefore, we examined what happens in the continuous-trait model if the $i$-th copier evaluates its own optimal success-bias weight, $\alpha^*_i$, which minimizes the expected squared error between the chosen trait value and the `successful' trait value $\hat{A}$,
-\begin{equation}\label{eq:optimal_alpha}
-\alpha^*_i = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_{i-1,j}}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_{i-1,l}} (\hat{A}-A_j)^2 \;,
-\end{equation}
-where $A_j$ is the trait of role-model $j$ and $K_{i-1,j}$ is the number of copiers that already chose role-model~$j$ by the time the $i$-the copier chooses a role-model.
-Simply put, each copier $i$ estimates what success-bias weight $\alpha^*_i$ will result in copying a trait that is most similar to the `successful' trait value $\hat{A}$.
-Indeed, if the trait value is correlated with fitness, the optimal success-bias weight would increase the fitness of individuals.
-However, here we ignore the effects of natural selection, focusing instead on selectively neutral traits.
-
-We find that when copiers choose their success-bias weight according to \cref{eq:optimal_alpha}, it quickly decreases with the number of copiers that have already chosen a role-model and then stays at what appears to be an equilibrium~(\Cref{fig:influence_advantage}).
-Moreover, the estimation error is much lower compared to a constant success-bias weight, which gives roughly the same high estimation error to all copiers (compare \Cref{fig:influence_advantage}B and C): in this example, the optimal success-bias weight gives an estimation error (difference between the chosen and `successful' trait) that converges to $0.046$, whereas a constant success-bias weight gives values greater than 0.74.
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{choose_bias.pdf}
-  \caption{
-  \textbf{Advantage of an optimal success-bias weight.}
-  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
-However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error does not decrease, regardless of $\alpha$ or $\eta$.
-The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
-Here, the x-axis is the index of the choosing copier, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), markers are average of $300$ simulations.
-}	
-  \label{fig:influence_advantage}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-Some cultural traits or cultural role-models may be copied more often than others due to transmission biases. 
-One such bias is success bias, in which copiers are more likely to copy a successful role-model. 
-It has been suggested that because it is hard to estimate success, a more common bias is a bias towards role-models \emph{perceived} to be successful.
-This perceived success can be determined by performance with respect to another trait, i.e., \emph{indirect success} \citep{evolutionBook,fijian_social_bias}, or by ``the amount of voluntary deference and attention received by models'' \citep{prestigeSocialLearn}, i.e., \emph{prestige} \citep{prestige_cultural_learning,prestige_evolution,Nakata2024} (but see Chellappoo~\citep{rethinkPrestige} for a critical examination of the concept of prestige).
-
-We developed two cultural-evolutionary models, one with continuous and one with dichotomous trait values.
-Our models include both indirect success and prestige biases, where the latter is a bias towards role-models with many copiers.
-We model these biases using a stochastic role-model choice process: each copier, in turn, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).
-Hence, our models have two ``nested'' stochastic processes: the role-model choice process within each generation, and the cultural-evolutionary process between generations.
-To simplify the mathematical and computational analysis, we developed analytic approximations for the role-model choice process using the {\em generalized binomial distribution} (GBD, \Cref{res:GBD}) and the {\em Dirichlet-Multinomial distribution} (DMD, \Cref{cor:dirichlet}).
-The latter is especially useful, as it approximates the entire role-model choice process and only requires us to assume that the relative effect of success and prestige is a characteristic of the role-model and not the copier.
-
-Analyzing the dichotomous-trait model using the DMD approximation, we found approximations for the fixation probability and fixation time of a cultural trait under biased transmission in a constant environment.
-Our approximations are similar to Kimura's evolutionary-genetic approximations, in that (i) the strength of success bias towards the invading cultural trait, $\beta=\beta(\hat{A}) / \beta(A)$, is equivalent to the selection coefficient in favor of a beneficial allele, $s$, and (ii) decreasing the relative weight of success versus prestige bias, $\alpha$, decreases the effective population size, $N_e$.
-Therefore, when either $\alpha$ or $1-\beta$ increases, the fixation probability increases~(\Cref{fig:var_alpha}A and \Cref{fig:var_alpha}B).
-However, while increasing the $s=1-\beta$ decreases the  fixation time, as `selection' is stronger (\Cref{fig:var_alpha}D), increasing the success-bias weight $\alpha$ increases the conditional fixation time (\Cref{fig:var_alpha}C).
-This is because, when the invading phenotype manages to fix in a population with strong prestige bias, it will do so faster compared to a population with weak prestige bias, as strong prestige leads to a \emph{rich-getting-richer} process.
-
-We also analyzed the dichotomous--trait model in a periodically changing environment in which the identity of the success-biased trait switches after a fixed amount of generations~(\Cref{fig:ch_env_alpha_beta}).
-We again derive an approximation for the fixation probability, which works well when the success coefficient $1-\beta$ is low. 
-In the case of a changing environment, two key values are the number of generations $k$ and $l$  in which the invading and resident traits are favored by success bias, respectively.
-When $k>l$, strong success (high $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta_k_large}),
-but when $k<l$, strong prestige (low $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}A).
-This is because prestige accelerates the evolutionary dynamics, which allows the invading trait to fix before the environment changes to favor the resident trait.
-In all cases increasing the success coefficient $1-\beta$, which is equivalent to increasing the strength of selection, will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}B).
-
-Lastly, we examined a scenario in which copiers can adjust their success-bias weight, $\alpha$, to minimize their copying error, i.e., copy trait values closer to the optimal value.
-We found that as the role-model choice process proceeds (that is, more copiers make their choices), both the success-bias weight (adjusted by copiers) and the estimation error decrease. 
-The latter is significantly lower than in a population using a constant, fixed success-bias weight, regardless of the value of the constant weight (\Cref{fig:influence_advantage}).
-This suggests that the later a copier makes its choice, the more it should rely on choices of previous copiers (prestige), and the less it should rely on its own estimation of the success of role-models.
-The rationale, then, is that the more information a copier has, e.g., by using others as information sources, the more informative and effective his choice can be.
-
-Chudek et al.~\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
-Their definition of prestige is similar to ours.
-They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of learning from a role model whom bystanders ignored.
-They also note that prestige effects are domain sensitive: they found that prestigious role-models were attended more when demonstrating artifact use, whereas role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact use vs.
-food preference) can affect the attendance, and hence the prestige of the role-model.
-This led to the suggestion that when the trait is costly to learn individually, prestige will have a stronger bias \citep{prestige_cultural_learning}.
-It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.
-
-According to Henrich and Broesch~\citep{fijian_social_bias}, natural selection has favored the emergence of psychological biases for learning from those individuals most likely to possess adaptive information.
-The authors studied Fijian villages to examine if and how such biases emerge in a small-scale society.
-They found that Fijian villagers are more likely to learn from role-models perceived as more successful/knowledgeable, both within and across domains.
-Their research thus suggests that copying from those perceived as successful, rather than who are actually successful, is a common phenomenon.
-They show that the social networks representing copier--role-model relationships are centralized, which is consistent with the prediction that people substantially share notions about who is a good cultural model, but that individuals' role-model selections are influenced by multiple factors.
-
-Dunbar~\citep{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
-Following this, Muthukrishnan and Henrich \citep{collective_brains} suggested that prestige can directly affect human physical evolution.
-They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
-They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. 
-They also presented the \emph{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning.
-As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge.
-These strategies and biases include direct and indirect cues of the popularity of cultural traits (e.g.
-success and prestige biases).
-They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to `cheaply' acquire adaptive knowledge via transmission biases such as prestige.
-
-Prestige bias can help to cheaply estimate and acquire knowledge, which may facilitate survival and reproduction.
-However, it is not always the case, and there could be negative repercussions to this bias, such as invasion of maladaptive traits.
-Takahashi and Ihara~\citep{best_of_k} mention that social learning not only takes the form of random copying of other individuals, but also involves learners' choice of what to learn and from whom to learn.
-They suggest a best-of-k model where an individual samples~$k$ role-models and chooses the one he deems most "successful".
-They mention that a previous mathematical analysis has shown that it may sometimes result in maladaptive cultural evolution when the payoffs associated with cultural variants vary stochastically.
-In such a case, learners may be selectively disfavored and in the long run replaced by unbiased learners, who simply copy someone chosen at random.
-They developed new mathematical models that are simpler and mathematically tractable.
-They found that best-of-k learning, unlike unbiased learning, can facilitate the invasion of an on average inferior variant that sometimes gives a very high payoff (see Fogarty et al.\ \citep{Fogarty2017} and references there).
-Our model, which includes both success and prestige bias, is consistent with this claim.
-When a maladaptive trait is `piggybacking' on a role-model with high influence (joint effect of success and prestige), the former could spread in the population.
-In addition, best-of-k learning can be stable against invasion by unbiased learning if social learning is sometimes combined with individual learning \citep{best_of_k}. 
-Our model includes only social learning, and not individual learning, but it could be interesting to combine it with individual learning and see how it affects the dynamics.
-
-Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
-Efferson et al.~\citep{harmful_traditions} suggest a \emph{spillover} mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
-They find that there are individuals who act as \emph{agents}, who are often observed, and therefore they are ideal targets for interventions.
-This is similar to prestigious role-models in our model, which are copied more often, and will therefore spread their trait faster and wider in the population.
-They also suggest a way to use this phenomenon to change existing traditions in a population.
-It is very clear however, that just as it can be used to end harmful traditions, the same agents could start harmful traditions.
-
-Others have analyzed models with interactions between different transmission biases.
-Hong~\citep{payoff} studied a model with both conformity and success bias (which he calls `payoff bias'). 
-He showed that an intermediate level of conformity bias--not too little but not too much--can be adaptive and evolve to prevent invasion of low-success traits while allowing the invasion of high-success traits (for another example of adaptive filtering, see~\citep{adaptive_filtering}).
-Similar to our model (\cref{eq:prestige}), Hong~\citep{payoff} also additively combined the two transmission biases (his eq.~1). However, transmission biases can be combined in many ways. 
-For example, Denton et al.~\citep{Denton2022} combined frequency-dependent bias and genetically determined content bias multiplicatively (their eq.~1). 
-Ammar et al.~\citep{Ammar2023} studied a model in which individuals have a repertoire of cultural variants to choose from, and both variant choice and transmission via social learning are success-biased.
-Moreover, they also included the possibility to `forget' infrequently used variants; therefore, because usage is success-biased, memory is also success-biased.
-It remains to be seen how different assumptions on the mechanisms of learning and forgetting affect the evolutionary dynamics under different and interacting transmission biases.
-
-One path forward is an analysis of the dynamics of the optimal success-bias weight model, in which every copier chooses its $\alpha$.
-It would be interesting to see the if the mean estimation error and the varying weight, $\alpha^*$, converge to specific values, and how they are affected by the model parameters.
-It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
-Another possibility is to model prestige bias in a different way.
-For example, using a Moran model \citep{Moran1958}, one could build model with overlapping generations, which would mix the within-generation model role-model choice process and the between-generation evolutionary dynamics.
-Lastly, it would be interesting to analyze the fixation probability and time in the continuous model and determine how the results compare to those from the dichotomous model.
-
-Another way to expand our model is to account for the two types of prestige or leadership suggested by Van Vugt and Smith~\citep{dual_leadership} that are attributed to Confucius and Machiavelli.
-Confucius viewed leaders as role-models who exercise influence through possessing superior knowledge, skills, and (outstanding) personal qualities.
-This fits the success bias in our model.
-In contrast, Machiavelli viewed leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence.
-Van Vugt and Smith suggest that these opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view of the complex and dynamic concept of leadership.
-Henrich and Gil-White~\citep{prestige_evolution} have suggested a similar distinction between `prestige and `dominance', or between `persuasion' and `force'.
-Several adjustments could be made so that our model reflects these leadership styles, such as assuming there is a correlation between phenotype and leadership style.
-The resulting cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.
-
-\paragraph{Conclusions.}
-We studied a model of cultural evolution under two transmission biases: the commonly studied success bias, together with prestige bias, which has so far received less attention by modelers.
-We found approximations for this complex dynamics.
-We then showed that success bias affects the evolutionary dynamics much like natural selection does, whereas prestige bias has a similar effect to random genetic drift.
-We also find a clear advantage to individuals that can choose the relative weight of the two biases.
-
-{\small
-\section*{Acknowledgements}
-We thank Marc Feldman, Martin Pontz, Gili Greenbaum, Alon Rozen, Tal Simon and three anonymous reviewers for discussions and comments.
-This work was supported in part by 
-Minerva Stiftung Center for Lab Evolution~(YR) and  the John Templeton Foundation~(YR 61809).
-}
-
-\newpage
-
-\section*{References}
-\nolinenumbers
-\begin{thebibliography}{}
-
-\bibitem{prestigeSocialLearn}
-Jiménez, Ángel V., and Alex Mesoudi. (2019) "Prestige-biased social learning: Current evidence and outstanding questions." Palgrave Communications 5.1 (2019).
-
-\bibitem{rethinkPrestige}
-Chellappoo, Azita. (2021) "Rethinking prestige bias." Synthese 198.9: 8191-8212.
-
-\bibitem{fliesPaper}
-Battesti, Marine, Celine Moreno, Dominique Joly, and Frederic Mery. (2012) "Spread of Social Information and Dynamics of Social Transmission within Drosophila Groups." Current Biology 22 (4): 309–13.
-
-\bibitem{transmissionVectors}
-Creanza, Nicole, Oren Kolodny, and Marcus W. Feldman. (2017) "Cultural evolutionary theory: How culture evolves and why it matters." Proceedings of the National Academy of Sciences 114.30: 7782-7789.
-
-\bibitem{negativeFrequency}
-Aljadeff, Naama, Luc-Alain Giraldeau, and Arnon Lotem.
-(2020) "Competitive advantage of rare behaviours induces adaptive diversity rather than social conformity in skill learning." Proceedings of the Royal Society B: Biological Sciences 287.1933: 20201259.
-
-\bibitem{transmissionVectorsBook}
-Cavalli-Sforza, Luigi Luca, and Marcus W. Feldman. (1981) :Cultural transmission and evolution: A quantitative approach." No. 16. Princeton University Press.
-
-\bibitem{evolutionBook}
-Boyd, Robert, and Peter J. Richerson. (1985) "Culture and the Evolutionary Process". University of Chicago Press.
-
-\bibitem{complexityPaper}
-Fogarty, Laurel, Joe Yuichiro Wakano, Marcus W.
-Feldman, and Kenichi Aoki.
-(2017) "The Driving Forces of Cultural Complexity: Neanderthals, Modern Humans, and the Question of Population Size." Human Nature 28 (1): 39–52.
-
-\bibitem{strategiesPaper}
-Rendell, Luke E., Robert Boyd, D.
-Cownden, M.
-Enquist, K.
-Eriksson, Marcus W.
-Feldman, Laurel Fogarty, S.
-Ghirlanda, T.
-Lillicrap, and Kevin N.
-Laland.
-(2010) "Why Copy Others?
-Insights from the Social Learning Strategies Tournament." Science 328 (5975): 208–13.
-
-\bibitem{sexualSelectionBook}
-Andersson, Malte, and Yoh Iwasa. (1996) "Sexual selection." Trends in ecology \& evolution 11.2: 53-58.
-
-\bibitem{chimpsCopy}
-Kendal, Rachel L., Lydia M.
-Hopper, Andrew Whiten, Sarah F.
-Brosnan, Susan P.
-Lambeth, Steven J.
-Schapiro, and William J.E.
-Hoppitt.
-(2015) "Chimpanzees Copy Dominant and Knowledgeable Individuals: Implications for Cultural Diversity." Evolution and Human Behaviour 36 (1): 65–72.
-
-\bibitem{chimpsPrestige}
-Horner, Victoria, Darby Proctor, Kristin E. Bonnie, Andrew Whiten, and Frans B.M. de Waal. (2010) "Prestige Affects Cultural Learning in Chimpanzees." PLoS ONE 5 (5): 1–5.
-
-\bibitem{dualEvolution}
-Henrich, Joseph, and Richard McElreath.
-(2012) "Dual-Inheritance Theory: The Evolution of Human Cultural Capacities and Cultural Evolution." In Oxford Handbook of Evolutionary Psychology, edited by Louise Barrett and Robin Dunbar, 1st ed., 555–70.
-Oxford University Press.
-
-\bibitem{elepahntsRepo}
-McComb, K., C. Moss, Sarah M. Durant, L. Baker, and S. Sayialel. (2001) "Matriarchs As Repositories of Social Knowledge in African Elephants." Science 292 (5516): 491–94.
-
-\bibitem{wtfGene}
-Eickbush, Michael T., Janet M. Young, and Sarah E. Zanders. (2019) "Killer meiotic drive and dynamic evolution of the wtf gene family." Molecular Biology and Evolution 36.6: 1201-1214.
-
-\bibitem{pageRank}
-Xing, Wenpu, and Ali Ghorbani. (2004) "Weighted pagerank algorithm." Proceedings. Second Annual Conference on Communication Networks and Services Research, IEEE.
-
-\bibitem{conformism}
-Molleman, Lucas, Ido Pen, and Franz J. Weissing. "Effects of conformism on the cultural evolution of social behaviour." PloS one 8.7 (2013): e68153.
-
-\bibitem{GBD}
-Drezner, Zvi, and Nicholas Farnum. "A generalized binomial distribution." Communications in Statistics-Theory and Methods 22.11 (1993): 3051-3063.
-
-\bibitem{dirichlet}
-Frigyik, Bela A., Amol Kapila, and Maya R.
-Gupta.
-"Introduction to the Dirichlet distribution and related processes." Department of Electrical Engineering, University of Washignton, UWEETR-2010-0006 6 (2010): 1-27.
-
-\bibitem{martingaleBook}
-Durrett, Richard, and R. Durrett. Essentials of stochastic processes. Vol. 1. New York: Springer, 1999.
-
-\bibitem{kimura}
-Kimura, Motoo. "On the probability of fixation of mutant genes in a population." Genetics 47.6 (1962): 713.
-
-\bibitem{durret}
-Durrett, Richard, and Richard Durrett. Probability models for DNA sequence evolution. Vol. 2. New York: Springer, 2008.
-
-\bibitem{changeEnv}
-Ram, Yoav, Uri Liberman, and Marcus W. Feldman. (2018) "Evolution of vertical and oblique transmission under fluctuating selection." Proceedings of the National Academy of Sciences 115.6: E1174-E1183.
-
-\bibitem{animal_leadership}
-King, Andrew J., and Guy Cowlishaw. (2009) "Leaders, followers, and group decision-making." Communicative \& integrative biology 2.2: 147-150.
-
-\bibitem{dual_leadership}
-Van Vugt, Mark, and Jennifer E. Smith. (2019) "A dual model of leadership and hierarchy: Evolutionary synthesis." Trends in Cognitive Sciences 23.11: 952-967.
-
-\bibitem{fijian_social_bias}
-Henrich, Joseph, and James Broesch.
-(2011) "On the nature of cultural transmission networks: evidence from Fijian villages for adaptive learning biases." Philosophical Transactions of the Royal Society B: Biological Sciences 366.1567: 1139-1148.
-
-\bibitem{harmful_traditions}
-Efferson, Charles, Sonja Vogt, and Ernst Fehr. (2020) "The promise and the peril of using social influence to reverse harmful traditions." Nature human behaviour 4.1: 55-68.
-
-\bibitem{prestige_evolution}
-Henrich, Joseph, and Francisco J.
-Gil-White.
-(2001) "The evolution of prestige: Freely conferred deference as a mechanism for enhancing the benefits of cultural transmission." Evolution and human behavior 22.3: 165-196.
-
-\bibitem{best_of_k}
-Takahashi, Takuya, and Yasuo Ihara. (2019) "Cultural and evolutionary dynamics with best-of-k learning when payoffs are uncertain." Theoretical Population Biology 128: 27-38.
-
-\bibitem{collective_brains}
-Muthukrishna, Michael, and Joseph Henrich. (2016) "Innovation in the collective brain." Philosophical Transactions of the Royal Society B: Biological Sciences 371.1690: 20150192.
-
-\bibitem{social_brains}
-Dunbar, Robin IM. (2009) "The social brain hypothesis and its implications for social evolution." Annals of human biology 36.5: 562-572.
-
-\bibitem{prestige_cultural_learning}
-Chudek, Maciej, Sarah Heller, Susan Birch, and Joseph Henrich.
-(2012) "Prestige-Biased Cultural Learning: Bystander’s Differential Attention to Potential Models Influences Children’s Learning." Evolution and Human Behavior 33 (1): 46–56.
-
-\bibitem{evolution_of_cultural_evolution}
-Henrich, Joseph, and Richard McElreath. (2003) "The evolution of cultural evolution." Evolutionary Anthropology: Issues, News, and Reviews 12.3: 123-135.
-
-\bibitem{cultural_traits}
-O’Brien, Michael J., R.
-Lee Lyman, Alex Mesoudi, and Todd L.
-Van Pool.
-(2010) "Cultural Traits as Units of Analysis." Philosophical Transactions of the Royal Society B: Biological Sciences 365 (1559): 3797–3806.
-
-\bibitem{dolphins_whales}
-Whitehead, Hal. (2017) "Gene–culture coevolution in whales and dolphins." Proceedings of the National Academy of Sciences 114.30: 7814-7821.
-
-\bibitem{cooperation}
-Cohen, Dor, Ohad Lewin-Epstein, Marcus W.
-Feldman, and Yoav Ram.
-(2021) "Non-Vertical Cultural Transmission, Assortment and the Evolution of Cooperation." Proceedings of the Royal Society B: Biological Sciences 288 (1951): 20203162.
-https://doi.org/10.1098/rspb.2020.3162.
-
-\bibitem{Denton2022}
-Denton, Kaleda K., Yoav Ram, and Marcus W. Feldman. (2022) "Conformity and content-biased cultural transmission in the evolution of altruism." Theoretical Population Biology 143: 52-61.
-
-\bibitem{Denton2021}
-Denton, Kaleda K., Uri Liberman, and Marcus W. Feldman. (2021) "On randomly changing conformity bias in cultural transmission." Proceedings of the National Academy of Sciences 118.34: e2107204118.
-
-\bibitem{Denton2020}
-Denton, Kaleda Krebs, Yoav Ram, Uri Liberman, and Marcus W. Feldman. (2020) "Cultural evolution of conformity and anticonformity." Proceedings of the National Academy of Sciences 117 (24): 13603–14.
-
-\bibitem{facebook_marketing}
-Lee, Woojin, Lina Xiong, and Clark Hu.
-(2012) "The effect of Facebook users’ arousal and valence on intention to go to the festival: Applying an extension of the technology acceptance model." International Journal of Hospitality Management 31.3: 819-827.
-
-\bibitem{social_influence}
-Anagnostopoulos, Aris, Ravi Kumar, and Mohammad Mahdian.
-(2008) "Influence and correlation in social networks." Proceedings of the 14th ACM SIGKDD international conference on Knowledge discovery and data mining.
-
-\bibitem{influence_analysis}
-Peng, Sancheng, Yongmei Zhou, Lihong Cao, Shui Yu, Jianwei Niu, and Weijia Jia.
-(2018) "Influence Analysis in Social Networks: A Survey." Journal of Network and Computer Applications 106 (March): 17–32.
-
-\bibitem{social_media}
-Diga, Marichris, and Tom Kelleher. (2009) "Social media use, perceptions of decision-making power, and public relations roles." Public Relations Review 35.4: 440-442.
-
-\bibitem{python}
-Van Rossum, Guido. (2007) "Python Programming Language." USENIX annual technical conference. Vol. 41. No. 1.
-
-\bibitem{numpy}
-Van Der Walt, Stefan, S. Chris Colbert, and Gael Varoquaux. (2011) "The NumPy array: a structure for efficient numerical computation." Computing in Science \& Engineering 13.2: 22-30.
-
-\bibitem{mathplotlib}
-Hunter, John D. (2007) "Matplotlib: A 2D graphics environment." Computing in Science \& Engineering 9.03: 90-95.
-
-\bibitem{kimura_average}
-Kimura, Motoo, and Tomoko Ohta. (1969) "The average number of generations until fixation of a mutant gene in a finite population." Genetics 61.3: 763.
-
-\bibitem{otto_fixation}
-Slatkin, Montgomery. (1981) "Fixation probabilities and fixation times in a subdivided population." Evolution: 477-488.
-
-\bibitem{lemurs}
-Erhart, Elizabeth M., and Deborah J. Overdorff. (1999) "Female coordination of group travel in wild Propithecus and Eulemur." International Journal of Primatology 20: 927-940.
-
-\bibitem{no_replication}
-Boyd, Robert, and Joseph Henrich. (2002) "On modeling cognition and culture: Why cultural evolution does not require replication of representations." Journal of cognition and culture 2.2: 87-112.
-
-\bibitem{kin_selection}
-Gardner, Andy, Stuart A. West, and Geoff Wild. (2011) "The genetical theory of kin selection." Journal of evolutionary biology 24.5: 1020-1043.
-
-\bibitem{Truskanov2020}
-Truskanov, Noa, Yasmin Emery, and Redouan Bshary. (2020) "Juvenile cleaner fish can socially learn the consequences of cheating." Nature communications 11.1: 1159.
-
-\bibitem{Kolodny2022}
-Kolodny, Oren, Marcus W.
-Feldman, Arnon Lotem, and Yoav Ram.
-(2022) "Differential Application of Cultural Practices at the Family and Individual Levels May Alter Heritability Estimates." Behavioral and Brain Sciences 45 (September): e167.
-
-\bibitem{Borofsky2022}
-Borofsky, Talia, and Marcus W. Feldman. (2022) "Success-biased social learning in a one-consumer, two-resource model." Theoretical Population Biology 146: 29-35.
-
-\bibitem{Mesoudi2008}
-Mesoudi, Alex, and Michael J. O’Brien. (2008) "The Cultural Transmission of Great Basin Projectile-Point Technology II: An Agent-Based Computer Simulation." American Antiquity 73 (4): 627–44.
-
-\bibitem{Lehmann2009}
-Lehmann, L., and M.W.
-Feldman.
-(2009) Coevolution of adaptive technology, maladaptive culture, and population size in a producer-scrounger game.
-Proceedings of the Royal Society B: Biological Sciences 276: 3853-3862.
-
-\bibitem{Fogarty2017} 
-Fogarty, L., J. Y. Wakano, M. W. Feldman, and K. Aoki. (2017) The driving forces of cultural complexity: Neanderthals, modern humans, and the question of population size. Human Nature : 28: 39-52.
-
-\bibitem{cumul_culture}
-Denton, Kaleda K, Yoav Ram, and Marcus W. Feldman. (2023) "Conditions That Favour Cumulative Cultural Evolution." Philosophical Transactions of the Royal Society B: Biological Sciences 378 (1872).
-
-\bibitem{payoff}
-Hong, Ze. (2022) "Combining Conformist and Payoff Bias in Cultural Evolution: An Integrated Model for Human Decision-Making." Human Nature 33.4: 463-484.
-
-\bibitem{adaptive_filtering}
- Enquist, Magnus, and Stefano Ghirlanda. (2007) "Evolution of Social Learning Does Not Explain the Origin of Human Cumulative Culture." Journal of Theoretical Biology 246 (1): 129–35.
-
-\bibitem{Ammar2023}
-Ammar, Madeleine, Laurel Fogarty, and Anne Kandler. (2023) "Social Learning and Memory." Proceedings of the National Academy of Sciences 120 (33): e2310033120.
-
-\bibitem{Moran1958}
-Moran, P. A. P. (1958) "Random Processes in Genetics." Mathematical Proceedings of the Cambridge Philosophical Society 54 (1): 60–71.
-
-\bibitem{Nakata2024}
-Nakata, Seiya, Akira Masumi, and Genta Toya. (2024) "Formalising Prestige Bias: Differences between Models with First-Order and Second-Order Cues." Evolutionary Human Sciences 6: e21.
-
-\end{thebibliography}
-
-\pagebreak
-
-\begin{appendices}
-\renewcommand{\theequation}{\thesection\arabic{equation}}
-\counterwithin*{equation}{section}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{General binomial distribution approximation} \label{sec:GBD}
-
-\paragraph{Proving $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the {average} in the denominator is over the role-models index, $j$.}
-
-\begin{proof}
-The initial influence of role-model $j$ based on \cref{eq:prestige} is
-\begin{equation}\label{eq:initial_prob}
-G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
-\end{equation}
-The denominator of \cref{eq:initial_prob} can also be formulated as:
-\begin{equation}\label{eq:denominator}
- \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
-\end{equation}
-where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$.
-Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
-\begin{equation}
-\E[K_{N,j}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
-\end{equation}
-\end{proof}
-
-\section{Drift and diffusion in a constant environment} \label{sec:drift_diff_const}
-
-\paragraph{Proving drift and diffusion terms in a constant environment.}
-Let $x$ and $x'$ be the frequency of type $\hat{A}$ in a population with $N$ individuals in the current and next generation, and  $\beta$ {be} the success coefficient of phenotype $A$, $\beta = \beta(A) < \beta(\hat{A}) = 1$.
-Then,
-\begin{equation*}
-E[x'-x] \approx x(1-x)(1-\beta) \;, 
-\quad
-V(x'-x) \approx x(1-x)\Big(\frac{1}{\alpha N + (1-\alpha)}\Big) \;.
-\end{equation*}
-
-\begin{proof}
-Let $X$ be the number of individuals of type $\hat{A}$ such that $x=X/N$. $X'$ is the number of individuals with $\hat{A}$ in the next generation.
-The expected number of individuals is (due to the DM approximation),
-\begin{equation}
-E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2} \;,
-\end{equation}
-where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
-To use frequencies instead of counts, $E[x'] = E[X'/N] = \frac{1}{N}E[X']$.
-Putting it together,
-\begin{equation}
-\begin{split}
-E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}
-	  = \frac{x}{x + (1-x)\beta} \\
-	  &= \frac{x}{x + (1-x) -(1-x) + (1-x)\beta}
-	  = x \frac{1}{1 -(1-x)(1-\beta)}  \\
-	  &= x \big(1 + (1-x)(1-\beta) + o(1-\beta)\big)
-	  = x + x(1-x)(1-\beta) + o(1-\beta) \;, 
-\end{split}
-\end{equation}
-following Durrett~\citep[p.~253, ch~7.2]{durret} and because $1/(1-y)=1+y+y^2+\ldots$.
-
-%By definition, $x$ is constant, so $E[x] = x$.
-{We} therefore have
-\begin{equation}\label{eq:expec_freq}
-E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta) \;,
-\end{equation}
-which gives us the drift term of the diffusion equation.
-
-Using the variance of the DMD,
-\begin{equation}
-V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}
-\Big(1-\frac{\alpha_1}{\alpha_1+\alpha_2}\Big)
-\Big(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2}\Big) \;.
-\end{equation}
-Again, we want to use frequencies so we have $V(X'/N) = \frac{1}{N^2}V(x')$.
-Putting it together with our model notations,
-\begin{equation}
-V(x') = \frac{1}{N^2}N\frac{x}{x+(1-x)\beta}\Big(1-\frac{x}{x+(1-x)\beta}\Big)
-\Big(\frac{N + \alpha' xN + \alpha' N(1-x)\beta}{1 + \alpha' xN + \alpha' N(1-x)\beta}\Big) \;.
-\end{equation}
-
-Following Durrett~\citep[ch~7.2]{durret}, we assume $\beta \approx 1$, such that
-\begin{equation}
-\frac{x}{x + (1-x)\beta} \approx x \,
-\end{equation}
-and for the entire variance expression we get
-\begin{equation}
-%\begin{split}
-V(x') \approx  \frac{1}{N} x(1-x)
-\Big(\frac{N + \alpha' xN + \alpha' N - \alpha' xN}{1 + \alpha' xN + \alpha' N - \alpha' xN}\Big)
-= x(1-x)\Big(\frac{1 + \alpha'}{1 + \alpha' N}\Big) \;.
-%\end{split}
-\end{equation}
-The current frequency $x$ is a given, such that $V(x) = 0$,
-and therefore
-\begin{equation}\label{eq:var_diff_durret}
-V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N}) \;.
-\end{equation}
-$\alpha'$ is the odds ratio of the bias weight, 
-\begin{equation}\label{eq:success_ratio}
-\alpha' = \frac{\alpha}{1-\alpha} \;.
-\end{equation}
-Combining \cref{eq:var_diff_durret} and \cref{eq:success_ratio} we get:
-\begin{equation}\label{eq:const_var}
-\begin{split}
-V(x'-x) \approx x(1-x)\Big(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N}\Big)
-% &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\
-% &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\
-  = x(1-x)(\frac{1}{\alpha N + (1-\alpha)}) \;.
-\end{split}
-\end{equation}
-This gives the diffusion term of the diffusion equation.
-\end{proof}
-
-\section{Drift and diffusion in a changing environment} \label{sec:drift_diff_chang}
-\paragraph{Proving drift and diffusion terms in a changing environment.}
-Let $x$ be the initial frequency of the invading phenotype and $X_t$ is the number of individuals with the phenotype at time $t$.
-Then,
-\begin{equation*}
-E[X_t/N - x] \simeq x(1-x) S_t / N_e \;, 
-\quad
-\text{and}
-\quad
-V(X_t/N-x) \simeq  t x(1-x) / N_e \;,
-\end{equation*}
-where $S_t=\sum\limits_{i=1}^{t} N (1-\beta_t)$.
-
-\begin{proof}
-Let $s_t=N(1-\beta_t)$, and $S_n=\sum\limits_{i=1}^n s_i$, where $\beta_t$ is $\beta(A)$ at generation $t$.
-We prove by induction both terms in \cref{eq:ch_expected_and_var}.
-From \cref{eq:expec_freq} we know that
-\begin{equation}\label{eq:ch_1}
-%\begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] 
-= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) 
-= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1} \;.
-%\end{split}
-\end{equation}
-Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
-\begin{equation}
-\begin{split}
-E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
-&= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] 
-= E\left[\frac{X_t}{N}\right] - E\left[\left(\frac{X_t}{N}\right)^2\right] \\
-&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2 \;.
-\end{split}
-\end{equation}
-
-We can now use the induction assumption of $V\big(\frac{X_t}{N}\big)$ to get
-\begin{equation}
-\begin{split}
-E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
-&\simeq E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x) \;.
-\end{split}
-\end{equation}
-From \cref{eq:ch_1} we know that
-\begin{equation}
-\begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
-&= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] 
-\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\
-&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x) \;.
-\end{split}
-\end{equation}
-Now we omit $O\big(\frac{1}{Ne\cdot N}\big)$ and get
-\begin{equation}\label{eq:ch_2}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) \;.
-\end{equation}
-
-We now look at the induction assumption to see that
-\begin{equation}
-E\left[\frac{X_t}{N}-x\right]
-= E\left[\frac{X_t}{N}\right]-E[x]
-= E\left[\frac{X_t}{N}\right]-x \;,
-\end{equation}
-so using the assumption we get
-\begin{equation}
-\begin{split}
-E\left[\frac{X_t}{N}\right] 
-&\simeq \frac{1}{N} S_t x(1-x)+x \;, \\
-1 - E\left[\frac{X_t}{N}\right] 
-&\simeq 1- \frac{1}{N} S_t x(1-x)+x \;.
-\end{split}
-\end{equation}
-We use both expressions in \cref{eq:ch_2} and get
-\begin{equation}\label{eq:ch_3}
-\begin{split}
-E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] 
-&\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
-&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x) \;,
-\end{split}
-\end{equation}
-after again omitting $O\big(\frac{1}{N^2}\big)$ terms.
-To conclude the proof, we note that
-\begin{equation}
-E\left[\frac{X_{t+1}}{N}-x\right] 
-= E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right] \;,
-\end{equation}
-so again using the induction assumption, together with \cref{eq:ch_3} we get
-\begin{equation}
-\begin{split}
-E\left[\frac{X_{t+1}}{N}-x\right] \simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
-\simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) 
-\simeq \frac{1}{N} S_{t+1} x(1-x) \;,
-\end{split}
-\end{equation}
-which proves the drift term.
-
-For the diffusion term, we use a property of variance,
-\begin{equation}\label{eq:ch_var}
-V\left(\frac{X_{t+1}}{N}\right) 
-= E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) \;.
-\end{equation}
-
-Using \cref{eq:ch_1} we see that
-\begin{equation}\label{eq:ch_var1}
-\begin{split}
-&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] 
-= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\
-&E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] 
-= \frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;.
-\end{split}
-\end{equation}
-
-Using \cref{eq:const_var} we get
-\begin{equation}
-V\left(\frac{X_{t+1}}{N} \bigg|X_t \right) 
-= \frac{1}{N_e}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \;,
-\end{equation}
-and using the equation $y'(1-y') \simeq y(1-y)$ on the first part of \cref{eq:ch_var} we get
-\begin{equation}\label{eq:ch_var2}
-E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] 
-= \frac{1}{N_e}E\left[\frac{X_t}{N}\left(1- \frac{X_t}{N}\right) \right] \simeq \frac{1}{N_e} x(1-x) \;.
-\end{equation}
-Moving on to simplify the second part of \cref{eq:ch_var} using \cref{eq:ch_var1},
-\begin{equation}
-V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
-= V\left(\frac{X_t}{N} + \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \;.\right) \right)
-\end{equation}
-Now, because $\frac{X_t}{N}$ is a frequency, i.e $0 \leq X_t/N \leq 1$, we know that $V\left(\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)\leq\frac{1}{4}$. We therefore find that
-\begin{equation}
-V\left(\frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \right)
-\leq \frac{1}{4N^2}s^2_{t+1} ;,
-\end{equation}
-and so it can be ignored.
-Combining our equations we get
-\begin{equation}
-V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right) 
-= V\left(\frac{X_t}{N}\right) + O\left(\frac{1}{N^2}\right)\simeq V\left(\frac{X_t}{N}\right) \;.
-\end{equation}
-Using the induction assumption and \cref{eq:ch_var2},
-\begin{equation}
-V\left(\frac{X_{t+1}}{N}\right) 
-\simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1) \,
-\end{equation}
-which proves the diffusion term.
-\end{proof}
-\end{appendices}
-
-%%%
-
-\newpage
-\section*{Supplementary Figures}
 \beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
@@
   \textbf{Example dynamics of the dichotomous model with varying bias weight.}
-  The dichotomous model is defined in \cref{eq:binary-model}. Shown are full dynamics without DM or GBD approximations.
+  The dichotomous model is defined in eq.~11. Shown are full dynamics without DM or GBD approximations.
   Here, population size, $N=1,000$; ideal phenotype value, $\hat{A}=1$; success bias value, $\beta(A)=0.99$; initial phenotype frequencies are 50\%-50\%.
@@
   \textbf{Numerical validation of the DM approximation.}
-  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared the distribution of the number of copiers to simulations when using the DMD approximation (\Cref{cor:dirichlet}).
+  We performed computational simulations of the role-model choice process (eq.~10) and compared the distribution of the number of copiers to simulations when using the DMD approximation (corollary 2).
   \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
@@
   Our DMD approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
-  Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
+  Both fluctuate around the analytic fixation probability approximation (black; eq.~19).
   Markers are averages across simulations, error bars are 95\% confidence intervals.
@@
 When success bias is large ($1-\beta > 0.1$),  
-simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}).
-With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
+simulation results (orange) are underestimated by the changing environment approximation (blue; eq.~23).
+With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; eq.~19) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
 Markers show average of $10,000$ simulations, error bars show 75\% (panel A) and 95\% (panel B) confidence intervals.
@@
 In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=80$, and $l=20$;
-In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=80$, and $l=20$, $\alpha=0.1$; 
+In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and eq.~5, $k=80$, and $l=20$, $\alpha=0.1$; 
 }

### 2024-06-02 ms/ms.tex
minor revision

@@
 We implement our stochastic models and approximations, perform statistical analyses, and produce figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
-Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.
+Source code is available on GitHub (\href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}) and deposited on Zenodo (doi:10.5281/zenodo.11424199).
 
@@
 Complementing this, the probability of the $i$-th copier to copy phenotype $\hat{A}$ is $G_{i, \hat{A}} = 1-G_{i,A}$.
-\Cref{fig:timeseries} shows some examples of model dynamics for various values of $\alpha$.
+Figure S1 shows some examples of model dynamics for various values of $\alpha$.
 
@@
 
-Although basic, \Cref{fig:GBD} shows a good fit of the GBD approximation.
+Although basic, Figure S2 shows a good fit of the GBD approximation.
 We perform more extensive validations on the Dirichlet-Multinomial approximation (see below), because that is what we will use in our analysis.
@@
 First, we computed an observed distribution of the number of copiers from the average empirical distribution of multiple simulations.
-We then compared this observed distribution with the expected theoretical DMD (\Cref{fig:DM_validation}A).
+We then compared this observed distribution with the expected theoretical DMD (Figure S3A).
 The difference in distributions was not perceived when plotting both distributions on the same figure, so we used the difference instead.
 The maximum difference is 0.5 role-models, which indicates a very good fit.
-In addition, we tested the likelihood of the observed data to be drawn from the DMD, against a shuffle of the parameters vector of the DMD itself (\Cref{fig:DM_validation}B).
+In addition, we tested the likelihood of the observed data to be drawn from the DMD, against a shuffle of the parameters vector of the DMD itself (Figure S3B).
 We see that the negative log likelihood of the observed data is much higher than any other shuffled version of the parameters vector, strongly supporting our approximation.
@@
 Thus, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. 
-We find that the number of simulations needed to sufficiently approximate our model with the DMD approximation is roughly $1,000$ (\Cref{fig:num_sims}).
+We find that the number of simulations needed to sufficiently approximate our model with the DMD approximation is roughly $1,000$ (Figure S4).
 We examined the robustness of the DMD approximation to relaxing the following assumptions.
@@
 When estimation error is applied, we sample $e_i$ for each copier $i$ from a normal distribution with expected value zero and variance $\eta^2$.
-Even when the estimation error variance is $0.1$, both the fixation probability and fixation time DMD approximations are accurate~(\Cref{fig:hetro_error}). 
+Even when the estimation error variance is $0.1$, both the fixation probability and fixation time DMD approximations are accurate~(Figure S5). 
 We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$).
 We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(0.5, \epsilon)$ where $\epsilon$ is between $10^{-7}$ and $10^{-1}$.
-We found again that results of the DMD approximation are similar to those from stochastic simulations of the full model~(\Cref{fig:hetro_alpha}).
+We found again that results of the DMD approximation are similar to those from stochastic simulations of the full model~(Figure S6).
 
@@
 \begin{figure}[h]
-    \includegraphics[width=0.9\linewidth]{kimura_var.pdf}
+    \includegraphics[width=0.9\linewidth]{../figures/kimura_var.pdf}
   \caption{\textbf{Fixation probability and time in a constant environment.}
@@
 	\centering
-    \includegraphics[width=\linewidth]{ch_env.pdf}
+    \includegraphics[width=\linewidth]{../figures/ch_env.pdf}
   \caption{\textbf{Fixation probability in a changing environment, $k<l$.}
@@
 Markers show average of $10,000$ simulations, error bars show 75\% (panels A and C) and 95\% (panel B) confidence intervals.
-See \Cref{fig:ch_env_alpha_beta_k_large} for the scenario where $k>l$.
+See Figure S7 for the scenario where $k>l$.
 Here, population size is $N=1,000$;
@@
 \begin{figure}[h]
-    \includegraphics[width=\linewidth]{choose_bias.pdf}
+    \includegraphics[width=\linewidth]{../figures/choose_bias.pdf}
   \caption{
@@
 In the case of a changing environment, two key values are the number of generations $k$ and $l$  in which the invading and resident traits are favored by success bias, respectively.
-When $k>l$, strong success (high $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta_k_large}),
+When $k>l$, strong success (high $\alpha$) will increase the fixation probability (Figure S7),
 but when $k<l$, strong prestige (low $\alpha$) will increase the fixation probability (\Cref{fig:ch_env_alpha_beta}A).
@@
 
-\newpage
-
 \section*{References}
@@
 
-\newpage
-\section*{Supplementary Figures}
-\beginsupplement % https://support.authorea.com/en-us/article/how-to-create-an-appendix-section-or-supplementary-information-1g25i5a/
-
-\begin{figure}[h]
-    \includegraphics[width=1\linewidth]{timeseries.pdf}
-  \caption{
-  \textbf{Example dynamics of the dichotomous model with varying bias weight.}
-  The dichotomous model is defined in \cref{eq:binary-model}. Shown are full dynamics without DM or GBD approximations.
-  Here, population size, $N=1,000$; ideal phenotype value, $\hat{A}=1$; success bias value, $\beta(A)=0.99$; initial phenotype frequencies are 50\%-50\%.
-  }	
-  \label{fig:timeseries}
-\end{figure}
-
-\begin{figure}[h]
-    \includegraphics[width=0.7\linewidth]{GBD_validation.pdf}
-  \caption{
-  \textbf{Numerical validation of the GB approximation.}
-  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. 
-  Here, population size, $N=2,000$; bias weight, $\alpha=0.1$; {ideal} phenotype value, $\hat{A}=1$; role-model traits $\vec{A} \sim N(0,1)$; success bias value, $\beta(A)=0.956$.}	
-  \label{fig:GBD}
-\end{figure}
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{DM_validation.pdf}
-  \caption{
-  \textbf{Numerical validation of the DM approximation.}
-  We performed computational simulations of the role-model choice process (\Cref{eq:prestige}) and compared the distribution of the number of copiers to simulations when using the DMD approximation (\Cref{cor:dirichlet}).
-  \textbf{(A)} The difference between the DM distribution (orange) and the empirical distribution of the simulations (blue) is very small. 
-  \textbf{(B)} The log-likelihood of the DMD for results of the simulations (red vertical line) is much higher {than} the log-likelihood of permutations of simulations (blue histogram).
-  Here, population size, $N=100$; number of simulations, $m=100$; phenotype values, $\hat{A}=1$, $A \sim N(0,1)$; success-bias weight, $\alpha=0.5$.
-  No estimation error or bias is applied, and traits are estimated and copied perfectly.}	
-  \label{fig:DM_validation}
-\end{figure}
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{num_sims.pdf}
-  \caption{
-  \textbf{DMD approximation precision as function of number of simulations.}
-  Our DMD approximation (orange) agrees with stochastic simulation results (blue) when using 1,000 or more simulations.
-  Both fluctuate around the analytic fixation probability approximation (black; \cref{eq:kimura_p}).
-  Markers are averages across simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; success-bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success-bias value, $\beta(A)=0.956$.}	
-  \label{fig:num_sims}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{full_vs_dm_mutation.pdf}
-  \caption{
-  \textbf{Robustness of DMD approximations to success estimation error.}
-  Both the DMD approximation (orange) and our approximation (black) agree with the stochastic simulations (blue), even with a high estimation error.
-  Markers are averages across simulations, error bars are 95\% confidence intervals.
-  5,000 simulations per data point; population size, $N=1000$; success-bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,\eta^2)$ where $\eta^2$ in on the x-axis.
-  }	
-  \label{fig:hetro_error}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\linewidth]{full_vs_dm_changing_alpha.pdf}
-   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
-   Fixation probability does not seem to be affected by variation in success bias weight between role-models.
-    Thus, both the DM approximation (orange) and Kimura's equation (black line) have a good fit to results of stochastic simulations (blue).
-   Markers for average across $5,000$ simulations, error bars are 95\% confidence intervals.
-  Here, population size, $N=1000$; 
-  success bias weight is normally distributed, $\alpha_j \sim N(0.5,\epsilon^2)$ where $10^{-7}\le \epsilon^2 \le 10^{-1}$; 
-  phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
-  \label{fig:hetro_alpha}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \includegraphics[width=\linewidth]{ch_env_k_large.pdf}
-  \caption{\textbf{Fixation probability in a changing environment, $k>l$.}
-\textbf{(A)} Fixation probability decreases with {the} success-bias weight (bottom x-axis) and effective population size (top x-axis).
-The approximation (blue; \cref{eq:ch_env}) agrees with simulation results (orange).
-\textbf{(B)} Fixation probability increases with the success coefficient, $\beta$.
-When success bias is large ($1-\beta > 0.1$),  
-simulation results (orange) are underestimated by the changing environment approximation (blue; \cref{eq:ch_env}).
-With even larger success bias ($1-\beta > 0.35$), even the constant environment approximation (green; \cref{eq:kimura_p}) slightly underestimates simulation results, likely because the diffusion equation approximation assumes weak `selection'.
-Markers show average of $10,000$ simulations, error bars show 75\% (panel A) and 95\% (panel B) confidence intervals.
-Here, population size is $N=1,000$;
-In panel A, $A=0.9$, $\hat{A}=1$ ($1-\beta=s=0.005$), $k=80$, and $l=20$;
-In panel B, $0.01 < A< 0.99$, and $\hat{A}=1$, which determines $1-\beta$ via $\beta = \beta(A)/\beta(\hat{A})$ and \cref{eq:success_bias}, $k=80$, and $l=20$, $\alpha=0.1$; 
-}
-\label{fig:ch_env_alpha_beta_k_large}
-\end{figure}
-
 \end{document}
